### 2019-06-03 abstract.tex
Initial Overleaf Import

\begin{resumen}

\end{resumen}

%\begin{abstract}

%\end{abstract}

### 2019-06-03 notacion.tex
Initial Overleaf Import

\begin{notation}
\renewcommand\arraystretch{1.5}

\section*{Geometría básica}
\begin{center}
	%\begin{tabulary}{0.9\textwidth}{RCL}
	\begin{tabular}{l c p{12cm}}
		$\Rn{N}$ 							& : & Espacio euclideano de dimension $N$.
		\\ 
		$\notatScalar{p}$ 					& : & Valor escalar.
		\\ 
		$\notatVector{p}$ 					& : & Vector real.
		\\
		$\notatHomog{p}$ 					& : & Vector en coordenadas homogéneas.
		\\
		$\notatMatrix{A}$ 					& : & Matriz real.
		\\
		$\notatMatrix{I}$ 					& : & Matriz identidad (dimensión dependiente del contexto).
		\\
		$\notatMatrix{0}$					& : & Matriz de ceros (dimensión dependiente del contexto).
		\\
		$\notatFrame{A}$					& : & Sistema de referencia o \emph{frame} $A$.
		\\
		$\notationMatrixFrame{T}{C}{AB}$			& : & Matriz de transformación de $4\times4$ que transforma del sistema de coordenadas $\notatFrame{A}$ al $\notatFrame{B}$, definido en $\notatFrame{C}$.
		\\
		$\hatop{\left(\cdot\right)}$			& : & Operador sombrero o \emph{hat}.
		\\
		$\veeop{\left(\cdot\right)}$			& : & Operador \emph{vee}.
		\\
	\end{tabular} 
	%\end{tabulary} 
\end{center}

\section*{Estadística y optimización}
\begin{center}
	%\begin{tabulary}{0.9\textwidth}{RCL}
	\begin{tabular}{l c p{12cm}}
		$\notatMatrix{\Sigma}$							& : & Matriz de covarianza.
		\\
		$\notatMatrix{\Omega}$							& : & Matriz de información, $\notatMatrix{\Omega} = \notatMatrix{\Sigma}^{-1}$.
		\\
		$\mahalanobisNorm{\cdot}{\notatMatrix{\Omega}}$	& : & Distancia de Mahalanobis con matriz de información $\notatMatrix{\Omega}$.
		\\
		$\mahalanobisNorm{\cdot}{\notatMatrix{\Sigma}}$	& : & Distancia de Mahalanobis con matriz de covarianza $\notatMatrix{\Sigma}$.
		\\
		$\huberNorm{\cdot}{\notatMatrix{\Omega}}$		& : & Distancia de Mahalanobis con kernel robusto Huber y matriz de información $\notatMatrix{\Omega}$		
		\\
		$\huberNorm{\cdot}{\notatMatrix{\Sigma}}$		& : & Distancia de Mahalanobis con kernel robusto Huber y matriz de covarianza $\notatMatrix{\Sigma}$.
		\\
		$\noisy{\left(\cdot\right)}$			& : & Distribución de probabilidad. Variable con ruido.
		\\
		$\optimum{\left(\cdot\right)}$			& : & Variable óptima, solución de un proceso de optimización.
	\end{tabular} 
	%\end{tabulary} 
\end{center}

\section*{Variedades y Grupos de Lie}
\begin{center}
	%\begin{tabulary}{0.9\textwidth}{RCL}
	\begin{tabular}{l c p{12cm}}
		$\notationManifold{M}{\notatManifold{x}}$ 	& : & Variedad o \emph{manifold}.
		\\ 
		$\notatManifold{X},\notatManifold{Z}$ 				& : & Elemento de la variedad diferenciable $\notationManifold{M}{\notatManifold{x}}, \notationManifold{M}{\notatManifold{z}}$.
		\\
		$\boxplus$ 				& : & Operador aditivo de una variedad. diferenciable $\notatManifold{M}$
		\\
		$\boxminus$ 				& : & Operador sustractivo de una variedad diferenciable $\notatManifold{M}$.
		\\
		$\SOthree$ 							& : & Grupo Ortogonal Especial (\emph{Special Orthogonal Group}).
		\\ 
		$\sothree$ 							& : & Álgebra de Lie asociada a $\SOthree$.
		\\ 
		$\SEthree$ 							& : & Grupo Euclideano Especial (\emph{Special Euclidean Group}).
		\\
		$\sethree$ 							& : & Álgebra de Lie asociada a $\SEthree$.
		\\
		$\Simthree$ 						& : & Grupo de semejanza (\emph{Similarity Group}).
		\\
		$\simthree$ 						& : & Álgebra de Lie asociada a $\Simthree$.
		\\
		$\Expmap{\cdot}$				& : & Mapa exponencial.
		\\
		$\ExpmapSEthree{\cdot}$			& : & Mapa exponencial de $\SEthree$.
		\\
		$\ExpmapSOthree{\cdot}$			& : & Mapa exponencial de $\SOthree$.
		\\
		$\Logmap{\cdot}$				& : & Mapa logarítmico.
		\\
		$\LogmapSEthree{\cdot}$			& : & Mapa logarítmico de $\SEthree$.
		\\
		$\LogmapSOthree{\cdot}$			& : & Mapa logarítmico de $\SOthree$.
		\\
		$\JacR{\cdot}$					& : & Jacobiano del grupo de Lie, definido \emph{por la derecha}.
		\\
		$\JacL{\cdot}$					& : & Jacobiano del grupo de Lie, definido \emph{por la izquierda}.
		\\
		$\Adjop{\cdot}$					& : & Representación adjunta (\emph{adjoint}) de un elemento del grupo de Lie.
		\\
		$\adjop{\cdot}$					& : & Representación adjunta de un elemento del álgebra de Lie.
		\\
		$\adjhat{\left( \cdot \right)}$	& : & Representación adjunta de un elemento del espacio euclideano asociado al álgebra de Lie.
		\\
		$\adjvee{\left( \cdot \right)}$	& : & Operador que convierte un elemento de la representación adjunta de vuelta espacio euclideano asociado.
		\\
	\end{tabular} 
	%\end{tabulary} 
\end{center}
\end{notation}

### 2019-07-11 introduction.tex
WASP-18 chapter advanced

\chapter{Introduction}\label{chap:intro}

\section{Transiting Exoplanets}

\section{Transit Timing Variations}

\section{The Transit Monitoring in the South project}

### 2019-07-11 wasp18.tex
WASP-18 chapter advanced

\chapter{The case of WASP-18b}\label{chap:wasp18}

\section{The system}
WASP-18b is a transiting hot Jupiter discovered by \cite{Hellier2009} within the WASP-South transit survey \citep{Pollacco2006}. It is an extremely close-in planet orbiting a F6 type star with a period of 0.94 days. Regarding its physical properties, WASP-18b is about ten times more massive than Jupiter with approximately the same size ($M_{P}=10.3\,{\rm M_{Jupiter}}$, $R_{P}=1.1\,{\rm R_{Jupiter}}$). Even though a rapid orbital decay was predicted theoretically \citep{Hellier2009}, it is not observed yet \citep{Wilkins2017} and new theoretical models proposed a variation of less than 4 seconds in the transit time over a 20-yr baseline \citep{CollierCameron2018}.

\section{Observations and Data Reduction}

\begin{table}
\caption{Log of Observations}             
\label{log_table}      
\centering          
\begin{tabular}{cccccccc}
\hline\hline       
 Date & Epoch\footnotemark{a} & Telescope & Filter & Total exposures & Exposure time\footnotemark{b} & RMS\footnotemark{c} \\
 (UTC) &       &           &       &                   & (seconds) & (mmag)\\
\hline  
 2009 Oct 28 &-1904 & SMARTS 1 m & $I$ & 1412 & 1.5 & 8.49  \\
 2009 Oct 29 & -1903 & SMARTS 1 m & $I$ & 1435 & 2 & 5.67 \\
2009 Oct 30 & -1902 & SMARTS 1 m & $I$ & 1198 & 2  & 4.50 \\
 2011 Sep 06 & -1184 & SMARTS 1 m & $I$ & 203 & 15 & 2.40 \\
2016 Sep 24\footnotemark{d} & 776 & Danish 1.54 m & $I$ & 138 & 90 & 1.05  \\
2016 Sep 25\footnotemark{d} & 777 &Danish 1.54 m & $I$ & 159 & 90  & 0.96  \\
2016 Sep 26\footnotemark{d} & 778 & Danish 1.54 m & $I$ & 113 & 90 & 0.87  \\ \smallskip
2017 Sep 29\footnotemark{d} & 1169 & Danish 1.54 m & $R$ & 330 & 30 & 2.53 \\
\hline                  
\end{tabular}
\footnotetext{a}{The epoch 0 is $T_{0}$ in Tables , for WASP-18b, WASP-19b and WASP-77Ab, respectively.}
\footnotetext{b}{For the variable exposure times, we consider the average during the night.}
\footnotetext{c}{The RMS values were computed from the best fitted model of each light curve.}
\footnotetext{d}{Light curves obtained with only one reference star.}
\end{table}

\section{Transit Parameters and Physical Properties}\label{transitparams}

The resulting parameters from the global fit of WASP-18 in comparison the with results of the discovery paper \cite{Hellier2009} and the most recent analysis with TESS data \citep{Shporer2018}, are listed in Table~\ref{wasp18}. While in \cite{Hellier2009} the analysis was performed combining photometry and RV data, in \cite{Shporer2018} only photometric data was used.

%Stellar params
As the stellar spectroscopic priors were taken from the discovery paper \cite{Hellier2009}, our results for the stellar mass $M_*$ and radius $R_*$ are in good agreement with theirs, as expected, as well as the rest of the stellar parameters. \cite{Shporer2018} do not present results of stellar parameters.

%Primary transit params
In the case of the primary transit parameters, the greatest difference is found in the radius of the planet in stellar radii $R_{p}/R_{*}$. Our reported $R_{p}/R_{*}$ is $7.8\sigma$ and $4.4\sigma$ larger that the reported by \cite{Hellier2009} on the discovery paper and the recent result from \cite{Shporer2018}, respectively.  Our transit duration $T_{14}$ is also $3.4\sigma$ larger than the value from \cite{Hellier2009}.

% RV params
For the radial velocity parameters, the RV semi-amplitude derived from our analysis is consistent with the value of \cite{Hellier2009}, as the same data was used.

% Derived params
Finally, the derived parameters of the system are, in general, in good agreement with the values from \cite{Hellier2009} and \cite{Shporer2018}.

\begin{table*}
\caption{System parameter of WASP-18}
\label{wasp18}
\centering
\begin{tabular}{lcccc}
\hline \hline
~~~~Parameter & Units & This work & \cite{Hellier2009} & \cite{Shporer2018} \\
\hline
\smallskip\\\multicolumn{2}{l}{Stellar Parameters:}&\smallskip\\
~~~~$M_*$\dotfill &Mass (\(M_\odot\))\dotfill &$1.294^{+0.063}_{-0.061}$ & $1.25\pm0.13$ &  \\
~~~~$R_*$\dotfill &Radius (\(R_\odot\))\dotfill &$1.319^{+0.061}_{-0.062}$ &$1.26^{+0.067}_{-0.054}$ & \\
~~~~$L_*$\dotfill &Luminosity (\(L_\odot\))\dotfill &$2.68^{+0.28}_{-0.26}$ & &\\
~~~~$\rho_*$\dotfill &Density (cgs)\dotfill &$0.795^{+0.11}_{-0.089}$ & $ 0.707^{+0.056}_{-0.096}$&\\
~~~~$\log{g}$\dotfill & Surface gravity (cgs)\dotfill &$4.310^{+0.036}_{-0.033}$ &$4.367^{+0.028}_{-0.042}$ & \\
~~~~$T_{\rm eff}$\dotfill &Effective Temperature (K)\dotfill &$6432\pm48$ & $6400\pm100$& \\
~~~~$[{\rm Fe/H}]$\dotfill &Metallicity \dotfill &$0.107\pm0.080$ & $0.00\pm0.09$ & \\
~~~~$Age$\dotfill &Age (Gyr)\dotfill &$1.57^{+1.4}_{-0.94}$ & $0.5-1.5$ & \\
%~~~~$d$\dotfill &Distance (pc)\dotfill &$122.2^{+9.9}_{-8.2}$ & $100\pm10$ & \\

\smallskip\\\multicolumn{2}{l}{Planetary Parameters:}&\smallskip\\
~~~~$R_P$\dotfill &Radius (\rj)\dotfill &$1.310\pm0.071$ & $1.106^{+0.072}_{-0.054}$& $1.192\pm0.038$\\
~~~~$M_P$\dotfill &Mass (\mj)\dotfill &$10.48^{+0.42}_{-0.40}$ & $10.30\pm0.69$ & \\
~~~~$P$\dotfill &Period (days)\dotfill &$0.94145236\pm(49)$ & $0.94145299\pm(87)$& $0.9414576^{(+34)}_{(-35)}$ \\
~~~~$e$\dotfill &Eccentricity \dotfill &$0.0061^{+0.0089}_{-0.0044}$ & &\\
~~~~$a$\dotfill &Semi-major axis (AU)\dotfill &$0.02054^{+0.00033}_{-0.00032}$ & $0.02045\pm0.00067$&\\
~~~~$\omega_*$\dotfill &Argument of Periastron (Degrees)\dotfill &$-100^{+110}_{-120}$ &  &\\
~~~~$\rho_P$\dotfill &Density (cgs)\dotfill &$5.79^{+0.97}_{-0.78}$& $7.73^{+0.78}_{-1.27}$\footnotemark{b} & \\
~~~~$logg_P$\dotfill &Surface gravity \dotfill &$4.180^{+0.044}_{-0.041}$ & $4.289^{+0.027}_{-0.050}$ &\\
~~~~$T_{eq}$\dotfill &Equilibrium temperature (K)\dotfill &$2485^{+53}_{-56}$ & $2384^{+58}_{-30}$ & \\
~~~~$\Theta$\dotfill &Safronov Number \dotfill &$0.254^{+0.015}_{-0.014}$ & &\\
~~~~$\fave$\dotfill &Incident Flux (\fluxcgs)\dotfill &$8.66^{+0.77}_{-0.75}$ & & \\

\smallskip\\\multicolumn{2}{l}{Primary Transit Parameters:}&\smallskip\\
~~~~$T_0$\dotfill &Transit time (\bjdtdb)\dotfill &$2456740.80560\pm(19)$ & $2454221.48163\pm(38)$ & $2458361.048072^{(+34)}_{(-35)}$\\
~~~~$i$\dotfill &Inclination (Degrees)\dotfill &$83.5^{+2.0}_{-1.6}$ & $86.0\pm2.5$ & $84.31^{+0.40}_{-0.37}$\\
~~~~$R_P/R_*$\dotfill &Radius of planet in stellar radii \dotfill &$0.1021\pm0.0011$ &  $0.0935\pm0.0011$ & $0.09721^{+0.00016}_{-0.00017}$\\
~~~~$a/R_*$\dotfill &Semi-major axis in stellar radii \dotfill &$3.35^{+0.15}_{-0.13}$ & & $3.523^{+0.028}_{-0.027}$\\
~~~~$b$\dotfill &Impact parameter \dotfill &$0.433^{+0.07}_{-0.10}$ & $0.25\pm0.15$ & $0.349^{+0.020}_{-0.022}$\\
~~~~$\delta$\dotfill &Transit depth (fraction)\dotfill &$0.01041\pm0.00022$ & & $0.009449^{+0.000032}_{-0.000032}$\\
~~~~$u_{1,I}$\dotfill &linear LD coeff., I band\dotfill &$0.207\pm0.019$ & &\\
~~~~$u_{2,I}$\dotfill &quadratic LD coeff., I band\dotfill &$0.313\pm0.019$& &\\
~~~~$u_{1,R}$\dotfill &linear LD coeff., R band\dotfill & $0.257\pm0.045$ & &\\
~~~~$u_{2,R}$\dotfill &quadratic LD coeff., R band\dotfill &$0.309\pm0.048$ & &\\
~~~~$T_{14}$\dotfill &Total transit duration (days)\dotfill &$0.0931^{+0.0011}_{-0.0010}$ & $0.08932\pm0.00068$ &\\
~~~~$P_T$\dotfill &A priori non-grazing transit prob \dotfill &$0.268^{+0.011}_{-0.012}$ & &\\
~~~~$P_{T,G}$\dotfill &A priori transit prob \dotfill &$0.328^{+0.014}_{-0.015}$ & &\\
~~~~$\tau$\dotfill &Ingress/egress transit duration (days)\dotfill &$0.0107\pm0.0010$ & &\\

\smallskip\\\multicolumn{2}{l}{RV Parameters:}&\smallskip\\
~~~~$ecos{\omega_*}$\dotfill & \dotfill &$-0.0004^{+0.0038}_{-0.0045}$ & &\\
~~~~$esin{\omega_*}$\dotfill & \dotfill &$-0.0008^{+0.0056}_{-0.0092}$ & &\\
~~~~$K$\dotfill &RV semi-amplitude (m/s)\dotfill &$1807^{+34}_{-36}$ & $1818.3\pm8.0$ &\\
~~~~$M_P\sin i$\dotfill &Minimum mass (\mj)\dotfill &$10.40\pm0.40$ & &\\
\smallskip\\\multicolumn{2}{l}{Secondary Eclipse Parameters:}&\smallskip\\
~~~~$T_S$\dotfill &Time of eclipse (\bjdtdb)\dotfill &$2457657.3076^{+0.0023}_{-0.0027}$ & &\\
~~~~$b_S$\dotfill &Eclipse impact parameter \dotfill &$0.431^{+0.070}_{-0.100}$ & &\\
~~~~$\tau_S$\dotfill &Ingress/egress eclipse duration (days)\dotfill &$0.0106^{+0.0011}_{-0.0010}$ & &\\
~~~~$T_{S,14}$\dotfill &Total eclipse duration (days)\dotfill &$0.0929\pm0.0017$ & &\\
~~~~$P_S$\dotfill &A priori non-grazing eclipse prob \dotfill &$0.269^{+0.010}_{-0.011}$ & &\\
~~~~$P_{S,G}$\dotfill &A priori eclipse prob \dotfill &$0.330^{+0.013}_{-0.014}$ & &\\
\hline
\end{tabular}
%\tablefoot{
%\tablefoottext{a}{Value converted to cgs units multiplying by the Sun density $\rho_{\odot}=1.408\,$cgs.}
%\tablefoottext{b}{Value converted to cgs units multiplying by the Jupiter density $\rho_{J}=1.33\,$cgs.}
%\tablefoottext{c}{Values enclosed in parentheses correspond to the uncertainties of the last digits of the nominal value.}}
\end{table*}

\section{Transit Timing Variations}\label{ttvsection}

%\begin{figure*}
%\vspace{0cm}\hspace{0cm}
%\includegraphics[width=1.0\textwidth]{TTVs.png}
%\centering
%\caption{Observed minus calculated mid-transit times (TTV) for WASP-18b (top), WASP-19b (center) and WASP-77Ab (bottom). The dashed black line corresponds to the proposed linear ephemeris, i.e. zero deviation from the predicted transit time (See Section \ref{ttvsection}) computed from our refined orbital period. For that, we considered 19, 59 and 11 transit times of WASP-18b, WASP-19b, and WASP-77Ab, respectively. The grey area corresponds to the error propagation at $1\sigma$, where the quadratic trend looks almost horizontal. The points in color are the TTV from the newly light curves of the TraMoS project (WASP-18b: light blue, WASP-19b: orange, WASP-77Ab: pink) and the black points in the three panels are TTVs measured from previous published transit times. The RMS scatter from the linear ephemeris are 83 seconds for WASP-18b; 75 seconds for WASP-19b, and 121 seconds for WASP-77Ab.}
%\label{ttv}
%\end{figure*}

For this system, the proposed linear ephemeris equation is:

\begin{equation} \label{eq1_w18}
T_{\rm C}(E)=2456926.27460\pm(94)+E \cdot 0.941452232\pm(89)
\end{equation}

The orbital period $P$ in Eq.~\ref{eq1_w18} is in complete agreement with the value computed only with the TraMoS light curves in Table~\ref{wasp18}.

Table~\ref{times_wasp18} lists the TTV of our transit times and also, of data from previous works \citep{Triaud2010,Hellier2009,Maxted2013b} of WASP-18b.

The top panel of Figure... is the linear plot of TTV versus epoch for this planet. The deviations of the transit times from the linear ephemeris has an RMS of 83 seconds. The greater deviations come from the transit time of the epochs $-1904$ and $-1184$, which are over the linear ephemeris by $2.5\sigma$ and $1.9\sigma$, respectively. If those values are removed, the RMS decreases to 61 seconds. Considering all the transit times in Table~\ref{times_wasp18} without the epochs $-1904$ and $-1184$, all the TTVs lie within $1.6\sigma$ in the linear fit.

The epoch $-1184$ has the greatest error in our sample because it is not a complete transit.

When testing the goodness of the linear fit, $\chi^{2}_{red} =0.56$, while for a second degree polynomial is $\chi^{2}_{red}=0.48$, therefore an orbital decay can be discarded in agreement with theoretical estimations \citep{CollierCameron2018}.

\begin{table}
%\tablewidth{0pt}
\caption{Transit mid-times for WASP-18b}
\label{times_wasp18}
\begin{tabular}{cccc}
\hline \hline
Epoch & Transit mid-time & TTV & References\\
      & (${\rm BJD_{TDB}}$) & (min) & \\
\hline 
-2873 & $2454221.48238$ & $0.1\pm1.5$ & 1\\
-2402 & $2454664.9061$ & $-0.4\pm1.4$ & 2 \\
-1904 & $2455133.7472$ & $-3.4\pm1.7$ & This work \\
-1903 & $2455134.6914$ & $0.6\pm1.7$ & This work \\
-1902 & $2455135.6331$  & $0.9\pm1.7$  & This work \\
-1811 & $2455221.3042$ & $-0.6\pm1.4$  & 3\\
-1629 & $2455392.6474$ & $-2.2\pm1.5$& 3 \\
-1601 & $2455419.0083$ & $-1.8\pm2.2$& 3\\
-1587 & $2455432.1897$ & $-0.3\pm1.4$ & 3\\
-1546 & $2455470.7885$ & $-1.4\pm1.4$ & 3\\
-1543 & $2455473.6144$ & $0.9\pm1.9$& 3\\
-1457 & $2455554.5786$ & $-0.2\pm1.5$&3 \\
-1440 & $2455570.5842$ & $1.2\pm1.6$& 3\\
-1184 & $2455811.5970$ &  $2.7\pm5.9$ & This work  \\
-1115 & $2455876.5559$ & $0.8\pm2.3$ & 3 \\ 
776 & $2457656.84078$ & $-1.1\pm1.4$ & This work  \\
777 & $2457657.78359$   & $0.9\pm1.4$ & This work\\
778 & $2457658.72404$ & $-0.6\pm1.4$ & This work \\
1169 & $2458026.83186$ & $-0.6\pm1.5$ & This work  \\
\hline
\end{tabular}
%\tablebib{(1)~\citet{Hellier2009};
%(2) \citet{Triaud2010}; (3) \citet{Maxted2013}.}
\end{table}

### 2019-07-11 wasp77.tex
WASP-18 chapter advanced

\chapter{The case of WASP-77Ab}\label{chap:wasp77}

### 2019-07-12 wasp19.tex
New chapters for three targets

\chapter{The case of WASP-19b}\label{chap:wasp19}

\section{The system}

\section{Transit Parameters and Physical Properties}

\section{Transit Timing Variations}

\section{Limits on an additional perturber}

### 2019-07-19 obs.tex
WASP18 chapter more complete. Added Obs and Data Reduction chapter.

\chapter{Observations and Data Reduction}\label{chap:obs}

We collected 8 light curves for WASP-18b between 2009 and 2017, 9 light curves for WASP-19b between 2011 and 2017, and 5 light curves for WASP-77Ab between 2015 and 2017. We included 4 transits of WASP-77Ab from the Exoplanet Transit Database (ETD) in order to cover a larger timespan.

All of the photometry are collected by using either the Danish 1.54 m telescope at ESO La Silla Observatory, or the SMARTS 1 m at Cerro Tololo Observatory (CTIO), except for one transit of WASP-77Ab that was observed with the Warsaw 1.3 m at Las Campanas Observatory (LCO). The log of our observations is shown in Table XXX. All the new light curves used for this work are presented in Figure XXX.

For the photometric observations conducted on the Danish telescope, we used the Danish Faint Object Spectrograph and Camera (DFOSC) instrument, which has a $2{\rm K} \times 2{\rm K}$ CCD with a 13.7 x 13.7 arcmin$^2$ field of view (FoV) and a pixel scale of 0.39" per pixel. To reduce the readout time, some of the Danish 1.54 m images were windowed to only include the target star and its closest reference stars. The observations of the transits of WASP-18b during 2016 and 2017 were forced to be windowed due to a malfunction of the CCD. For those transits, only one reference star was used to perform the photometry.

The SMARTS 1 m has the Y4KCam instrument which is a $4{\rm K} \times 4{\rm K}$ CCD camera with a $20\times20$ arcmin$^2$ FoV and a pixel scale of 0.289" per pixel.

For the observation on the Warsaw 1.3 m telescope, we used a $2048 \times 4096$ CCD camera chip with a 1.4 square degrees of FoV and 0.26" per pixel scale. No windowing or binning was used during the observations on both SMARTS 1m and the Warsaw 1.3m telescope.

As suggested by \cite{Southworth2009}, most of our observation, especially those conducted after 2011, used the defocus technique, which allows longer exposure times in bright targets and improves the photometric precision. We adjust the exposure time during the observations if the weather is not ideal. The recorded Julian Date in the Coordinated Universal Time (${\rm JD_{UTC}}$) were converted into Barycentric Julian Date in the Barycentric Dynamical Time standard (${\rm BJD_{TDB}}$) by following the procedure as in \citet{Eastman2010}.

We reduced the data by using our custom pipeline. It follows the standard procedures of reduction, calibration, and aperture photometry, but customized for each used instrument. The pipeline semi-automatically finds the best aperture and ring size, for the sky that produces the light curve with less RMS. Then, we manually choose the reference stars to produce the differential light curves for each targets.

### 2019-07-19 wasp18.tex
WASP18 chapter more complete. Added Obs and Data Reduction chapter.

@@
 
-\begin{table}
+\begin{table*}
 \caption{Log of Observations}             
@@
 \footnotetext{d}{Light curves obtained with only one reference star.}
-\end{table}
+\end{table*}
 
@@
 \end{table}
+
+\subsection{Limits on an additional perturber}
+
+For the WASP-18b system we find a large region of instability when compared to the other two systems with the boundaries at the 1:2 interior
+and 2:1 exterior mean-motion resonance. By over-plotting the RMS scatter of mid-transit times ($\rm TTV_{\rm RMS}$) for a certain value, we find
+that the TTVs are relatively more sensitive at orbital architectures involving mean-motion resonances confirming the results by \citet{Agol2005} and \citet{Holman2005}.
+%This also applies to WASP-19 and WASP-77A.
+
+As shown in Figure~\ref{megno_wasp18}, we find that a perturbing body of mass (upper limit) around $7-500~M_{\oplus}$ will produce an RMS of $83\,{\rm s}$ when located in the $P_2/P_1=$ 7:3, 5:2, 3:1, 17:5 and 4:1 exterior resonance.
+For the 1:3 interior resonance, a perturber mass (upper limit) as small as $1.9~M_{\oplus}$ could also cause a RMS mid-transit time scatter of $83\,{\rm s}$.
+
+\begin{figure}
+\includegraphics[width=1.0\columnwidth]{imagenes/WASP18_TraMos_83sec_Map001_GIMP_scaled.png}
+\caption{MEGNO ($\langle Y \rangle$) stability map for the WASP-18 system.
+We over-plot the map with an upper mass of a hypothetical perturbing planet introducing a mid-transit time $\rm TTV_{\rm RMS}$ scatter of $83\,{\rm s}$ (solid line) as obtained in this study.
+The stipulated line is the upper mass limit as obtained from the RMS scatter $(30.9\, \rm m/s)$ of the radial-velocity curve.
+For initial conditions resulting in a quasi-periodic (i.e bounded) motion of the system, the $\langle Y\rangle$ value is close to 2.0 (color coded blue).
+For chaotic (i.e unstable) motion, the $\langle Y \rangle$ is diverging away from 2.0 (color coded red to yellow).
+Vertical arrows indicate $(P_2/P_1)$ orbital resonances between the perturbing body and the transiting planet.
+The two planets were assumed to be co-planar, and the perturbing planet's eccentricity was initially set to zero.
+\emph{See electronic version for colors}.}
+\label{megno_wasp18}
+\end{figure}

### 2019-07-19 wasp18.tex
Added chapters from paper

@@
 
-\begin{table*}
+\begin{landscape}
+\begin{longtable}{llccc}
 \caption{System parameter of WASP-18}
@@
 \centering
-\begin{tabular}{lcccc}
-\hline \hline
-~~~~Parameter & Units & This work & \cite{Hellier2009} & \cite{Shporer2018} \\
+\tabularnewline
+\hline 
+Parameter & Units & This work & \cite{Hellier2009} & \cite{Shporer2018} \\
 \hline
 \smallskip\\\multicolumn{2}{l}{Stellar Parameters:}&\smallskip\\
-~~~~$M_*$\dotfill &Mass (\(M_\odot\))\dotfill &$1.294^{+0.063}_{-0.061}$ & $1.25\pm0.13$ &  \\
-~~~~$R_*$\dotfill &Radius (\(R_\odot\))\dotfill &$1.319^{+0.061}_{-0.062}$ &$1.26^{+0.067}_{-0.054}$ & \\
-~~~~$L_*$\dotfill &Luminosity (\(L_\odot\))\dotfill &$2.68^{+0.28}_{-0.26}$ & &\\
-~~~~$\rho_*$\dotfill &Density (cgs)\dotfill &$0.795^{+0.11}_{-0.089}$ & $ 0.707^{+0.056}_{-0.096}$&\\
-~~~~$\log{g}$\dotfill & Surface gravity (cgs)\dotfill &$4.310^{+0.036}_{-0.033}$ &$4.367^{+0.028}_{-0.042}$ & \\
-~~~~$T_{\rm eff}$\dotfill &Effective Temperature (K)\dotfill &$6432\pm48$ & $6400\pm100$& \\
-~~~~$[{\rm Fe/H}]$\dotfill &Metallicity \dotfill &$0.107\pm0.080$ & $0.00\pm0.09$ & \\
-~~~~$Age$\dotfill &Age (Gyr)\dotfill &$1.57^{+1.4}_{-0.94}$ & $0.5-1.5$ & \\
-%~~~~$d$\dotfill &Distance (pc)\dotfill &$122.2^{+9.9}_{-8.2}$ & $100\pm10$ & \\
+~~~~$M_*$  &Mass (\(M_\odot\))  &$1.294^{+0.063}_{-0.061}$ & $1.25\pm0.13$ &  \\
+~~~~$R_*$  &Radius (\(R_\odot\))  &$1.319^{+0.061}_{-0.062}$ &$1.26^{+0.067}_{-0.054}$ & \\
+~~~~$L_*$  &Luminosity (\(L_\odot\))  &$2.68^{+0.28}_{-0.26}$ & &\\
+~~~~$\rho_*$  &Density (cgs)  &$0.795^{+0.11}_{-0.089}$ & $ 0.707^{+0.056}_{-0.096}$&\\
+~~~~$\log{g}$  & Surface gravity (cgs)  &$4.310^{+0.036}_{-0.033}$ &$4.367^{+0.028}_{-0.042}$ & \\
+~~~~$T_{\rm eff}$  &Effective Temperature (K)  &$6432\pm48$ & $6400\pm100$& \\
+~~~~$[{\rm Fe/H}]$  &Metallicity   &$0.107\pm0.080$ & $0.00\pm0.09$ & \\
+~~~~$Age$  &Age (Gyr)  &$1.57^{+1.4}_{-0.94}$ & $0.5-1.5$ & \\
+%~~~~$d$  &Distance (pc)  &$122.2^{+9.9}_{-8.2}$ & $100\pm10$ & \\
 
 \smallskip\\\multicolumn{2}{l}{Planetary Parameters:}&\smallskip\\
-~~~~$R_P$\dotfill &Radius (\rj)\dotfill &$1.310\pm0.071$ & $1.106^{+0.072}_{-0.054}$& $1.192\pm0.038$\\
-~~~~$M_P$\dotfill &Mass (\mj)\dotfill &$10.48^{+0.42}_{-0.40}$ & $10.30\pm0.69$ & \\
-~~~~$P$\dotfill &Period (days)\dotfill &$0.94145236\pm(49)$ & $0.94145299\pm(87)$& $0.9414576^{(+34)}_{(-35)}$ \\
-~~~~$e$\dotfill &Eccentricity \dotfill &$0.0061^{+0.0089}_{-0.0044}$ & &\\
-~~~~$a$\dotfill &Semi-major axis (AU)\dotfill &$0.02054^{+0.00033}_{-0.00032}$ & $0.02045\pm0.00067$&\\
-~~~~$\omega_*$\dotfill &Argument of Periastron (Degrees)\dotfill &$-100^{+110}_{-120}$ &  &\\
-~~~~$\rho_P$\dotfill &Density (cgs)\dotfill &$5.79^{+0.97}_{-0.78}$& $7.73^{+0.78}_{-1.27}$\footnotemark{b} & \\
-~~~~$logg_P$\dotfill &Surface gravity \dotfill &$4.180^{+0.044}_{-0.041}$ & $4.289^{+0.027}_{-0.050}$ &\\
-~~~~$T_{eq}$\dotfill &Equilibrium temperature (K)\dotfill &$2485^{+53}_{-56}$ & $2384^{+58}_{-30}$ & \\
-~~~~$\Theta$\dotfill &Safronov Number \dotfill &$0.254^{+0.015}_{-0.014}$ & &\\
-~~~~$\fave$\dotfill &Incident Flux (\fluxcgs)\dotfill &$8.66^{+0.77}_{-0.75}$ & & \\
+~~~~$R_P$  &Radius (\rj)  &$1.310\pm0.071$ & $1.106^{+0.072}_{-0.054}$& $1.192\pm0.038$\\
+~~~~$M_P$  &Mass (\mj)  &$10.48^{+0.42}_{-0.40}$ & $10.30\pm0.69$ & \\
+~~~~$P$  &Period (days)  &$0.94145236\pm(49)$ & $0.94145299\pm(87)$& $0.9414576^{(+34)}_{(-35)}$ \\
+~~~~$e$  &Eccentricity   &$0.0061^{+0.0089}_{-0.0044}$ & &\\
+~~~~$a$  &Semi-major axis (AU)  &$0.02054^{+0.00033}_{-0.00032}$ & $0.02045\pm0.00067$&\\
+~~~~$\omega_*$  &Argument of Periastron (Degrees)  &$-100^{+110}_{-120}$ &  &\\
+~~~~$\rho_P$  &Density (cgs)  &$5.79^{+0.97}_{-0.78}$& $7.73^{+0.78}_{-1.27}$\footnotemark{b} & \\
+~~~~$logg_P$  &Surface gravity   &$4.180^{+0.044}_{-0.041}$ & $4.289^{+0.027}_{-0.050}$ &\\
+~~~~$T_{eq}$  &Equilibrium temperature (K)  &$2485^{+53}_{-56}$ & $2384^{+58}_{-30}$ & \\
+~~~~$\Theta$  &Safronov Number   &$0.254^{+0.015}_{-0.014}$ & &\\
+~~~~$\fave$  &Incident Flux (\fluxcgs)  &$8.66^{+0.77}_{-0.75}$ & & \\
 
 \smallskip\\\multicolumn{2}{l}{Primary Transit Parameters:}&\smallskip\\
-~~~~$T_0$\dotfill &Transit time (\bjdtdb)\dotfill &$2456740.80560\pm(19)$ & $2454221.48163\pm(38)$ & $2458361.048072^{(+34)}_{(-35)}$\\
-~~~~$i$\dotfill &Inclination (Degrees)\dotfill &$83.5^{+2.0}_{-1.6}$ & $86.0\pm2.5$ & $84.31^{+0.40}_{-0.37}$\\
-~~~~$R_P/R_*$\dotfill &Radius of planet in stellar radii \dotfill &$0.1021\pm0.0011$ &  $0.0935\pm0.0011$ & $0.09721^{+0.00016}_{-0.00017}$\\
-~~~~$a/R_*$\dotfill &Semi-major axis in stellar radii \dotfill &$3.35^{+0.15}_{-0.13}$ & & $3.523^{+0.028}_{-0.027}$\\
-~~~~$b$\dotfill &Impact parameter \dotfill &$0.433^{+0.07}_{-0.10}$ & $0.25\pm0.15$ & $0.349^{+0.020}_{-0.022}$\\
-~~~~$\delta$\dotfill &Transit depth (fraction)\dotfill &$0.01041\pm0.00022$ & & $0.009449^{+0.000032}_{-0.000032}$\\
-~~~~$u_{1,I}$\dotfill &linear LD coeff., I band\dotfill &$0.207\pm0.019$ & &\\
-~~~~$u_{2,I}$\dotfill &quadratic LD coeff., I band\dotfill &$0.313\pm0.019$& &\\
-~~~~$u_{1,R}$\dotfill &linear LD coeff., R band\dotfill & $0.257\pm0.045$ & &\\
-~~~~$u_{2,R}$\dotfill &quadratic LD coeff., R band\dotfill &$0.309\pm0.048$ & &\\
-~~~~$T_{14}$\dotfill &Total transit duration (days)\dotfill &$0.0931^{+0.0011}_{-0.0010}$ & $0.08932\pm0.00068$ &\\
-~~~~$P_T$\dotfill &A priori non-grazing transit prob \dotfill &$0.268^{+0.011}_{-0.012}$ & &\\
-~~~~$P_{T,G}$\dotfill &A priori transit prob \dotfill &$0.328^{+0.014}_{-0.015}$ & &\\
-~~~~$\tau$\dotfill &Ingress/egress transit duration (days)\dotfill &$0.0107\pm0.0010$ & &\\
+~~~~$T_0$  &Transit time (\bjdtdb)  &$2456740.80560\pm(19)$ & $2454221.48163\pm(38)$ & $2458361.048072^{(+34)}_{(-35)}$\\
+~~~~$i$  &Inclination (Degrees)  &$83.5^{+2.0}_{-1.6}$ & $86.0\pm2.5$ & $84.31^{+0.40}_{-0.37}$\\
+~~~~$R_P/R_*$  &Radius of planet in stellar radii   &$0.1021\pm0.0011$ &  $0.0935\pm0.0011$ & $0.09721^{+0.00016}_{-0.00017}$\\
+~~~~$a/R_*$  &Semi-major axis in stellar radii   &$3.35^{+0.15}_{-0.13}$ & & $3.523^{+0.028}_{-0.027}$\\
+~~~~$b$  &Impact parameter   &$0.433^{+0.07}_{-0.10}$ & $0.25\pm0.15$ & $0.349^{+0.020}_{-0.022}$\\
+~~~~$\delta$  &Transit depth (fraction)  &$0.01041\pm0.00022$ & & $0.009449^{+0.000032}_{-0.000032}$\\
+~~~~$u_{1,I}$  &linear LD coeff., I band  &$0.207\pm0.019$ & &\\
+~~~~$u_{2,I}$  &quadratic LD coeff., I band  &$0.313\pm0.019$& &\\
+~~~~$u_{1,R}$  &linear LD coeff., R band  & $0.257\pm0.045$ & &\\
+~~~~$u_{2,R}$  &quadratic LD coeff., R band  &$0.309\pm0.048$ & &\\
+~~~~$T_{14}$  &Total transit duration (days)  &$0.0931^{+0.0011}_{-0.0010}$ & $0.08932\pm0.00068$ &\\
+~~~~$P_T$  &A priori non-grazing transit prob   &$0.268^{+0.011}_{-0.012}$ & &\\
+~~~~$P_{T,G}$  &A priori transit prob   &$0.328^{+0.014}_{-0.015}$ & &\\
+~~~~$\tau$  &Ingress/egress transit duration (days)  &$0.0107\pm0.0010$ & &\\
 
 \smallskip\\\multicolumn{2}{l}{RV Parameters:}&\smallskip\\
-~~~~$ecos{\omega_*}$\dotfill & \dotfill &$-0.0004^{+0.0038}_{-0.0045}$ & &\\
-~~~~$esin{\omega_*}$\dotfill & \dotfill &$-0.0008^{+0.0056}_{-0.0092}$ & &\\
-~~~~$K$\dotfill &RV semi-amplitude (m/s)\dotfill &$1807^{+34}_{-36}$ & $1818.3\pm8.0$ &\\
-~~~~$M_P\sin i$\dotfill &Minimum mass (\mj)\dotfill &$10.40\pm0.40$ & &\\
+~~~~$ecos{\omega_*}$  &   &$-0.0004^{+0.0038}_{-0.0045}$ & &\\
+~~~~$esin{\omega_*}$  &   &$-0.0008^{+0.0056}_{-0.0092}$ & &\\
+~~~~$K$  &RV semi-amplitude (m/s)  &$1807^{+34}_{-36}$ & $1818.3\pm8.0$ &\\
+~~~~$M_P\sin i$  &Minimum mass (\mj)  &$10.40\pm0.40$ & &\\
 \smallskip\\\multicolumn{2}{l}{Secondary Eclipse Parameters:}&\smallskip\\
-~~~~$T_S$\dotfill &Time of eclipse (\bjdtdb)\dotfill &$2457657.3076^{+0.0023}_{-0.0027}$ & &\\
-~~~~$b_S$\dotfill &Eclipse impact parameter \dotfill &$0.431^{+0.070}_{-0.100}$ & &\\
-~~~~$\tau_S$\dotfill &Ingress/egress eclipse duration (days)\dotfill &$0.0106^{+0.0011}_{-0.0010}$ & &\\
-~~~~$T_{S,14}$\dotfill &Total eclipse duration (days)\dotfill &$0.0929\pm0.0017$ & &\\
-~~~~$P_S$\dotfill &A priori non-grazing eclipse prob \dotfill &$0.269^{+0.010}_{-0.011}$ & &\\
-~~~~$P_{S,G}$\dotfill &A priori eclipse prob \dotfill &$0.330^{+0.013}_{-0.014}$ & &\\
+~~~~$T_S$  &Time of eclipse (\bjdtdb)  &$2457657.3076^{+0.0023}_{-0.0027}$ & &\\
+~~~~$b_S$  &Eclipse impact parameter   &$0.431^{+0.070}_{-0.100}$ & &\\
+~~~~$\tau_S$  &Ingress/egress eclipse duration (days)  &$0.0106^{+0.0011}_{-0.0010}$ & &\\
+~~~~$T_{S,14}$  &Total eclipse duration (days)  &$0.0929\pm0.0017$ & &\\
+~~~~$P_S$  &A priori non-grazing eclipse prob   &$0.269^{+0.010}_{-0.011}$ & &\\
+~~~~$P_{S,G}$  &A priori eclipse prob   &$0.330^{+0.013}_{-0.014}$ & &\\
 \hline 
-\end{tabular}
+\end{longtable}
+\end{landscape}
 %\tablefoot{
@@
 %\tablefoottext{c}{Values enclosed in parentheses correspond to the uncertainties of the last digits of the nominal value.}}
-\end{table*}
 
@@
 
-\begin{table}
+\begin{table}[H]
 %\tablewidth{0pt}
+\centering
 \caption{Transit mid-times for WASP-18b}
@@
 
-\subsection{Limits on an additional perturber}
+\section{Limits on an additional perturber}
 
@@
 
-\begin{figure}
+\begin{figure}[H]
 \includegraphics[width=1.0\columnwidth]{imagenes/WASP18_TraMos_83sec_Map001_GIMP_scaled.png}

### 2019-07-19 wasp19.tex
Added chapters from paper

@@
 \section{The system}
+WASP-18b is a transiting hot Jupiter discovered by \citet{Hellier2009} within the WASP-South transit survey \citep{Pollacco2006}.
+It is an extremely close-in planet orbiting a F6 type star with a period of 0.94 days.
+Regarding its physical properties, WASP-18b is about ten times more massive than Jupiter with approximately the same size ($M_{P}=10.3\,{\rm M_{Jupiter}}$, $R_{P}=1.1\,{\rm R_{Jupiter}}$).
+Even though a rapid orbital decay was predicted theoretically \citep{Hellier2009}, it is not observed yet \citep{Wilkins2017} and new theoretical models proposed a variation of less than 4 seconds in the transit time over a 20-yr baseline
+\citep{CollierCameron2018}.
 
 \section{Transit Parameters and Physical Properties}
+The results of the global fit of WASP-19 are listed in Table~\ref{tab:wasp19}, in comparison with the previous values from the discovery paper \citep{Hebb2010}, and a more recent work \citep{Lendl2013}.
+
+To estimate the stellar parameters of WASP-19, we used as priors the stellar spectroscopic parameters from \cite{Hebb2010}.
+Thus, in general, our results are in agreement with the those from the discovery paper.
+The most important discrepancies are the density of the star $\rho_*$ and the surface gravity $\log{g}$, showing $+2.5\sigma$ and $-3.2\sigma$ difference, respectively.
+Comparing with the results from \cite{Lendl2013}, ours are all in good agreement.
+
+For values of the primary transit parameters obtained from the light curves, the greatest differences are found in the orbital inclination $i$ and the total transit duration $T_{14}$.
+We report an inclination value $5.1\sigma$ smaller than \cite{Hebb2010}, but in agreement with the estimate of \cite{Lendl2013}.
+In the other hand, our estimation of $T_{14}$ is significantly larger than \cite{Hebb2010} by $9\sigma$, but the difference is only $3.5\sigma$ when compared with \cite{Lendl2013}.
+We also report a preciser impact parameter $b$ and transit depth $\delta$.
+
+As the same RV data set from the discovery paper \citep{Hebb2010} was used to perform our analysis, the almost identical values in the RV semi-amplitude $K$ is not a surprise.
+Moreover, the values from \cite{Lendl2013} are also in agreement.
+
+The planetary parameters derived from the light curve and radial velocity analysis are almost all in good agreement with the comparison works.
+The only parameter with a difference greater than $3\sigma$ is our estimation of the Equilibrium Temperature $T_{eq}$ compared with the result of \cite{Hebb2010}.
+However, our result is in better agreement with \cite{Lendl2013} by less than $2\sigma$.
+
+\begin{landscape}
+\begin{longtable}{llccc}
+\caption{System parameter of WASP-19}
+\label{tab:wasp19}
+\centering
+\tabularnewline
+\hline 
+~~~Parameter & Units & This work & \cite{Hebb2010}\footnote{a} & \cite{Lendl2013}\\
+\hline
+\smallskip\\\multicolumn{2}{l}{Stellar Parameters:}&\smallskip\\
+~~~~$M_*$\dotfill &Mass (\(M_\odot\))\dotfill &$0.965^{+0.091}_{-0.095}$ & $0.95\pm0.10$ & $0.968^{+0.084}_{-0.079}$ \\
+~~~~$R_*$\dotfill &Radius (\(R_\odot\))\dotfill &$1.006^{+0.031}_{-0.034}$ & $0.93^{+0.05}_{-0.04}$& $0.994\pm0.031$\\
+~~~~$L_*$\dotfill &Luminosity (\(L_\odot\))\dotfill &$0.905^{+0.071}_{-0.069}$\\
+~~~~$\rho_*$\dotfill &Density (cgs)\dotfill &$1.339^{+0.056}_{-0.058}$ & $1.19^{+0.12}_{-0.11}$\footnote{b}  & $1.384^{+0.055}_{-0.051}$\footnote{b}\\
+~~~~$\log{g}$\dotfill &Surface gravity (cgs)\dotfill &$4.417^{+0.020}_{-0.021}$ & $4.48\pm0.03$\\
+~~~~$T_{\rm eff}$\dotfill &Effective Temperature (K)\dotfill &$5616^{+66}_{-65}$ & $5500\pm100$\\
+~~~~$[{\rm Fe/H}]$\dotfill &Metallicity \dotfill &$0.04^{+0.25}_{-0.30}$ & $0.02\pm0.09$\\
+~~~~$Age$\dotfill &Age (Gyr)\dotfill &$6.4^{+4.1}_{-3.5}$ & $5.5^{+9.0}_{-4.5}$\\
+%~~~~$d$\dotfill &Distance (pc)\dotfill &$270.2\pm1.7$\\
+
+\smallskip\\\multicolumn{2}{l}{Planetary Parameters:}&\smallskip\\
+~~~~$R_P$\dotfill &Radius (\rj)\dotfill &$1.415^{+0.044}_{-0.048}$ & $1.28\pm0.07$ & $1.376\pm0.046$\\
+~~~~$M_P$\dotfill &Mass (\mj)\dotfill &$1.154^{+0.078}_{-0.080}$ & $1.14\pm0.07$ & $1.165\pm0.068$\\
+~~~~$P$\dotfill &Period (days)\dotfill &$0.78883852^{+(75)}_{-(82)}$ & $0.7888399\pm(8)$  & $0.7888390\pm(2)$\\
+~~~~$e$\dotfill &Eccentricity \dotfill &$0.0126^{+0.014}_{-0.0089}$ & & $0.0077^{+0.0068}_{-0.0032}$\\
+~~~~$a$\dotfill &Semi-major axis (AU)\dotfill &$0.01652^{+0.00050}_{-0.00056}$ & $0.0164^{+0.0005}_{-0.0006}$ & $0.01653\pm0.00046$\\
+~~~~$\omega_*$\dotfill &Argument of Periastron (Degrees)\dotfill &$51^{+89}_{-190}$ & $-76^{+112}_{-23}$ & $43^{+28}_{-67}$\\
+~~~~$\rho_P$\dotfill &Density (cgs)\dotfill &$0.506^{+0.031}_{-0.030}$ & $0.54^{+0.07}_{-0.06}$& $0.595^{+0.036}_{-0.033}$\footnote{c}\\
+~~~~$logg_P$\dotfill &Surface gravity \dotfill &$3.155^{+0.018}_{-0.019}$ & $3.20\pm0.03$ & $3.184\pm0.015$\\
+~~~~$T_{eq}$\dotfill &Equilibrium temperature (K)\dotfill &$2113\pm29$ & $1993^{+32}_{-33}$ & $2058\pm40$\\
+~~~~$\Theta$\dotfill &Safronov Number \dotfill &$0.0279^{+0.0012}_{-0.0011}$\\
+~~~~$\fave$\dotfill &Incident Flux (\fluxcgs)\dotfill &$4.52^{+0.26}_{-0.24}$\\
+
+\smallskip\\\multicolumn{2}{l}{Primary Transit Parameters:}&\smallskip\\
+~~~~$T_0$\dotfill & Transit Time (\bjdtdb)\dotfill &$2456402.7128^{+(17)}_{-(14)}$ & $2454775.3372\pm(2)$ & $2456029.59204\pm(13)$\\
+~~~~$i$\dotfill &Inclination (Degrees)\dotfill &$79.08^{+0.34}_{-0.37}$ & $80.8\pm0.8$  & $79.54\pm0.33$\\
+~~~~$R_P/R_*$\dotfill &Radius of planet in stellar radii \dotfill &$0.14410^{+0.00049}_{-0.00050}$ & $0.1425\pm0.0014$\\
+~~~~$a/R_*$\dotfill &Semi-major axis in stellar radii \dotfill &$3.533^{+0.048}_{-0.052}$ &  & $3.573\pm0.046$\\
+~~~~$b$\dotfill &Impact parameter \dotfill &$0.6671^{+0.0087}_{-0.0091}$ & $0.62\pm0.03$ & $0.645\pm0.012$\\
+~~~~$\delta$\dotfill &Transit depth (fraction)\dotfill &$0.02077\pm0.00014$ & $0.0203\pm0.0004$ & $0.02018\pm0.00021$\\
+~~~~$u_{1,I}$\dotfill &linear LD coeff., I band\dotfill &$0.287^{+0.027}_{-0.029}$&\\
+~~~~$u_{2,I}$\dotfill &quadratic LD coeff., I band\dotfill &$0.263\pm0.024$&\\
+~~~~$u_{1,R}$\dotfill &linear LD coeff., R band \dotfill &$0.383^{+0.029}_{-0.032}$\\
+~~~~$u_{2,R}$\dotfill &quadratic LD coeff., R band\dotfill &$0.246^{+0.027}_{-0.025}$\\
+~~~~$T_{14}$\dotfill &Total transit duration (days)\dotfill &$0.06697^{+0.00031}_{-0.00030}$ & $0.0643^{+0.0006}_{-0.0007}$ & $0.06586^{+0.00033}_{-0.00031}$\\
+~~~~$P_T$\dotfill &A priori non-grazing transit prob \dotfill &$0.2426^{+0.0066}_{-0.0051}$\\
+~~~~$P_{T,G}$\dotfill &A priori transit prob \dotfill &$0.3246^{+0.0089}_{-0.0069}$\\
+~~~~$\tau$\dotfill &Ingress/egress transit duration (days)\dotfill &$0.01459\pm0.00035$\\
+
+\smallskip\\\multicolumn{2}{l}{RV Parameters:}&\smallskip\\
+~~~~$e\cos{\omega_*}$\dotfill & \dotfill &$-0.0027^{+0.0077}_{-0.013}$ & $0.004\pm0.009$ &$0.0024\pm0.0020$ \\
+~~~~$e\sin{\omega_*}$\dotfill & \dotfill &$0.0016^{+0.014}_{-0.0092}$ & $-0.02\pm0.02$ & $0.000\pm0.005$\\
+~~~~$K$\dotfill &RV semi-amplitude (m/s)\dotfill &$255.4^{+6.1}_{-6.2}$ & $256\pm5$  & $257.7\pm2.9$\\
+~~~~$M_P\sin i$\dotfill &Minimum mass (\mj)\dotfill &$1.133^{+0.078}_{-0.079}$\\
+
+\smallskip\\\multicolumn{2}{l}{Secondary Eclipse Parameters:}&\smallskip\\
+~~~~$T_S$\dotfill &Time of eclipse (\bjdtdb)\dotfill &$2455169.3621^{+(41)}_{-(51)}$ & $2456030.77766\pm(88)$\\
+~~~~$b_S$\dotfill &Eclipse impact parameter \dotfill &$0.670^{+0.020}_{-0.017}$ & $0.652\pm0.015$\\
+~~~~$\tau_S$\dotfill &Ingress/egress eclipse duration (days)\dotfill &$0.01472^{+0.00085}_{-0.00066}$\\
+~~~~$T_{S,14}$\dotfill &Total eclipse duration (days)\dotfill &$0.06812^{+0.00087}_{-0.00074}$\\
+~~~~$P_S$\dotfill &A priori non-grazing eclipse prob \dotfill &$0.2415\pm0.0021$\\
+~~~~$P_{S,G}$\dotfill &A priori eclipse prob \dotfill &$0.3232\pm0.0030$\\
+\hline
+%\end{tabular}
+%\tablefoot{
+%\tablefoottext{a}{For comparison, the results from \cite{Hellier2009} that considered free eccentricity were used.}
+%%\tablefoottext{b}{Values converted to cgs units multiplying by the Sun density $\rho_{\odot}=1.408\,$cgs.}
+%\tablefoottext{c}{Values converted to cgs units multiplying by the Jupiter density $\rho_{J}=1.33\,$cgs}
+%\tablefoottext{d}{Values enclosed in parentheses correspond to the uncertainties of the last digits of the nominal value.}}
+\end{longtable}
+\end{landscape}
 
@@
 
+The proposed equation for linear ephemeris, considering 59 transit times of WASP-19b is:
+\begin{equation} \label{eq1_w19}
+T_{\rm C}(E)=2456402.7128\pm(16)+E \cdot 0.788838858\pm(47)
+\end{equation}
+
+The TTV values from the proposed linear ephemeris are listed in Table \ref{times_wasp19}, including transit times from the previous works \citep{Hebb2010,Anderson2010,Lendl2013,Tregloan2013,Bean2013,Mancini2013}.
+
+At the middle panel of Figure XXX are the TTV values versus epoch, for all the transit time considered in this work.
+
+The RMS from the linear ephemeris is about 75 seconds.
+The epoch of $-1011$ is the only one with a transit time deviation above $1.5\,\sigma$ from the linear ephemeris.
+If it is removed, then the RMS decreases to 69 seconds.
+Moreover, in our data the epoch $-611$ has one of the greatest errors due to bad weather conditions.
+
+Considering all the transit times from Table~\ref{times_wasp19}, the linear fit has $\chi^{2}_{red} = 0.16$.
+This an indication of an overestimation of the errors.
+A second degree polynomial was also tested in order to reject or not a possible orbital decay.
+The goodness of that fit is $\chi^{2}_{red}=0.12$.
+
+%\begin{longtable}[H]
+
+\begin{longtable}{cccc}
+\caption{Transit mid-times for WASP-19b}
+\label{times_wasp19}
+\tabularnewline
+\hline \hline
+Epoch & Transit mid-time & TTV & References\\
+      & (${\rm BJD_{TDB}}$) & (min) &  \\
+\hline
+-2063 & $2454775.3372$ & $-1.6\pm3.2$ & 1\\
+-2061 & $2454776.91566$ & $-0.5\pm2.3$ & 2 \\
+-2010 & $2454817.14633$ & $-0.6\pm2.3$ & 3 \\
+-1525 & $2455199.73343$ & $-0.2\pm2.6$& 4\\
+-1459 & $2455251.79657$ & $-0.6\pm2.3$& 5 \\
+-1458 & $2455252.58544$ & $-0.5\pm2.3$& 5 \\
+-1454 & $2455255.74077$ & $-0.6\pm2.3$& 5 \\
+-1449 & $2455259.68448$ & $-1.3\pm2.4$& 4 \\ 
+-1431 & $2455273.88282$ & $-2.4\pm2.5$& 4 \\
+-1399 & $2455299.12768$ & $0.6\pm2.4$& 4 \\
+-1354 & $2455334.6254$ & $0.5\pm2.3$ & 6\\
+-1349 & $2455338.56927$ & $0.1\pm2.3$& 3 \\ 
+-1330 & $2455353.55659$ & $-0.8\pm2.3$& 6\\
+-1317 & $2455363.81131$ & $-1.1\pm2.4$& 4  \\
+-1311 & $2455368.54285$ & $-3.3\pm3.8$& 6 \\ 
+-1094 & $2455539.72327$ & $0.2\pm2.4$ & 3 \\
+-1056 & $2455569.69826$ & $-1.1\pm2.4$ & 3\\
+-1039 & $2455583.10979$ & $0.8\pm2.6$ & 4 \\
+-1037 & $2455584.68693$ & $0.0\pm2.3$ & 3 \\
+-1025 & $2455594.15188$ &  $-1.6\pm3.3$ & 6 \\
+-1016 & $2455601.25164$ & $-1.3\pm2.5$ & 6\\
+-1014 & $2455602.83138$ & $1.7\pm2.4$ & 3 \\
+-1011 & $2455605.19414$ & $-3.8\pm3.5$ & 6 \\
+-1009 & $2455606.77464$ & $0.3\pm2.3$ & 3 \\
+-1008 & $2455607.56241$ & $-1.2\pm2.4$ & 3 \\
+-989 & $2455622.55057$ & $-0.9\pm2.3$ & 3 \\
+-987 & $2455624.12787$ & $-1.5\pm3.1$ & 6 \\
+-976 & $2455632.80612$ & $0.0\pm2.3$ & 3 \\
+-947 & $2455655.68222$ & $-0.3\pm2.4$ & 3 \\
+-928 & $2455670.66976$ & $-0.9\pm2.5$ & 3 \\
+-923 & $2455674.61367$ & $-1.3\pm2.4$ & This work \\
+-919 & $2455677.77038$ & $0.7\pm3.6$ & 6  \\
+-905 & $2455688.81201$ & $-2.4\pm5.3$ & 6 \\
+-904 & $2455689.60276$ & $0.4\pm2.4$ & 6 \\
+-900 & $2455692.75674$ & $-1.6\pm4.3$ & 6 \\
+-899 & $2455693.54639$ & $-0.5\pm2.3$ & 6  \\
+-886 & $2455703.79933$ & $-3.3\pm6.4$ & 6 \\
+-885 & $2455704.59078$ & $0.5\pm2.4$ & 6 \\
+-880 & $2455708.534626$ & $0.0\pm 2.3$ & 6  \\
+-654 & $2455886.81234$ &  $0.2\pm3.8$ & 6 \\
+-642 & $2455896.27611$ & $-3.1\pm3.8$ & 6 \\
+-618 & $2455915.20980$ & $-0.9\pm2.5$ & 6  \\
+-613 & $2455919.15485$ & $0.4\pm 2.7$ & 6\\
+-611 & $2455920.7353$ & $0.0\pm5.4$ & This work \\
+-609 & $2455922.30966$ & $-0.4\pm8.3$ & 6 \\
+-511 & $2455999.6163$ & $0.2\pm2.3$ & 7 \\
+-483 & $2456021.70374$ & $0.1\pm2.3$ & 7 \\
+-473 & $2456029.5925$ & $0.7\pm 2.4$ &3 \\
+-468 & $2456033.53643$ &  $0.3\pm 2.3$ & 6  \\
+-430 & $2456063.51174$ & $-0.5\pm 2.3$ & 3 \\
+-86 & $2456334.87208$ & $-0.8\pm2.4$ & 4 \\
+-47 & $2456365.6373$  & $-0.1\pm2.3$& This work \\
+1 & $2456403.50158$ &  $-0.1\pm2.3$ & This work \\
+729 & $2456977.77722$  & $1.3\pm2.3$ & 8 \\
+867 & $2457086.63571$ & $-0.5\pm2.3$& This work \\
+1383 & $2457493.67676$   & $-0.2\pm2.3$& This work  \\
+1771 & $2457799.74612$ &  $-0.3\pm2.3$ & This work \\
+1838 & $2457852.597807$ & $-0.7\pm2.3$ & This work\\ 
+2064 & $2458030.8751$  & $-1.5\pm3.2$& This work \\
+\hline
+%\end{tabular}
+%\tablebib{(1)~\citet{Hebb2010};
+%(2) \citet{Anderson2010}; (3) \citet{Lendl2013}; (4) Exoplanet Transit Database (ETD) \url{var2.astro.cz/ETD}; (5) \citet{Tregloan2013}; (6) \citet{Mancini2013}; (7) \citet{Bean2013}; (8) \citet{Sedaghati2015}.}
+\end{longtable}
+
 \section{Limits on an additional perturber}
+
+For the WASP-19b system the measured transit-timing RMS scatter was $\rm TTV_{\rm RMS}=75,\rm s$.
+Additional bodies with a mass of $500~M_{\oplus}$ and as low as $2.0~M_{\oplus}$ and $0.9~M_{\oplus}$ at the 1:3, 1:2 (interior) and 2:1 (exterior) mean-motion resonances could cause the observed RMS scatter.
+Hypothetical planets of $6~M_{\oplus}$, $3~M_{\oplus}$ and $2~M_{\oplus}$ could cause the observed RMS scatter at the 5:3, 5:2 and 3:1 exterior mean-motion resonances, respectively.
+We refer to Fig.~\ref{megno_wasp19}.
+
+\begin{figure}
+\includegraphics[width=1.0\columnwidth]{imagenes/WASP19_TraMos_Map001_GIMP_scaled.png}
+\caption{Same as Fig.~\ref{megno_wasp18}, but this time for WASP-19 with an $\rm TTV_{\rm RMS}$ of 75 s. The
+RMS for the radial-velocity measurements was $(18.2\,\rm m/s)$. \emph{See electronic version for colors}.}
+\label{megno_wasp19}
+\end{figure}

### 2019-07-19 wasp77.tex
New chapters for three targets
Added chapters from paper

@@
 \chapter{The case of WASP-77Ab}\label{chap:wasp77}
+
+\section{The system}
+The third exoplanet we followed-up in this work, WASP-77Ab, was first presented by \cite{Maxted2013}.
+WASP-77Ab has a mass of $1.8\,{\rm M_{Jupiter}}$ and a radius of $1.2\,{\rm R_{Jupiter}}$, and orbital period of 1.36 days.
+It transits a G8 star in the visual binary system with a separation of 3.3 arcsec.
+
+\section{Transit Parameters and Physical Properties}
+Table~\ref{tab:wasp77} lists the results of the global fit of WASP-77Ab, in comparison with the values from its discovery paper \citep{Maxted2013} on which photometry and RV data were used.
+No other previous work has reported bulk measurements for this system.
+
+Almost all the stellar parameters are in agreement with \citep{Maxted2013}, except for a $-9.7\sigma$ difference in the stellar surface gravity $\log{g}$, where our reported value is preciser.
+
+The primary transit parameters, as well as the RV parameters and the derived planetary parameters, are consistent with the results from \cite{Maxted2013}.
+
+\begin{landscape}
+\begin{longtable}{llcc}
+\caption{System parameter of WASP-77A}
+\label{tab:wasp77}
+\centering
+\tabularnewline
+\hline 
+~~~~~Parameter & Units & This work & \cite{Maxted2013}\\
+\hline
+\smallskip\\\multicolumn{2}{l}{Stellar Parameters:}&\smallskip\\
+~~~~$M_*$\dotfill &Mass (\(M_\odot\))\dotfill &$0.903^{+0.066}_{-0.059}$ & $1.002\pm0.045$\\
+~~~~$R_*$\dotfill &Radius (\(R_\odot\))\dotfill &$0.910^{+0.025}_{-0.023}$ & $0.955\pm0.015$\\
+~~~~$L_*$\dotfill &Luminosity (\(L_\odot\))\dotfill &$0.743^{+0.065}_{-0.058}$ & \\
+~~~~$\rho_*$\dotfill &Density (cgs)\dotfill &$1.692^{+0.056}_{-0.069}$\footnote{a} & $1.629^{+0.023}_{-0.028}$\footnote{a}\\
+~~~~$\log{g}$\dotfill &Surface gravity (cgs)\dotfill &$4.476^{+0.014}_{-0.015}$ & $4.33\pm0.08$\\
+~~~~$T_{\rm eff}$\dotfill &Effective Temperature (K)\dotfill &$5617\pm72$ & $5500\pm80$\\
+~~~~$[{\rm Fe/H}]$\dotfill &Metallicity \dotfill &$-0.10^{+0.10}_{-0.11}$ & $0.00\pm0.11$\\
+~~~~$Age$\dotfill &Age (Gyr)\dotfill &$6.2^{+4.0}_{-3.5}$ & $0.5-1.0$\\
+
+\smallskip\\\multicolumn{2}{l}{Planetary Parameters:}&\smallskip\\
+~~~~$R_P$\dotfill &Radius (\rj)\dotfill &$1.183^{+0.034}_{-0.031}$ & $1.21\pm0.02$\\
+~~~~$M_P$\dotfill &Mass (\mj)\dotfill &$1.650^{+0.082}_{-0.075}$ & $1.76\pm0.06$\\
+~~~~$P$\dotfill &Period (days)\dotfill &$1.3600290^{+(18)}_{-(20)}$ & $1.3600309\pm(20)$\\
+~~~~$e$\dotfill &Eccentricity \dotfill&$0.0074^{+0.0075}_{-0.0051}$\\
+~~~~$a$\dotfill &Semi-major axis (AU)\dotfill &$0.02323^{+0.00056}_{-0.00052}$ & $0.0240\pm0.00036$\\
+~~~~$\omega_*$\dotfill &Argument of Periastron (Degrees)\dotfill &$-30^{+170}_{-120}$\\
+~~~~$\rho_P$\dotfill &Density (cgs)\dotfill &$1.240^{+0.060}_{-0.067}$ & $1.33\pm0.04$\footnote{b}\\
+~~~~$logg_P$\dotfill &Surface gravity \dotfill &$3.467^{+0.012}_{-0.015}$ & $3.441\pm0.008$\\
+~~~~$T_{eq}$\dotfill &Equilibrium temperature (K)\dotfill &$1695^{+25}_{-24}$\\
+~~~~$\Theta$\dotfill &Safronov Number \dotfill &$0.0717\pm0.0021$\\
+~~~~$\fave$\dotfill &Incident Flux (\fluxcgs)\dotfill &$1.87^{+0.11}_{-0.10}$\\
+
+\smallskip\\\multicolumn{2}{l}{Primary Transit Parameters:}&\smallskip\\
+~~~~$T_0$\dotfill &Transit Time (\bjdtdb)\dotfill &$2457420.88439^{(+80)}_{(-85)}$ & $2455870.44977\pm(20)$\\
+~~~~$i$\dotfill &Inclination (Degrees)\dotfill &$88.91^{+0.74}_{-0.95}$ & $89.4^{+0.4}_{-0.7}$\\
+~~~~$R_P/R_*$\dotfill &Radius of planet in stellar radii \dotfill &$0.13352^{+0.00074}_{-0.00070}$\\
+~~~~$a/R_*$\dotfill &Semi-major axis in stellar radii \dotfill &$5.493^{+0.060}_{-0.075}$\\
+~~~~$b$\dotfill &Impact parameter \dotfill &$0.105^{+0.089}_{-0.071}$ & $0.06^{+0.07}_{-0.05}$\\
+~~~~$\delta$\dotfill &Transit depth (fraction)\dotfill &$0.01783^{+0.00020}_{-0.00019}$\\
+~~~~$u_{1,B}$\dotfill &linear LD coeff., B band \dotfill &$0.680\pm0.054$&\\
+~~~~$u_{2,B}$\dotfill &quadratic LD coeff., B band\dotfill &$0.140^{+0.052}_{-0.053}$&\\
+~~~~$u_{1,clear}$\dotfill &linear LD coeff., \emph{clear} band \dotfill &$0.386\pm0.029$\\
+~~~~$u_{2,clear}$\dotfill &quadratic LD coeff., \emph{clear} band \dotfill &$0.227\pm0.029$&\\
+~~~~$u_{1,I}$\dotfill &linear LD coeff., I band \dotfill &$0.311\pm0.025$&\\
+~~~~$u_{2,I}$\dotfill &quadratic LD coeff., I band \dotfill &$0.294\pm0.033$&\\
+~~~~$u_{1,R}$\dotfill &linear LD coeff., R band \dotfill &$0.312\pm0.023$\\
+~~~~$u_{2,R}$\dotfill &quadratic LD coeff., R band \dotfill &$0.237^{+0.029}_{-0.028}$\\
+~~~~$T_{14}$\dotfill &Total transit duration (days)\dotfill &$0.08952^{+0.00053}_{-0.00051}$\\
+~~~~$P_T$\dotfill &A priori non-grazing transit prob \dotfill &$0.1578^{+0.0029}_{-0.0025}$\\
+~~~~$P_{T,G}$\dotfill &A priori transit prob \dotfill &$0.2064^{+0.0039}_{-0.0033}$\\
+~~~~$\tau$\dotfill &Ingress/egress transit duration (days)\dotfill &$0.01075^{+0.00032}_{-0.00015}$\\
+
+\smallskip\\\multicolumn{2}{l}{RV Parameters:}&\smallskip\\
+~~~~$e\cos{\omega_*}$\dotfill & \dotfill &$-0.0033^{+0.0041}_{-0.0065}$\\
+~~~~$e\sin{\omega_*}$\dotfill & \dotfill &$-0.0002^{+0.0061}_{-0.0073}$\\
+~~~~$K$\dotfill &RV semi-amplitude (m/s)\dotfill &$323.4^{+3.7}_{-3.3}$ & $321.9\pm3.9$\\
+~~~~$M_P\sin i$\dotfill &Minimum mass (\mj)\dotfill &$1.649^{+0.082}_{-0.075}$\\
+
+\smallskip\\\multicolumn{2}{l}{Secondary Eclipse Parameters:}&\smallskip\\
+~~~~$T_S$\dotfill &Time of eclipse (\bjdtdb)\dotfill &$2457659.5665^{+0.0038}_{-0.0056}$\\
+~~~~$b_S$\dotfill &Eclipse impact parameter \dotfill &$0.104^{+0.089}_{-0.071}$\\
+~~~~$\tau_S$\dotfill &Ingress/egress eclipse duration (days)\dotfill &$0.01076^{+0.00035}_{-0.00023}$\\
+~~~~$T_{S,14}$\dotfill &Total eclipse duration (days)\dotfill &$0.0895^{+0.0013}_{-0.0014}$\\
+~~~~$P_S$\dotfill &A priori non-grazing eclipse prob \dotfill &$0.1578^{+0.0018}_{-0.0012}$\\
+~~~~$P_{S,G}$\dotfill &A priori eclipse prob \dotfill &$0.2063^{+0.0025}_{-0.0016}$\\
+\hline
+%\end{tabular}
+%\tablefoot{
+%\tablefoottext{a}{Value converted to cgs units multiplying by the Sun density $\rho_{\odot}=1.408\,$cgs.}
+%\tablefoottext{b}{Value converted to cgs units multiplying by the Jupiter density $\rho_{J}=1.33\,$cgs.}
+%\tablefoottext{c}{Values enclosed in parentheses correspond to the uncertainties of the last digits of the nominal value.}
+%}
+\end{longtable}
+\end{landscape}
+
+\section{Transit Timing Variations}
+
+As in the previous targets, we computed a refined linear ephemeris equation for WASP-77A considering 11 transit times:
+\begin{equation} \label{eq1_w77}
+T_{\rm C}(E)=2457420.88439\pm(85)+E \cdot 1.36002854\pm(52)
+\end{equation}
+
+In Table~\ref{tab:wasp77} are listed the TTV values of our transit times and from previous works \citep{Turner2016,Maxted2013} of WASP-77Ab and, at the bottom of Figure XXX are plotted versus epoch.
+The scatter of all the transit times is about $RMS=121$ seconds.
+
+The epochs $175$ and $229$ are above $2\,\sigma$ from the expected transit time following the linear ephemeris, while all the others epochs lie within $1.5\,\sigma$ from it.
+When removing the epochs $175$ and $229$, the RMS decreases to 88 seconds.
+
+Considering all the transit times, the linear fit has $\chi^{2}_{red}=1.4$, and the second degree polynomial has $\chi^{2}_{red}=1.39$ . However, we chose the linear fit as it suppose a simpler model.
+
+\begin{table}
+\caption{Transit mid-times for WASP-77Ab}
+\label{times_wasp77}
+\centering
+\begin{tabular}{cccc}
+\hline \hline
+Epoch & Transit mid-time & TTV & References\\
+      & (${\rm BJD_{TDB}}$) & (min) &  \\
+\hline
+-1140 & $2455870.45054$ & $-2.0\pm1.5$ & 1 \\
+-845 & $2456271.65888$ & $-2.0\pm1.4$ & 2 \\
+-659 & $2456524.62617$ & $0.8\pm1.8$ & This work\footnote{a} \\
+-606 & $2456596.70591$ & $-1.7\pm1.5$  & This work\footnote{a}  \\
+-92 & $2457295.7626$  & $1.2\pm1.3$& This work \\
+-89 & $2457299.84119$ &  $-1.0\pm1.3$ & This work \\
+175 & $2457658.88744$ & $-2.8\pm1.5$ & This work\\
+177 & $2457661.60987$   & $0.6\pm1.7$ & This work\footnote{a} \\
+183 & $2457669.77054$ &  $1.4\pm1.4$  & This work  \\
+229 & $2457732.33382$ & $4.2\pm1.4$& This work\footnote{a} \\
+447 & $2458028.8159$  & $-1.8\pm6.5$ & This work\\ 
+\hline
+\end{tabular}
+%\tablebib{(1) \citet{Maxted2013}; (2) \cite{Turner2016}.}
+%\tablefoot{
+%\tablefoottext{a}{From the Exoplanet Transit Database (ETD)  \url{var2.astro.cz/ETD}}}
+\end{table}
+
+\section{Limits on an additional perturber}
+For the WASP-77Ab system the results are somewhat similar to WASP-19b.
+We refer to Fig.~\ref{megno_wasp77}.
+The measured RMS of mid-transit timing variations around the linear ephemeris was $\rm TTV_{\rm RMS}=121\rm s$.
+For interior mean-motion resonances the 1:2 and 2:3 commensurabilities could cause the observed $\rm TTV_{\rm RMS}$ by an additional planet of mass around $3.5~M_{\oplus}$ and $7~M_{\oplus}$.
+However, the 2:3 resonance is very close to the general instability area rendering the orbit likely to be unstable.
+Further a $1~M_{\oplus}$ mass planet at the 1:3 interior resonance could also cause a $\rm TTV_{\rm RMS}$ of 121 s.
+A $2~M_{\oplus}$ mass planet located at the 3:5 resonance, although relatively close to the inner edge of the general instability region, could also explain the observed timing variation.
+For exterior
+mean-motion resonances of 2:1, 3:1 and 4:1 an additional planet of mass $3.5~M_{\oplus}, 4.5~M_{\oplus}$ and $60~M_{\oplus}$, could cause a $\rm TTV_{\rm RMS}=121\rm s$, respectively.
+A subtle difference from the WASP-19b system is found at the 5:2 resonance, which does not exhibit any significant decrease in upper mass planet detection sensitivity.
+
+\begin{figure}
+\includegraphics[width=1.0\columnwidth]{imagenes/WASP77_TraMos_121sec_Map001_GIMP_scaled.png}
+\caption{Same as Fig.~\ref{megno_wasp18}, but this time for WASP-77 with an $\rm TTV_{\rm RMS}$ of 121 s. The RMS for the radial-velocity measurements was $(12.0\,\rm m/s)$.
+\emph{See electronic version for colors}.}
+\label{megno_wasp77}
+\end{figure}

### 2019-07-24 introduction.tex
Work done in the Introduction

@@
 \chapter{Introduction}\label{chap:intro}
+The existence of planets orbiting other stars different from our Sun, lived in the human imagination for centuries.
+During the sixteenth century, the Italian philosopher Giordano Bruno suggested, for the first time in history, that more planet could be outside the Solar System.
+Even though the first claims of exoplanet detection began at the end of the nineteenth century, it was not until more than four hundred years after the statement of Giordano Bruno, that the first exoplanet was confirmed in 1992.
+Surprisingly it was not just one exoplanet but three, orbiting the pulsar PSR B1257+12 more than 1000 light-years away from us.
+Today, more than 4,000 exoplanet are confirmed, and thousands more are waiting for their confirmation.
+
+The increasing number of discovered exoplanets have been reach thanks to two techniques: Radial Velocity and Transits.
+Each one of these techniques had their own advantages depending on the physical properties of the planetary system.
+When the orbit of the exoplanet is aligned with the line of sight from Earth, the pass of the planet in front of its host star, the star's flux decreases proportionally to the size of the planet.
+Thus, its radius, in comparison with the radius of the star, can be determined directly using the Transit method.
+In the other hand, the gravity due to the presence of a planet will set the center of mass of the system, in a place different from the star's center.
+Therefore, the star will move in its own small orbit with a size proportional to the mass of the planet.
+In this case, the planet's minimum mass ($M_{p}\cdot \sin i$) can be determined.
+The perfect scenario comes when both method can be use in the same planetary system, allowing to derived essential properties as the real mass and the mean density of the planet.
 
 \section{Transiting Exoplanets}
+The Transit method is today the most successful technique to discover extrasolar planets. The Kepler mission was launched in 2009 and during its almost nine years of 
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\columnwidth]{imagenes/transit.png}
+\caption{Architecture of a transiting exoplanet.}
+\label{transit}
+\end{figure}
+
+\begin{figure}[H]
+\includegraphics[width=1.0\columnwidth]{imagenes/transit_examples.png}
+\caption{Examples of transiting exoplanets and how their light curves differ between them thanks to the physical properties of the exoplanet.}
+\label{transit_examples}
+\end{figure}
 

### 2019-07-28 introduction.tex
Updated Introduction, new chapter about TraMoS

@@
 Even though the first claims of exoplanet detection began at the end of the nineteenth century, it was not until more than four hundred years after the statement of Giordano Bruno, that the first exoplanet was confirmed in 1992.
-Surprisingly it was not just one exoplanet but three, orbiting the pulsar PSR B1257+12 more than 1000 light-years away from us.
+Surprisingly, it was not just one exoplanet but three, orbiting the pulsar PSR B1257+12 more than 1000 light-years away from us.
 Today, more than 4,000 exoplanet are confirmed, and thousands more are waiting for their confirmation.
 
-The increasing number of discovered exoplanets have been reach thanks to two techniques: Radial Velocity and Transits.
+The increasing number of discovered exoplanets have been reached thank to two techniques: Radial Velocity and Transits.
 Each one of these techniques had their own advantages depending on the physical properties of the planetary system.
-When the orbit of the exoplanet is aligned with the line of sight from Earth, the pass of the planet in front of its host star, the star's flux decreases proportionally to the size of the planet.
+When the orbit of the exoplanet is aligned with the line of sight from Earth, the pass of the planet in front of its host star causes that the star's flux decreases proportionally to the size of the planet.
 Thus, its radius, in comparison with the radius of the star, can be determined directly using the Transit method.
@@
 Therefore, the star will move in its own small orbit with a size proportional to the mass of the planet.
-In this case, the planet's minimum mass ($M_{p}\cdot \sin i$) can be determined.
-The perfect scenario comes when both method can be use in the same planetary system, allowing to derived essential properties as the real mass and the mean density of the planet.
+In this case, the Radial Velocity method unveils the planet's minimum mass ($M_{p}\sin i$).
+The perfect scenario comes when both methods can be used in the same planetary system, allowing to derive essential properties such as the real mass and the mean density of the planet.
 
 \section{Transiting Exoplanets}
-The Transit method is today the most successful technique to discover extrasolar planets. The Kepler mission was launched in 2009 and during its almost nine years of 
+The Transit method is today the most successful technique to discover extrasolar planets (see Fig.~\ref{amount_exoplanet}).
+The Kepler mission was launched in 2009 and during its almost nine years of provided thousands of discoveries due to this method.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\columnwidth]{imagenes/exo_dischist_cumulative.png}
+\caption{Accumulative number of discovered exoplanets by year.}
+\label{amount_exoplanet}
+\end{figure}
+
+The light curve produced by a transit event provides important information of the planetary system.
+For example, it is the only way on which we can derived directly the proportion between the exoplanet's and star's radii.
+It can also give information about the impact parameter, and therefore, the inclination of the orbit.
+
+In Figure~\ref{transit} is described the architecture of a transiting exoplanet.
+When the planet passes in front of its star produced a dimming in its flux called primary transit.
+The maximum drop during the transit event defines the transit depth $\Delta{F}$:
+
+\begin{equation}
+    \Delta{F} = \left(\frac{R_{p}}{R_{*}}\right)^2 
+\end{equation}
+
+Where $R_{p}$ and $R_{*}$ are the planet and star radius, respectively.
+The numbers 1, 2, 3 and 4 correspond to the contact times: $t_{1}$, $t_{2}$, $t_{3}$ and $t_{4}$.
+The total duration of the transit is $t_{T} = t_{4}-t_{1}$ and the full duration is $t_{F}=t_{3}-t_{2}$.
+The total duration of the transit can be also described considering planetary parameters such as the period $P$, semi-major axis $a$ and orbital inclination $i$:
+
+\begin{equation}
+    t_{T} = \frac{PR_{star}}{\pi a} \sqrt{\left(1+\frac{R_{p}}{R_{*}}\right)^2-\left(\frac{a\cos i}{R_{*}}\right)}
+\end{equation}
+
+The impact parameter $b$, is the sky-projected distance between the center of the star and the planet at conjunction:
+
+\begin{equation}
+    b = \frac{a\cos{i}}{R_{*}}\left(\frac{1-e^2}{1+e\sin{\omega}}\right)
+\label{impact_param}
+\end{equation}
+
+Where $\omega$ is the periastron longitude. In the case of circular orbits, the eccentricity is zero, thus Eq.~\ref{impact_param} is simplified to:
+
+\begin{equation}
+    b = \frac{a\cos{i}}{R_{*}}
+\label{impact_param_simple}
+\end{equation}
+
 \begin{figure}[H]
@@
 \includegraphics[width=0.8\columnwidth]{imagenes/transit.png}
-\caption{Architecture of a transiting exoplanet.}
+\caption{Architecture of a transiting exoplanet and the observed light curve.
+Based on the light curve itself it is possible to measure the transit depth $\Delta F$, the impact parameter $b$.
+From them, the planet-to-star radius ratio $R_{p}/R_{*}$ and the orbital inclination $i$ can be derived.
+Figure from The Handbook of Exoplanets by M.
+Perryman.}
 \label{transit}
@@
 
+Depending on the orbital and physical parameters of the exoplanet, the shape of the observed light curve will vary.
+For example, Figure \ref{transit_examples} shows how the light curve reflects the configuration of the system.
+Hot Jupiters are the kind of planet easier to detect, since their planet-to-star radius ratio is larger.
+But an smaller planet orbiting a dwarf star could produce a similar ratio of the radius.
+In the other hand, exoplanets with larger orbital inclinations will produce shorter drops in the flux, in comparison with planets in the same orbital-plane with the host star.
+
 \begin{figure}[H]
-\includegraphics[width=1.0\columnwidth]{imagenes/transit_examples.png}
+\centering
+\includegraphics[width=0.8\columnwidth]{imagenes/transit_examples.png}
 \caption{Examples of transiting exoplanets and how their light curves differ between them thanks to the physical properties of the exoplanet.}
@@
 \section{Transit Timing Variations}
-
-\section{The Transit Monitoring in the South project}

### 2019-07-28 tramos.tex
Updated Introduction, new chapter about TraMoS

\chapter{The Transit Monitoring in the South project}\label{chap:tramos}

High-precision long-term transit follow-ups provide tremendous opportunities in improving our understanding of exoplanets, leading to obtain more accurate measurements of planetary radius, especially those detected with ground-based transit surveys (e.g., HATNet and HATSouth, \citealt{Bakos2012}; SuperWASP, \citealt{Pollacco2006}; KELT, \citealt{Pepper2007}; TRES, \citealt{Alonso2007}, CSTAR, \citealt{WangS2014}). With improved photometry, we can refine planetary orbital ephemeris \citep{TEMP1}, which is vital to schedule future transit-related observations, such as Rossiter-Mclaughlin effect measurement \citep{Nutzman2011,Sanchis2011,Sanchis2013,WangS2018} and transmission spectrum follow-up \citep{Mancini2016b,Mackebrandt2017}.

%Long-term photometric follow-up also provides a unique chance to study the variations of the orbital periods. A recent study shows the apparent orbital decay in the WASP-12 system \citep{Patra2017}, which intrigues a series of theoretical studies \citep{Millholland2018,Weinberg2017} to discuss the potential mechanisms. The transit follow-up also plays an important role in exoplanet system which shows interesting Transit Timing Variations (TTV) \citep{Ballard2011,Ford2012a,Steffen2012,Fabrycky2012,Mancini2016,WangS2017,Wu2018}.

%\cite{Ballard2018} predicted that around 5\% of planets discovered by TESS \citep{Ricker2014} will show TTVs. Transit follow-up of these targets is very critical, because most of them will only be monitored for $\sim27$ days, whereas the typical TTV period is around years.

%Furthermore, extended TTV studies are crucial to confirm or rule out exoplanetary systems, in cases where space-based observations will not cover the long-time scales required to characterize them \citep{vonEssen2018}. Thus, combining ground and space-based observations will be crucial.

%The TTV method \citep{Miralda2002,Agol2005,Holman2005}  also provides a powerful tool to detect additional low-mass planets in hot Jupiter systems, which is usually hard to find by using other techniques \citep{Steffen2012b}. Many efforts have been devoted to this field \citep{Pal2011,Hoyer2012,Hoyer2013,Szabo2013}, but so far only two hot Jupiters have been found to accompanies with additional close-in planets (WASP-47: \cite{Becker2015}, and Kepler-730: \cite{Canas2019}). The accurate occurrence rate of the `WASP-47-like' system is still unknown.

%To refine orbital parameters of currently known exoplanets, and to search for additional planets by using TTV method, we organized the Transit Monitoring in the South hemisphere (TraMoS) project \citep{Hoyer2011} since 2008. We uses one-meter class telescopes in the north of Chile to conduct high-precision long-term transit follow-up.

%Following the previous efforts from the TraMoS project, in this work, we present new light curves of three hot Jupiters: WASP-18b, WASP-19b, WASP-77Ab. Combining our new light curves, and archival photometric and radial velocity data sets, we refined the orbital and physical parameters of the systems, and constrained the upper mass limit of potential additional planetary companions.

### 2019-07-29 introduction.tex
Started TTV section. Added section This work

@@
 In Figure~\ref{transit} is described the architecture of a transiting exoplanet.
+Thanks to its geometry, the transit event as well as some parameters of the planetary system can be described with a few simple relations (cite Seager and Mallean y Winn).
 When the planet passes in front of its star produced a dimming in its flux called primary transit.
@@
 
+TO DO: Add studies about transmission spectroscopy.
+
 \begin{figure}[H]
@@
 \section{Transit Timing Variations}
+
+Since the discovery of the first exoplanet, one of the principal questions that arose was: are they alone in their systems?
+The idea of multiplanetary system is a consequence of our knowlegde about the planetary system where we live in, and until today the Solar System has the larger number of orbiting planets.
+Besides the Solar System, Kepler-90 has the same number of confirmed exoplanets: eight.
+Statistically, around a 20\% of the confirmed exoplanets live in a multiplanetary system, but this number is theoretically larger (cite).
+
+The Transit Timing Variations technique was proposed as a way to detect Earth-mass planet in multiplanetary systems due to gravitational interactions \citep{Holman2005,Agol2005}.
+A planet in a Keplerian orbit will transit its star following a linear function of the orbital period, but the presence of a second planet could produce transits no exactly periodic.
+
+\section{This work}

### 2019-07-29 introduction.tex
More work in Introduction TTV

@@
 The light curve produced by a transit event provides important information of the planetary system.
-For example, it is the only way on which we can derived directly the proportion between the exoplanet's and star's radii.
+For example, it is the only way on which we can derived directly the proportion between the exoplanet and star radius.
 It can also give information about the impact parameter, and therefore, the inclination of the orbit.
@@
 Since the discovery of the first exoplanet, one of the principal questions that arose was: are they alone in their systems?
-The idea of multiplanetary system is a consequence of our knowlegde about the planetary system where we live in, and until today the Solar System has the larger number of orbiting planets.
+The idea of multiplanetary system is a consequence of our knowledge about the planetary system where we live in, and until today the Solar System has the larger number of orbiting planets.
 Besides the Solar System, Kepler-90 has the same number of confirmed exoplanets: eight.
@@
 The Transit Timing Variations technique was proposed as a way to detect Earth-mass planet in multiplanetary systems due to gravitational interactions \citep{Holman2005,Agol2005}.
-A planet in a Keplerian orbit will transit its star following a linear function of the orbital period, but the presence of a second planet could produce transits no exactly periodic.
+A planet in a Keplerian orbit will transit its star following a linear function of the orbital period (Eq.~\ref{linear_ephemeris}), but the presence of a second planet could produce transits no exactly periodic, thus the time between two consecutive transits varies.
+
+\begin{equation}
+T_{c}(E) = T_{0} + E \cdot P
+\label{linear_ephemeris} 
+\end{equation}
+
+In Equation .~\ref{linear_ephemeris}, $P$ is the orbital period and $E$ is an arbitrary epoch with the corresponding transit time $T_{c}(E)$.
+For a given light curve (see Figure \ref{transit}), the transit time is computed as:
+
+\begin{equation}
+T_{c} = \frac{t_T}{2}
+\end{equation}
+
+The variation in time produced by the perturbing body depends on the mass and geometry of their orbits. The magnitude of the variation between successive  transit is:
+
+\begin{equation}
+\Delta t = \frac{45\pi}{16} \frac{M_2}{M_*} P_{1} \alpha^3_{e} (1-	\sqrt{2}\alpha^{3/2})^{-2}
+\end{equation}
+
+Where $\alpha_e = \frac{a_1}{a_2(1-e_2)}$, $a_1$ and $P_1$ are the semi-major axis and orbital period of the transiting exoplanet, while the perturbing planet has a mass $M_2$, semi-major axis $a_2$  and orbital period $P_2$
 

### 2019-07-31 introduction.tex
Figures W18 added, more writting in Intro TTV

@@
 \centering
-\includegraphics[width=0.8\columnwidth]{imagenes/exo_dischist_cumulative.png}
+\includegraphics[width=0.7\columnwidth]{imagenes/exo_dischist_cumulative.png}
 \caption{Accumulative number of discovered exoplanets by year.}
@@
 
-The Transit Timing Variations technique was proposed as a way to detect Earth-mass planet in multiplanetary systems due to gravitational interactions \citep{Holman2005,Agol2005}.
-A planet in a Keplerian orbit will transit its star following a linear function of the orbital period (Eq.~\ref{linear_ephemeris}), but the presence of a second planet could produce transits no exactly periodic, thus the time between two consecutive transits varies.
+The Transit Timing Variations (TTV) technique was first proposed as a way to detect Earth-mass planets in multiplanetary systems due to gravitational interactions with a transiting exoplanet \citep{Holman2005,Agol2005}.
+However, TTVs can be also use to measure tidal interactions between the planet and the star or to detect exomoons \citep{Kipping2009a,Kipping2009b}, among others.
+
+For a given light curve of a transiting exoplanet (see Fig. \ref{transit}), the transit time $T_{c}$ (or central time of the transit) is computed as:
+
+\begin{equation}
+T_{c} = \frac{t_T}{2}
+\end{equation}
+
+A single transiting planet will stay in a Keplerian orbit around its host star, producing a transit time strictly periodic.
+Thus, the transit time $T_c$ follows a linear function of the orbital period $P$:
 
@@
 
-In Equation .~\ref{linear_ephemeris}, $P$ is the orbital period and $E$ is an arbitrary epoch with the corresponding transit time $T_{c}(E)$.
-For a given light curve (see Figure \ref{transit}), the transit time is computed as:
-
-\begin{equation}
-T_{c} = \frac{t_T}{2}
-\end{equation}
-
-The variation in time produced by the perturbing body depends on the mass and geometry of their orbits. The magnitude of the variation between successive  transit is:
+Where $T_0$ is a reference transit time and $E$ is the number of epochs since $T_0$.
+The presence of a second planet produces transits no exactly periodic, hence Eq.~\ref{linear_ephemeris} will not be valid.
+As the transit times will be no longer a linear function,  the time between  transits varies.
+The variation in time produced by the perturbing body depends on the mass and geometry of their orbits.
+The magnitude of this variation between successive transits of the transiting planet is:
 
@@
 \Delta t = \frac{45\pi}{16} \frac{M_2}{M_*} P_{1} \alpha^3_{e} (1-	\sqrt{2}\alpha^{3/2})^{-2}
+\label{delta_t}
 \end{equation}
 
-Where $\alpha_e = \frac{a_1}{a_2(1-e_2)}$, $a_1$ and $P_1$ are the semi-major axis and orbital period of the transiting exoplanet, while the perturbing planet has a mass $M_2$, semi-major axis $a_2$  and orbital period $P_2$
+Where $\alpha_e = a_1/(a_2(1-e_2))$ is the ratio of the semi-major axis of the planets, considering a nonzero eccentricity for the perturbing planet ($e_2 \neq 0$) and $a_1 < a_2$.
+The semi-major axis of the transiting exoplanet is $a_1$ and its orbital period $P_1$, while the perturbing planet has a mass $M_2$, semi-major axis $a_2$, orbital period $P_2$ and eccentricity $e_2$.
+Assuming that the orbital parameters of the known transiting exoplanet are already derived from its light curve, the orbital parameters and mass of the hypothetical pertuber can be estimate numerically \citep{Nesvorny2008,Nesvorny2009}, even if the second planet does not transit the star.
+
+The TTV method is a efficient tool to search for additional unseen companions, since in order to employ this technique only photometry of the transiting exoplanet during a transit events is required.
+Moreover, this technique enhances its sensitivity when the two bodies in the system are close to Mean Motion Resonances (MMR) \citep{Agol2005,Steffen2005,Agol2007} (see Figure~\ref{rms_ttv_amplitude}) .
+
+\begin{figure}
+\centering
+\includegraphics[width=0.6\columnwidth]{imagenes/rms_ttv_amplitude}
+\caption{Example of a system with a transiting exoplanet of $1~M_{J}$ in a 10-day orbit, around a star with $0.367~M_{\odot}$.
+The perturber is a Earth-mass planet.
+Panel \textbf{a} is an O-C diagram showing the measured TTV when the pertuber has a period of 16.11 days, not in Mean Motion Resonance with the transiting planet.
+Panel \textbf{b} shows the TTV when the transiting planet and the perturbing planet are near an interior 2:1 resonance.
+The amplification of the TTV signal is by an order of magnitude.
+(Figure from \cite{Haghighipour2011})}
+\label{rms_ttv_amplitude}
+\end{figure}
+
+\cite{Holman2010} presented the first multiplanetary system confirmed using the TTV method: Kepler-9b and Kepler-9c.
+
+The no detection of TTV is also important: architecture of the system.
 
 \section{This work}
+
+This thesis is an extension of the Transit Monitoring in the South project (TraMoS, see Chapter\ref{chap:tramos}) started in 2008 by Sergio Hoyer and Patricio Rojo.
+I selected a new sample of transiting exoplanets, all of them hot Jupiters without any companions detected to date.

### 2019-07-31 paper.tex
Full paper in thesis, removed separated chapters

\chapter{Analysis and Results of WASP-18b, WASP-19b, and WASP-77Ab}\label{chap:paper}

\section*{TraMoS V: Updated ephemeris and transit timing variations of the hot Jupiters WASP-18b, WASP-19b and WASP-77Ab}

\chapterauthor{P\'ia Cort\'es-Zuleta, Patricio Rojo, Songhu Wang, Tobias C. Hinse, Sergio Hpyer, Bastian Sanhueza, Patricio Correa-Amaro, Julio Albornoz}

\subsection*{Abstract}

We present 22 new transit observations for the exoplanets WASP-18b, WASP-19b, and WASP-77Ab, from the Transit Monitoring in the South (\emph{TraMoS}) project. We simultaneously model our newly collected transit light curves, as well as archival photometry and radial velocity data to obtain refined physical and orbital parameters. We did not find significant $\rm TTV_{RMS}$ variations larger than 83, 75, and 121 seconds for WASP-18b, WASP-19b, and WASP-77Ab, respectively. Dynamical simulations were carried out to constrain the masses of a possible perturber. The observed RMS could be produced by a perturber body with an upper limit mass of 5 and $7~M_{\oplus}$ in 1:2 and 3:1 resonance, and $25~M_{\oplus}$ in 2:1 resonance for WASP-18b. In the case of WASP-19b, companions with masses up to 0.9, 2 and $6~M_{\oplus}$, in 2:1, 3:1, and 5:3 resonances, reproduce the RMS. In this system, we also discard a hypothetical perturber of $500~M_{\oplus}$ in 1:3 resonance, because of the mass limit from RV variations. For WASP-77Ab a planet with masses between $1-7~M_{\oplus}$ in 1:2, 1:3, 2:1, 2:3, 3:1, 3:5, 5:3 resonances could reproduce the observed RMS in the TTVs. Finally, using a Lomb-Scargle period search we find no evidence of a periodic trend on our TTV data for the three exoplanets.

\section{Introduction}

High-precision long-term transit follow-ups provide tremendous opportunities in improving our understanding of exoplanets, leading to obtain more accurate measurements of planetary radius, especially those detected with ground-based transit surveys (e.g., HATNet and HATSouth, \citealt{Bakos2012}; SuperWASP, \citealt{Pollacco2006}; KELT, \citealt{Pepper2007}; TRES, \citealt{Alonso2007}, CSTAR, \citealt{WangS2014}). With improved photometry, we can refine planetary orbital ephemeris \citep{TEMP1}, which is vital to schedule future transit-related observations, such as Rossiter-Mclaughlin effect measurement \citep{Nutzman2011,Sanchis2011,Sanchis2013,WangS2018} and transmission spectrum follow-up \citep{Mancini2016b,Mackebrandt2017}.

Long-term photometric follow-up also provides a unique chance to study the variations of the orbital periods. A recent study shows the apparent orbital decay in the WASP-12 system \citep{Patra2017}, which intrigues a series of theoretical studies \citep{Millholland2018,Weinberg2017} to discuss the potential mechanisms. The transit follow-up also plays an important role in exoplanet system which shows interesting Transit Timing Variations (TTV) \citep{Ballard2011,Ford2012a,Steffen2012,Fabrycky2012,Mancini2016,WangS2017,Wu2018}.

\cite{Ballard2018} predicted that around 5\% of planets discovered by TESS \citep{Ricker2014} will show TTVs. Transit follow-up of these targets is very critical, because most of them will only be monitored for $\sim27$ days, whereas the typical TTV period is around years.

Furthermore, extended TTV studies are crucial to confirm or rule out exoplanetary systems, in cases where space-based observations will not cover the long-time scales required to characterize them \citep{vonEssen2018}. Thus, combining ground and space-based observations will be crucial.

The TTV method \citep{Miralda2002,Agol2005,Holman2005}  also provides a powerful tool to detect additional low-mass planets in hot Jupiter systems, which is usually hard to find by using other techniques \citep{Steffen2012b}. Many efforts have been devoted to this field \citep{Pal2011,Hoyer2012,Hoyer2013,Szabo2013}, but so far only two hot Jupiters have been found to accompanies with additional close-in planets (WASP-47: \cite{Becker2015}, and Kepler-730: \cite{Canas2019}). The accurate occurrence rate of the `WASP-47-like' system is still unknown.

To refine orbital parameters of currently known exoplanets, and to search for additional planets by using TTV method, we organized the Transit Monitoring in the South hemisphere (TraMoS) project \citep{Hoyer2011} since 2008. We uses one-meter class telescopes in the north of Chile to conduct high-precision long-term transit follow-up.

Following the previous efforts from the TraMoS project, in this work, we present new light curves of three hot Jupiters: WASP-18b, WASP-19b, WASP-77Ab. Combining our new light curves, and archival photometric and radial velocity data sets, we refined the orbital and physical parameters of the systems, and constrained the upper mass limit of potential additional planetary companions.

%\subsection{Systems}
WASP-18b is a transiting hot Jupiter discovered by \citet{Hellier2009} within the WASP-South transit survey \citep{Pollacco2006}. It is an extremely close-in planet orbiting a F6 type star with a period of 0.94 days. Regarding its physical properties, WASP-18b is about ten times more massive than Jupiter with approximately the same size ($M_{P}=10.3\,{\rm M_{Jupiter}}$, $R_{P}=1.1\,{\rm R_{Jupiter}}$). Even though a rapid orbital decay was predicted theoretically \citep{Hellier2009}, it is not observed yet \citep{Wilkins2017} and new theoretical models proposed a variation of less than 4 seconds in the transit time over a 20-yr baseline \citep{CollierCameron2018}.

The hot Jupiter WASP-19b was first reported by \cite{Hebb2010}. It is known as one of the currently hot Jupiters with shortest orbital period ($P=0.788\,{\rm days}$). With a mass of $1.15\,{\rm M_{Jupiter}}$ and a radius of $1.31\,{\rm R_{Jupiter}}$, the planet orbits an active G8 dwarf.

The third exoplanet we followed-up in this work, WASP-77Ab, was first presented by \cite{Maxted2013}. WASP-77Ab has a mass of $1.8\,{\rm M_{Jupiter}}$ and a radius of $1.2\,{\rm R_{Jupiter}}$, and orbital period of 1.36 days. It transits a G8 star in the visual binary system with a separation of 3.3 arcsec.

This paper is organized as follows. In Section~\ref{obs} are summarized the photometric observations and their reduction process. In Section~\ref{lc} we present the new light curves of the targets and the description of the technique used to obtain their orbital and physical parameters. The principal results and their consequences are presented in Section~\ref{res}. Finally, a summary and conclusions are described in Section~\ref{summary}.

\section{Observations and Data Reduction}

We collected 8 light curves for WASP-18b between 2009 and 2017, 9 light curves for WASP-19b between 2011 and 2017, and 5 light curves for WASP-77Ab between 2015 and 2017. We included 4 transits of WASP-77Ab from the Exoplanet Transit Database (ETD) in order to cover a larger timespan.

All of the photometry are collected by using either the Danish 1.54 m telescope at ESO La Silla Observatory, or the SMARTS 1 m at Cerro Tololo Observatory (CTIO), except for one transit of WASP-77Ab that was observed with the Warsaw 1.3 m at Las Campanas Observatory (LCO). The log of our observations is shown in Table \ref{log_table}. All the new light curves used for this work are presented in Figure~\ref{transits}.

For the photometric observations conducted on the Danish telescope, we used the Danish Faint Object Spectrograph and Camera (DFOSC) instrument, which has a $2{\rm K} \times 2{\rm K}$ CCD with a 13.7 x 13.7 arcmin$^2$ field of view (FoV) and a pixel scale of 0.39" per pixel. To reduce the readout time, some of the Danish 1.54 m images were windowed to only include the target star and its closest reference stars. The observations of the transits of WASP-18b during 2016 and 2017 were forced to be windowed due to a malfunction of the CCD. For those transits, only one reference star was used to perform the photometry.

The SMARTS 1 m has the Y4KCam instrument which is a $4{\rm K} \times 4{\rm K}$ CCD camera with a $20\times20$ arcmin$^2$ FoV and a pixel scale of 0.289" per pixel.

For the observation on the Warsaw 1.3 m telescope, we used a $2048 \times 4096$ CCD camera chip with a 1.4 square degrees of FoV and 0.26" per pixel scale. No windowing or binning was used during the observations on both SMARTS 1m and the Warsaw 1.3m telescope.

As suggested by \cite{Southworth2009}, most of our observation, especially those conducted after 2011, used the defocus technique, which allows longer exposure times in bright targets and improves the photometric precision. We adjust the exposure time during the observations if the weather is not ideal. The recorded Julian Date in the Coordinated Universal Time (${\rm JD_{UTC}}$) were converted into Barycentric Julian Date in the Barycentric Dynamical Time standard (${\rm BJD_{TDB}}$) by following the procedure as in \citet{Eastman2010}.

We reduced the data by using our custom pipeline. It follows the standard procedures of reduction, calibration, and aperture photometry, but customized for each used instrument. The pipeline semi-automatically finds the best aperture and ring size, for the sky that produces the light curve with less RMS. Then, we manually choose the reference stars to produce the differential light curves for each targets.

\begin{table*}
\caption{Log of Observations}             
\label{log_table}      
\centering          
\begin{tabular}{cccccccc}
\hline\hline       
Target & Date & Epoch\footnotemark{a} & Telescope & Filter & N & $t_{exp}$\footnotemark{b} & RMS\footnotemark{c} \\
& (UTC) &       &           &       &                   & (seconds) & (mmag)\\
\hline  
WASP-18 & 2009 Oct 28 &-1904 & SMARTS 1 m & $I$ & 1412 & 1.5 & 8.49  \\
 				& 2009 Oct 29 & -1903 & SMARTS 1 m & $I$ & 1435 & 2 & 5.67 \\
				& 2009 Oct 30 & -1902 & SMARTS 1 m & $I$ & 1198 & 2  & 4.50 \\
 				& 2011 Sep 06 & -1184 & SMARTS 1 m & $I$ & 203 & 15 & 2.40 \\
				& 2016 Sep 24\footnotemark{d} & 776 & Danish 1.54 m & $I$ & 138 & 90 & 1.05  \\
				& 2016 Sep 25\footnotemark{d} & 777 &Danish 1.54 m & $I$ & 159 & 90  & 0.96  \\
			    & 2016 Sep 26\footnotemark{d} & 778 & Danish 1.54 m & $I$ & 113 & 90 & 0.87  \\ \smallskip
				& 2017 Sep 29\footnotemark{d} & 1169 & Danish 1.54 m & $R$ & 330 & 30 & 2.53 \\
WASP-19 & 2011 Apr 22 & -923 & SMARTS 1 m &   $I$ &  626  & 12  & 4.31   \\
     & 2011 Dec 24 & -611 & SMARTS 1 m &   $I$ & 364  & 18  & 35.9 \\
     & 2013 Mar 13 & -47 & Danish 1.54 m & $R$ & 336 & 35 & 2.15\\
     & 2013 Apr 20 & 1 & Danish 1.54 m & $R$ & 153 & 100 & 0.80 \\
     & 2015 Mar 04 & 867 & Danish 1.54 m & $R$ & 235 & 60 & 0.84\\
     & 2016 Apr 14 & 1383 & Danish 1.54 m & $I$ & 87 & 100 & 0.71\\
     & 2017 Feb 14 & 1771 & Danish 1.54 m & $I$ & 137 & 90 & 0.79\\
     & 2017 Apr 08 & 1838 & Danish 1.54 m & $R$ & 125 & 90 & 0.81\\\smallskip
     & 2017 Oct 03 & 2064 & Danish 1.54 m & $R$ & 43 & 110 & 1.70\\ 
 WASP-77 & 2013 Aug 20 & -659 & ETD\footnotemark{e} & $clear$ & 103 & 120 & 3.87  \\
    & 2013 Oct 30 & -606 & ETD\footnotemark{e} & $clear$ & 690 & 12 & 5.91 \\
    & 2015 Sep 29 & -92 & Danish 1.54 m & $R$ &  244 & 30 &  0.84\\
      & 2015 Oct 03 & -89 & Danish 1.54 m & $R$ &  138 & 60 &  1.84\\
      & 2016 Sep 26 & 175 & Danish 1.54 m & $I$ &  90 & 90 &  0.47\\
      & 2016 Sep 30 & 177 & ETD\footnotemark{e}& $clear$ & 66 & 180 & 2.74 \\
      & 2016 Oct 07 & 183 & Warsaw 1.3 m & $I$ & 237 & 60 &  2.38 \\ 
      & 2016 Dec 09 & 229 & ETD\footnotemark{e} & $R$ & 57 & 180 & 2.11 \\ 
      & 2017 Oct 01 & 447 & Danish 1.54 m & $B$ &  224 & 30 &   3.48\\
\hline                  
\end{tabular}
\footnotetext{a}{The epoch 0 is $T_{0}$ in Tables , for WASP-18b, WASP-19b and WASP-77Ab, respectively.}
\footnotetext{b}{For the variable exposure times, we consider the average during the night.}
\footnotetext{c}{The RMS values were computed from the best fitted model of each light curve.}
\footnotetext{d}{Light curves obtained with only one reference star.}
\end{table*}

\begin{table}

\caption{Example photometry of WASP-18, WASP-19 and WASP-77A}
\label{examplephot}
\centering
\begin{tabular}{c c c c}
\hline \hline
Target & ${\rm BJD_{TDB}}$\footnotemark{a} & Relative flux & Error\\
\hline
    WASP-18b &  2457658.658241   & 1.00168 & 0.00078 \\
             &  2457658.660591   & 1.00138 & 0.00080 \\
             &  2457658.661771   & 1.00195 & 0.00082 \\
             &  2457658.662940   & 1.00261 & 0.00085 \\
             &  2457658.664109   & 1.00137 & 0.00086 \\\smallskip
      & ...           & ...         &    ... \\
    WASP-19b & 2457086.543926   & 1.00099 & 0.00086  \\
             & 2457086.544916   & 1.00173 & 0.00091  \\
             & 2457086.545905   & 1.00139 & 0.00086  \\
             & 2457086.546895   & 1.00045 & 0.00094  \\
             & 2457086.547886   & 1.00064 & 0.00093  \\\smallskip
     &  ...           & ...         &    ...  \\
WASP-77Ab & 2457299.78624 & 1.00229 & 0.00028 \\ 
         & 2457299.78764 & 1.00116 & 0.00022 \\
         & 2457299.78855 & 1.00201 & 0.00022 \\
         & 2457299.78946 & 1.00216 & 0.00022 \\
         & 2457299.79092 & 1.00133 & 0.00021 \\
         & ...           & ...         &    ... \\    
\hline
\end{tabular}
\footnotetext{These tables are available in machine-readable form.\\
\footnotetext{a}{The column time was converted to (${\rm BJD_{TDB}}$), following the procedure of \cite{Eastman2010}.}
}
\end{table}

\section{Light curve and RV analysis}

To obtain the refined orbital and physical parameters of WASP-18b, WASP-19b, and WASP-77Ab, as well as their transit mid-time ($T_{c}$), we used EXOFASTv2 \citep{Eastman2013,Eastman2017} to model the light curves together with archived RV data \cite{Hellier2009, Hebb2010, Maxted2013}.

EXOFASTv2 is an IDL code designed to simultaneously fit transits and radial velocity measurements obtained from different filters or different telescopes. It uses the Differential Evolution Markov chain Monte Carlo (DE-MCMC) method to derive the values and their uncertainties of the stellar, orbital and physical parameters of the system.

The stellar parameters of WASP-18, WASP-19, and WASP-77A were computed using the MESA Isochrones and Stellar Tracks (MIST) model \citep{Dotter2016} included in EXOFASTv2. We applied Gaussian priors in surface gravity $\log{g}$, effective temperature $T_{\rm eff}$, and metallicity [Fe/H] of the stars, from \cite{Hellier2009},\cite{Hebb2010} and \cite{Maxted2013} for WASP-18, WASP-19 and WASP-77A, respectively. 
We were not able to separate the contribution of the two companions of the binary system WASP-77, because the separation is 3.3 arcsec, but our photometry aperture is about 10 arcsec. Thus, we computed the dilution factor -- fraction of the light that comes from the companion star -- for each filter of our data set in order to get the real transit depth of WASP-77Ab. Because of the lack of good quality magnitude measurements for the fainter companion WASP-77B in the $B$, $I$, $R$ and $clear$ pass bands, we derived them from the \emph{Gaia} magnitude ($G=11.8356$) assuming Black Body radiation. The derived magnitudes for WASP-77B are $V=11.97$, $B=12.72$, $R=11.57$, $I=10.95$ and $\emph{clear}=11.78$.

We set previous published values as uniform priors for the DE-MCMC in all the transit, RV parameters, quadratic limb darkening coefficients and $T_{c}$. The priors were taken from the discovery papers of WASP-18b \citep{Hellier2009}, WASP-19b \citep{Hebb2010} and WASP-77Ab \citep{Maxted2013}.

In order to reduce significantly the convergence time of the chains during the EXOFASTv2 fitting, we started from shorter chains. Thus, the total time to complete that run is reduced. After it finished, we took the values from its best model and used them as priors for the next short run. This process was repeated until the chains were converged and well-mixed.

The best-fitted model is presented in Figure~\ref{transits} for our transit data from the TraMoS project, and in Figure~\ref{rv} for the RV archival data.

\begin{figure*}
\centering
\includegraphics[width=1.0\textwidth]{imagenes/light_curves2.pdf}
\caption{Light curves of WASP-18, WASP19 and WASP77 during 8, 9 and 9 different transits, respectively, from the TraMoS project. The fitted best model from EXOFASTv2 is shown as a light blue solid line for WASP-18b, orange for WASP-19b and pink for WASP-77Ab. To the right of each panel are the corresponding residuals of the model. For clarity, both light curves and their residual are offset artificially. The epoch number is indicated above each light curve. The technical information about each observation is listed in Table~\ref{log_table}.}
\label{transits}
\end{figure*}

\begin{figure*}
%\vspace{0.1cm}\hspace{0.2cm}
\includegraphics[width=1.0\textwidth]{imagenes/rv_all.pdf}
\caption{Radial velocity observations of WASP-18, WASP-19 and WASP-77A from \cite{Hellier2009}, \cite{Hebb2010} and \cite{Maxted2013}, respectively. The best fitted model from the joint modeling of RV and light curves with EXOFASTv2 is in solid line color: light blue for WASP-18b, orange for WASP-19b and pink for WASP-77Ab. The residuals of the model are shown at the bottom panel of each figure.}
\label{rv}
\end{figure*}

\begin{figure}
%\vspace{0.2cm}\hspace{0.2cm}
\centering
\includegraphics[width=0.7\columnwidth]{imagenes/phase.pdf}
\caption{Phased light curv of WASP-18b, WASP-19b and WASP-77Ab transits, from the TraMoS project. The three data set of light curves are fitted simultaneously with RV archival data using EXOFASTv2, in order to estimate the orbital and physical parameters of the system. In the top panel, the light blue solid line is the best fitting model for WASP-18b, and bellow are the residuals in color grey. The same for WASP-19b in color orange at the center panel, and for WASP-77Ab in color pink at the bottom panel.}
\label{phase}
\end{figure}

\section{Results and Discussion}

\subsection{Transit Parameters and Physical Properties}\label{transitparams}

\subsubsection{WASP-18b}

The resulting parameters from the global fit of WASP-18 in comparison the with results of the discovery paper \cite{Hellier2009} and the most recent analysis with TESS data \citep{Shporer2018}, are listed in Table~\ref{wasp18}. While in \cite{Hellier2009} the analysis was performed combining photometry and RV data, in \cite{Shporer2018} only photometric data was used.

%Stellar params
As the stellar spectroscopic priors were taken from the discovery paper \cite{Hellier2009}, our results for the stellar mass $M_*$ and radius $R_*$ are in good agreement with theirs, as expected, as well as the rest of the stellar parameters. \cite{Shporer2018} do not present results of stellar parameters.

%Primary transit params
In the case of the primary transit parameters, the greatest difference is found in the radius of the planet in stellar radii $R_{p}/R_{*}$. Our reported $R_{p}/R_{*}$ is $7.8\sigma$ and $4.4\sigma$ larger that the reported by \cite{Hellier2009} on the discovery paper and the recent result from \cite{Shporer2018}, respectively.  Our transit duration $T_{14}$ is also $3.4\sigma$ larger than the value from \cite{Hellier2009}.

% RV params
For the radial velocity parameters, the RV semi-amplitude derived from our analysis is consistent with the value of \cite{Hellier2009}, as the same data was used.

% Derived params
Finally, the derived parameters of the system are, in general, in good agreement with the values from \cite{Hellier2009} and \cite{Shporer2018}.

\begin{landscape}
\begin{longtable}{llccc}
\caption{System parameter of WASP-18}
\label{wasp18}
\centering
\tabularnewline
\hline 
Parameter & Units & This work & \cite{Hellier2009} & \cite{Shporer2018} \\
\hline
\smallskip\\\multicolumn{2}{l}{Stellar Parameters:}&\smallskip\\
~~~~$M_*$  &Mass (\(M_\odot\))  &$1.294^{+0.063}_{-0.061}$ & $1.25\pm0.13$ &  \\
~~~~$R_*$  &Radius (\(R_\odot\))  &$1.319^{+0.061}_{-0.062}$ &$1.26^{+0.067}_{-0.054}$ & \\
~~~~$L_*$  &Luminosity (\(L_\odot\))  &$2.68^{+0.28}_{-0.26}$ & &\\
~~~~$\rho_*$  &Density (cgs)  &$0.795^{+0.11}_{-0.089}$ & $ 0.707^{+0.056}_{-0.096}$&\\
~~~~$\log{g}$  & Surface gravity (cgs)  &$4.310^{+0.036}_{-0.033}$ &$4.367^{+0.028}_{-0.042}$ & \\
~~~~$T_{\rm eff}$  &Effective Temperature (K)  &$6432\pm48$ & $6400\pm100$& \\
~~~~$[{\rm Fe/H}]$  &Metallicity   &$0.107\pm0.080$ & $0.00\pm0.09$ & \\
~~~~$Age$  &Age (Gyr)  &$1.57^{+1.4}_{-0.94}$ & $0.5-1.5$ & \\
%~~~~$d$  &Distance (pc)  &$122.2^{+9.9}_{-8.2}$ & $100\pm10$ & \\

\smallskip\\\multicolumn{2}{l}{Planetary Parameters:}&\smallskip\\
~~~~$R_P$  &Radius (\rj)  &$1.310\pm0.071$ & $1.106^{+0.072}_{-0.054}$& $1.192\pm0.038$\\
~~~~$M_P$  &Mass (\mj)  &$10.48^{+0.42}_{-0.40}$ & $10.30\pm0.69$ & \\
~~~~$P$  &Period (days)  &$0.94145236\pm(49)$ & $0.94145299\pm(87)$& $0.9414576^{(+34)}_{(-35)}$ \\
~~~~$e$  &Eccentricity   &$0.0061^{+0.0089}_{-0.0044}$ & &\\
~~~~$a$  &Semi-major axis (AU)  &$0.02054^{+0.00033}_{-0.00032}$ & $0.02045\pm0.00067$&\\
~~~~$\omega_*$  &Argument of Periastron (Degrees)  &$-100^{+110}_{-120}$ &  &\\
~~~~$\rho_P$  &Density (cgs)  &$5.79^{+0.97}_{-0.78}$& $7.73^{+0.78}_{-1.27}$\footnotemark{b} & \\
~~~~$logg_P$  &Surface gravity   &$4.180^{+0.044}_{-0.041}$ & $4.289^{+0.027}_{-0.050}$ &\\
~~~~$T_{eq}$  &Equilibrium temperature (K)  &$2485^{+53}_{-56}$ & $2384^{+58}_{-30}$ & \\
~~~~$\Theta$  &Safronov Number   &$0.254^{+0.015}_{-0.014}$ & &\\
~~~~$\fave$  &Incident Flux (\fluxcgs)  &$8.66^{+0.77}_{-0.75}$ & & \\

\smallskip\\\multicolumn{2}{l}{Primary Transit Parameters:}&\smallskip\\
~~~~$T_0$  &Transit time (\bjdtdb)  &$2456740.80560\pm(19)$ & $2454221.48163\pm(38)$ & $2458361.048072^{(+34)}_{(-35)}$\\
~~~~$i$  &Inclination (Degrees)  &$83.5^{+2.0}_{-1.6}$ & $86.0\pm2.5$ & $84.31^{+0.40}_{-0.37}$\\
~~~~$R_P/R_*$  &Radius of planet in stellar radii   &$0.1021\pm0.0011$ &  $0.0935\pm0.0011$ & $0.09721^{+0.00016}_{-0.00017}$\\
~~~~$a/R_*$  &Semi-major axis in stellar radii   &$3.35^{+0.15}_{-0.13}$ & & $3.523^{+0.028}_{-0.027}$\\
~~~~$b$  &Impact parameter   &$0.433^{+0.07}_{-0.10}$ & $0.25\pm0.15$ & $0.349^{+0.020}_{-0.022}$\\
~~~~$\delta$  &Transit depth (fraction)  &$0.01041\pm0.00022$ & & $0.009449^{+0.000032}_{-0.000032}$\\
~~~~$u_{1,I}$  &linear LD coeff., I band  &$0.207\pm0.019$ & &\\
~~~~$u_{2,I}$  &quadratic LD coeff., I band  &$0.313\pm0.019$& &\\
~~~~$u_{1,R}$  &linear LD coeff., R band  & $0.257\pm0.045$ & &\\
~~~~$u_{2,R}$  &quadratic LD coeff., R band  &$0.309\pm0.048$ & &\\
~~~~$T_{14}$  &Total transit duration (days)  &$0.0931^{+0.0011}_{-0.0010}$ & $0.08932\pm0.00068$ &\\
~~~~$P_T$  &A priori non-grazing transit prob   &$0.268^{+0.011}_{-0.012}$ & &\\
~~~~$P_{T,G}$  &A priori transit prob   &$0.328^{+0.014}_{-0.015}$ & &\\
~~~~$\tau$  &Ingress/egress transit duration (days)  &$0.0107\pm0.0010$ & &\\

\smallskip\\\multicolumn{2}{l}{RV Parameters:}&\smallskip\\
~~~~$ecos{\omega_*}$  &   &$-0.0004^{+0.0038}_{-0.0045}$ & &\\
~~~~$esin{\omega_*}$  &   &$-0.0008^{+0.0056}_{-0.0092}$ & &\\
~~~~$K$  &RV semi-amplitude (m/s)  &$1807^{+34}_{-36}$ & $1818.3\pm8.0$ &\\
~~~~$M_P\sin i$  &Minimum mass (\mj)  &$10.40\pm0.40$ & &\\
\smallskip\\\multicolumn{2}{l}{Secondary Eclipse Parameters:}&\smallskip\\
~~~~$T_S$  &Time of eclipse (\bjdtdb)  &$2457657.3076^{+0.0023}_{-0.0027}$ & &\\
~~~~$b_S$  &Eclipse impact parameter   &$0.431^{+0.070}_{-0.100}$ & &\\
~~~~$\tau_S$  &Ingress/egress eclipse duration (days)  &$0.0106^{+0.0011}_{-0.0010}$ & &\\
~~~~$T_{S,14}$  &Total eclipse duration (days)  &$0.0929\pm0.0017$ & &\\
~~~~$P_S$  &A priori non-grazing eclipse prob   &$0.269^{+0.010}_{-0.011}$ & &\\
~~~~$P_{S,G}$  &A priori eclipse prob   &$0.330^{+0.013}_{-0.014}$ & &\\
\hline 
\end{longtable}
\end{landscape}
%\tablefoot{
%\tablefoottext{a}{Value converted to cgs units multiplying by the Sun density $\rho_{\odot}=1.408\,$cgs.}
%\tablefoottext{b}{Value converted to cgs units multiplying by the Jupiter density $\rho_{J}=1.33\,$cgs.}
%\tablefoottext{c}{Values enclosed in parentheses correspond to the uncertainties of the last digits of the nominal value.}}

\subsubsection{WASP-19b}
The results of the global fit of WASP-19 are listed in Table~\ref{tab:wasp19}, in comparison with the previous values from the discovery paper \citep{Hebb2010}, and a more recent work \citep{Lendl2013}.

To estimate the stellar parameters of WASP-19, we used as priors the stellar spectroscopic parameters from \cite{Hebb2010}. Thus, in general, our results are in agreement with the those from the discovery paper. The most important discrepancies are the density of the star $\rho_*$ and the surface gravity $\log{g}$, showing $+2.5\sigma$ and $-3.2\sigma$ difference, respectively. Comparing with the results from \cite{Lendl2013}, ours are all in good agreement.

For values of the primary transit parameters obtained from the light curves, the greatest differences are found in the orbital inclination $i$ and the total transit duration $T_{14}$. We report an inclination value $5.1\sigma$ smaller than \cite{Hebb2010}, but in agreement with the estimate of \cite{Lendl2013}. In the other hand, our estimation of $T_{14}$ is significantly larger than \cite{Hebb2010} by $9\sigma$, but the difference is only $3.5\sigma$ when compared with \cite{Lendl2013}. We also report a preciser impact parameter $b$ and transit depth $\delta$.

As the same RV data set from the discovery paper \citep{Hebb2010} was used to perform our analysis, the almost identical values in the RV semi-amplitude $K$ is not a surprise. Moreover, the values from \cite{Lendl2013} are also in agreement.

The planetary parameters derived from the light curve and radial velocity analysis are almost all in good agreement with the comparison works. The only parameter with a difference greater than $3\sigma$ is our estimation of the Equilibrium Temperature $T_{eq}$ compared with the result of \cite{Hebb2010}. However, our result is in better agreement with \cite{Lendl2013} by less than $2\sigma$.

\begin{landscape}
\begin{longtable}{llccc}
\caption{System parameter of WASP-19}
\label{tab:wasp19}
\centering
\tabularnewline
\hline 
~~~Parameter & Units & This work & \cite{Hebb2010}\footnote{a} & \cite{Lendl2013}\\
\hline
\smallskip\\\multicolumn{2}{l}{Stellar Parameters:}&\smallskip\\
~~~~$M_*$\dotfill &Mass (\(M_\odot\))\dotfill &$0.965^{+0.091}_{-0.095}$ & $0.95\pm0.10$ & $0.968^{+0.084}_{-0.079}$ \\
~~~~$R_*$\dotfill &Radius (\(R_\odot\))\dotfill &$1.006^{+0.031}_{-0.034}$ & $0.93^{+0.05}_{-0.04}$& $0.994\pm0.031$\\
~~~~$L_*$\dotfill &Luminosity (\(L_\odot\))\dotfill &$0.905^{+0.071}_{-0.069}$\\
~~~~$\rho_*$\dotfill &Density (cgs)\dotfill &$1.339^{+0.056}_{-0.058}$ & $1.19^{+0.12}_{-0.11}$\footnote{b}  & $1.384^{+0.055}_{-0.051}$\footnote{b}\\
~~~~$\log{g}$\dotfill &Surface gravity (cgs)\dotfill &$4.417^{+0.020}_{-0.021}$ & $4.48\pm0.03$\\
~~~~$T_{\rm eff}$\dotfill &Effective Temperature (K)\dotfill &$5616^{+66}_{-65}$ & $5500\pm100$\\
~~~~$[{\rm Fe/H}]$\dotfill &Metallicity \dotfill &$0.04^{+0.25}_{-0.30}$ & $0.02\pm0.09$\\
~~~~$Age$\dotfill &Age (Gyr)\dotfill &$6.4^{+4.1}_{-3.5}$ & $5.5^{+9.0}_{-4.5}$\\
%~~~~$d$\dotfill &Distance (pc)\dotfill &$270.2\pm1.7$\\

\smallskip\\\multicolumn{2}{l}{Planetary Parameters:}&\smallskip\\
~~~~$R_P$\dotfill &Radius (\rj)\dotfill &$1.415^{+0.044}_{-0.048}$ & $1.28\pm0.07$ & $1.376\pm0.046$\\
~~~~$M_P$\dotfill &Mass (\mj)\dotfill &$1.154^{+0.078}_{-0.080}$ & $1.14\pm0.07$ & $1.165\pm0.068$\\
~~~~$P$\dotfill &Period (days)\dotfill &$0.78883852^{+(75)}_{-(82)}$ & $0.7888399\pm(8)$  & $0.7888390\pm(2)$\\
~~~~$e$\dotfill &Eccentricity \dotfill &$0.0126^{+0.014}_{-0.0089}$ & & $0.0077^{+0.0068}_{-0.0032}$\\
~~~~$a$\dotfill &Semi-major axis (AU)\dotfill &$0.01652^{+0.00050}_{-0.00056}$ & $0.0164^{+0.0005}_{-0.0006}$ & $0.01653\pm0.00046$\\
~~~~$\omega_*$\dotfill &Argument of Periastron (Degrees)\dotfill &$51^{+89}_{-190}$ & $-76^{+112}_{-23}$ & $43^{+28}_{-67}$\\
~~~~$\rho_P$\dotfill &Density (cgs)\dotfill &$0.506^{+0.031}_{-0.030}$ & $0.54^{+0.07}_{-0.06}$& $0.595^{+0.036}_{-0.033}$\footnote{c}\\
~~~~$logg_P$\dotfill &Surface gravity \dotfill &$3.155^{+0.018}_{-0.019}$ & $3.20\pm0.03$ & $3.184\pm0.015$\\
~~~~$T_{eq}$\dotfill &Equilibrium temperature (K)\dotfill &$2113\pm29$ & $1993^{+32}_{-33}$ & $2058\pm40$\\
~~~~$\Theta$\dotfill &Safronov Number \dotfill &$0.0279^{+0.0012}_{-0.0011}$\\
~~~~$\fave$\dotfill &Incident Flux (\fluxcgs)\dotfill &$4.52^{+0.26}_{-0.24}$\\

\smallskip\\\multicolumn{2}{l}{Primary Transit Parameters:}&\smallskip\\
~~~~$T_0$\dotfill & Transit Time (\bjdtdb)\dotfill &$2456402.7128^{+(17)}_{-(14)}$ & $2454775.3372\pm(2)$ & $2456029.59204\pm(13)$\\
~~~~$i$\dotfill &Inclination (Degrees)\dotfill &$79.08^{+0.34}_{-0.37}$ & $80.8\pm0.8$  & $79.54\pm0.33$\\
~~~~$R_P/R_*$\dotfill &Radius of planet in stellar radii \dotfill &$0.14410^{+0.00049}_{-0.00050}$ & $0.1425\pm0.0014$\\
~~~~$a/R_*$\dotfill &Semi-major axis in stellar radii \dotfill &$3.533^{+0.048}_{-0.052}$ &  & $3.573\pm0.046$\\
~~~~$b$\dotfill &Impact parameter \dotfill &$0.6671^{+0.0087}_{-0.0091}$ & $0.62\pm0.03$ & $0.645\pm0.012$\\
~~~~$\delta$\dotfill &Transit depth (fraction)\dotfill &$0.02077\pm0.00014$ & $0.0203\pm0.0004$ & $0.02018\pm0.00021$\\
~~~~$u_{1,I}$\dotfill &linear LD coeff., I band\dotfill &$0.287^{+0.027}_{-0.029}$&\\
~~~~$u_{2,I}$\dotfill &quadratic LD coeff., I band\dotfill &$0.263\pm0.024$&\\
~~~~$u_{1,R}$\dotfill &linear LD coeff., R band \dotfill &$0.383^{+0.029}_{-0.032}$\\
~~~~$u_{2,R}$\dotfill &quadratic LD coeff., R band\dotfill &$0.246^{+0.027}_{-0.025}$\\
~~~~$T_{14}$\dotfill &Total transit duration (days)\dotfill &$0.06697^{+0.00031}_{-0.00030}$ & $0.0643^{+0.0006}_{-0.0007}$ & $0.06586^{+0.00033}_{-0.00031}$\\
~~~~$P_T$\dotfill &A priori non-grazing transit prob \dotfill &$0.2426^{+0.0066}_{-0.0051}$\\
~~~~$P_{T,G}$\dotfill &A priori transit prob \dotfill &$0.3246^{+0.0089}_{-0.0069}$\\
~~~~$\tau$\dotfill &Ingress/egress transit duration (days)\dotfill &$0.01459\pm0.00035$\\

\smallskip\\\multicolumn{2}{l}{RV Parameters:}&\smallskip\\
~~~~$e\cos{\omega_*}$\dotfill & \dotfill &$-0.0027^{+0.0077}_{-0.013}$ & $0.004\pm0.009$ &$0.0024\pm0.0020$ \\
~~~~$e\sin{\omega_*}$\dotfill & \dotfill &$0.0016^{+0.014}_{-0.0092}$ & $-0.02\pm0.02$ & $0.000\pm0.005$\\
~~~~$K$\dotfill &RV semi-amplitude (m/s)\dotfill &$255.4^{+6.1}_{-6.2}$ & $256\pm5$  & $257.7\pm2.9$\\
~~~~$M_P\sin i$\dotfill &Minimum mass (\mj)\dotfill &$1.133^{+0.078}_{-0.079}$\\

\smallskip\\\multicolumn{2}{l}{Secondary Eclipse Parameters:}&\smallskip\\
~~~~$T_S$\dotfill &Time of eclipse (\bjdtdb)\dotfill &$2455169.3621^{+(41)}_{-(51)}$ & $2456030.77766\pm(88)$\\
~~~~$b_S$\dotfill &Eclipse impact parameter \dotfill &$0.670^{+0.020}_{-0.017}$ & $0.652\pm0.015$\\
~~~~$\tau_S$\dotfill &Ingress/egress eclipse duration (days)\dotfill &$0.01472^{+0.00085}_{-0.00066}$\\
~~~~$T_{S,14}$\dotfill &Total eclipse duration (days)\dotfill &$0.06812^{+0.00087}_{-0.00074}$\\
~~~~$P_S$\dotfill &A priori non-grazing eclipse prob \dotfill &$0.2415\pm0.0021$\\
~~~~$P_{S,G}$\dotfill &A priori eclipse prob \dotfill &$0.3232\pm0.0030$\\
\hline
%\end{tabular}
%\tablefoot{
%\tablefoottext{a}{For comparison, the results from \cite{Hellier2009} that considered free eccentricity were used.}
%%\tablefoottext{b}{Values converted to cgs units multiplying by the Sun density $\rho_{\odot}=1.408\,$cgs.}
%\tablefoottext{c}{Values converted to cgs units multiplying by the Jupiter density $\rho_{J}=1.33\,$cgs}
%\tablefoottext{d}{Values enclosed in parentheses correspond to the uncertainties of the last digits of the nominal value.}}
\end{longtable}
\end{landscape}

\subsubsection{WASP-77Ab}
Table~\ref{tab:wasp77} lists the results of the global fit of WASP-77Ab, in comparison with the values from its discovery paper \citep{Maxted2013} on which photometry and RV data were used. No other previous work has reported bulk measurements for this system.

Almost all the stellar parameters are in agreement with \citep{Maxted2013}, except for a $-9.7\sigma$ difference in the stellar surface gravity $\log{g}$, where our reported value is preciser.

The primary transit parameters, as well as the RV parameters and the derived planetary parameters, are consistent with the results from \cite{Maxted2013}.

\begin{landscape}
\begin{longtable}{llcc}
\caption{System parameter of WASP-77A}
\label{tab:wasp77}
\centering
\tabularnewline
\hline 
~~~~~Parameter & Units & This work & \cite{Maxted2013}\\
\hline
\smallskip\\\multicolumn{2}{l}{Stellar Parameters:}&\smallskip\\
~~~~$M_*$\dotfill &Mass (\(M_\odot\))\dotfill &$0.903^{+0.066}_{-0.059}$ & $1.002\pm0.045$\\
~~~~$R_*$\dotfill &Radius (\(R_\odot\))\dotfill &$0.910^{+0.025}_{-0.023}$ & $0.955\pm0.015$\\
~~~~$L_*$\dotfill &Luminosity (\(L_\odot\))\dotfill &$0.743^{+0.065}_{-0.058}$ & \\
~~~~$\rho_*$\dotfill &Density (cgs)\dotfill &$1.692^{+0.056}_{-0.069}$\footnote{a} & $1.629^{+0.023}_{-0.028}$\footnote{a}\\
~~~~$\log{g}$\dotfill &Surface gravity (cgs)\dotfill &$4.476^{+0.014}_{-0.015}$ & $4.33\pm0.08$\\
~~~~$T_{\rm eff}$\dotfill &Effective Temperature (K)\dotfill &$5617\pm72$ & $5500\pm80$\\
~~~~$[{\rm Fe/H}]$\dotfill &Metallicity \dotfill &$-0.10^{+0.10}_{-0.11}$ & $0.00\pm0.11$\\
~~~~$Age$\dotfill &Age (Gyr)\dotfill &$6.2^{+4.0}_{-3.5}$ & $0.5-1.0$\\

\smallskip\\\multicolumn{2}{l}{Planetary Parameters:}&\smallskip\\
~~~~$R_P$\dotfill &Radius (\rj)\dotfill &$1.183^{+0.034}_{-0.031}$ & $1.21\pm0.02$\\
~~~~$M_P$\dotfill &Mass (\mj)\dotfill &$1.650^{+0.082}_{-0.075}$ & $1.76\pm0.06$\\
~~~~$P$\dotfill &Period (days)\dotfill &$1.3600290^{+(18)}_{-(20)}$ & $1.3600309\pm(20)$\\
~~~~$e$\dotfill &Eccentricity \dotfill&$0.0074^{+0.0075}_{-0.0051}$\\
~~~~$a$\dotfill &Semi-major axis (AU)\dotfill &$0.02323^{+0.00056}_{-0.00052}$ & $0.0240\pm0.00036$\\
~~~~$\omega_*$\dotfill &Argument of Periastron (Degrees)\dotfill &$-30^{+170}_{-120}$\\
~~~~$\rho_P$\dotfill &Density (cgs)\dotfill &$1.240^{+0.060}_{-0.067}$ & $1.33\pm0.04$\footnote{b}\\
~~~~$logg_P$\dotfill &Surface gravity \dotfill &$3.467^{+0.012}_{-0.015}$ & $3.441\pm0.008$\\
~~~~$T_{eq}$\dotfill &Equilibrium temperature (K)\dotfill &$1695^{+25}_{-24}$\\
~~~~$\Theta$\dotfill &Safronov Number \dotfill &$0.0717\pm0.0021$\\
~~~~$\fave$\dotfill &Incident Flux (\fluxcgs)\dotfill &$1.87^{+0.11}_{-0.10}$\\

\smallskip\\\multicolumn{2}{l}{Primary Transit Parameters:}&\smallskip\\
~~~~$T_0$\dotfill &Transit Time (\bjdtdb)\dotfill &$2457420.88439^{(+80)}_{(-85)}$ & $2455870.44977\pm(20)$\\
~~~~$i$\dotfill &Inclination (Degrees)\dotfill &$88.91^{+0.74}_{-0.95}$ & $89.4^{+0.4}_{-0.7}$\\
~~~~$R_P/R_*$\dotfill &Radius of planet in stellar radii \dotfill &$0.13352^{+0.00074}_{-0.00070}$\\
~~~~$a/R_*$\dotfill &Semi-major axis in stellar radii \dotfill &$5.493^{+0.060}_{-0.075}$\\
~~~~$b$\dotfill &Impact parameter \dotfill &$0.105^{+0.089}_{-0.071}$ & $0.06^{+0.07}_{-0.05}$\\
~~~~$\delta$\dotfill &Transit depth (fraction)\dotfill &$0.01783^{+0.00020}_{-0.00019}$\\
~~~~$u_{1,B}$\dotfill &linear LD coeff., B band \dotfill &$0.680\pm0.054$&\\
~~~~$u_{2,B}$\dotfill &quadratic LD coeff., B band\dotfill &$0.140^{+0.052}_{-0.053}$&\\
~~~~$u_{1,clear}$\dotfill &linear LD coeff., \emph{clear} band \dotfill &$0.386\pm0.029$\\
~~~~$u_{2,clear}$\dotfill &quadratic LD coeff., \emph{clear} band \dotfill &$0.227\pm0.029$&\\
~~~~$u_{1,I}$\dotfill &linear LD coeff., I band \dotfill &$0.311\pm0.025$&\\
~~~~$u_{2,I}$\dotfill &quadratic LD coeff., I band \dotfill &$0.294\pm0.033$&\\
~~~~$u_{1,R}$\dotfill &linear LD coeff., R band \dotfill &$0.312\pm0.023$\\
~~~~$u_{2,R}$\dotfill &quadratic LD coeff., R band \dotfill &$0.237^{+0.029}_{-0.028}$\\
~~~~$T_{14}$\dotfill &Total transit duration (days)\dotfill &$0.08952^{+0.00053}_{-0.00051}$\\
~~~~$P_T$\dotfill &A priori non-grazing transit prob \dotfill &$0.1578^{+0.0029}_{-0.0025}$\\
~~~~$P_{T,G}$\dotfill &A priori transit prob \dotfill &$0.2064^{+0.0039}_{-0.0033}$\\
~~~~$\tau$\dotfill &Ingress/egress transit duration (days)\dotfill &$0.01075^{+0.00032}_{-0.00015}$\\

\smallskip\\\multicolumn{2}{l}{RV Parameters:}&\smallskip\\
~~~~$e\cos{\omega_*}$\dotfill & \dotfill &$-0.0033^{+0.0041}_{-0.0065}$\\
~~~~$e\sin{\omega_*}$\dotfill & \dotfill &$-0.0002^{+0.0061}_{-0.0073}$\\
~~~~$K$\dotfill &RV semi-amplitude (m/s)\dotfill &$323.4^{+3.7}_{-3.3}$ & $321.9\pm3.9$\\
~~~~$M_P\sin i$\dotfill &Minimum mass (\mj)\dotfill &$1.649^{+0.082}_{-0.075}$\\

\smallskip\\\multicolumn{2}{l}{Secondary Eclipse Parameters:}&\smallskip\\
~~~~$T_S$\dotfill &Time of eclipse (\bjdtdb)\dotfill &$2457659.5665^{+0.0038}_{-0.0056}$\\
~~~~$b_S$\dotfill &Eclipse impact parameter \dotfill &$0.104^{+0.089}_{-0.071}$\\
~~~~$\tau_S$\dotfill &Ingress/egress eclipse duration (days)\dotfill &$0.01076^{+0.00035}_{-0.00023}$\\
~~~~$T_{S,14}$\dotfill &Total eclipse duration (days)\dotfill &$0.0895^{+0.0013}_{-0.0014}$\\
~~~~$P_S$\dotfill &A priori non-grazing eclipse prob \dotfill &$0.1578^{+0.0018}_{-0.0012}$\\
~~~~$P_{S,G}$\dotfill &A priori eclipse prob \dotfill &$0.2063^{+0.0025}_{-0.0016}$\\
\hline
%\end{tabular}
%\tablefoot{
%\tablefoottext{a}{Value converted to cgs units multiplying by the Sun density $\rho_{\odot}=1.408\,$cgs.}
%\tablefoottext{b}{Value converted to cgs units multiplying by the Jupiter density $\rho_{J}=1.33\,$cgs.}
%\tablefoottext{c}{Values enclosed in parentheses correspond to the uncertainties of the last digits of the nominal value.}
%}
\end{longtable}
\end{landscape}

\subsection{Transit Timing Variations}\label{ttvsection}

 A transit timing variation is represented trough a difference in time from the transit mid-time $T_c$, for a planet in Keplerian motion following a linear ephemeris of the orbital period. The TTVs were computed considering our transit times from the TraMoS project, as well as including previous published ones. A refined orbital period was linearly fitted, considering 19, 59 and 11 transit times of WASP-18b, WASP-19b, and WASP-77Ab, respectively. Along the linear fit, we also tested a second degree polynomial fit to analyze a possible orbital decay. Both fit considered the errors of the data. In Figure~\ref{ttv} are presented all the TTV values for the transit times of WASP-18b, WASP-19b and WASP-77Ab.

If the planet stays in a Keplerian orbit, its transit time $T_{c}$ of each epoch $E$ should follow a linear function of the orbital period $P$.

\begin{equation} \label{eq1}
T_{\rm C}(E)=T_{\rm C}(0)+E \cdot P
\end{equation}

Where $T_{c}(0)$ is the optimal transit time in an arbitrary zero epoch. The best-fitted values of $T_{c}(0)$ for WASP-18b, WASP-19b and WASP-77Ab, are listed in Tables~\ref{wasp18},~\ref{tab:wasp19} and \ref{tab:wasp77}, respectively.

\subsubsection{WASP-18b}
For this system, the proposed linear ephemeris equation is:

\begin{equation} \label{eq1_w18}
T_{\rm C}(E)=2456926.27460\pm(94)+E \cdot 0.941452232\pm(89)
\end{equation}

The orbital period $P$ in Eq.~\ref{eq1_w18} is in complete agreement with the value computed only with the TraMoS light curves in Table~\ref{wasp18}.

Table~\ref{times_wasp18} lists the TTV of our transit times and also, of data from previous works \citep{Triaud2010,Hellier2009,Maxted2013b} of WASP-18b.

The top panel of Figure~\ref{ttv} is the linear plot of TTV versus epoch for this planet. The deviations of the transit times from the linear ephemeris has an RMS of 83 seconds. The greater deviations come from the transit time of the epochs $-1904$ and $-1184$, which are over the linear ephemeris by $2.5\sigma$ and $1.9\sigma$, respectively. If those values are removed, the RMS decreases to 61 seconds. Considering all the transit times in Table~\ref{times_wasp18} without the epochs $-1904$ and $-1184$, all the TTVs lie within $1.6\sigma$ in the linear fit.

The epoch $-1184$ has the greatest error in our sample because it is not a complete transit.

When testing the goodness of the linear fit, $\chi^{2}_{red} =0.56$, while for a second degree polynomial is $\chi^{2}_{red}=0.48$, therefore an orbital decay can be discarded in agreement with theoretical estimations \citep{CollierCameron2018}.

\begin{table}[H]
%\tablewidth{0pt}
\centering
\caption{Transit mid-times for WASP-18b}
\label{times_wasp18}
\begin{tabular}{cccc}
\hline \hline
Epoch & Transit mid-time & TTV & References\\
      & (${\rm BJD_{TDB}}$) & (min) & \\
\hline 
-2873 & $2454221.48238$ & $0.1\pm1.5$ & 1\\
-2402 & $2454664.9061$ & $-0.4\pm1.4$ & 2 \\
-1904 & $2455133.7472$ & $-3.4\pm1.7$ & This work \\
-1903 & $2455134.6914$ & $0.6\pm1.7$ & This work \\
-1902 & $2455135.6331$  & $0.9\pm1.7$  & This work \\
-1811 & $2455221.3042$ & $-0.6\pm1.4$  & 3\\
-1629 & $2455392.6474$ & $-2.2\pm1.5$& 3 \\
-1601 & $2455419.0083$ & $-1.8\pm2.2$& 3\\
-1587 & $2455432.1897$ & $-0.3\pm1.4$ & 3\\
-1546 & $2455470.7885$ & $-1.4\pm1.4$ & 3\\
-1543 & $2455473.6144$ & $0.9\pm1.9$& 3\\
-1457 & $2455554.5786$ & $-0.2\pm1.5$&3 \\
-1440 & $2455570.5842$ & $1.2\pm1.6$& 3\\
-1184 & $2455811.5970$ &  $2.7\pm5.9$ & This work  \\
-1115 & $2455876.5559$ & $0.8\pm2.3$ & 3 \\ 
776 & $2457656.84078$ & $-1.1\pm1.4$ & This work  \\
777 & $2457657.78359$   & $0.9\pm1.4$ & This work\\
778 & $2457658.72404$ & $-0.6\pm1.4$ & This work \\
1169 & $2458026.83186$ & $-0.6\pm1.5$ & This work  \\
\hline
\end{tabular}
%\tablebib{(1)~\citet{Hellier2009};
%(2) \citet{Triaud2010}; (3) \citet{Maxted2013}.}
\end{table}

\subsubsection{WASP-19b}
%The best values of the parameters in Equation \ref{eq1} for WASP-19b are $T_{c}=2456402.7128^{+(17)}_{-(14)}\,[\rm{BJD_{TDB}}]$ and $P=0.78883852^{+(75)}_{-(82)}\,{\rm days}$.

The proposed equation for linear ephemeris, considering 59 transit times of WASP-19b is:
\begin{equation} \label{eq1_w19}
T_{\rm C}(E)=2456402.7128\pm(16)+E \cdot 0.788838858\pm(47)
\end{equation}

The TTV values from the proposed linear ephemeris are listed in Table \ref{times_wasp19}, including transit times from the previous works \citep{Hebb2010,Anderson2010,Lendl2013,Tregloan2013,Bean2013,Mancini2013}.

At the middle panel of Figure~\ref{ttv} are the TTV values versus epoch, for all the transit time considered in this work.

The RMS from the linear ephemeris is about 75 seconds. The epoch of $-1011$ is the only one with a transit time deviation above $1.5\,\sigma$ from the linear ephemeris. If it is removed, then the RMS decreases to 69 seconds. Moreover, in our data the epoch $-611$ has one of the greatest errors due to bad weather conditions.

Considering all the transit times from Table~\ref{times_wasp19}, the linear fit has $\chi^{2}_{red} = 0.16$. This an indication of an overestimation of the errors. A second degree polynomial was also tested in order to reject or not a possible orbital decay. The goodness of that fit is $\chi^{2}_{red}=0.12$.

\begin{longtable}{cccc}
\caption{Transit mid-times for WASP-19b}
\label{times_wasp19}
\tabularnewline
\hline \hline
Epoch & Transit mid-time & TTV & References\\
      & (${\rm BJD_{TDB}}$) & (min) &  \\
\hline
-2063 & $2454775.3372$ & $-1.6\pm3.2$ & 1\\
-2061 & $2454776.91566$ & $-0.5\pm2.3$ & 2 \\
-2010 & $2454817.14633$ & $-0.6\pm2.3$ & 3 \\
-1525 & $2455199.73343$ & $-0.2\pm2.6$& 4\\
-1459 & $2455251.79657$ & $-0.6\pm2.3$& 5 \\
-1458 & $2455252.58544$ & $-0.5\pm2.3$& 5 \\
-1454 & $2455255.74077$ & $-0.6\pm2.3$& 5 \\
-1449 & $2455259.68448$ & $-1.3\pm2.4$& 4 \\ 
-1431 & $2455273.88282$ & $-2.4\pm2.5$& 4 \\
-1399 & $2455299.12768$ & $0.6\pm2.4$& 4 \\
-1354 & $2455334.6254$ & $0.5\pm2.3$ & 6\\
-1349 & $2455338.56927$ & $0.1\pm2.3$& 3 \\ 
-1330 & $2455353.55659$ & $-0.8\pm2.3$& 6\\
-1317 & $2455363.81131$ & $-1.1\pm2.4$& 4  \\
-1311 & $2455368.54285$ & $-3.3\pm3.8$& 6 \\ 
-1094 & $2455539.72327$ & $0.2\pm2.4$ & 3 \\
-1056 & $2455569.69826$ & $-1.1\pm2.4$ & 3\\
-1039 & $2455583.10979$ & $0.8\pm2.6$ & 4 \\
-1037 & $2455584.68693$ & $0.0\pm2.3$ & 3 \\
-1025 & $2455594.15188$ &  $-1.6\pm3.3$ & 6 \\
-1016 & $2455601.25164$ & $-1.3\pm2.5$ & 6\\
-1014 & $2455602.83138$ & $1.7\pm2.4$ & 3 \\
-1011 & $2455605.19414$ & $-3.8\pm3.5$ & 6 \\
-1009 & $2455606.77464$ & $0.3\pm2.3$ & 3 \\
-1008 & $2455607.56241$ & $-1.2\pm2.4$ & 3 \\
-989 & $2455622.55057$ & $-0.9\pm2.3$ & 3 \\
-987 & $2455624.12787$ & $-1.5\pm3.1$ & 6 \\
-976 & $2455632.80612$ & $0.0\pm2.3$ & 3 \\
-947 & $2455655.68222$ & $-0.3\pm2.4$ & 3 \\
-928 & $2455670.66976$ & $-0.9\pm2.5$ & 3 \\
-923 & $2455674.61367$ & $-1.3\pm2.4$ & This work \\
-919 & $2455677.77038$ & $0.7\pm3.6$ & 6  \\
-905 & $2455688.81201$ & $-2.4\pm5.3$ & 6 \\
-904 & $2455689.60276$ & $0.4\pm2.4$ & 6 \\
-900 & $2455692.75674$ & $-1.6\pm4.3$ & 6 \\
-899 & $2455693.54639$ & $-0.5\pm2.3$ & 6  \\
-886 & $2455703.79933$ & $-3.3\pm6.4$ & 6 \\
-885 & $2455704.59078$ & $0.5\pm2.4$ & 6 \\
-880 & $2455708.534626$ & $0.0\pm 2.3$ & 6  \\
-654 & $2455886.81234$ &  $0.2\pm3.8$ & 6 \\
-642 & $2455896.27611$ & $-3.1\pm3.8$ & 6 \\
-618 & $2455915.20980$ & $-0.9\pm2.5$ & 6  \\
-613 & $2455919.15485$ & $0.4\pm 2.7$ & 6\\
-611 & $2455920.7353$ & $0.0\pm5.4$ & This work \\
-609 & $2455922.30966$ & $-0.4\pm8.3$ & 6 \\
-511 & $2455999.6163$ & $0.2\pm2.3$ & 7 \\
-483 & $2456021.70374$ & $0.1\pm2.3$ & 7 \\
-473 & $2456029.5925$ & $0.7\pm 2.4$ &3 \\
-468 & $2456033.53643$ &  $0.3\pm 2.3$ & 6  \\
-430 & $2456063.51174$ & $-0.5\pm 2.3$ & 3 \\
-86 & $2456334.87208$ & $-0.8\pm2.4$ & 4 \\
-47 & $2456365.6373$  & $-0.1\pm2.3$& This work \\
1 & $2456403.50158$ &  $-0.1\pm2.3$ & This work \\
729 & $2456977.77722$  & $1.3\pm2.3$ & 8 \\
867 & $2457086.63571$ & $-0.5\pm2.3$& This work \\
1383 & $2457493.67676$   & $-0.2\pm2.3$& This work  \\
1771 & $2457799.74612$ &  $-0.3\pm2.3$ & This work \\
1838 & $2457852.597807$ & $-0.7\pm2.3$ & This work\\ 
2064 & $2458030.8751$  & $-1.5\pm3.2$& This work \\
\hline
%\end{tabular}
%\tablebib{(1)~\citet{Hebb2010};
%(2) \citet{Anderson2010}; (3) \citet{Lendl2013}; (4) Exoplanet Transit Database (ETD) \url{var2.astro.cz/ETD}; (5) \citet{Tregloan2013}; (6) \citet{Mancini2013}; (7) \citet{Bean2013}; (8) \citet{Sedaghati2015}.}
\end{longtable}

\subsubsection{WASP-77Ab}

As in the previous targets, we computed a refined linear ephemeris equation for WASP-77A considering 11 transit times:
\begin{equation} \label{eq1_w77}
T_{\rm C}(E)=2457420.88439\pm(85)+E \cdot 1.36002854\pm(52)
\end{equation}

In Table~\ref{tab:wasp77} are listed the TTV values of our transit times and from previous works \citep{Turner2016,Maxted2013} of WASP-77Ab and, at the bottom of Figure~\ref{ttv} are plotted versus epoch. The scatter of all the transit times is about $RMS=121$ seconds.

The epochs $175$ and $229$ are above $2\,\sigma$ from the expected transit time following the linear ephemeris, while all the others epochs lie within $1.5\,\sigma$ from it. When removing the epochs $175$ and $229$, the RMS decreases to 88 seconds.

Considering all the transit times, the linear fit has $\chi^{2}_{red}=1.4$, and the second degree polynomial has $\chi^{2}_{red}=1.39$ . However, we chose the linear fit as it suppose a simpler model.

\begin{table}
\caption{Transit mid-times for WASP-77Ab}
\label{times_wasp77}
\centering
\begin{tabular}{cccc}
\hline \hline
Epoch & Transit mid-time & TTV & References\\
      & (${\rm BJD_{TDB}}$) & (min) &  \\
\hline
-1140 & $2455870.45054$ & $-2.0\pm1.5$ & 1 \\
-845 & $2456271.65888$ & $-2.0\pm1.4$ & 2 \\
-659 & $2456524.62617$ & $0.8\pm1.8$ & This work\footnote{a} \\
-606 & $2456596.70591$ & $-1.7\pm1.5$  & This work\footnote{a}  \\
-92 & $2457295.7626$  & $1.2\pm1.3$& This work \\
-89 & $2457299.84119$ &  $-1.0\pm1.3$ & This work \\
175 & $2457658.88744$ & $-2.8\pm1.5$ & This work\\
177 & $2457661.60987$   & $0.6\pm1.7$ & This work\footnote{a} \\
183 & $2457669.77054$ &  $1.4\pm1.4$  & This work  \\
229 & $2457732.33382$ & $4.2\pm1.4$& This work\footnote{a} \\
447 & $2458028.8159$  & $-1.8\pm6.5$ & This work\\ 
\hline
\end{tabular}
%\tablebib{(1) \citet{Maxted2013}; (2) \cite{Turner2016}.}
%\tablefoot{
%\tablefoottext{a}{From the Exoplanet Transit Database (ETD)  \url{var2.astro.cz/ETD}}}
\end{table}

### 2019-07-31 tramos.tex
Full paper in thesis, removed separated chapters

@@
 \chapter{The Transit Monitoring in the South project}\label{chap:tramos}
-
-High-precision long-term transit follow-ups provide tremendous opportunities in improving our understanding of exoplanets, leading to obtain more accurate measurements of planetary radius, especially those detected with ground-based transit surveys (e.g., HATNet and HATSouth, \citealt{Bakos2012}; SuperWASP, \citealt{Pollacco2006}; KELT, \citealt{Pepper2007}; TRES, \citealt{Alonso2007}, CSTAR, \citealt{WangS2014}).
-With improved photometry, we can refine planetary orbital ephemeris \citep{TEMP1}, which is vital to schedule future transit-related observations, such as Rossiter-Mclaughlin effect measurement \citep{Nutzman2011,Sanchis2011,Sanchis2013,WangS2018} and transmission spectrum follow-up \citep{Mancini2016b,Mackebrandt2017}.
-
-%Long-term photometric follow-up also provides a unique chance to study the variations of the orbital periods.
-A recent study shows the apparent orbital decay in the WASP-12 system \citep{Patra2017}, which intrigues a series of theoretical studies \citep{Millholland2018,Weinberg2017} to discuss the potential mechanisms.
-The transit follow-up also plays an important role in exoplanet system which shows interesting Transit Timing Variations (TTV) \citep{Ballard2011,Ford2012a,Steffen2012,Fabrycky2012,Mancini2016,WangS2017,Wu2018}.
-
-%\cite{Ballard2018} predicted that around 5\% of planets discovered by TESS \citep{Ricker2014} will show TTVs.
-Transit follow-up of these targets is very critical, because most of them will only be monitored for $\sim27$ days, whereas the typical TTV period is around years.
-
-%Furthermore, extended TTV studies are crucial to confirm or rule out exoplanetary systems, in cases where space-based observations will not cover the long-time scales required to characterize them \citep{vonEssen2018}.
-Thus, combining ground and space-based observations will be crucial.
-
-%The TTV method \citep{Miralda2002,Agol2005,Holman2005}  also provides a powerful tool to detect additional low-mass planets in hot Jupiter systems, which is usually hard to find by using other techniques \citep{Steffen2012b}.
-Many efforts have been devoted to this field \citep{Pal2011,Hoyer2012,Hoyer2013,Szabo2013}, but so far only two hot Jupiters have been found to accompanies with additional close-in planets (WASP-47: \cite{Becker2015}, and Kepler-730: \cite{Canas2019}).
-The accurate occurrence rate of the `WASP-47-like' system is still unknown.
-
-%To refine orbital parameters of currently known exoplanets, and to search for additional planets by using TTV method, we organized the Transit Monitoring in the South hemisphere (TraMoS) project \citep{Hoyer2011} since 2008.
-We uses one-meter class telescopes in the north of Chile to conduct high-precision long-term transit follow-up.
-
-%Following the previous efforts from the TraMoS project, in this work, we present new light curves of three hot Jupiters: WASP-18b, WASP-19b, WASP-77Ab.
-Combining our new light curves, and archival photometric and radial velocity data sets, we refined the orbital and physical parameters of the systems, and constrained the upper mass limit of potential additional planetary companions.

### 2019-08-01 paper.tex
Full paper on thesis

@@
 
-\section*{TraMoS V: Updated ephemeris and transit timing variations of the hot Jupiters WASP-18b, WASP-19b and WASP-77Ab}
+\section*{TraMoS V: Updated ephemeris and transit timing variations of the hot Jupiters WASP-18b, WASP-19b and WASP-77Ab\footnote{Copy of paper submitted to A\%A on July 9, 2019.}}
 

### 2019-08-01 paper.tex
Full paper on thesis

--- 2019-07-31 paper.tex
@@
 
-\section*{TraMoS V: Updated ephemeris and transit timing variations of the hot Jupiters WASP-18b, WASP-19b and WASP-77Ab}
+\section*{TraMoS V: Updated ephemeris and transit timing variations of the hot Jupiters WASP-18b, WASP-19b and WASP-77Ab\footnote{Copy of paper submitted to A\&A on July 9, 2019.}}
 
-\chapterauthor{P\'ia Cort\'es-Zuleta, Patricio Rojo, Songhu Wang, Tobias C. Hinse, Sergio Hpyer, Bastian Sanhueza, Patricio Correa-Amaro, Julio Albornoz}
+\chapterauthor{P\'ia Cort\'es-Zuleta, Patricio Rojo, Songhu Wang, Tobias C. Hinse, Sergio Hoyer, Bastian Sanhueza, Patricio Correa-Amaro, Julio Albornoz}
 

### 2019-08-02 conclusion.tex
New chapters

\chapter{Conclusions and Future work}\label{chap:conclusion}

### 2019-08-02 tess.tex
New chapters

\chapter{TraMoS in the TESS era}\label{chap:tess}

### 2019-08-06 paper.tex
TTV figures added for WASP18, WASP19

@@
 
-\section*{TraMoS V: Updated ephemeris and transit timing variations of the hot Jupiters WASP-18b, WASP-19b and WASP-77Ab\footnote{Copy of paper submitted to A\&A on July 9, 2019.}}
+\section*{TraMoS V: Updated ephemeris and transit timing variations of the hot Jupiters WASP-18b, WASP-19b and WASP-77Ab\footnote{Based on paper submitted to A\&A on July 9, 2019.}}
 
@@
 
+\begin{figure*}
+%\vspace{0.1cm}\hspace{0.2cm}
+\includegraphics[width=1.0\textwidth]{imagenes/WASP18_TTV.png}
+\caption{Observed minus calculated mid-transit times (TTV) for WASP-18b.
+The dashed black line corresponds to the proposed linear ephemeris, i.e.
+zero deviation from the predicted transit time  computed from our refined orbital period.
+For that, we considered 63 transit times from the TraMoS project (in light blue), published works and TESS (both in black).
+The grey area corresponds to the error propagation at $1\sigma$, where the quadratic trend looks almost horizontal.
+The RMS scatter from the linear ephemeris is 47 seconds.}
+\label{wasp18_ttv}
+\end{figure*}
+
 \subsubsection{WASP-19b}
@@
 
+\begin{figure*}
+%\vspace{0.1cm}\hspace{0.2cm}
+\includegraphics[width=1.0\textwidth]{imagenes/WASP19_TTV.png}
+\caption{Observed minus calculated mid-transit times (TTV) for WASP-19b.
+The dashed black line corresponds to the proposed linear ephemeris, i.e.
+zero deviation from the predicted transit time  computed from our refined orbital period.
+For that, we considered 87 transit times from the TraMoS project (in light blue), published works and TESS (both in black).
+The grey area corresponds to the error propagation at $1\sigma$, where the quadratic trend looks almost horizontal.
+The RMS scatter from the linear ephemeris is 65 seconds.}
+\label{wasp19_ttv}
+\end{figure*}
+
 \subsubsection{WASP-77Ab}

### 2019-08-06 introduction.tex
More writtingggg

--- 2019-07-29 introduction.tex
@@
 \end{figure}
-
-\section{Transit Timing Variations}
-
-Since the discovery of the first exoplanet, one of the principal questions that arose was: are they alone in their systems?
-The idea of multiplanetary system is a consequence of our knowlegde about the planetary system where we live in, and until today the Solar System has the larger number of orbiting planets.
-Besides the Solar System, Kepler-90 has the same number of confirmed exoplanets: eight.
-Statistically, around a 20\% of the confirmed exoplanets live in a multiplanetary system, but this number is theoretically larger (cite).
-
-The Transit Timing Variations technique was proposed as a way to detect Earth-mass planet in multiplanetary systems due to gravitational interactions \citep{Holman2005,Agol2005}.
-A planet in a Keplerian orbit will transit its star following a linear function of the orbital period, but the presence of a second planet could produce transits no exactly periodic.
-
-\section{This work}

### 2019-08-06 paper.tex
More writtingggg

@@
 
-\section{Observations and Data Reduction}
+\section{Observations and Data Reduction}\label{obs}
 
@@
 
-\section{Light curve and RV analysis}
+\section{Light curve and RV analysis}\label{lc}
 
@@
 
-\section{Results and Discussion}
+\section{Results and Discussion}\label{res}
 
@@
 \end{table}
+
+\subsection{Limits on an Additional Perturber \label{addper}}
+%Comments: Do not delete
+%Written by Tobias C. Hinse
+%The following text was largely taken from TEMPIV paper as the underlying methodology follows exactly that
+%paper (and other papers).
+
+The results from our mid-transit time study in Section~\ref{ttvsection}, allow us to infer an upper mass limit for an additional planet in each system.
+A perturbing planet will introduce a change in the mid-transit times of a known planet, which can be quantified by the RMS scatter around the nominal (unperturbed) linear ephemeris.
+The TTV effect is amplified for orbital configurations involving mean-motion resonances \citep{Agol2005, Holman2005, 2008ApJ...688..636N}.
+In principle, this amplification would allow the detection of a low-mass planetary perturbing body.
+A larger perturbation implies a larger RMS scatter around the nominal ephemeris.
+
+The applied method follows the technique described in \citet{TEMP1,TEMP2,TEMP4}.
+The calculation of an upper mass limit is performed numerically via direct orbit integrations.
+For this task, we have modified the \texttt{FORTRAN}-based \texttt{MICROFARM}\footnote{\url{https://bitbucket.org/chdianthus/microfarm/src}}
+package \citep{go2003,go2008} which utilizes OpenMPI\footnote{\url{https://www.open-mpi.org}} to spawn hundreds of single-task parallel jobs on a suitable super-computing facility.
+The package's main purpose is the numerical computation of the Mean Exponential Growth factor of Nearby Orbits
+\citep[MEGNO]{cincsimo2000, go2001, ci2003} over a grid of initial values of orbital parameters for an $n$-body problem.
+The calculation of the RMS scatter of TTVs in the present work follows a direct brute-force method, which proved to be robust given the availability of computing power.
+
+Within the framework of the three-body problem, we integrated the orbits of one of our three hot Jupiters and an additional perturbing planet around their host stars.
+The mid-transit time was calculated iteratively to a high precision from a series of back-and-forth integrations once a transit of the transiting planet was detected.
+The best-fit radii of both the planet and the host star were accounted for.
+We then calculated an analytic least-squares regression to the time-series of transit numbers and mid-transit times to determine a best-fitting linear ephemeris with an associated RMS statistic for the TTVs.
+The RMS statistic was based on a 20-year integration corresponding to 7763 transits for WASP-18b, 9270 transits for WASP-19b, and 5371 transit events for WASP-77Ab.
+This procedure was then applied to a grid of masses and semi-major axes of the perturbing planet while fixing all the other orbital parameters.
+In this study, we have chosen to start the perturbing planet on a circular orbit that is co-planar with the transiting planet; this implies that $\Omega_2=0^{\circ}$ and $\omega_2=0^{\circ}$ for the perturbing and $\Omega_1 = 0^{\circ}$ for the transiting planet.
+This setting provides a most conservative estimate of the upper mass limit of a possible perturber \citep{bean2009, fukui2011, Hoyer2011, Hoyer2012}.
+For the interested readers, we refer to \citet{TEMP4}, which has studied the effects of TTVs on varying initial orbital parameters.
+
+\begin{table}
+\caption{Approximate upper mass limits of a putative perturber in various orbital resonances for each system}
+\label{masstable}
+\centering
+\begin{tabular}{cccc}
+\hline \hline
+MMR & WASP-18 & WASP-19 & WASP-77A \\
+($P_{2}/P_{1}$) & $[M_{\oplus}]$ & $[M_{\oplus}]$ & $[M_{\oplus}]$ \\
+\hline
+1:3 & 1.9    & 500\footnote{b} & 1.0 \\
+2:5 & 4.0    & -   & -   \\
+1:2 & 5.0\footnote{a} & 2.0 & 3.5 \\
+3:5 & -      & -      & 2.0 \\
+2:3 & -      & -      & 7.0\footnote{a} \\
+5:3 & -      & 6.0    & 6.0   \\
+7:4 & -      & -      & 10.0 \\
+2:1 & 25\footnote{a}    & 0.9    & 3.5 \\
+7:3 & 80.0\footnote{c}   & -      & -   \\
+5:2 & 10.0   & 3.0    & -   \\
+3:1 & 7.0    & 2.0    & 4.5 \\
+17:5 & 500.0\footnote{d} & -      & -    \\
+4:1 & 50.0   & 100.0\footnote{e}  & 60.0\footnote{f} \\
+\hline
+\end{tabular}
+%\tablefoot{
+%\tablefoottext{a}{Very close to the general instability area.}
+%\tablefoottext{b}{This value is constraint by RV limit of 17.8 $[M_{\oplus}]$}
+%\tablefoottext{c}{This value is constraint by RV limit of 74.6 $[M_{\oplus}]$}
+%\tablefoottext{d}{This value is constraint by RV limit of 82.8 $[M_{\oplus}]$}
+%\tablefoottext{e}{This value is constraint by RV limit of 40.8 $[M_{\oplus}]$}
+%\tablefoottext{f}{This value is constraint by RV limit of 30.8 $[M_{\oplus}]$}}
+\end{table}
+
+In order to calculate the location of mean-motion resonances, we have used the same code to calculate MEGNO on the same parameter grid.
+However, this time we integrated each initial grid point for 1000 years, allowing this study to highlight the location of weak chaotic high-order mean-motion resonances.
+In short, MEGNO quantitatively measures the degree of stochastic behaviour of a non-linear dynamical system and has been proven useful in the detection of chaotic resonances \citep{go2001, hi2010}.
+In addition to the Newtonian equations of motion, the associated variational equations of motion are solved simultaneously allowing the calculation of MEGNO at each integration time step.
+The \texttt{MICROFARM} package implements the \texttt{ODEX}\footnote{\url{https://www.unige.ch/~hairer/prog/nonstiff/odex.f}} extrapolation algorithm to numerically solve the system of first-order differential equations.
+
+Following the definition of MEGNO \citep{cincsimo2000} (denoted as $\langle Y\rangle$ in Figures~\ref{megno_wasp18}-\ref{megno_wasp77}), in a dynamical system that evolves quasi-periodically, the quantity $\langle Y \rangle$ will asymptotically approach 2.0 for $t \rightarrow \infty$.
+In that case, often the orbital elements associated with that orbit are bounded.
+In case of a chaotic time evolution, the $\langle Y\rangle$ diverges away from 2.0 with orbital parameters exhibiting erratic temporal excursions.
+For quasi-periodic orbits, we typically have $|\langle Y \rangle - 2.0| < 0.001$ at the end of each integration.
+
+Importantly, MEGNO is unable to prove that a dynamical system is evolving quasi-periodically, meaning that a given system cannot be proven to be stable or bounded for all times.
+The integration of the equations of motion only considers a limited time period.
+However, once a given initial condition has found to be chaotic, there is no doubt about its erratic nature in the future.
+
+In the following, we will present the results of each system for which we have calculated the RMS scatter of TTVs on a grid of the masses and semi-major axes of a perturbing planet in a circular, co-planar orbit.
+Results are shown in Figures~\ref{megno_wasp18} - \ref{megno_wasp77} and Table \ref{masstable}.
+In each of the three cases, we find the usual instability region located in the proximity of the transiting planet with MEGNO color-coded as yellow (corresponding to $\langle Y\rangle > 5$).
+The extent of these regions coincides with the results presented in \citet{barnes2006}.
+The locations of mean-motion resonances are indicated by arrows in each map.
+
+\subsubsection{WASP-18b}
+For the WASP-18b system we find a large region of instability when
+compared to the other two systems with the boundaries at the 1:2 interior
+and 2:1 exterior mean-motion resonance. By over-plotting the RMS scatter
+of mid-transit times ($\rm TTV_{\rm RMS}$) for a certain value, we find
+that the TTVs are relatively more sensitive at orbital architectures
+involving mean-motion resonances confirming the results by
+\citet{Agol2005} and \citet{Holman2005}. This also applies to WASP-19 and
+WASP-77A.
+
+As shown in Figure~\ref{megno_wasp18}, we find that a perturbing body of mass (upper limit) around $7-500~M_{\oplus}$ will produce an RMS of $83\,{\rm s}$ when located in the $P_2/P_1=$ 7:3, 5:2, 3:1, 17:5 and 4:1 exterior resonance.
+For the 1:3 interior resonance, a perturber mass (upper limit) as small as $1.9~M_{\oplus}$ could also cause a RMS mid-transit time scatter of $83\,{\rm s}$.
+
+\subsubsection{WASP-19b}
+For the WASP-19b system the measured transit-timing RMS scatter was $\rm TTV_{\rm RMS}=75,\rm s$.
+Additional bodies with a mass of $500~M_{\oplus}$ and as low as $2.0~M_{\oplus}$ and $0.9~M_{\oplus}$ at the 1:3, 1:2 (interior) and 2:1 (exterior) mean-motion resonances could cause the observed RMS scatter.
+Hypothetical planets of $6~M_{\oplus}$, $3~M_{\oplus}$ and $2~M_{\oplus}$ could cause the observed RMS scatter at the 5:3, 5:2 and 3:1 exterior mean-motion resonances, respectively.
+We refer to Fig.~\ref{megno_wasp19}.
+
+\subsubsection{WASP-77Ab}
+For the WASP-77Ab system the results are somewhat similar to WASP-19b.
+We refer to Fig.~\ref{megno_wasp77}.
+The measured RMS of mid-transit timing variations around the linear ephemeris was $\rm TTV_{\rm RMS}=121\rm s$.
+For interior mean-motion resonances the 1:2 and 2:3 commensurabilities could cause the observed $\rm TTV_{\rm RMS}$ by an additional planet of mass around $3.5~M_{\oplus}$ and $7~M_{\oplus}$.
+However, the 2:3 resonance is very close to the general instability area rendering the orbit likely to be unstable.
+Further a $1~M_{\oplus}$ mass planet at the 1:3 interior resonance could also cause a $\rm TTV_{\rm RMS}$ of 121 s.
+A $2~M_{\oplus}$ mass planet located at the 3:5 resonance, although relatively close to the inner edge of the general instability region, could also explain the observed timing variation.
+For exterior
+mean-motion resonances of 2:1, 3:1 and 4:1 an additional planet of mass $3.5~M_{\oplus}, 4.5~M_{\oplus}$ and $60~M_{\oplus}$, could cause a $\rm TTV_{\rm RMS}=121\rm s$, respectively.
+A subtle difference from the WASP-19b system is found at the 5:2 resonance, which does not exhibit any significant decrease in upper mass planet detection sensitivity.
+
+\subsection{TTV period search}
+
+We have carried out a Lomb-Scargle period analysis \citep{Lomb1976, Scargle1982} for each system's TTVs residuals to search for a significant periodic trend.
+For this we applied the \texttt{LombScargle}\footnote{\url{http://docs.astropy.org/en/stable/stats/lombscargle.html}} (LS) algorithm available within the \texttt{Astropy} (v3.1.1) Python package \citep{2012cidu.conf...47V, 2015ApJ...812...18V}.
+
+The algorithm is suitable for unevenly-sampled data.
+We chose to carry out computations using the observed transit epochs for each system as the independent variable.
+Each epoch is determined with a high degree of confidence.
+TTV measurement uncertainties were not accounted for since no convincing periodic trend were detected.
+Default settings were avoided in order to safeguard the analysis from an inappropriate frequency grid choice.
+We made use of the minimum and maximum frequency heuristic.
+Periods between 1 and 5000 epochs were searched for.
+Furthermore, we sampled each peak twelve times.
+Noteworthy to mention, and often overlooked, is the possible detection of frequencies much larger than the Nyquist sampling frequency \citep{2018ApJS..236...16V}.
+
+The result for each system is shown in Figs.~\ref{LS_wasp18_random} to \ref{LS_wasp77_random}, were we show the Lomb-Scargle power $P$ from the standard normalization method with $0\le P<1$.
+The final period is found by multiplying with the final best-fit period for each system.
+To quantify the significance of period-peaks we calculated the false-alarm probability (FAP) for three different $p$-values.
+The FAP encodes the probability of detecting a peak of a given height (or higher) and is conditioned on the null-hypothesis that the data is characterized by normal random noise.
+
+To avoid misinterpretation of the FAP we have calculated synthetic random TTVs for each system in a single realization.
+For each known epoch, we drew a normal random point with mean zero and standard deviation in accordance with the measured RMS for each timing data set (83 s for WASP-18, 75 s for WASP-19 and 121 s for WASP-77A).
+
+We then recomputed the LS periodogram for each synthetic data set.
+This method enables a meaningful quantitative assessment of a minimum requirement of the FAP to detect a true periodic signal which clearly stands out from Gaussian noise.
+We plot the LS periodograms for the synthetic TTVs in the bottom panels of Figs.~\ref{LS_wasp18_random} to \ref{LS_wasp77_random}.
+For the case of WASP-19 and WASP-77, we found that a reasonable minimum FAP of 0.01\% is required in order to distinguish any signal from white noise.
+For the case of WASP-18 the threshold is just above 0.01\%.
+In generally, we found no significant (99.99\% level) periodicity peaks for all three cases.
+%However, with some good will, qualitatively, the LS periodogram for WASP-19 shows a slight decrease in FAP for two periods (at 0.8 and 1.2 in Fig.
+\ref{LS_wasp19_random}) when compared to the white noise data case.
+
+\begin{figure}
+%% Toby's internal figure note (DO NOT DELETE!!):
+%% Project path: /home/tobiash/simulations/TRAMOS_PiaCortesZuleta/TTVMEGNOMAPS/WASP18
+%% imported to GIMP, resolution 300, anti-aliasing, rotated, cropped (removing white space), added alpha 
+%% channel, scaled to 12cm, then saved as PNG
+\includegraphics[width=1.0\columnwidth]{imagenes/WASP18_TraMos_83sec_Map001_GIMP_scaled.png}
+\caption{MEGNO ($\langle Y \rangle$) stability map for the WASP-18 system.
+We over-plot the map with an upper mass of a hypothetical perturbing planet introducing a mid-transit time $\rm TTV_{\rm RMS}$ scatter of $83\,{\rm s}$ (solid line) as obtained in this study.
+The stipulated line is the upper mass limit as obtained from the RMS scatter $(30.9\, \rm m/s)$ of the radial-velocity curve.
+For initial conditions resulting in a quasi-periodic (i.e bounded) motion of the system, the $\langle Y\rangle$ value is close to 2.0 (color coded blue).
+For chaotic (i.e unstable) motion, the $\langle Y \rangle$ is diverging away from 2.0 (color coded red to yellow).
+Vertical arrows indicate $(P_2/P_1)$ orbital resonances between the perturbing body and the transiting planet.
+The two planets were assumed to be co-planar, and the perturbing planet's eccentricity was initially set to zero.
+\emph{See electronic version for colors}.}
+\label{megno_wasp18}
+\end{figure}
+
+\begin{figure}
+%% Toby's internal figure note (DO NOT DELETE!!):
+%% Project path: /home/tobiash/simulations/TRAMOS_PiaCortesZuleta/TTVMEGNOMAPS/WASP19
+%% imported to GIMP, resolution 300, anti-aliasing, rotated, cropped (removing white space), added alpha 
+%% channel, scaled to 12cm, then saved as PNG
+\includegraphics[width=1.0\columnwidth]{imagenes/WASP19_TraMos_Map001_GIMP_scaled.png}
+\caption{Same as Fig.~\ref{megno_wasp18}, but this time for WASP-19 with an $\rm TTV_{\rm RMS}$ of 75 s. The
+RMS for the radial-velocity measurements was $(18.2\,\rm m/s)$. \emph{See electronic version for colors}.}
+\label{megno_wasp19}
+\end{figure}
+
+\begin{figure}
+%% Toby's internal figure note (DO NOT DELETE!!):
+%% Project path: /home/tobiash/simulations/TRAMOS_PiaCortesZuleta/TTVMEGNOMAPS/WASP77
+%% imported to GIMP, resolution 300, anti-aliasing, rotated, cropped (removing white space), added alpha 
+%% channel, scaled to 12cm, then saved as PNG
+\includegraphics[width=1.0\columnwidth]{imagenes/WASP77_TraMos_121sec_Map001_GIMP_scaled.png}
+\caption{Same as Fig.~\ref{megno_wasp18}, but this time for WASP-77 with an $\rm TTV_{\rm RMS}$ of 121 s. The RMS for the radial-velocity measurements was $(12.0\,\rm m/s)$.
+\emph{See electronic version for colors}.}
+\label{megno_wasp77}
+\end{figure}
+
+\begin{figure*}
+\centering
+%% Toby's internal figure note (DO NOT DELETE!!):
+%% Project path: /home/tobiash/simulations/TRAMOS_PiaCortesZuleta/LombScargle/GnuPlotPlotting/WASP18
+%% Project path: /home/tobiash/simulations/TRAMOS_PiaCortesZuleta/LombScargle/Python/WASP18/testingLS
+%% GIMP, original was rotated, cropped (removing white space), scaled to 120cm, then saved as PNG
+\includegraphics[width=0.7\columnwidth]{imagenes/LS_WASP18_New_GIMP.png}
+\includegraphics[width=0.7\columnwidth]{imagenes/LS_WASP18_NormRandom_New_GIMP.png}
+\caption{Lomb-Scargle (standard normalized) power vs period for observed TTV residuals of WASP-18 (\emph{top panel}) and for a simulated set of TTVs randomly drawn from a normal distribution with mean zero and standard deviation of 1.38 minutes (\emph{lower panel}).
+See text for more details.}
+\label{LS_wasp18_random}
+\end{figure*}
+
+\begin{figure*}
+\centering
+%% Toby's internal figure note (DO NOT DELETE!!):
+%% Project path: /home/tobiash/simulations/TRAMOS_PiaCortesZuleta/LombScargle/GnuPlotPlotting/WASP19
+%% Project path: /home/tobiash/simulations/TRAMOS_PiaCortesZuleta/LombScargle/Python/WASP19/testingLS
+%% GIMP, original was rotated, cropped (removing white space), scaled to 120cm, then saved as PNG
+\includegraphics[width=0.7\columnwidth]{imagenes/LS_WASP19_New_GIMP.png}
+\includegraphics[width=0.7\columnwidth]{imagenes/LS_WASP19_NormRandom_New_GIMP.png}
+\caption{Lomb-Scargle (standard normalized) power vs period for observed TTV residuals of WASP-19 (\emph{top
+panel}) and for a simulated set of TTVs randomly drawn from a normal distribution with mean zero and standard
+deviation of 1.33 minutes (\emph{lower panel}). See text for more details.}
+\label{LS_wasp19_random}
+\end{figure*}
+
+\begin{figure*}
+\centering
+%% Toby's internal figure note (DO NOT DELETE!!):
+%% Project path: /home/tobiash/simulations/TRAMOS_PiaCortesZuleta/LombScargle/GnuPlotPlotting/WASP77
+%% Project path: /home/tobiash/simulations/TRAMOS_PiaCortesZuleta/LombScargle/Python/WASP77/testingLS
+%% GIMP, original was rotated, cropped (removing white space), scaled to 120cm, then saved as PNG
+\includegraphics[width=0.7\columnwidth]{imagenes/LS_WASP77_New_GIMP.png}
+\includegraphics[width=0.7\columnwidth]{imagenes/LS_WASP77_NormRandom_New_GIMP.png}
+\caption{Lomb-Scargle (standard normalized) power vs period for observed TTV residuals of WASP-77 
+(\emph{top panel}) and for a simulated set of TTVs randomly drawn from a normal distribution with mean zero
+and standard deviation of 2.02 minutes (\emph{lower panel}). See text for more details.}
+\label{LS_wasp77_random}
+\end{figure*}
+
+\section{Summary and Conclusions}\label{summary}
+We performed photometric follow-ups of the transiting exoplanets WASP-18b, WASP-19b and WASP-77Ab with one meter-class telescopes within the TraMoS project.
+Our 22 new high-precision light curves and archive data were combined together to refine physical and orbital parameters of the systems.
+
+For WASP-18b we find a larger value for the fraction of the radius $R_p/R_*$ than the most recent work with TESS data \cite{Shporer2018}, and a larger total transit duration $T_{14}$ comparing with \cite{Hellier2009}.
+The rest of stellar and planetary parameters are all in good agreement with previous results.
+
+In the analysis of WASP-19b, our results are in general, in good agreement with previous works \citep{Hebb2010,Lendl2013}.
+Only the inclination $i$ and the total duration of the transit $T_{14}$ show important differences.
+
+In this work we reported the first bulk measurements of the WASP-77Ab system. We find almost no disagreement in the orbital and physical parameters with the discovery paper \cite{Maxted2013}.
+
+We included archival transit times along with the transits from the TraMoS project to obtained refined values for the period $P$ of the three exoplanets, as well as updated linear ephemeris.
+We report a period of $P=0.94145223\pm9\times10^{-8}$ days for WASP-18b, $P=0.788838852\pm5\times10^{-9}$ days for WASP-19b, and $P=1.3600285\pm5\times10^{-7}$ days for WASP-77Ab.
+With the proposed linear ephemeris we found $\rm TTV_{RMS}$ of 83 seconds, 75 seconds, and 121 seconds, for WASP-18b, WASP-19b, and WASP-77Ab, respectively.
+Also, we find a lack of significant TTV periodic signals.
+
+The $\rm TTV_{RMS}$ could be produce by a perturber body bounded gravitationally with our targets.
+Thus, we performed orbit integrations in order to find upper mass limits for possible companions.
+We find that, for WASP-18b, the observed RMS could be produce by a perturber with an upper limit mass of $7-80~M_{\oplus}$ in 3:1, 4:1, 5:2, and 7:3 exterior resonances.
+For the interior resonances 1:3 and 2:5, a body with a limit mass of $1.9~M_{\oplus}$ and $4~M_{\oplus}$, respectively, could produce the observed $\rm TTV_{RMS}$.
+
+In the case WASP-19b, companions with masses of  0.9, 3, 6 and $2~M_{\oplus}$, in 2:1, 5:2, 5:3 and 3:1 exterior resonances, could reproduce the 75 seconds of scatter.
+For WASP-77Ab a planet with masses 3.5, 1, 3.5, 4.5, 2, and $10~M_{\oplus}$ in resonances 1:2, 1:3, 2:1, 3:1, 3:5, and 7:4 could produce the observed RMS in the TTVs.
+
+The hypothetical perturbers with the greatest masses for the three targets are discarded, as they are constrained by RV variations.
+Theses cases are: a body up to $500~M_{\oplus}$ in 17:5 resonance for WASP-18b, $500~M_{\oplus}$ and $100~M_{\oplus}$ in 1:3 and 3:1 resonances for WASP-19b, and $60~M_{\oplus}$ in 4:1 resonances for WASP-77Ab.
+
+We found no significant periodicity in any of the systems by performing a Lomb-Scargle period analysis.
+
+% Add why we can discard an rapid orbital decay
+The absence of a significant TTV signal in WASP-18b and the poor quality of a second order fit, support the conclusion that there is no evidence for a rapid orbital decay, as proposed by \cite{Wilkins2017}.
+As the TTV technique is sensitive to detect tidal decays on the exoplanets orbits, we could detect any trending in the TTV data, which is not the case.
+Moreover, theoretical studies \citep{CollierCameron2018} suggest a time span of around 20 years to observe a variations of 4 seconds in this system.
+Our result support that prediction.
+
+Previous photometric studies of WASP-19b \citep{Lendl2013,Wong2016} also suggest the lack of TTV on this system.
+Our results include more transit times, 59 versus 56 in \cite{Wong2016} and 14 in \cite{Lendl2013}, and also more recent transits being the last one from the end of 2017.
+Finding a no periodic TTV signal is consistent with their results.
+
+This is the first detailed study of WASP-77Ab.
+Our results will served as base for future photometric and dynamic studies where an extensive follow-up should be performed.
+WASP-77Ab shows the larger deviation for the linear ephemeris of our targets, with more than 2 minutes.
+Furthermore, the linear fit on the TTV is not fully representing the data as $\chi^{2}_{red}=1.4$, and a second degree fit shows almost the same value of $\chi^{2}_{red}$.
+More consecutive transit times are needed in order to understand the truly nature of this planet and its possible companions.

### 2019-08-06 tramos.tex
TODO in TraMoS chapter
TTV figures added for WASP18, WASP19
More writtingggg

@@
 \chapter{The Transit Monitoring in the South project}\label{chap:tramos}
+
+The Transit Monitoring in the South (TraMoS) project started in 2008 aiming to perform photometric follow-up of transiting exoplanets using telescopes located in Chile.
+Through photometric monitoring of transiting events, important information of the planetary system can be obtained, such as the planetary radius, inclination of the orbit, precise planetary mass, among others.
+Moreover, this kind of analysis allows the detection of variability in the transit's parameters (TPV), if several epochs of the transit event are included.
+The TraMoS project aims, on the one hand, to refine the physical and orbital parameters of selected exoplanets systems through photometric follow-up and, on the other hand, to search variations in that parameters that could suggest the presence of additional bodies in the system.
+
+To date, almost 400 transit events have been observed of 144 transiting exoplanets (see Figure XXX).
+The bulk of the targets in the TraMoS project are hot Jupiters due to its short orbital period and large transit depth.
+Several facilities were used to perform the photometric follow-up such as the VLT of ESO, the SMARTS 0.9 m and 1 m at Cerro Tololo Inter.American Observatory, the Danish 1.54 m at La Silla Observatory, SWOPE and Du Pont telescopes at Las Campanas Observatory and SOAR telescope at Cerro Pachón Observatory, among others.
+The diameter size of the telescopes ranges from 0.6 meters to 8 meters.
+However, in the last stage of the TraMoS project, we built the team expertise using 1 meter-class telescopes, for example in the Danish, SWOPE and SMARTS.
+
+\begin{figure}
+\centering
+\includegraphics[width=1.0\columnwidth]{imagenes/tramos.png}
+\caption{Histogram of the 30 transiting exoplanets with the largest amount of observations within the TraMoS project.
+The exoplanets WASP-4b and WASP5-b were presented in \cite{Hoyer2012} and \cite{Hoyer2013}.
+The results from the analysis of WASP-18b, WASP-19b and WASP77A-b are in Cortés-Zuleta et al.
+2019 (submitted, see Chapter \ref{chap:paper} for further details).
+In any of those systems a significant TTV signal was detected.}
+\label{tramos}
+\end{figure}
+
+The first studies within the TraMoS project were conducted by Sergio Hoyer, former PhD student of Patricio Rojo.
+In summary, a possible orbital decay of WASP-43b \citep{Hoyer2016b} and OGLE-TR-113b \citep{Hoyer2016} was ruled out, and no significant TTV signal was detected in WASP-4b \citep{Hoyer2012} and WASP-5b \citep{Hoyer2013}.
+
+\section{Transit Timing Variations}
+
+Since the discovery of the first exoplanet, one of the principal questions that arose was: are they alone in their systems?
+The idea of multiplanetary system is a consequence of our knowledge about the planetary system where we live in, and until today the Solar System has the larger number of orbiting planets.
+Besides the Solar System, Kepler-90 has the same number of confirmed exoplanets: eight.
+Statistically, around a 20\% of the confirmed exoplanets live in a multiplanetary system, but this number is theoretically larger (cite).
+
+The Transit Timing Variations (TTV) technique was first proposed as a way to detect Earth-mass planets in multiplanetary systems due to gravitational interactions with a transiting exoplanet \citep{Holman2005,Agol2005}.
+However, TTVs can be also use to measure tidal interactions between the planet and the star or to detect exomoons \citep{Kipping2009a,Kipping2009b}, among others.
+
+For a given light curve of a transiting exoplanet (see Fig. \ref{transit}), the transit time $T_{c}$ (or central time of the transit) is computed as:
+
+\begin{equation}
+T_{c} = \frac{t_T}{2}
+\end{equation}
+
+A single transiting planet will stay in a Keplerian orbit around its host star, producing a transit time strictly periodic.
+Thus, the transit time $T_c$ follows a linear function of the orbital period $P$:
+
+\begin{equation}
+T_{c}(E) = T_{0} + E \cdot P
+\label{linear_ephemeris} 
+\end{equation}
+
+Where $T_0$ is a reference transit time and $E$ is the number of epochs since $T_0$.
+The presence of a second planet produces transits no exactly periodic, hence Eq.~\ref{linear_ephemeris} will not be valid.
+As the transit times will be no longer a linear function,  the time between  transits varies.
+The variation in time produced by the perturbing body depends on the mass and geometry of their orbits.
+The magnitude of this variation between successive transits of the transiting planet is:
+
+\begin{equation}
+\Delta t = \frac{45\pi}{16} \frac{M_2}{M_*} P_{1} \alpha^3_{e} (1-	\sqrt{2}\alpha^{3/2})^{-2}
+\label{delta_t}
+\end{equation}
+
+Where $\alpha_e = a_1/(a_2(1-e_2))$ is the ratio of the semi-major axis of the planets, considering a nonzero eccentricity for the perturbing planet ($e_2 \neq 0$) and $a_1 < a_2$.
+The semi-major axis of the transiting exoplanet is $a_1$ and its orbital period $P_1$, while the perturbing planet has a mass $M_2$, semi-major axis $a_2$, orbital period $P_2$ and eccentricity $e_2$.
+Assuming that the orbital parameters of the known transiting exoplanet are already derived from its light curve, the orbital parameters and mass of the hypothetical pertuber can be estimate numerically \citep{Nesvorny2008,Nesvorny2009}, even if the second planet does not transit the star.
+
+The TTV method is a efficient tool to search for additional unseen companions, since in order to employ this technique only photometry of the transiting exoplanet during a transit events is required.
+Moreover, this technique enhances its sensitivity when the two bodies in the system are close to Mean Motion Resonances (MMR) \citep{Agol2005,Steffen2005,Agol2007} (see Figure~\ref{rms_ttv_amplitude}) .
+
+\begin{figure}
+\centering
+\includegraphics[width=0.6\columnwidth]{imagenes/rms_ttv_amplitude}
+\caption{Example of a system with a transiting exoplanet of $1~M_{J}$ in a 10-day orbit, around a star with $0.367~M_{\odot}$.
+The perturber is a Earth-mass planet.
+Panel \textbf{a} is an O-C diagram showing the measured TTV when the pertuber has a period of 16.11 days, not in Mean Motion Resonance with the transiting planet.
+Panel \textbf{b} shows the TTV when the transiting planet and the perturbing planet are near an interior 2:1 resonance.
+The amplification of the TTV signal is by an order of magnitude.
+(Figure from \cite{Haghighipour2011})}
+\label{rms_ttv_amplitude}
+\end{figure}
+
+\cite{Holman2010} presented the first multiplanetary system confirmed using the TTV method: Kepler-9b and Kepler-9c.
+
+The no detection of TTV is also important: architecture of the system.
+
+\section{This work}
+
+This thesis is an extension of the Transit Monitoring in the South project (TraMoS, see Chapter\ref{chap:tramos}) started in 2008 by Sergio Hoyer and Patricio Rojo.
+I selected a new sample of transiting exoplanets, all of them hot Jupiters without any companions detected to date.

### 2019-08-07 paper.tex
More writting

@@
 \centering
-\includegraphics[width=0.7\columnwidth]{imagenes/phase.pdf}
+\includegraphics[width=0.6\columnwidth]{imagenes/phase.pdf}
 \caption{Phased light curv of WASP-18b, WASP-19b and WASP-77Ab transits, from the TraMoS project.
@@
 Both fit considered the errors of the data.
-In Figure~\ref{ttv} are presented all the TTV values for the transit times of WASP-18b, WASP-19b and WASP-77Ab.
+In Figures~\ref{wasp18_ttv}, \ref{wasp19_ttv}, and XXX, are presented all the TTV values for the transit times of WASP-18b, WASP-19b and WASP-77Ab, respectively.
 
@@
 
-The top panel of Figure~\ref{ttv} is the linear plot of TTV versus epoch for this planet.
+Shown in Figure~\ref{wasp18_ttv} is the linear plot of TTV versus epoch for this planet.
 The deviations of the transit times from the linear ephemeris has an RMS of 83 seconds.
@@
 
-At the middle panel of Figure~\ref{ttv} are the TTV values versus epoch, for all the transit time considered in this work.
+Figure~\ref{wasp19_ttv} shows the TTV values versus epoch, for all the transit time considered in this work.
 
@@
 
-In Table~\ref{tab:wasp77} are listed the TTV values of our transit times and from previous works \citep{Turner2016,Maxted2013} of WASP-77Ab and, at the bottom of Figure~\ref{ttv} are plotted versus epoch.
+In Table~\ref{tab:wasp77} are listed the TTV values of our transit times and from previous works \citep{Turner2016,Maxted2013} of WASP-77Ab and, at the bottom of Figure  XXX are plotted versus epoch.
 The scatter of all the transit times is about $RMS=121$ seconds.

### 2019-08-07 tess.tex
More writting

@@
 \chapter{TraMoS in the TESS era}\label{chap:tess}
+
+With the end of the Kepler mission, thousands of possible exoplanets remain as candidates known as Kepler Objects of Interest (KOI).
+The Kepler Object of Interest Network (KOINet: \citep{vonEssen2018,Freuddenthal2018}) in the Northern hemisphere, is a network of ground-based telescopes performing photometric follow-up of KOIs to continue what Kepler left undone.
+The main goal of KOINet is to combine Kepler data with ground-based observations in order to confirm and characterise the masses of exoplanet candidates using TTVs.
+
+It is crucial for TTV studies to continue the work of space missions from ground.
+It is unlike to only with space-based observations to cover the interaction timescales to dynamically prove the TTV signal and the existence of some exoplanets companions, as in shown in Figure \ref{koinet} from the KOINet project.
+In this figure, new data from ground-based telescopes were fundamental to confirm the TTV signal, and therefore to perform a proper characterization of the system.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.7\columnwidth]{imagenes/koinet.png}
+\caption{Observed minus calculated (O-C) diagram of the KOI-525b transit times, from the KOINet project.
+The observations from Kepler are in blue, and two different models were fitted on those data: an orbital decay model is in red, and a periodical TTV model is in green.
+If only Kepler data is considered, the two model could be plausible.
+The new ground-based observations (in pink) were essential to confirm the TTV nature of the system, discarding an orbital decay}
+\label{koinet}
+\end{figure}
+
+The new space telescope Transiting Exoplanet Survey Satellite (TESS: \cite{Ricker2014}) is providing its first discoveries.
+The TESS observation plan divided in 13 sectors will challenge the confirmation process and characterization of possible exoplanets.
+During the $\sim27$ days of each sector, many candidates will not be observed enough time to confirm and characterize them.
+However, this special feature will provide a huge amount of new transit events of already known transiting exoplanets.
+Combining the new TESS data with ground-base follow- up observations, many possible TTVs could be confirm or rule out.
+Moreover, \cite{Ballard2018} predicted that around 5\% of the planets discovered by TESS will exhibit measurable TTV signals, similar to Kepler’s results.
+
+Thus, for the future stage of the TraMoS project, archival data - collected since 2008 - will be combined with the upcoming TESS data and new ground-based observations using one-meter class telescopes.

### 2019-08-07 tramos.tex
More writting

@@
 
-To date, almost 400 transit events have been observed of 144 transiting exoplanets (see Figure XXX).
+To date, almost 400 transit events have been observed of 144 transiting exoplanets (see Figure \ref{tramos}).
 The bulk of the targets in the TraMoS project are hot Jupiters due to its short orbital period and large transit depth.
-Several facilities were used to perform the photometric follow-up such as the VLT of ESO, the SMARTS 0.9 m and 1 m at Cerro Tololo Inter.American Observatory, the Danish 1.54 m at La Silla Observatory, SWOPE and Du Pont telescopes at Las Campanas Observatory and SOAR telescope at Cerro Pachón Observatory, among others.
-The diameter size of the telescopes ranges from 0.6 meters to 8 meters.
+Several facilities were used to perform the photometric follow-up such as the VLT of European Southern Observatory, the SMARTS 0.9 m and 1 m at Cerro Tololo Inter-American Observatory, the Danish 1.54 m at La Silla Observatory, SWOPE and Du Pont telescopes at Las Campanas Observatory and SOAR telescope at Cerro Pachón Observatory, among others.
+The diameter size of the used telescopes ranges from 0.6 meters to 8 meters.
 However, in the last stage of the TraMoS project, we built the team expertise using 1 meter-class telescopes, for example in the Danish, SWOPE and SMARTS.
@@
 The exoplanets WASP-4b and WASP5-b were presented in \cite{Hoyer2012} and \cite{Hoyer2013}.
-The results from the analysis of WASP-18b, WASP-19b and WASP77A-b are in Cortés-Zuleta et al.
+The results from the analysis of WASP-18b, WASP-19b and WASP77-Ab are in Cortés-Zuleta et al.
 2019 (submitted, see Chapter \ref{chap:paper} for further details).
@@
 
-The first studies within the TraMoS project were conducted by Sergio Hoyer, former PhD student of Patricio Rojo.
+The first studies within the TraMoS project were conducted by Sergio Hoyer, former PhD student of Professor Patricio Rojo.
 In summary, a possible orbital decay of WASP-43b \citep{Hoyer2016b} and OGLE-TR-113b \citep{Hoyer2016} was ruled out, and no significant TTV signal was detected in WASP-4b \citep{Hoyer2012} and WASP-5b \citep{Hoyer2013}.

### 2019-08-08 paper.tex
Fixed tables, new images HD

@@
 
-\chapterauthor{P\'ia Cort\'es-Zuleta, Patricio Rojo, Songhu Wang, Tobias C. Hinse, Sergio Hoyer, Bastian Sanhueza, Patricio Correa-Amaro, Julio Albornoz}
+\chapterauthor{P\'ia Cort\'es-Zuleta$^{1,2}$, Patricio Rojo$^{1}$, Songhu Wang$^{2,5}$, Tobias C.
+Hinse$^{3}$, Sergio Hoyer$^{4}$, Bastian Sanhueza$^{1}$, Patricio Correa-Amaro$^{1}$, Julio Albornoz$^{1}$}
+
+\begin{flushleft}
+\vspace{-1cm}
+$^{1}$ Departamento de Astronom\'ia, Universidad de Chile, Camino El Observatorio 1515, Las Condes, Santiago, Chile \\
+$^{2}$ Department of Astronomy, Yale University, New Haven, CT 06511, USA \\
+$^{3}$ Chungnam National University, Department of Astronomy and Space Science, 34134 Daejeon, Republic of Korea \\ 
+$^{4}$ Aix Marseille Univ, CNRS, CNES, LAM, Marseille, France \\
+$^{5}$ \emph{51 Pegasi b} Fellow \\
+\end{flushleft}
 
@@
 
-We collected 8 light curves for WASP-18b between 2009 and 2017, 9 light curves for WASP-19b between 2011 and 2017, and 5 light curves for WASP-77Ab between 2015 and 2017.
-We included 4 transits of WASP-77Ab from the Exoplanet Transit Database (ETD) in order to cover a larger timespan.
-
-All of the photometry are collected by using either the Danish 1.54 m telescope at ESO La Silla Observatory, or the SMARTS 1 m at Cerro Tololo Observatory (CTIO), except for one transit of WASP-77Ab that was observed with the Warsaw 1.3 m at Las Campanas Observatory (LCO).
-The log of our observations is shown in Table \ref{log_table}.
-All the new light curves used for this work are presented in Figure~\ref{transits}.
-
-For the photometric observations conducted on the Danish telescope, we used the Danish Faint Object Spectrograph and Camera (DFOSC) instrument, which has a $2{\rm K} \times 2{\rm K}$ CCD with a 13.7 x 13.7 arcmin$^2$ field of view (FoV) and a pixel scale of 0.39" per pixel.
-To reduce the readout time, some of the Danish 1.54 m images were windowed to only include the target star and its closest reference stars.
-The observations of the transits of WASP-18b during 2016 and 2017 were forced to be windowed due to a malfunction of the CCD.
-For those transits, only one reference star was used to perform the photometry.
-
-The SMARTS 1 m has the Y4KCam instrument which is a $4{\rm K} \times 4{\rm K}$ CCD camera with a $20\times20$ arcmin$^2$ FoV and a pixel scale of 0.289" per pixel.
-
-For the observation on the Warsaw 1.3 m telescope, we used a $2048 \times 4096$ CCD camera chip with a 1.4 square degrees of FoV and 0.26" per pixel scale.
-No windowing or binning was used during the observations on both SMARTS 1m and the Warsaw 1.3m telescope.
-
-As suggested by \cite{Southworth2009}, most of our observation, especially those conducted after 2011, used the defocus technique, which allows longer exposure times in bright targets and improves the photometric precision.
-We adjust the exposure time during the observations if the weather is not ideal.
-The recorded Julian Date in the Coordinated Universal Time (${\rm JD_{UTC}}$) were converted into Barycentric Julian Date in the Barycentric Dynamical Time standard (${\rm BJD_{TDB}}$) by following the procedure as in \citet{Eastman2010}.
-
-We reduced the data by using our custom pipeline.
-It follows the standard procedures of reduction, calibration, and aperture photometry, but customized for each used instrument.
-The pipeline semi-automatically finds the best aperture and ring size, for the sky that produces the light curve with less RMS.
-Then, we manually choose the reference stars to produce the differential light curves for each targets.
-
-\begin{table*}
+\begin{table}
 \caption{Log of Observations}             
@@
 \centering          
+\begin{threeparttable}
 \begin{tabular}{cccccccc}
 \hline\hline       
-Target & Date & Epoch\footnotemark{a} & Telescope & Filter & N & $t_{exp}$\footnotemark{b} & RMS\footnotemark{c} \\
+Target & Date & Epoch\tnote{a} & Telescope & Filter & N & $t_{exp}$\tnote{b} & RMS\tnote{c} \\
 & (UTC) &       &           &       &                   & (seconds) & (mmag)\\
@@
  				& 2011 Sep 06 & -1184 & SMARTS 1 m & $I$ & 203 & 15 & 2.40 \\
-				& 2016 Sep 24\footnotemark{d} & 776 & Danish 1.54 m & $I$ & 138 & 90 & 1.05  \\
-				& 2016 Sep 25\footnotemark{d} & 777 &Danish 1.54 m & $I$ & 159 & 90  & 0.96  \\
-			    & 2016 Sep 26\footnotemark{d} & 778 & Danish 1.54 m & $I$ & 113 & 90 & 0.87  \\ \smallskip
-				& 2017 Sep 29\footnotemark{d} & 1169 & Danish 1.54 m & $R$ & 330 & 30 & 2.53 \\
+				& 2016 Sep 24\tnote{d} & 776 & Danish 1.54 m & $I$ & 138 & 90 & 1.05  \\
+				& 2016 Sep 25\tnote{d} & 777 &Danish 1.54 m & $I$ & 159 & 90  & 0.96  \\
+			    & 2016 Sep 26\tnote{d} & 778 & Danish 1.54 m & $I$ & 113 & 90 & 0.87  \\ \smallskip
+				& 2017 Sep 29\tnote{d} & 1169 & Danish 1.54 m & $R$ & 330 & 30 & 2.53 \\
 WASP-19 & 2011 Apr 22 & -923 & SMARTS 1 m &   $I$ &  626  & 12  & 4.31   \\
@@
      & 2017 Oct 03 & 2064 & Danish 1.54 m & $R$ & 43 & 110 & 1.70\\ 
- WASP-77 & 2013 Aug 20 & -659 & ETD\footnotemark{e} & $clear$ & 103 & 120 & 3.87  \\
-    & 2013 Oct 30 & -606 & ETD\footnotemark{e} & $clear$ & 690 & 12 & 5.91 \\
+ WASP-77 & 2013 Aug 20 & -659 & ETD\tnote{e} & $clear$ & 103 & 120 & 3.87  \\
+    & 2013 Oct 30 & -606 & ETD\tnote{e} & $clear$ & 690 & 12 & 5.91 \\
     & 2015 Sep 29 & -92 & Danish 1.54 m & $R$ &  244 & 30 &  0.84\\
@@
       & 2016 Sep 26 & 175 & Danish 1.54 m & $I$ &  90 & 90 &  0.47\\
-      & 2016 Sep 30 & 177 & ETD\footnotemark{e}& $clear$ & 66 & 180 & 2.74 \\
+      & 2016 Sep 30 & 177 & ETD\tnote{e}& $clear$ & 66 & 180 & 2.74 \\
       & 2016 Oct 07 & 183 & Warsaw 1.3 m & $I$ & 237 & 60 &  2.38 \\ 
-      & 2016 Dec 09 & 229 & ETD\footnotemark{e} & $R$ & 57 & 180 & 2.11 \\ 
+      & 2016 Dec 09 & 229 & ETD\tnote{e} & $R$ & 57 & 180 & 2.11 \\ 
       & 2017 Oct 01 & 447 & Danish 1.54 m & $B$ &  224 & 30 &   3.48\\
@@
 \end{tabular}
-\footnotetext{a}{The epoch 0 is $T_{0}$ in Tables , for WASP-18b, WASP-19b and WASP-77Ab, respectively.}
-\footnotetext{b}{For the variable exposure times, we consider the average during the night.}
-\footnotetext{c}{The RMS values were computed from the best fitted model of each light curve.}
-\footnotetext{d}{Light curves obtained with only one reference star.}
-\end{table*}
-
-\begin{table}
-
+\begin{tablenotes}
+	\footnotesize
+	\item[a] The epoch 0 is $T_{0}$ in Tables \ref{wasp18},\ref{tab:wasp19} and \ref{tab:wasp77}, for WASP-18b, WASP-19b and WASP-77Ab, respectively.
+	\item[b] For the variable exposure times, we consider the average during the night.
+	\item[c] RMS values were computed from the best fitted model of each light curve.
+	\item[d] Light curves obtained with only one reference star.
+	\item[e] These light curves were obtained from the Exoplanet Transit Database (ETD) \url{var2.astro.cz/ETD}.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+We collected 8 light curves for WASP-18b between 2009 and 2017, 9 light curves for WASP-19b between 2011 and 2017, and 5 light curves for WASP-77Ab between 2015 and 2017.
+We included 4 transits of WASP-77Ab from the Exoplanet Transit Database (ETD) in order to cover a larger timespan.
+
+All of the photometry are collected by using either the Danish 1.54 m telescope at ESO La Silla Observatory, or the SMARTS 1 m at Cerro Tololo Observatory (CTIO), except for one transit of WASP-77Ab that was observed with the Warsaw 1.3 m at Las Campanas Observatory (LCO).
+The log of our observations is shown in Table \ref{log_table}.
+All the new light curves used for this work are presented in Figure~\ref{transits}.
+
+For the photometric observations conducted on the Danish telescope, we used the Danish Faint Object Spectrograph and Camera (DFOSC) instrument, which has a $2{\rm K} \times 2{\rm K}$ CCD with a 13.7 x 13.7 arcmin$^2$ field of view (FoV) and a pixel scale of 0.39" per pixel.
+To reduce the readout time, some of the Danish 1.54 m images were windowed to only include the target star and its closest reference stars.
+The observations of the transits of WASP-18b during 2016 and 2017 were forced to be windowed due to a malfunction of the CCD.
+For those transits, only one reference star was used to perform the photometry.
+
+The SMARTS 1 m has the Y4KCam instrument which is a $4{\rm K} \times 4{\rm K}$ CCD camera with a $20\times20$ arcmin$^2$ FoV and a pixel scale of 0.289" per pixel.
+
+For the observation on the Warsaw 1.3 m telescope, we used a $2048 \times 4096$ CCD camera chip with a 1.4 square degrees of FoV and 0.26" per pixel scale.
+No windowing or binning was used during the observations on both SMARTS 1m and the Warsaw 1.3m telescope.
+
+As suggested by \cite{Southworth2009}, most of our observation, especially those conducted after 2011, used the defocus technique, which allows longer exposure times in bright targets and improves the photometric precision.
+We adjust the exposure time during the observations if the weather is not ideal.
+The recorded Julian Date in the Coordinated Universal Time (${\rm JD_{UTC}}$) were converted into Barycentric Julian Date in the Barycentric Dynamical Time standard (${\rm BJD_{TDB}}$) by following the procedure as in \citet{Eastman2010}.
+
+We reduced the data by using our custom pipeline.
+It follows the standard procedures of reduction, calibration, and aperture photometry, but customized for each used instrument.
+The pipeline semi-automatically finds the best aperture and ring size, for the sky that produces the light curve with less RMS.
+Then, we manually choose the reference stars to produce the differential light curves for each targets.
+
+\begin{table}[ht]
 \caption{Example photometry of WASP-18, WASP-19 and WASP-77A}
@@
 \centering
+\begin{threeparttable}
 \begin{tabular}{c c c c}
 \hline \hline
-Target & ${\rm BJD_{TDB}}$\footnotemark{a} & Relative flux & Error\\
+Target & ${\rm BJD_{TDB}}$\tnote{a} & Relative flux & Error\\
 \hline
@@
 \end{tabular}
-\footnotetext{These tables are available in machine-readable form.\\
-\footnotetext{a}{The column time was converted to (${\rm BJD_{TDB}}$), following the procedure of \cite{Eastman2010}.}
-}
+\begin{tablenotes}
+\item These tables are available in machine-readable form.
+\item[a]The column time was converted to (${\rm BJD_{TDB}}$), following the procedure of \cite{Eastman2010}.
+\end{tablenotes}
+\end{threeparttable}
 \end{table}
@@
 
-\begin{figure*}
+\begin{figure}
 \centering
@@
 \label{transits}
-\end{figure*}
-
-\begin{figure*}
+\end{figure}
+
+\begin{figure}
 %\vspace{0.1cm}\hspace{0.2cm}
@@
 \label{rv}
-\end{figure*}
+\end{figure}
 
@@
 \begin{landscape}
+\begin{ThreePartTable}
+\begin{TableNotes}
+\item Values enclosed in parentheses correspond to the uncertainties of the last digits of the nominal value.
+\item[a] Value converted to cgs units multiplying by the Jupiter density $\rho_{J}=1.33\,$cgs.
+\end{TableNotes}
 \begin{longtable}{llccc}
@@
 \smallskip\\\multicolumn{2}{l}{Stellar Parameters:}&\smallskip\\
-~~~~$M_*$  &Mass (\(M_\odot\))  &$1.294^{+0.063}_{-0.061}$ & $1.25\pm0.13$ &  \\
-~~~~$R_*$  &Radius (\(R_\odot\))  &$1.319^{+0.061}_{-0.062}$ &$1.26^{+0.067}_{-0.054}$ & \\
-~~~~$L_*$  &Luminosity (\(L_\odot\))  &$2.68^{+0.28}_{-0.26}$ & &\\
-~~~~$\rho_*$  &Density (cgs)  &$0.795^{+0.11}_{-0.089}$ & $ 0.707^{+0.056}_{-0.096}$&\\
-~~~~$\log{g}$  & Surface gravity (cgs)  &$4.310^{+0.036}_{-0.033}$ &$4.367^{+0.028}_{-0.042}$ & \\
-~~~~$T_{\rm eff}$  &Effective Temperature (K)  &$6432\pm48$ & $6400\pm100$& \\
-~~~~$[{\rm Fe/H}]$  &Metallicity   &$0.107\pm0.080$ & $0.00\pm0.09$ & \\
-~~~~$Age$  &Age (Gyr)  &$1.57^{+1.4}_{-0.94}$ & $0.5-1.5$ & \\
-%~~~~$d$  &Distance (pc)  &$122.2^{+9.9}_{-8.2}$ & $100\pm10$ & \\
+~~~~$M_*$\dotfill &Mass (\(M_\odot\))\dotfill &$1.294^{+0.063}_{-0.061}$ & $1.25\pm0.13$ &  \\
+~~~~$R_*$\dotfill &Radius (\(R_\odot\))\dotfill &$1.319^{+0.061}_{-0.062}$ &$1.26^{+0.067}_{-0.054}$ & \\
+~~~~$L_*$\dotfill &Luminosity (\(L_\odot\))\dotfill &$2.68^{+0.28}_{-0.26}$ & &\\
+~~~~$\rho_*$\dotfill &Density (cgs)\dotfill &$0.795^{+0.11}_{-0.089}$ & $ 0.707^{+0.056}_{-0.096}$&\\
+~~~~$\log{g}$\dotfill & Surface gravity (cgs)\dotfill &$4.310^{+0.036}_{-0.033}$ &$4.367^{+0.028}_{-0.042}$ & \\
+~~~~$T_{\rm eff}$\dotfill &Effective Temperature (K)\dotfill &$6432\pm48$ & $6400\pm100$& \\
+~~~~$[{\rm Fe/H}]$\dotfill &Metallicity \dotfill &$0.107\pm0.080$ & $0.00\pm0.09$ & \\
+~~~~$Age$\dotfill &Age (Gyr)\dotfill &$1.57^{+1.4}_{-0.94}$ & $0.5-1.5$ & \\
+%~~~~$d$\dotfill &Distance (pc)\dotfill &$122.2^{+9.9}_{-8.2}$ & $100\pm10$ & \\
 
 \smallskip\\\multicolumn{2}{l}{Planetary Parameters:}&\smallskip\\
-~~~~$R_P$  &Radius (\rj)  &$1.310\pm0.071$ & $1.106^{+0.072}_{-0.054}$& $1.192\pm0.038$\\
-~~~~$M_P$  &Mass (\mj)  &$10.48^{+0.42}_{-0.40}$ & $10.30\pm0.69$ & \\
-~~~~$P$  &Period (days)  &$0.94145236\pm(49)$ & $0.94145299\pm(87)$& $0.9414576^{(+34)}_{(-35)}$ \\
-~~~~$e$  &Eccentricity   &$0.0061^{+0.0089}_{-0.0044}$ & &\\
-~~~~$a$  &Semi-major axis (AU)  &$0.02054^{+0.00033}_{-0.00032}$ & $0.02045\pm0.00067$&\\
-~~~~$\omega_*$  &Argument of Periastron (Degrees)  &$-100^{+110}_{-120}$ &  &\\
-~~~~$\rho_P$  &Density (cgs)  &$5.79^{+0.97}_{-0.78}$& $7.73^{+0.78}_{-1.27}$\footnotemark{b} & \\
-~~~~$logg_P$  &Surface gravity   &$4.180^{+0.044}_{-0.041}$ & $4.289^{+0.027}_{-0.050}$ &\\
-~~~~$T_{eq}$  &Equilibrium temperature (K)  &$2485^{+53}_{-56}$ & $2384^{+58}_{-30}$ & \\
-~~~~$\Theta$  &Safronov Number   &$0.254^{+0.015}_{-0.014}$ & &\\
-~~~~$\fave$  &Incident Flux (\fluxcgs)  &$8.66^{+0.77}_{-0.75}$ & & \\
+~~~~$R_P$\dotfill &Radius (\rj)\dotfill &$1.310\pm0.071$ & $1.106^{+0.072}_{-0.054}$& $1.192\pm0.038$\\
+~~~~$M_P$\dotfill &Mass (\mj)\dotfill &$10.48^{+0.42}_{-0.40}$ & $10.30\pm0.69$ & \\
+~~~~$P$\dotfill &Period (days)\dotfill &$0.94145236\pm(49)$ & $0.94145299\pm(87)$& $0.9414576^{(+34)}_{(-35)}$ \\
+~~~~$e$\dotfill &Eccentricity \dotfill &$0.0061^{+0.0089}_{-0.0044}$ & &\\
+~~~~$a$\dotfill &Semi-major axis (AU)\dotfill &$0.02054^{+0.00033}_{-0.00032}$ & $0.02045\pm0.00067$&\\
+~~~~$\omega_*$\dotfill &Argument of Periastron (Degrees)\dotfill &$-100^{+110}_{-120}$ &  &\\
+~~~~$\rho_P$\dotfill &Density (cgs)\dotfill &$5.79^{+0.97}_{-0.78}$& $7.73^{+0.78}_{-1.27}$\tnote{a} & \\
+~~~~$logg_P$\dotfill &Surface gravity \dotfill &$4.180^{+0.044}_{-0.041}$ & $4.289^{+0.027}_{-0.050}$ &\\
+~~~~$T_{eq}$\dotfill &Equilibrium temperature (K)\dotfill &$2485^{+53}_{-56}$ & $2384^{+58}_{-30}$ & \\
+~~~~$\Theta$\dotfill &Safronov Number \dotfill &$0.254^{+0.015}_{-0.014}$ & &\\
+~~~~$\fave$\dotfill &Incident Flux (\fluxcgs)\dotfill &$8.66^{+0.77}_{-0.75}$ & & \\
 
 \smallskip\\\multicolumn{2}{l}{Primary Transit Parameters:}&\smallskip\\
-~~~~$T_0$  &Transit time (\bjdtdb)  &$2456740.80560\pm(19)$ & $2454221.48163\pm(38)$ & $2458361.048072^{(+34)}_{(-35)}$\\
-~~~~$i$  &Inclination (Degrees)  &$83.5^{+2.0}_{-1.6}$ & $86.0\pm2.5$ & $84.31^{+0.40}_{-0.37}$\\
-~~~~$R_P/R_*$  &Radius of planet in stellar radii   &$0.1021\pm0.0011$ &  $0.0935\pm0.0011$ & $0.09721^{+0.00016}_{-0.00017}$\\
-~~~~$a/R_*$  &Semi-major axis in stellar radii   &$3.35^{+0.15}_{-0.13}$ & & $3.523^{+0.028}_{-0.027}$\\
-~~~~$b$  &Impact parameter   &$0.433^{+0.07}_{-0.10}$ & $0.25\pm0.15$ & $0.349^{+0.020}_{-0.022}$\\
-~~~~$\delta$  &Transit depth (fraction)  &$0.01041\pm0.00022$ & & $0.009449^{+0.000032}_{-0.000032}$\\
-~~~~$u_{1,I}$  &linear LD coeff., I band  &$0.207\pm0.019$ & &\\
-~~~~$u_{2,I}$  &quadratic LD coeff., I band  &$0.313\pm0.019$& &\\
-~~~~$u_{1,R}$  &linear LD coeff., R band  & $0.257\pm0.045$ & &\\
-~~~~$u_{2,R}$  &quadratic LD coeff., R band  &$0.309\pm0.048$ & &\\
-~~~~$T_{14}$  &Total transit duration (days)  &$0.0931^{+0.0011}_{-0.0010}$ & $0.08932\pm0.00068$ &\\
-~~~~$P_T$  &A priori non-grazing transit prob   &$0.268^{+0.011}_{-0.012}$ & &\\
-~~~~$P_{T,G}$  &A priori transit prob   &$0.328^{+0.014}_{-0.015}$ & &\\
-~~~~$\tau$  &Ingress/egress transit duration (days)  &$0.0107\pm0.0010$ & &\\
+~~~~$T_0$\dotfill &Transit time (\bjdtdb)\dotfill &$2456740.80560\pm(19)$ & $2454221.48163\pm(38)$ & $2458361.048072^{(+34)}_{(-35)}$\\
+~~~~$i$\dotfill &Inclination (Degrees)\dotfill &$83.5^{+2.0}_{-1.6}$ & $86.0\pm2.5$ & $84.31^{+0.40}_{-0.37}$\\
+~~~~$R_P/R_*$\dotfill &Radius of planet in stellar radii \dotfill &$0.1021\pm0.0011$ &  $0.0935\pm0.0011$ & $0.09721^{+0.00016}_{-0.00017}$\\
+~~~~$a/R_*$\dotfill &Semi-major axis in stellar radii \dotfill &$3.35^{+0.15}_{-0.13}$ & & $3.523^{+0.028}_{-0.027}$\\
+~~~~$b$\dotfill &Impact parameter \dotfill &$0.433^{+0.07}_{-0.10}$ & $0.25\pm0.15$ & $0.349^{+0.020}_{-0.022}$\\
+~~~~$\delta$\dotfill &Transit depth (fraction)\dotfill &$0.01041\pm0.00022$ & & $0.009449^{+0.000032}_{-0.000032}$\\
+~~~~$u_{1,I}$\dotfill &linear LD coeff., I band\dotfill &$0.207\pm0.019$ & &\\
+~~~~$u_{2,I}$\dotfill &quadratic LD coeff., I band\dotfill &$0.313\pm0.019$& &\\
+~~~~$u_{1,R}$\dotfill &linear LD coeff., R band\dotfill & $0.257\pm0.045$ & &\\
+~~~~$u_{2,R}$\dotfill &quadratic LD coeff., R band\dotfill &$0.309\pm0.048$ & &\\
+~~~~$T_{14}$\dotfill &Total transit duration (days)\dotfill &$0.0931^{+0.0011}_{-0.0010}$ & $0.08932\pm0.00068$ &\\
+~~~~$P_T$\dotfill &A priori non-grazing transit prob \dotfill &$0.268^{+0.011}_{-0.012}$ & &\\
+~~~~$P_{T,G}$\dotfill &A priori transit prob \dotfill &$0.328^{+0.014}_{-0.015}$ & &\\
+~~~~$\tau$\dotfill &Ingress/egress transit duration (days)\dotfill &$0.0107\pm0.0010$ & &\\
 
 \smallskip\\\multicolumn{2}{l}{RV Parameters:}&\smallskip\\
-~~~~$ecos{\omega_*}$  &   &$-0.0004^{+0.0038}_{-0.0045}$ & &\\
-~~~~$esin{\omega_*}$  &   &$-0.0008^{+0.0056}_{-0.0092}$ & &\\
-~~~~$K$  &RV semi-amplitude (m/s)  &$1807^{+34}_{-36}$ & $1818.3\pm8.0$ &\\
-~~~~$M_P\sin i$  &Minimum mass (\mj)  &$10.40\pm0.40$ & &\\
+~~~~$e\cos{\omega_*}$\dotfill & \dotfill &$-0.0004^{+0.0038}_{-0.0045}$ & &\\
+~~~~$e\sin{\omega_*}$\dotfill & \dotfill &$-0.0008^{+0.0056}_{-0.0092}$ & &\\
+~~~~$K$\dotfill &RV semi-amplitude (m/s)\dotfill &$1807^{+34}_{-36}$ & $1818.3\pm8.0$ &\\
+~~~~$M_P\sin i$\dotfill &Minimum mass (\mj)\dotfill &$10.40\pm0.40$ & &\\
 \smallskip\\\multicolumn{2}{l}{Secondary Eclipse Parameters:}&\smallskip\\
-~~~~$T_S$  &Time of eclipse (\bjdtdb)  &$2457657.3076^{+0.0023}_{-0.0027}$ & &\\
-~~~~$b_S$  &Eclipse impact parameter   &$0.431^{+0.070}_{-0.100}$ & &\\
-~~~~$\tau_S$  &Ingress/egress eclipse duration (days)  &$0.0106^{+0.0011}_{-0.0010}$ & &\\
-~~~~$T_{S,14}$  &Total eclipse duration (days)  &$0.0929\pm0.0017$ & &\\
-~~~~$P_S$  &A priori non-grazing eclipse prob   &$0.269^{+0.010}_{-0.011}$ & &\\
-~~~~$P_{S,G}$  &A priori eclipse prob   &$0.330^{+0.013}_{-0.014}$ & &\\
-\hline 
+~~~~$T_S$\dotfill &Time of eclipse (\bjdtdb)\dotfill &$2457657.3076^{+0.0023}_{-0.0027}$ & &\\
+~~~~$b_S$\dotfill &Eclipse impact parameter \dotfill &$0.431^{+0.070}_{-0.100}$ & &\\
+~~~~$\tau_S$\dotfill &Ingress/egress eclipse duration (days)\dotfill &$0.0106^{+0.0011}_{-0.0010}$ & &\\
+~~~~$T_{S,14}$\dotfill &Total eclipse duration (days)\dotfill &$0.0929\pm0.0017$ & &\\
+~~~~$P_S$\dotfill &A priori non-grazing eclipse prob \dotfill &$0.269^{+0.010}_{-0.011}$ & &\\
+~~~~$P_{S,G}$\dotfill &A priori eclipse prob \dotfill &$0.330^{+0.013}_{-0.014}$ & &\\
+\hline
+\insertTableNotes \\
 \end{longtable}
+\end{ThreePartTable}
 \end{landscape}
@@
 Both fit considered the errors of the data.
-In Figures~\ref{wasp18_ttv}, \ref{wasp19_ttv}, and XXX, are presented all the TTV values for the transit times of WASP-18b, WASP-19b and WASP-77Ab, respectively.
+In Figure \ref{all_ttv} are presented all the TTV values for the transit times of WASP-18b, WASP-19b and WASP-77Ab, respectively.
 
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=1.0\columnwidth]{imagenes/TTVs.png}
+\caption{Observed minus calculated mid-transit times (TTV) for WASP-18b (top), WASP-19b (center) and WASP-77Ab (bottom).
+The dashed black line corresponds to the proposed linear ephemeris, i.e.
+zero deviation from the predicted transit time (See Section \ref{ttvsection}) computed from our refined orbital period.
+For that, we considered 19, 59 and 11 transit times of WASP-18b, WASP-19b, and WASP-77Ab, respectively.
+The grey area corresponds to the error propagation at $1\sigma$, where the quadratic trend looks almost horizontal.
+The points in color are the TTV from the newly light curves of the TraMoS project (WASP-18b: light blue, WASP-19b: orange, WASP-77Ab: pink) and the black points in the three panels are TTVs measured from previous published transit times.
+The RMS scatter from the linear ephemeris are 83 seconds for WASP-18b; 75 seconds for WASP-19b, and 121 seconds for WASP-77Ab.}
+\label{all_ttv}
+\end{figure}
+
 \subsubsection{WASP-18b}
@@
 
-Shown in Figure~\ref{wasp18_ttv} is the linear plot of TTV versus epoch for this planet.
+The top panel of Figure~\ref{all_ttv} is the linear plot of TTV versus epoch for this planet.
 The deviations of the transit times from the linear ephemeris has an RMS of 83 seconds.
@@
 
-\begin{figure*}
-%\vspace{0.1cm}\hspace{0.2cm}
-\includegraphics[width=1.0\textwidth]{imagenes/WASP18_TTV.png}
-\caption{Observed minus calculated mid-transit times (TTV) for WASP-18b.
-The dashed black line corresponds to the proposed linear ephemeris, i.e.
-zero deviation from the predicted transit time  computed from our refined orbital period.
-For that, we considered 63 transit times from the TraMoS project (in light blue), published works and TESS (both in black).
-The grey area corresponds to the error propagation at $1\sigma$, where the quadratic trend looks almost horizontal.
-The RMS scatter from the linear ephemeris is 47 seconds.}
-\label{wasp18_ttv}
-\end{figure*}
-
 \subsubsection{WASP-19b}
@@
 
-Figure~\ref{wasp19_ttv} shows the TTV values versus epoch, for all the transit time considered in this work.
+At the middle panel of Figure~\ref{all_ttv} are the TTV values versus epoch, for all the transit time considered in this work.
 
@@
 
-\begin{figure*}
-%\vspace{0.1cm}\hspace{0.2cm}
-\includegraphics[width=1.0\textwidth]{imagenes/WASP19_TTV.png}
-\caption{Observed minus calculated mid-transit times (TTV) for WASP-19b.
-The dashed black line corresponds to the proposed linear ephemeris, i.e.
-zero deviation from the predicted transit time  computed from our refined orbital period.
-For that, we considered 87 transit times from the TraMoS project (in light blue), published works and TESS (both in black).
-The grey area corresponds to the error propagation at $1\sigma$, where the quadratic trend looks almost horizontal.
-The RMS scatter from the linear ephemeris is 65 seconds.}
-\label{wasp19_ttv}
-\end{figure*}
-
 \subsubsection{WASP-77Ab}
@@
 
-In Table~\ref{tab:wasp77} are listed the TTV values of our transit times and from previous works \citep{Turner2016,Maxted2013} of WASP-77Ab and, at the bottom of Figure  XXX are plotted versus epoch.
+In Table~\ref{tab:wasp77} are listed the TTV values of our transit times and from previous works \citep{Turner2016,Maxted2013} of WASP-77Ab and, at the bottom of Figure \ref{all_ttv} are plotted versus epoch.
 The scatter of all the transit times is about $RMS=121$ seconds.
@@
 
-\subsection{Limits on an Additional Perturber \label{addper}}
+\subsection{Limits on an Additional Perturber\footnote{This section was done by Tobias C. Hinse and it is added for completeness of the study.}}\label{addper}
 %Comments: Do not delete
@@
 For the 1:3 interior resonance, a perturber mass (upper limit) as small as $1.9~M_{\oplus}$ could also cause a RMS mid-transit time scatter of $83\,{\rm s}$.
-
-\subsubsection{WASP-19b}
-For the WASP-19b system the measured transit-timing RMS scatter was $\rm TTV_{\rm RMS}=75,\rm s$.
-Additional bodies with a mass of $500~M_{\oplus}$ and as low as $2.0~M_{\oplus}$ and $0.9~M_{\oplus}$ at the 1:3, 1:2 (interior) and 2:1 (exterior) mean-motion resonances could cause the observed RMS scatter.
-Hypothetical planets of $6~M_{\oplus}$, $3~M_{\oplus}$ and $2~M_{\oplus}$ could cause the observed RMS scatter at the 5:3, 5:2 and 3:1 exterior mean-motion resonances, respectively.
-We refer to Fig.~\ref{megno_wasp19}.
-
-\subsubsection{WASP-77Ab}
-For the WASP-77Ab system the results are somewhat similar to WASP-19b.
-We refer to Fig.~\ref{megno_wasp77}.
-The measured RMS of mid-transit timing variations around the linear ephemeris was $\rm TTV_{\rm RMS}=121\rm s$.
-For interior mean-motion resonances the 1:2 and 2:3 commensurabilities could cause the observed $\rm TTV_{\rm RMS}$ by an additional planet of mass around $3.5~M_{\oplus}$ and $7~M_{\oplus}$.
-However, the 2:3 resonance is very close to the general instability area rendering the orbit likely to be unstable.
-Further a $1~M_{\oplus}$ mass planet at the 1:3 interior resonance could also cause a $\rm TTV_{\rm RMS}$ of 121 s.
-A $2~M_{\oplus}$ mass planet located at the 3:5 resonance, although relatively close to the inner edge of the general instability region, could also explain the observed timing variation.
-For exterior
-mean-motion resonances of 2:1, 3:1 and 4:1 an additional planet of mass $3.5~M_{\oplus}, 4.5~M_{\oplus}$ and $60~M_{\oplus}$, could cause a $\rm TTV_{\rm RMS}=121\rm s$, respectively.
-A subtle difference from the WASP-19b system is found at the 5:2 resonance, which does not exhibit any significant decrease in upper mass planet detection sensitivity.
-
-\subsection{TTV period search}
-
-We have carried out a Lomb-Scargle period analysis \citep{Lomb1976, Scargle1982} for each system's TTVs residuals to search for a significant periodic trend.
-For this we applied the \texttt{LombScargle}\footnote{\url{http://docs.astropy.org/en/stable/stats/lombscargle.html}} (LS) algorithm available within the \texttt{Astropy} (v3.1.1) Python package \citep{2012cidu.conf...47V, 2015ApJ...812...18V}.
-
-The algorithm is suitable for unevenly-sampled data.
-We chose to carry out computations using the observed transit epochs for each system as the independent variable.
-Each epoch is determined with a high degree of confidence.
-TTV measurement uncertainties were not accounted for since no convincing periodic trend were detected.
-Default settings were avoided in order to safeguard the analysis from an inappropriate frequency grid choice.
-We made use of the minimum and maximum frequency heuristic.
-Periods between 1 and 5000 epochs were searched for.
-Furthermore, we sampled each peak twelve times.
-Noteworthy to mention, and often overlooked, is the possible detection of frequencies much larger than the Nyquist sampling frequency \citep{2018ApJS..236...16V}.
-
-The result for each system is shown in Figs.~\ref{LS_wasp18_random} to \ref{LS_wasp77_random}, were we show the Lomb-Scargle power $P$ from the standard normalization method with $0\le P<1$.
-The final period is found by multiplying with the final best-fit period for each system.
-To quantify the significance of period-peaks we calculated the false-alarm probability (FAP) for three different $p$-values.
-The FAP encodes the probability of detecting a peak of a given height (or higher) and is conditioned on the null-hypothesis that the data is characterized by normal random noise.
-
-To avoid misinterpretation of the FAP we have calculated synthetic random TTVs for each system in a single realization.
-For each known epoch, we drew a normal random point with mean zero and standard deviation in accordance with the measured RMS for each timing data set (83 s for WASP-18, 75 s for WASP-19 and 121 s for WASP-77A).
-
-We then recomputed the LS periodogram for each synthetic data set.
-This method enables a meaningful quantitative assessment of a minimum requirement of the FAP to detect a true periodic signal which clearly stands out from Gaussian noise.
-We plot the LS periodograms for the synthetic TTVs in the bottom panels of Figs.~\ref{LS_wasp18_random} to \ref{LS_wasp77_random}.
-For the case of WASP-19 and WASP-77, we found that a reasonable minimum FAP of 0.01\% is required in order to distinguish any signal from white noise.
-For the case of WASP-18 the threshold is just above 0.01\%.
-In generally, we found no significant (99.99\% level) periodicity peaks for all three cases.
-%However, with some good will, qualitatively, the LS periodogram for WASP-19 shows a slight decrease in FAP for two periods (at 0.8 and 1.2 in Fig.
-\ref{LS_wasp19_random}) when compared to the white noise data case.
 
@@
 
+\subsubsection{WASP-19b}
+For the WASP-19b system the measured transit-timing RMS scatter was $\rm TTV_{\rm RMS}=75,\rm s$.
+Additional bodies with a mass of $500~M_{\oplus}$ and as low as $2.0~M_{\oplus}$ and $0.9~M_{\oplus}$ at the 1:3, 1:2 (interior) and 2:1 (exterior) mean-motion resonances could cause the observed RMS scatter.
+Hypothetical planets of $6~M_{\oplus}$, $3~M_{\oplus}$ and $2~M_{\oplus}$ could cause the observed RMS scatter at the 5:3, 5:2 and 3:1 exterior mean-motion resonances, respectively.
+We refer to Fig.~\ref{megno_wasp19}.
+
 \begin{figure}
@@
 
+\subsubsection{WASP-77Ab}
+For the WASP-77Ab system the results are somewhat similar to WASP-19b.
+We refer to Fig.~\ref{megno_wasp77}.
+The measured RMS of mid-transit timing variations around the linear ephemeris was $\rm TTV_{\rm RMS}=121\rm s$.
+For interior mean-motion resonances the 1:2 and 2:3 commensurabilities could cause the observed $\rm TTV_{\rm RMS}$ by an additional planet of mass around $3.5~M_{\oplus}$ and $7~M_{\oplus}$.
+However, the 2:3 resonance is very close to the general instability area rendering the orbit likely to be unstable.
+Further a $1~M_{\oplus}$ mass planet at the 1:3 interior resonance could also cause a $\rm TTV_{\rm RMS}$ of 121 s.
+A $2~M_{\oplus}$ mass planet located at the 3:5 resonance, although relatively close to the inner edge of the general instability region, could also explain the observed timing variation.
+For exterior
+mean-motion resonances of 2:1, 3:1 and 4:1 an additional planet of mass $3.5~M_{\oplus}, 4.5~M_{\oplus}$ and $60~M_{\oplus}$, could cause a $\rm TTV_{\rm RMS}=121\rm s$, respectively.
+A subtle difference from the WASP-19b system is found at the 5:2 resonance, which does not exhibit any significant decrease in upper mass planet detection sensitivity.
+
 \begin{figure}
@@
 
-\begin{figure*}
+\subsection{TTV period search\footnote{This section was done by Tobias C. Hinse and it is added for completeness of the study.}}
+
+We have carried out a Lomb-Scargle period analysis \citep{Lomb1976, Scargle1982} for each system's TTVs residuals to search for a significant periodic trend.
+For this we applied the \texttt{LombScargle}\footnote{\url{http://docs.astropy.org/en/stable/stats/lombscargle.html}} (LS) algorithm available within the \texttt{Astropy} (v3.1.1) Python package \citep{2012cidu.conf...47V, 2015ApJ...812...18V}.
+
+The algorithm is suitable for unevenly-sampled data.
+We chose to carry out computations using the observed transit epochs for each system as the independent variable.
+Each epoch is determined with a high degree of confidence.
+TTV measurement uncertainties were not accounted for since no convincing periodic trend were detected.
+Default settings were avoided in order to safeguard the analysis from an inappropriate frequency grid choice.
+We made use of the minimum and maximum frequency heuristic.
+Periods between 1 and 5000 epochs were searched for.
+Furthermore, we sampled each peak twelve times.
+Noteworthy to mention, and often overlooked, is the possible detection of frequencies much larger than the Nyquist sampling frequency \citep{2018ApJS..236...16V}.
+
+The result for each system is shown in Figs.~\ref{LS_wasp18_random} to \ref{LS_wasp77_random}, were we show the Lomb-Scargle power $P$ from the standard normalization method with $0\le P<1$.
+The final period is found by multiplying with the final best-fit period for each system.
+To quantify the significance of period-peaks we calculated the false-alarm probability (FAP) for three different $p$-values.
+The FAP encodes the probability of detecting a peak of a given height (or higher) and is conditioned on the null-hypothesis that the data is characterized by normal random noise.
+
+To avoid misinterpretation of the FAP we have calculated synthetic random TTVs for each system in a single realization.
+For each known epoch, we drew a normal random point with mean zero and standard deviation in accordance with the measured RMS for each timing data set (83 s for WASP-18, 75 s for WASP-19 and 121 s for WASP-77A).
+
+We then recomputed the LS periodogram for each synthetic data set.
+This method enables a meaningful quantitative assessment of a minimum requirement of the FAP to detect a true periodic signal which clearly stands out from Gaussian noise.
+We plot the LS periodograms for the synthetic TTVs in the bottom panels of Figs.~\ref{LS_wasp18_random} to \ref{LS_wasp77_random}.
+For the case of WASP-19 and WASP-77, we found that a reasonable minimum FAP of 0.01\% is required in order to distinguish any signal from white noise.
+For the case of WASP-18 the threshold is just above 0.01\%.
+In generally, we found no significant (99.99\% level) periodicity peaks for all three cases.
+%However, with some good will, qualitatively, the LS periodogram for WASP-19 shows a slight decrease in FAP for two periods (at 0.8 and 1.2 in Fig.
+\ref{LS_wasp19_random}) when compared to the white noise data case.
+
+\begin{figure}
 \centering
@@
 \label{LS_wasp18_random}
-\end{figure*}
-
-\begin{figure*}
+\end{figure}
+
+\begin{figure}
 \centering
@@
 \label{LS_wasp19_random}
-\end{figure*}
-
-\begin{figure*}
+\end{figure}
+
+\begin{figure}
 \centering
@@
 \label{LS_wasp77_random}
-\end{figure*}
+\end{figure}
 

### 2019-08-08 tess.tex
Fixed tables, new images HD

@@
 \centering
-\includegraphics[width=0.7\columnwidth]{imagenes/koinet.png}
+\includegraphics[width=0.8\columnwidth]{imagenes/koinet.png}
 \caption{Observed minus calculated (O-C) diagram of the KOI-525b transit times, from the KOINet project.
@@
 Thus, for the future stage of the TraMoS project, archival data - collected since 2008 - will be combined with the upcoming TESS data and new ground-based observations using one-meter class telescopes.
+
+\section{WASP-18b}
+
+\begin{figure}[H]
+%\vspace{0.1cm}\hspace{0.2cm}
+\includegraphics[width=1.0\textwidth]{imagenes/WASP18_TTV.png}
+\caption{Observed minus calculated mid-transit times (TTV) for WASP-18b.
+The dashed black line corresponds to the proposed linear ephemeris, i.e.
+zero deviation from the predicted transit time  computed from our refined orbital period.
+For that, we considered 63 transit times from the TraMoS project (in light blue), published works and TESS (both in black).
+The grey area corresponds to the error propagation at $1\sigma$, where the quadratic trend looks almost horizontal.
+The RMS scatter from the linear ephemeris is 47 seconds.}
+\label{wasp18_ttv}
+\end{figure}
+
+\section{WASP-19b}
+
+\begin{figure}[H]
+%\vspace{0.1cm}\hspace{0.2cm}
+\includegraphics[width=1.0\textwidth]{imagenes/WASP19_TTV.png}
+\caption{Observed minus calculated mid-transit times (TTV) for WASP-19b.
+The dashed black line corresponds to the proposed linear ephemeris, i.e.
+zero deviation from the predicted transit time  computed from our refined orbital period.
+For that, we considered 87 transit times from the TraMoS project (in light blue), published works and TESS (both in black).
+The grey area corresponds to the error propagation at $1\sigma$, where the quadratic trend looks almost horizontal.
+The RMS scatter from the linear ephemeris is 65 seconds.}
+\label{wasp19_ttv}
+\end{figure}
+
+\section{WASP-77Ab}
+
+\section{WASP-36b}

### 2019-08-09 introduction.tex
Fixed tables, new images HD
All tables fixed

@@
 
-\section{Transiting Exoplanets}
-The Transit method is today the most successful technique to discover extrasolar planets (see Fig.~\ref{amount_exoplanet}).
-The Kepler mission was launched in 2009 and during its almost nine years of provided thousands of discoveries due to this method.
-
 \begin{figure}[H]
 \centering
-\includegraphics[width=0.7\columnwidth]{imagenes/exo_dischist_cumulative.png}
-\caption{Accumulative number of discovered exoplanets by year.}
-\label{amount_exoplanet}
+\includegraphics[width=1.0\columnwidth]{imagenes/exoplanets_hd.pdf}
+\caption{}
+\label{exoplanets}
 \end{figure}
 
-The light curve produced by a transit event provides important information of the planetary system.
-For example, it is the only way on which we can derived directly the proportion between the exoplanet and star radius.
-It can also give information about the impact parameter, and therefore, the inclination of the orbit.
+\section{This work}
 
-In Figure~\ref{transit} is described the architecture of a transiting exoplanet.
-Thanks to its geometry, the transit event as well as some parameters of the planetary system can be described with a few simple relations (cite Seager and Mallean y Winn).
-When the planet passes in front of its star produced a dimming in its flux called primary transit.
-The maximum drop during the transit event defines the transit depth $\Delta{F}$:
-
-\begin{equation}
-    \Delta{F} = \left(\frac{R_{p}}{R_{*}}\right)^2 
-\end{equation}
-
-Where $R_{p}$ and $R_{*}$ are the planet and star radius, respectively.
-The numbers 1, 2, 3 and 4 correspond to the contact times: $t_{1}$, $t_{2}$, $t_{3}$ and $t_{4}$.
-The total duration of the transit is $t_{T} = t_{4}-t_{1}$ and the full duration is $t_{F}=t_{3}-t_{2}$.
-The total duration of the transit can be also described considering planetary parameters such as the period $P$, semi-major axis $a$ and orbital inclination $i$:
-
-\begin{equation}
-    t_{T} = \frac{PR_{star}}{\pi a} \sqrt{\left(1+\frac{R_{p}}{R_{*}}\right)^2-\left(\frac{a\cos i}{R_{*}}\right)}
-\end{equation}
-
-The impact parameter $b$, is the sky-projected distance between the center of the star and the planet at conjunction:
-
-\begin{equation}
-    b = \frac{a\cos{i}}{R_{*}}\left(\frac{1-e^2}{1+e\sin{\omega}}\right)
-\label{impact_param}
-\end{equation}
-
-Where $\omega$ is the periastron longitude. In the case of circular orbits, the eccentricity is zero, thus Eq.~\ref{impact_param} is simplified to:
-
-\begin{equation}
-    b = \frac{a\cos{i}}{R_{*}}
-\label{impact_param_simple}
-\end{equation}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.8\columnwidth]{imagenes/transit.png}
-\caption{Architecture of a transiting exoplanet and the observed light curve.
-Based on the light curve itself it is possible to measure the transit depth $\Delta F$, the impact parameter $b$.
-From them, the planet-to-star radius ratio $R_{p}/R_{*}$ and the orbital inclination $i$ can be derived.
-Figure from The Handbook of Exoplanets by M.
-Perryman.}
-\label{transit}
-\end{figure}
-
-Depending on the orbital and physical parameters of the exoplanet, the shape of the observed light curve will vary.
-For example, Figure \ref{transit_examples} shows how the light curve reflects the configuration of the system.
-Hot Jupiters are the kind of planet easier to detect, since their planet-to-star radius ratio is larger.
-But an smaller planet orbiting a dwarf star could produce a similar ratio of the radius.
-In the other hand, exoplanets with larger orbital inclinations will produce shorter drops in the flux, in comparison with planets in the same orbital-plane with the host star.
-
-TO DO: Add studies about transmission spectroscopy.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.8\columnwidth]{imagenes/transit_examples.png}
-\caption{Examples of transiting exoplanets and how their light curves differ between them thanks to the physical properties of the exoplanet.}
-\label{transit_examples}
-\end{figure}
+This thesis is an extension of the Transit Monitoring in the South project (TraMoS, see Chapter\ref{chap:tramos}) started in 2008 by Sergio Hoyer and Patricio Rojo.
+I selected a new sample of transiting exoplanets, all of them hot Jupiters without any companions detected to date.

### 2019-08-09 paper.tex
All tables fixed

@@
 \hline 
+\endfirsthead
+\multicolumn{5}{c}
+{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
+\hline
+Parameter & Units & This work & \cite{Hellier2009} & \cite{Shporer2018} \\
+\hline
+\endhead
 Parameter & Units & This work & \cite{Hellier2009} & \cite{Shporer2018} \\
@@
 \begin{landscape}
+\begin{ThreePartTable}
+\begin{TableNotes}
+\item Values enclosed in parentheses correspond to the uncertainties of the last digits of the nominal value.
+\item[a] For comparison, the results from \cite{Hellier2009} that considered free eccentricity were used.
+\item[b] Values converted to cgs units multiplying by the Sun density $\rho_{\odot}=1.408\,$cgs.
+\item[c] Value converted to cgs units multiplying by the Jupiter density $\rho_{J}=1.33\,$cgs.
+\end{TableNotes}
 \begin{longtable}{llccc}
@@
 \hline 
-~~~Parameter & Units & This work & \cite{Hebb2010}\footnote{a} & \cite{Lendl2013}\\
+\endfirsthead
+\multicolumn{5}{c}
+{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
+\hline
+Parameter & Units & This work & \cite{Hebb2010}\tnote{a} & \cite{Lendl2013}\\
+\hline
+\endhead
+Parameter & Units & This work & \cite{Hebb2010}\tnote{a} & \cite{Lendl2013}\\
 \hline
@@
 ~~~~$L_*$\dotfill &Luminosity (\(L_\odot\))\dotfill &$0.905^{+0.071}_{-0.069}$\\
-~~~~$\rho_*$\dotfill &Density (cgs)\dotfill &$1.339^{+0.056}_{-0.058}$ & $1.19^{+0.12}_{-0.11}$\footnote{b}  & $1.384^{+0.055}_{-0.051}$\footnote{b}\\
+~~~~$\rho_*$\dotfill &Density (cgs)\dotfill &$1.339^{+0.056}_{-0.058}$ & $1.19^{+0.12}_{-0.11}$\tnote{b}  & $1.384^{+0.055}_{-0.051}$\tnote{b}\\
 ~~~~$\log{g}$\dotfill &Surface gravity (cgs)\dotfill &$4.417^{+0.020}_{-0.021}$ & $4.48\pm0.03$\\
@@
 ~~~~$\omega_*$\dotfill &Argument of Periastron (Degrees)\dotfill &$51^{+89}_{-190}$ & $-76^{+112}_{-23}$ & $43^{+28}_{-67}$\\
-~~~~$\rho_P$\dotfill &Density (cgs)\dotfill &$0.506^{+0.031}_{-0.030}$ & $0.54^{+0.07}_{-0.06}$& $0.595^{+0.036}_{-0.033}$\footnote{c}\\
+~~~~$\rho_P$\dotfill &Density (cgs)\dotfill &$0.506^{+0.031}_{-0.030}$ & $0.54^{+0.07}_{-0.06}$& $0.595^{+0.036}_{-0.033}$\tnote{c}\\
 ~~~~$logg_P$\dotfill &Surface gravity \dotfill &$3.155^{+0.018}_{-0.019}$ & $3.20\pm0.03$ & $3.184\pm0.015$\\
@@
 \hline
-%\end{tabular}
-%\tablefoot{
-%\tablefoottext{a}{For comparison, the results from \cite{Hellier2009} that considered free eccentricity were used.}
-%%\tablefoottext{b}{Values converted to cgs units multiplying by the Sun density $\rho_{\odot}=1.408\,$cgs.}
-%\tablefoottext{c}{Values converted to cgs units multiplying by the Jupiter density $\rho_{J}=1.33\,$cgs}
-%\tablefoottext{d}{Values enclosed in parentheses correspond to the uncertainties of the last digits of the nominal value.}}
+\insertTableNotes \\
 \end{longtable}
+\end{ThreePartTable}
 \end{landscape}
@@
 \begin{landscape}
+\begin{ThreePartTable}
+\begin{TableNotes}
+\item Values enclosed in parentheses correspond to the uncertainties of the last digits of the nominal value.
+\item[a] Values converted to cgs units multiplying by the Sun density $\rho_{\odot}=1.408\,$cgs.
+\item[b] Value converted to cgs units multiplying by the Jupiter density $\rho_{J}=1.33\,$cgs.
+\end{TableNotes}
 \begin{longtable}{llcc}
@@
 \hline 
-~~~~~Parameter & Units & This work & \cite{Maxted2013}\\
+\endfirsthead
+\multicolumn{4}{c}
+{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
+\hline
+Parameter & Units & This work & \cite{Maxted2013}\\
+\hline
+\endhead
+Parameter & Units & This work & \cite{Maxted2013}\\
 \hline
@@
 ~~~~$L_*$\dotfill &Luminosity (\(L_\odot\))\dotfill &$0.743^{+0.065}_{-0.058}$ & \\
-~~~~$\rho_*$\dotfill &Density (cgs)\dotfill &$1.692^{+0.056}_{-0.069}$\footnote{a} & $1.629^{+0.023}_{-0.028}$\footnote{a}\\
+~~~~$\rho_*$\dotfill &Density (cgs)\dotfill &$1.692^{+0.056}_{-0.069}$\tnote{a} & $1.629^{+0.023}_{-0.028}$\tnote{a}\\
 ~~~~$\log{g}$\dotfill &Surface gravity (cgs)\dotfill &$4.476^{+0.014}_{-0.015}$ & $4.33\pm0.08$\\
@@
 ~~~~$\omega_*$\dotfill &Argument of Periastron (Degrees)\dotfill &$-30^{+170}_{-120}$\\
-~~~~$\rho_P$\dotfill &Density (cgs)\dotfill &$1.240^{+0.060}_{-0.067}$ & $1.33\pm0.04$\footnote{b}\\
+~~~~$\rho_P$\dotfill &Density (cgs)\dotfill &$1.240^{+0.060}_{-0.067}$ & $1.33\pm0.04$\tnote{b}\\
 ~~~~$logg_P$\dotfill &Surface gravity \dotfill &$3.467^{+0.012}_{-0.015}$ & $3.441\pm0.008$\\
@@
 \hline
-%\end{tabular}
-%\tablefoot{
-%\tablefoottext{a}{Value converted to cgs units multiplying by the Sun density $\rho_{\odot}=1.408\,$cgs.}
-%\tablefoottext{b}{Value converted to cgs units multiplying by the Jupiter density $\rho_{J}=1.33\,$cgs.}
-%\tablefoottext{c}{Values enclosed in parentheses correspond to the uncertainties of the last digits of the nominal value.}
-%}
+\insertTableNotes \\
 \end{longtable}
+\end{ThreePartTable}
 \end{landscape}
@@
 
-\begin{table}[H]
+\begin{table}[ht]
+\centering
 %\tablewidth{0pt}
-\centering
+\begin{threeparttable}
 \caption{Transit mid-times for WASP-18b}
@@
 \end{tabular}
-%\tablebib{(1)~\citet{Hellier2009};
-%(2) \citet{Triaud2010}; (3) \citet{Maxted2013}.}
+\begin{tablenotes}
+\item \textbf{References:} 
+(1) \cite{Hellier2009}; 
+ (2) \cite{Triaud2010}; 
+ (3) \cite{Maxted2013}
+\end{tablenotes}
+\end{threeparttable}
 \end{table}
@@
 
+\begin{ThreePartTable}
+\begin{TableNotes}
+\item \textbf{References:} (1) \citet{Hebb2010}; (2) \citet{Anderson2010}; (3) \citet{Lendl2013}; (4) Exoplanet Transit Database (ETD) \url{var2.astro.cz/ETD}; (5) \citet{Tregloan2013}; (6) \citet{Mancini2013}; (7) \citet{Bean2013}; (8) \citet{Sedaghati2015}.
+\end{TableNotes}
 \begin{longtable}{cccc}
@@
 \hline \hline
+\endfirsthead
+\multicolumn{4}{c}
+{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
+\hline
+Epoch & Transit mid-time & TTV & References\\
+      & (${\rm BJD_{TDB}}$) & (min) &  \\
+\hline
+\endhead
 Epoch & Transit mid-time & TTV & References\\
@@
 \hline
-%\end{tabular}
-%\tablebib{(1)~\citet{Hebb2010};
-%(2) \citet{Anderson2010}; (3) \citet{Lendl2013}; (4) Exoplanet Transit Database (ETD) \url{var2.astro.cz/ETD}; (5) \citet{Tregloan2013}; (6) \citet{Mancini2013}; (7) \citet{Bean2013}; (8) \citet{Sedaghati2015}.}
+\insertTableNotes \\
 \end{longtable}
+\end{ThreePartTable}
 
@@
 
-\begin{table}
+\begin{table}[ht]
+\centering
+\begin{threeparttable}
 \caption{Transit mid-times for WASP-77Ab}
 \label{times_wasp77}
-\centering
 \begin{tabular}{cccc}
@@
 -845 & $2456271.65888$ & $-2.0\pm1.4$ & 2 \\
--659 & $2456524.62617$ & $0.8\pm1.8$ & This work\footnote{a} \\
--606 & $2456596.70591$ & $-1.7\pm1.5$  & This work\footnote{a}  \\
+-659 & $2456524.62617$ & $0.8\pm1.8$ & This work\tnote{a} \\
+-606 & $2456596.70591$ & $-1.7\pm1.5$  & This work\tnote{a}  \\
 -92 & $2457295.7626$  & $1.2\pm1.3$& This work \\
@@
 175 & $2457658.88744$ & $-2.8\pm1.5$ & This work\\
-177 & $2457661.60987$   & $0.6\pm1.7$ & This work\footnote{a} \\
+177 & $2457661.60987$   & $0.6\pm1.7$ & This work\tnote{a} \\
 183 & $2457669.77054$ &  $1.4\pm1.4$  & This work  \\
-229 & $2457732.33382$ & $4.2\pm1.4$& This work\footnote{a} \\
+229 & $2457732.33382$ & $4.2\pm1.4$& This work\tnote{a} \\
 447 & $2458028.8159$  & $-1.8\pm6.5$ & This work\\ 
@@
 \end{tabular}
-%\tablebib{(1) \citet{Maxted2013}; (2) \cite{Turner2016}.}
-%\tablefoot{
-%\tablefoottext{a}{From the Exoplanet Transit Database (ETD)  \url{var2.astro.cz/ETD}}}
+\begin{tablenotes}
+\item \textbf{References:} (1) \citet{Maxted2013}; (2) \cite{Turner2016}.
+\item[a] From the Exoplanet Transit Database (ETD)  \url{var2.astro.cz/ETD}
+\end{tablenotes}
+\end{threeparttable}
 \end{table}
 
-\subsection{Limits on an Additional Perturber\footnote{This section was done by Tobias C. Hinse and it is added for completeness of the study.}}\label{addper}
+\subsection{Limits on an Additional Perturber}\label{addper}
 %Comments: Do not delete
@@
 
-\begin{table}
+\begin{table}[ht]
+\centering
+\begin{threeparttable}
 \caption{Approximate upper mass limits of a putative perturber in various orbital resonances for each system}
 \label{masstable}
-\centering
 \begin{tabular}{cccc}
@@
 \hline
-1:3 & 1.9    & 500\footnote{b} & 1.0 \\
+1:3 & 1.9    & 500\tnote{b} & 1.0 \\
 2:5 & 4.0    & -   & -   \\
-1:2 & 5.0\footnote{a} & 2.0 & 3.5 \\
+1:2 & 5.0\tnote{a} & 2.0 & 3.5 \\
 3:5 & -      & -      & 2.0 \\
-2:3 & -      & -      & 7.0\footnote{a} \\
+2:3 & -      & -      & 7.0\tnote{a} \\
 5:3 & -      & 6.0    & 6.0   \\
 7:4 & -      & -      & 10.0 \\
-2:1 & 25\footnote{a}    & 0.9    & 3.5 \\
-7:3 & 80.0\footnote{c}   & -      & -   \\
+2:1 & 25\tnote{a}    & 0.9    & 3.5 \\
+7:3 & 80.0\tnote{c}   & -      & -   \\
 5:2 & 10.0   & 3.0    & -   \\
 3:1 & 7.0    & 2.0    & 4.5 \\
-17:5 & 500.0\footnote{d} & -      & -    \\
-4:1 & 50.0   & 100.0\footnote{e}  & 60.0\footnote{f} \\
+17:5 & 500.0\tnote{d} & -      & -    \\
+4:1 & 50.0   & 100.0\tnote{e}  & 60.0\tnote{f} \\
 \hline
 \end{tabular}
-%\tablefoot{
-%\tablefoottext{a}{Very close to the general instability area.}
-%\tablefoottext{b}{This value is constraint by RV limit of 17.8 $[M_{\oplus}]$}
-%\tablefoottext{c}{This value is constraint by RV limit of 74.6 $[M_{\oplus}]$}
-%\tablefoottext{d}{This value is constraint by RV limit of 82.8 $[M_{\oplus}]$}
-%\tablefoottext{e}{This value is constraint by RV limit of 40.8 $[M_{\oplus}]$}
-%\tablefoottext{f}{This value is constraint by RV limit of 30.8 $[M_{\oplus}]$}}
+\begin{tablenotes}
+\item[a] Very close to the general instability area.
+\item[b] Constraint by RV limit of 17.8 $[M_{\oplus}]$
+\item[c] Constraint by RV limit of 74.6 $[M_{\oplus}]$
+\item[d] Constraint by RV limit of 82.8 $[M_{\oplus}]$
+\item[e] Constraint by RV limit of 40.8 $[M_{\oplus}]$
+\item[f] Constraint by RV limit of 30.8 $[M_{\oplus}]$
+\end{tablenotes}
+\end{threeparttable}
 \end{table}
@@
 \subsubsection{WASP-18b}
-For the WASP-18b system we find a large region of instability when
-compared to the other two systems with the boundaries at the 1:2 interior
-and 2:1 exterior mean-motion resonance. By over-plotting the RMS scatter
-of mid-transit times ($\rm TTV_{\rm RMS}$) for a certain value, we find
-that the TTVs are relatively more sensitive at orbital architectures
-involving mean-motion resonances confirming the results by
-\citet{Agol2005} and \citet{Holman2005}. This also applies to WASP-19 and
-WASP-77A.
+For the WASP-18b system we find a large region of instability when compared to the other two systems with the boundaries at the 1:2 interior and 2:1 exterior mean-motion resonance.
+By over-plotting the RMS scatter of mid-transit times ($\rm TTV_{\rm RMS}$) for a certain value, we find that the TTVs are relatively more sensitive at orbital architectures involving mean-motion resonances confirming the results by \citet{Agol2005} and \citet{Holman2005}.
+This also applies to WASP-19 and WASP-77A.
 
@@
 
-\subsection{TTV period search\footnote{This section was done by Tobias C. Hinse and it is added for completeness of the study.}}
+\subsection{TTV period search}
 

### 2019-08-09 tramos.tex
Fixed tables, new images HD
All tables fixed

@@
 In summary, a possible orbital decay of WASP-43b \citep{Hoyer2016b} and OGLE-TR-113b \citep{Hoyer2016} was ruled out, and no significant TTV signal was detected in WASP-4b \citep{Hoyer2012} and WASP-5b \citep{Hoyer2013}.
+
+\section{Transiting Exoplanets}
+The Transit method is today the most successful technique to discover extrasolar planets (see Fig.~\ref{amount_exoplanet}).
+The Kepler mission was launched in 2009 and during its almost nine years of provided thousands of discoveries due to this method.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\columnwidth]{imagenes/exo_dischist_cumulative.png}
+\caption{Accumulative number of discovered exoplanets by year.}
+\label{amount_exoplanet}
+\end{figure}
+
+The light curve produced by a transit event provides important information of the planetary system.
+For example, it is the only way on which we can derived directly the proportion between the exoplanet and star radius.
+It can also give information about the impact parameter, and therefore, the inclination of the orbit.
+
+In Figure~\ref{transit} is described the architecture of a transiting exoplanet.
+Thanks to its geometry, the transit event as well as some parameters of the planetary system can be described with a few simple relations (cite Seager and Mallean y Winn).
+When the planet passes in front of its star produced a dimming in its flux called primary transit.
+The maximum drop during the transit event defines the transit depth $\Delta{F}$:
+
+\begin{equation}
+    \Delta{F} = \left(\frac{R_{p}}{R_{*}}\right)^2 
+\end{equation}
+
+Where $R_{p}$ and $R_{*}$ are the planet and star radius, respectively.
+The numbers 1, 2, 3 and 4 correspond to the contact times: $t_{1}$, $t_{2}$, $t_{3}$ and $t_{4}$.
+The total duration of the transit is $t_{T} = t_{4}-t_{1}$ and the full duration is $t_{F}=t_{3}-t_{2}$.
+The total duration of the transit can be also described considering planetary parameters such as the period $P$, semi-major axis $a$ and orbital inclination $i$:
+
+\begin{equation}
+    t_{T} = \frac{PR_{*}}{\pi a} \sqrt{\left(1+\frac{R_{p}}{R_{*}}\right)^2-\left(\frac{a\cos i}{R_{*}}\right)}
+\end{equation}
+
+The impact parameter $b$, is the sky-projected distance between the center of the star and the planet at conjunction:
+
+\begin{equation}
+    b = \frac{a\cos{i}}{R_{*}}\left(\frac{1-e^2}{1+e\sin{\omega}}\right)
+\label{impact_param}
+\end{equation}
+
+Where $\omega$ is the periastron longitude. In the case of circular orbits, the eccentricity is zero, thus Eq.~\ref{impact_param} is simplified to:
+
+\begin{equation}
+    b = \frac{a\cos{i}}{R_{*}}
+\label{impact_param_simple}
+\end{equation}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=1.0\columnwidth]{imagenes/transit_architecture.pdf}
+\caption{Architecture of a transiting exoplanet and the observed light curve.
+Based on the light curve itself it is possible to measure the transit depth $\Delta F$, the impact parameter $b$.
+From them, the planet-to-star radius ratio $R_{p}/R_{*}$ and the orbital inclination $i$ can be derived.
+Figure from The Handbook of Exoplanets by M.
+Perryman.}
+\label{transit}
+\end{figure}
+
+Depending on the orbital and physical parameters of the exoplanet, the shape of the observed light curve will vary.
+For example, Figure \ref{transit_examples} shows how the light curve reflects the configuration of the system.
+Hot Jupiters are the kind of planet easier to detect, since their planet-to-star radius ratio is larger.
+But an smaller planet orbiting a dwarf star could produce a similar ratio of the radius.
+In the other hand, exoplanets with larger orbital inclinations will produce shorter drops in the flux, in comparison with planets in the same orbital-plane with the host star.
+
+TO DO: Add studies about transmission spectroscopy.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\columnwidth]{imagenes/transit_example.pdf}
+\caption{Examples of transiting exoplanets and how their light curves differ between them thanks to the physical properties of the exoplanet.}
+\label{transit_examples}
+\end{figure}
 
@@
 The no detection of TTV is also important: architecture of the system.
-
-\section{This work}
-
-This thesis is an extension of the Transit Monitoring in the South project (TraMoS, see Chapter\ref{chap:tramos}) started in 2008 by Sergio Hoyer and Patricio Rojo.
-I selected a new sample of transiting exoplanets, all of them hot Jupiters without any companions detected to date.

### 2019-08-09 introduction.tex
More writting in Intro and TraMoS

@@
 \includegraphics[width=1.0\columnwidth]{imagenes/exoplanets_hd.pdf}
-\caption{}
+\caption{Mass and orbital period distribution of Exoplanets, and their corresponding discovery methods in color. In this plot are shown only the exoplanets with known masses}
 \label{exoplanets}
@@
 I selected a new sample of transiting exoplanets, all of them hot Jupiters without any companions detected to date.
+I analized 22 new light curves of the hot Jupiters WASP-18b, WASP-19b, and WASP-77Ab searching for periodic variations in the transit time (TTV) that could suggest the presence of additional bodies in their systems.
+
+This thesis is organized as follows: Chapter \ref{chap:tramos} summarizes the TraMoS project, its goals, techniques and achievements to date.
+Also, this chapter includes what we can learn from transit exoplanets' light curves and Transit Timing Variations.
+Chapter \ref{chap:paper} shows the analysis and results of the hot Jupiters WASP-18b, WASP-19b and WASP-77Ab, including  their observations and data reduction, light curve and RV analysis, measurements of TTVs and upper mass limit for possible companions in their systems.
+Then, Chapter\ref{chap:tess}  recapitulates the current stage of the TraMoS project on which TESS data is being incorporated.
+Here, I re-analyze the TTV curves of the previous targets WASP-18b, WASP-19b, and WASP-77Ab with new light curves from TESS and also, the preliminary results of WASP-36b are shown.
+Finally, Chapter \ref{chap:conclusion} contains the principal conclusions of this thesis as well as some ideas for future work.

### 2019-08-09 tramos.tex
More writting in Intro and TraMoS

@@
 
-TO DO: Add studies about transmission spectroscopy.
-
 \begin{figure}[H]
@@
 Since the discovery of the first exoplanet, one of the principal questions that arose was: are they alone in their systems?
-The idea of multiplanetary system is a consequence of our knowledge about the planetary system where we live in, and until today the Solar System has the larger number of orbiting planets.
+The idea of multiplanetary systems is a consequence of our knowledge about the planetary system where we live in, and until today the Solar System has the larger number of orbiting planets.
 Besides the Solar System, Kepler-90 has the same number of confirmed exoplanets: eight.
@@
 \cite{Holman2010} presented the first multiplanetary system confirmed using the TTV method: Kepler-9b and Kepler-9c.
+This two Saturn-size planets are in near 2:1 orbital resonance with periods of 19.2 and 38.9 days.
 

### 2019-08-11 tramos.tex
New references in TraMoS chapter

@@
 
-\cite{Holman2010} presented the first multiplanetary system confirmed using the TTV method: Kepler-9b and Kepler-9c.
-This two Saturn-size planets are in near 2:1 orbital resonance with periods of 19.2 and 38.9 days.
+\cite{Holman2010} presented the first multiplanetary system confirmed using the TTV method: two planets orbiting Kepler-9, a Sun-like star.
+These two Saturn-size planets are in near 2:1 orbital resonance with periods of 38.9 and 19.2 days.
+In order to model the dynamical interaction of the system, only 9 transits of Kepler-9b and 6 from Kepler-9c were required.
+This confirmed the effectiveness of the TTV method to characterize planetary systems with a scarce number of transits.
+
+Since the discovery of \cite{Holman2010}, around 20 exoplanets have been discovered and characterized thanks to the measurement of variations on their transit times and the following proper dynamical modelling of the system.
+Most of them are Kepler systems because of its high duty-cycle, on which it provided years on transits data.
+Kepler stopped working on 2018, but the Transit Exoplanet Satellite Survey (TESS) is currently providing its first results providing planetary systems showing TTVs.
+For example, two exoplanets (possibly one Jupiter and a sub-Saturn like) were recently discovered by \cite{Dawson2019} orbiting TOI-216, in near 2:1 resonance.
 

### 2019-08-13 tess.tex
More writting in TESS and TRAMOS chapter

@@
 
+In the following subsections, I present a re-analisys of the TTV curves of the hot Jupiters: WASP-18b, WASP-19b and WASP-77Ab including new transit times from TESS: 45, 28, and 15 for WASP-18b, WASP-19b and WASP-77Ab respectively.
+TESS data are reduced by the Science Processing Operations Center (SPOC) and after being processed, they are archived in the Mikulski Archive for Space Telescopes (MAST) catalogue, where can be download directly.
+
+In order to compute the transit time of each light curve, I used EXOFASTv2 but only to fit the transit time.
+The remaining planetary parameters were fixed with the values from Tables \ref{tab:wasp18}, \ref{tab:wasp19}, \ref{tab:wasp77}.
+
 \section{WASP-18b}
+
+The star WASP-18 was observed continuously during Sector 2 and 3 of the TESS mission, between August 22nd and October 18th, 2018.
+Theses observations provided 47 transits events of WASP-18b, but only 45 of them were complete transits, and then included into the TTV analysis.
+Figure \ref{wasp18_ttv} shows the
 

### 2019-08-13 tramos.tex
More writting in TESS and TRAMOS chapter

@@
 
-Since the discovery of \cite{Holman2010}, around 20 exoplanets have been discovered and characterized thanks to the measurement of variations on their transit times and the following proper dynamical modelling of the system.
+Since the discovery of \cite{Holman2010}, around 20 exoplanets have been discovered and characterized thanks to the measurement of variations on their transit times and the following proper dynamical model ling of the system.
 Most of them are Kepler systems because of its high duty-cycle, on which it provided years on transits data.
@@
 
+To date, only two hot Jupiters have been found to show TTV signals due to the presence of additional companions on their systems: WASP-47b \citep{Becker2015} and Kepler-730b \citep{Canas2019}, even though the TTV was proposed as a technique to search for additional companions of gas giants.
+The lack of observed companions in hot Jupiter systems could provide crucial information about planetary formation processes.
+
+Trough the TTV method not only the transiting exoplanet is being studied but the whole planetary system.
+Even the lack of variation in the transit timing gives clues related to the formation of close-in gas giant.
+
 The no detection of TTV is also important: architecture of the system.

### 2019-08-13 tess.tex
TESS blablabla

@@
 The Kepler Object of Interest Network (KOINet: \citep{vonEssen2018,Freuddenthal2018}) in the Northern hemisphere, is a network of ground-based telescopes performing photometric follow-up of KOIs to continue what Kepler left undone.
-The main goal of KOINet is to combine Kepler data with ground-based observations in order to confirm and characterise the masses of exoplanet candidates using TTVs.
+The main goal of KOINet is to combine Kepler data with ground-based observations in order to confirm and characterize the masses of exoplanet candidates using TTVs.
 
@@
 During the $\sim27$ days of each sector, many candidates will not be observed enough time to confirm and characterize them.
-However, this special feature will provide a huge amount of new transit events of already known transiting exoplanets.
+However, this special feature will provide a huge amount of new transit events of already known transiting exoplanets, specially for those with short-period.
 Combining the new TESS data with ground-base follow- up observations, many possible TTVs could be confirm or rule out.
@@
 
+Between Sector 1 and Sector 13, TESS observed around 15\% of stars with confirmed exoplanets but not all of them will produce a transit event within the 27 days of a sector duration (see Figure \ref{chap:tess}).
+Anyway, several complete light curves could be obtain and analyzed.
+TESS data are reduced by the Science Processing Operations Center (SPOC) and after being processed, they are archived in the Mikulski Archive for Space Telescopes (MAST) catalogue, where can be download directly by anyone.
+
+\begin{figure}
+\centering
+\includegraphics[width=1.0\columnwidth]{imagenes/tess_match.pdf}
+\caption{Match between all the stars with confirmed exoplanets and the TESS targets from Sector 1 to Sector 13.
+The empty red circles correspond to the star with confirmed exoplanets distributed by its position in the sky while the filled red circles indicate if the exoplanet has an orbital period of less than 27 days, which is the duration of one TESS sector.
+The black cross indicates which star was already observed by TESS.
+However, this does not indicate that transit light curves will be provided for sure since the orbital period of the exoplanet needs to be taken into account.
+Thus, TESS will only provide transit data of the filled red circle with a black cross exoplanets.}
+\label{match_tess}
+\end{figure}
+
 Thus, for the future stage of the TraMoS project, archival data - collected since 2008 - will be combined with the upcoming TESS data and new ground-based observations using one-meter class telescopes.
+As in the KOINet project, TESS will supply with consecutive transit light curves from southern targets - during its first year of mission - that will contribute to complete TTV curve specially for short-period planets, such as hot Jupiters.
 
 In the following subsections, I present a re-analisys of the TTV curves of the hot Jupiters: WASP-18b, WASP-19b and WASP-77Ab including new transit times from TESS: 45, 28, and 15 for WASP-18b, WASP-19b and WASP-77Ab respectively.
-TESS data are reduced by the Science Processing Operations Center (SPOC) and after being processed, they are archived in the Mikulski Archive for Space Telescopes (MAST) catalogue, where can be download directly.
 
 In order to compute the transit time of each light curve, I used EXOFASTv2 but only to fit the transit time.
-The remaining planetary parameters were fixed with the values from Tables \ref{tab:wasp18}, \ref{tab:wasp19}, \ref{tab:wasp77}.
+The remaining planetary parameters were fixed with the values from Tables \ref{wasp18}, \ref{tab:wasp19}, \ref{tab:wasp77}.
 
@@
 Theses observations provided 47 transits events of WASP-18b, but only 45 of them were complete transits, and then included into the TTV analysis.
-Figure \ref{wasp18_ttv} shows the
 
-\begin{figure}[H]
+The new best linear fit for the period considering the 63 transit times is:
+
+\begin{equation}
+P = 0.941452232 \pm 2.7\times10^{-8} ~\rm days
+\end{equation}
+
+This value differs from the previous reported in Eq.~\ref{eq1_w18} by $0.016$ seconds, and the error was reduced to a third.
+
+Figure \ref{wasp18_ttv} shows the extension of the TTV curve of WASP-18b considering the new data from TESS.
+Including these new transit times, the scatter from the linear ephemeris was reduced to 47 seconds.
+A possible second order fit - of a hypothetical orbital decay - has a reduced chi squared of $\chi^{2}_{red}=0.18$, while the linear fit - which corresponds to the linear ephemeris - has $\chi^{2}_{red}=0.19$.
+Furthermore, there is no strong evidence for an orbital decay in this system.
+
+Considering the lack of a clear sinusoidal TTV signal with even more transit time data, suggest that this exoplanet does not have a close-in companion.
+Moreover, the existence of a possible far-out companion is rejected by the lack of an additional signal in RV data.
+With this study, I can not discard the presence of any companion of WASP-18b but if there is one, it should be small.
+
+\begin{figure}[h]
 %\vspace{0.1cm}\hspace{0.2cm}
@@
 For that, we considered 63 transit times from the TraMoS project (in light blue), published works and TESS (both in black).
-The grey area corresponds to the error propagation at $1\sigma$, where the quadratic trend looks almost horizontal.
+The grey area corresponds to the error propagation at $1\sigma$.
 The RMS scatter from the linear ephemeris is 47 seconds.}
@@
 \section{WASP-19b}
+
+WASP-19 was observed during Sector 9 between February 28th and March 26th, 2019.
+During this time, 29 complete transit event were provided, and then considered to compute the new TTVs of WASP-19b.
+The new best fit for the orbital period P, considering the total of 88 transit times is:
+
+\begin{equation}
+P = 0.788838940 \pm 3.0\times10^{-8} ~\rm days
+\end{equation}
+
+The previous reported value in Eq.~\ref{eq1_wasp19} is $0.007$ seconds larger.
+
+As in the case of WASP-18b, the TTV scatter of WASP-19b was reduced when including new transit times data from TESS: $TTV_{RMS}=65~\rm seconds$.
+Again, a second order fit is not better that the linear one: $\chi^{2}_{red,lineal}= XXX$ and $\chi^{2}_{red,cuad}= XXX$.
 
@@
 For that, we considered 87 transit times from the TraMoS project (in light blue), published works and TESS (both in black).
-The grey area corresponds to the error propagation at $1\sigma$, where the quadratic trend looks almost horizontal.
+The grey area corresponds to the error propagation at $1\sigma$.
 The RMS scatter from the linear ephemeris is 65 seconds.}

### 2019-08-14 tess.tex
WASP-77 started

@@
 
-Between Sector 1 and Sector 13, TESS observed around 15\% of stars with confirmed exoplanets but not all of them will produce a transit event within the 27 days of a sector duration (see Figure \ref{chap:tess}).
+Between Sector 1 and Sector 13, TESS observed around 15\% of the stars with confirmed exoplanets but not all of them will produce a transit event within the 27 days of a sector duration (see Figure \ref{chap:tess}).
 Anyway, several complete light curves could be obtain and analyzed.
-TESS data are reduced by the Science Processing Operations Center (SPOC) and after being processed, they are archived in the Mikulski Archive for Space Telescopes (MAST) catalogue, where can be download directly by anyone.
+TESS data are reduced by the Science Processing Operations Center (SPOC) and after being processed, they are archived in the Mikulski Archive for Space Telescopes (MAST) catalogue, where can be downloaded directly by anyone.
 
@@
 However, this does not indicate that transit light curves will be provided for sure since the orbital period of the exoplanet needs to be taken into account.
-Thus, TESS will only provide transit data of the filled red circle with a black cross exoplanets.}
+Thus, the first year mission of TESS will provide for sure transit data of the exoplanets with filled red circle and a black cross .}
 \label{match_tess}
@@
 
-Thus, for the future stage of the TraMoS project, archival data - collected since 2008 - will be combined with the upcoming TESS data and new ground-based observations using one-meter class telescopes.
-As in the KOINet project, TESS will supply with consecutive transit light curves from southern targets - during its first year of mission - that will contribute to complete TTV curve specially for short-period planets, such as hot Jupiters.
+Thus, for the currently and future stage of the TraMoS project, archival data - collected since 2008 - will be combined with the upcoming TESS data and new ground-based observations using one-meter class telescopes.
+The main goal of the project will remain the same: refine orbital and physical parameters of exoplanetary system and search for variations in the transit time, that could suggest the presence of additional small bodies in the system.
+The KOINet project proved that ground-based follow-up are, in some cases, are essential to complete a possible TTV signal, and therefore, to confirm or rule out variations in the transit time.
+During its first year of mission, TESS will supply with consecutive transit light curves from southern targets, specially from short-period planets, such as hot Jupiters.
+This special feature is fundamental to construct TTV curves and then, complete them from ground-based follow-up.
 
 In the following subsections, I present a re-analisys of the TTV curves of the hot Jupiters: WASP-18b, WASP-19b and WASP-77Ab including new transit times from TESS: 45, 28, and 15 for WASP-18b, WASP-19b and WASP-77Ab respectively.
-
-In order to compute the transit time of each light curve, I used EXOFASTv2 but only to fit the transit time.
+In order to compute the transit time of each light curve, I used EXOFASTv2 but only to fit the transit time and the flux baseline.
 The remaining planetary parameters were fixed with the values from Tables \ref{wasp18}, \ref{tab:wasp19}, \ref{tab:wasp77}.
@@
 The star WASP-18 was observed continuously during Sector 2 and 3 of the TESS mission, between August 22nd and October 18th, 2018.
-Theses observations provided 47 transits events of WASP-18b, but only 45 of them were complete transits, and then included into the TTV analysis.
+Theses observations provided 47 transits events of WASP-18b, but only 45 of them were complete transits, and therefore included into the TTV analysis.
 
-The new best linear fit for the period considering the 63 transit times is:
+The new best linear fit for the period considering a total of 63 transit times is:
 
@@
 Including these new transit times, the scatter from the linear ephemeris was reduced to 47 seconds.
-A possible second order fit - of a hypothetical orbital decay - has a reduced chi squared of $\chi^{2}_{red}=0.18$, while the linear fit - which corresponds to the linear ephemeris - has $\chi^{2}_{red}=0.19$.
-Furthermore, there is no strong evidence for an orbital decay in this system.
+A possible second order fit of a hypothetical orbital decay, has a reduced chi squared of $\chi^{2}_{red}=0.18$, while the linear fit - which corresponds to the linear ephemeris - has $\chi^{2}_{red}=0.19$.
+Furthermore, there is no strong evidence for an orbital decay in this system as proposed by \cite{Wilkins2017}
 
-Considering the lack of a clear sinusoidal TTV signal with even more transit time data, suggest that this exoplanet does not have a close-in companion.
+Considering the lack of a clear sinusoidal TTV signal with even more transit time data, suggest that this exoplanet does not have a close-in companion in MMR.
 Moreover, the existence of a possible far-out companion is rejected by the lack of an additional signal in RV data.
-With this study, I can not discard the presence of any companion of WASP-18b but if there is one, it should be small.
+With this study, I can not discard the presence of any kind of companion of WASP-18b but if there is one, it should be small.
 
@@
 During this time, 29 complete transit event were provided, and then considered to compute the new TTVs of WASP-19b.
-The new best fit for the orbital period P, considering the total of 88 transit times is:
+The new best fit for the orbital period P, considering a total of 88 transit times is:
 
@@
 
-As in the case of WASP-18b, the TTV scatter of WASP-19b was reduced when including new transit times data from TESS: $TTV_{RMS}=65~\rm seconds$.
+As in the case of WASP-18b, the TTV scatter of WASP-19b was reduced when including new transit times data from TESS to: $TTV_{RMS}=65~\rm seconds$.
 Again, a second order fit is not better that the linear one: $\chi^{2}_{red,lineal}= XXX$ and $\chi^{2}_{red,cuad}= XXX$.
 
-\begin{figure}[H]
+\begin{figure}[ht]
 %\vspace{0.1cm}\hspace{0.2cm}
@@
 
+The third target presented in Cortés-Zuleta et al.
+2019 (submitted), was observed in Sector 4 between October 18th and November 15th, 2018.
+During this time, the planet transited its host star 17 times, but only 15 were complete light curves.
+From the previous study presented in this thesis, WASP-77Ab was the most interesting target, since its variation from the linear ephemeris was around  $121\,\rm seconds$.
+After including the new transit times, the best linear fit for the orbital period is:
+
 \section{WASP-36b}

### 2019-08-16 pipeline.tex
Appendix of the pipeline

\chapter{Aperture photometry pipeline}\label{chap:pipeline}

Since the beginning of the TraMoS project, an aperture photometry pipeline has been in development, on which several graduate and undergraduates students worked and are currently working on it. This pipeline is Python-based and includes standard procedures of reduction, calibrations and aperture photometry, including bias and flat field corrections. The user needs to give the coordinates of the target and reference stars and a range of pixels for a possible aperture. Then, in order to produce high-precision light curves of the target and reference stars, the pipeline semi-automatic finds the best aperture and ring size, for the sky that produces the less RMS in the light curves.

The pipeline works with a specific directories' structure where all the needed information should be:
\begin{itemize}
\item raw: Folder containing the raw data of the observations. It could be fits files or compressed fits (e.g \textit{fit.ZIP}.
\item calib: This folder should include the flats -- sky or dome -- and bias files.
\item data: Empty folder which will contain the output data after the aperture photometry procedure.
\item figures: Empty folder on which all the figures generated in the reduction process will be store.
\item log: Folder containing the Python script to run the pipeline for the specific data set.
\item extraction.tex: Latex file which generates the PDF file with all the important information related to the aperture photometry procedure process, such as images of the stamps, radial profile of the target star, FWHM plots, preview of the light curve, etc.
\item tramos\_custom.sty: Customizable file containing the information related to the telescope, target's name, filter, date of the observation, RA, DEC and target's magnitude. When the pipeline finishes, it fills this file with the best aperture size obtained.
\end{itemize}

I have implemented dictionaries to ease the use of the pipeline with different telescopes. One of the biggest problems that I faced when I started reducing data, was the distinctness between the headers produced from different telescopes. For exmaple, while some of them recorded the type of filter as \textit{FILTER}, other use could use \textit{FILTERB}. Also, as the TraMoS project has been collecting data since more than 10 year ago, some of our used telescopes were updated with new CCDs, producing that the pipeline were not longer functional. Currently, the pipeline works with data from the following telescopes: 
\begin{itemize}
\item La Silla Observatory: Danish 1.54 m (previous and after 2017) and REM.
\item Cerro Tololo Inter-American Observatory: SMARTS 0.9 m and 1 m.
\item Las Campanas Observatory: Warsaw, Swope, Du Pont.
\item Cerro Pachón: SOAR
\end{itemize}

In the sections ahead, I present the scripts for performing aperture photometry with the TraMoS pipeline of the targets studied in this thesis, following with an example of the PDF generated by the pipeline, containing all the relevant information of the procedure.

\section{Reduction script of WASP-18, WASP-19 and WASP-77A}

\section{Example of }

### 2019-08-16 tess.tex
Finished TESS Chapter

@@
 Including these new transit times, the scatter from the linear ephemeris was reduced to 47 seconds.
-A possible second order fit of a hypothetical orbital decay, has a reduced chi squared of $\chi^{2}_{red}=0.18$, while the linear fit - which corresponds to the linear ephemeris - has $\chi^{2}_{red}=0.19$.
-Furthermore, there is no strong evidence for an orbital decay in this system as proposed by \cite{Wilkins2017}
+A possible second order fit of a hypothetical orbital decay, has a reduced chi squared of $\chi^{2}_{red}=0.35$, while the linear fit - which corresponds to the linear ephemeris - has $\chi^{2}_{red}=0.36$.
+Furthermore, as there is no strong evidence for an orbital decay in this system as proposed by \cite{Wilkins2017}, the simpler model should be chosen: the linear model.
 
@@
 %\vspace{0.1cm}\hspace{0.2cm}
-\includegraphics[width=1.0\textwidth]{imagenes/WASP18_TTV.png}
+\includegraphics[width=1.0\textwidth]{imagenes/WASP18_TTV.pdf}
 \caption{Observed minus calculated mid-transit times (TTV) for WASP-18b.
@@
 WASP-19 was observed during Sector 9 between February 28th and March 26th, 2019.
-During this time, 29 complete transit event were provided, and then considered to compute the new TTVs of WASP-19b.
+During this time, 29 complete transit event were provided, and then considered to compute the new TTVs of WASP-19b show in Figure \ref{wasp19_ttv}.
 The new best fit for the orbital period P, considering a total of 88 transit times is:
@@
 As in the case of WASP-18b, the TTV scatter of WASP-19b was reduced when including new transit times data from TESS to: $TTV_{RMS}=65~\rm seconds$.
-Again, a second order fit is not better that the linear one: $\chi^{2}_{red,lineal}= XXX$ and $\chi^{2}_{red,cuad}= XXX$.
+Again, a second order fit is not better that the linear one: $\chi^{2}_{red,lineal}= 0.65$ and $\chi^{2}_{red,cuad}= 0.64$.
 
@@
 %\vspace{0.1cm}\hspace{0.2cm}
-\includegraphics[width=1.0\textwidth]{imagenes/WASP19_TTV.png}
+\includegraphics[width=1.0\textwidth]{imagenes/WASP19_TTV.pdf}
 \caption{Observed minus calculated mid-transit times (TTV) for WASP-19b.
@@
 
+\begin{equation}
+P = 1.36002866 \pm 1.7\times10^{-7} ~\rm days
+\end{equation}
+
+In Eq.~\ref{eq1_w77}, the value for the orbital period P is $0.01\,\rm seconds$ lower, and the scatter from the linear ephemeris was reduced to 86 seconds.
+The linear fit has a reduced chi squared of $\chi^2_{red}=1.03$, while a second degree polynomial has $\chi^2_{red}=0.72$.
+Anyway, the second order fit is highly dominated by the outlier transit time of epoch $229$ (see Figure \ref{wasp77_ttv}).
+After removing it, the reduced chi squared is  $\chi^2_{red}=0.37$.
+In all cases, the best fit correspond to the linear ephemeris.
+
+As the previous two targets, extending the TTV curve of WASP-77Ab with transit times from TESS light curve supported the conclusion from the previous study: there is not a clear sinusoidal signal in the variations of the transit times, that could suggest a periodic TTV in WASP-77Ab.
+However, from the current work this target is the one with less transit time data, thus, follow-up observations would be required to confirm the no existence of close-in companions in MMR.
+
+\begin{figure}[ht]
+%\vspace{0.1cm}\hspace{0.2cm}
+\includegraphics[width=1.0\textwidth]{imagenes/WASP77_TTV.pdf}
+\caption{Observed minus calculated mid-transit times (TTV) for WASP-77Ab.
+The dashed black line corresponds to the proposed linear ephemeris, i.e.
+zero deviation from the predicted transit time  computed from our refined orbital period.
+For that, we considered 26 transit times from the TraMoS project (in light blue), published works and TESS (both in black).
+The grey area corresponds to the error propagation at $1\sigma$.
+The RMS scatter from the linear ephemeris is 86 seconds.}
+\label{wasp77_ttv}
+\end{figure}
+
 \section{WASP-36b}
+
+The exoplanet WASP-36b was selected as the

### 2019-08-16 pipeline.tex
Appendix ready.

@@
 \begin{itemize}
-\item raw: Folder containing the raw data of the observations. It could be fits files or compressed fits (e.g \textit{fit.ZIP}.
+\item raw: Folder containing the raw data of the observations. It could be fits files or compressed fits (e.g \textit{fit.ZIP}).
 \item calib: This folder should include the flats -- sky or dome -- and bias files.
@@
 One of the biggest problems that I faced when I started reducing data, was the distinctness between the headers produced from different telescopes.
-For exmaple, while some of them recorded the type of filter as \textit{FILTER}, other use could use \textit{FILTERB}.
+For example, while some of them recorded the type of filter as \textit{FILTER}, other use could use \textit{FILTERB}.
 Also, as the TraMoS project has been collecting data since more than 10 year ago, some of our used telescopes were updated with new CCDs, producing that the pipeline were not longer functional.
@@
 
-In the sections ahead, I present the scripts for performing aperture photometry with the TraMoS pipeline of the targets studied in this thesis, following with an example of the PDF generated by the pipeline, containing all the relevant information of the procedure.
+In the sections ahead, I present the scripts for performing aperture photometry with the TraMoS pipeline of the targets studied in this thesis, following with an example of the PDF file generated by the pipeline, containing all the relevant information of the procedure.
 
 \section{Reduction script of WASP-18, WASP-19 and WASP-77A}
+\subsection*{WASP-18}
+\paragraph*{2009 Oct 28:}
+\begin{minted}{python}
+coords_xy = [[691,1625],[1911,1349],[1644,925]]
+ts, phot = pl.pipeline(files_path="raw/*.fits", calib_path="calib/*.fits", 
+				   coords_xy=coords_xy, target="WASP-18",
+                    object_in_hdr = "WASP-18",
+                    stamp_rad=20, recenter=True, brightest=1,
+                    sector=[500,650], sky_test=[13,20],
+                    aps=[5,12], filter_band = "I bessell Soar",
+                    labelsize=16, ccd_lims_xy=[1,2072,1,2072],
+                    max_counts = 60000, **pl.ctio_1m)
+\end{minted}
 
-\section{Example of }
+\paragraph*{2009 Oct 29:}
+\begin{minted}{python}
+coords_xy = [[645,1625],[1865,1344],[1598,921]]
+ts, phot = pl.pipeline(files_path="raw/*.fits", calib_path="calib/*.fits",
+                    coords_xy=coords_xy, target="WASP-18",
+                    object_in_hdr = "WASP-18",
+                    stamp_rad=24, recenter=True, brightest=1,
+                    sector=[1200,1350], sky_test=[15,23],
+                    aps=[5,14], filter_band = "I bessell Soar",
+                    labelsize=16, ccd_lims_xy=[1,2072,1,2072],
+                    max_counts = 60000, **pl.ctio_1m)
+\end{minted}
+
+\paragraph*{2009 Oct 30:}
+\begin{minted}{python}
+coords_xy = [[640,1624],[1865,1344],[1598,920]]
+ts, phot = pl.pipeline(files_path="raw/*.fits", calib_path="calib/*.fits",
+                    coords_xy=coords_xy, target="WASP-18",
+                    object_in_hdr = "WASP-18",
+                    stamp_rad=28, recenter=True, brightest=1,
+                    sector=[570,700], sky_test=[13,25],
+                    aps=[5,12],  filter_band = "I bessell Soar",
+                    labelsize=16, ccd_lims_xy=[1,2072,1,2072],
+                    max_counts = 60000, **pl.ctio_1m)
+\end{minted}
+
+\paragraph*{2011 Sep 06:}
+\begin{minted}{python}
+coords_xy = [[516,1496],[1731,1193],[1460,774]]
+ts, phot = pl.pipeline(files_path="raw/*.fits", calib_path="calib/*.fits",
+                    coords_xy=coords_xy, target="WASP-18",
+                    object_in_hdr = "wasp18",
+                    stamp_rad=24, recenter=True, brightest=1,
+                    sector=[160,200], sky_test=[15,23],
+                    aps=[5,14], filter_band = "I",
+                    labelsize=16, ccd_lims_xy=[1,2072,1,2072],
+                    max_counts = 60000, **pl.ctio_1m)
+\end{minted}
+
+\paragraph*{2016 Sep 24:}
+\begin{minted}{python}
+coords_xy = [[856,427],[455,710]]
+ts, phot = pl.pipeline(files_path="raw/wasp18I*.fits", calib_path="calib/*.fits",
+                    coords_xy=coords_xy, target="WASP-18",
+                    object_in_hdr = "wasp18I",
+                    stamp_rad=37, recenter=True, brightest=1,
+                    sector=[1,20], sky_test=[30,35],
+                    aps=[18,30], filter_band = "I",
+                    labelsize=16, ccd_lims_xy=[1,1020,1,1052],
+                    max_counts = 600000, **pl.dk154_old)
+\end{minted}
+
+\paragraph*{2016 Sep 25:}
+\begin{minted}{python}
+coords_xy = [[848,415],[445,699]]
+ts, phot = pl.pipeline(files_path="raw/wasp*.fits", calib_path="calib/*.fits",
+                    coords_xy=coords_xy,
+                    target="WASP-18",
+                    object_in_hdr = "wasp18I",
+                    stamp_rad=48, recenter=True, brightest=1,
+                    sector=[110,142], sky_test=[30,48],
+                    aps=[25,35], filter_band = "I",
+                    labelsize=16, ccd_lims_xy=[1,1020,1,1051],
+                    max_counts = 600000, **pl.dk154_2017)
+\end{minted}
+
+\paragraph*{2016 Sep 26:}
+\begin{minted}{python}
+coords_xy = [[469,873],[871,589]]
+ts, phot = pl.pipeline(files_path="raw/wasp*.fits", calib_path="calib/*.fits",
+                    coords_xy=coords_xy, target="WASP-18",
+                    object_in_hdr = "wasp18",
+                    stamp_rad=50, recenter=True, brightest=1,
+                    sector=[100,110], sky_test=[40,50],
+                    aps=[30,40], filter_band = "I",
+                    labelsize=16, ccd_lims_xy=[1,1018,1,1293],
+                    max_counts = 600000,  **pl.dk154_2017)
+\end{minted}
+
+\paragraph*{2017 Sep 29:}
+\begin{minted}{python}
+coords_xy = [[1752,417],[1347,700]]
+ts, phot = pl.pipeline(files_path="raw/Wasp-18*.fits", calib_path="calib/*.fits",
+                    coords_xy=coords_xy, target="WASP-18",
+                    object_in_hdr = "Wasp-18_R",
+                    stamp_rad=37, recenter=True, brightest=1,
+                    sector=[1,50], sky_test=[25,35],
+                    aps=[16,25], filter_band = "R",
+                    labelsize=16, ccd_lims_xy=[52,2099,1,1024],
+                    max_counts = 600000, **pl.dk154_2017)
+\end{minted}
+
+\subsection*{WASP-19}
+\paragraph*{2011 Apr 22:}
+\begin{minted}{python}
+coords_xy = [[1198,459],[841,621],[937,737],[877,450]]
+ts, phot = pl.pipeline(files_path="raw/*.fits", calib_path="calib/*.fits",
+                    coords_xy=coords_xy, target="WASP-19",
+                    object_in_hdr = "test",
+                    stamp_rad=20, recenter=True, brightest=1,
+                    sector=[30,90], sky_test=[10,20],
+                    aps=[3,10], filter_band = "I",
+                    labelsize=16, max_counts = 60000,
+                 ccd_lims_xy=[0,2072,0,2072], **pl.ctio_1m)
+\end{minted}
+\paragraph*{2011 Dec 24:}
+\begin{minted}{python}
+coords_xy = [[1204,428],[1840,204],[1702,928],[1222,646]]
+ts, phot = pl.pipeline(files_path="raw/*.fits", calib_path="calib/*.fits",
+                    coords_xy=coords_xy, target="WASP-19",
+                    object_in_hdr = "WASP19",
+                    stamp_rad=20, recenter=True, brightest=3,
+                    sector=[270,320], sky_test=[10,20],
+                    aps=[3,10], filter_band = "I",
+                    labelsize=16, ccd_lims_xy=[0,2072,0,2072],
+                    max_counts = 60000, **pl.ctio_1m)
+\end{minted}
+\paragraph*{2013 Mar 13:}
+\begin{minted}{python}
+coords_xy = [[1202,1182],[1179,860]]
+ts, phot = pl.pipeline(files_path="raw/WASP-19*.fits", calib_path="calib/*.fits",
+                    coords_xy=coords_xy, target="WASP-19",
+                    object_in_hdr=None,
+                    stamp_rad=25, recenter=True, brightest=1,
+                    sector=None, sky_test=[16,24],
+                    aps=[8,20], filter_band="R",
+                    labelsize=16, max_counts = 600000,
+                    ccd_lims_xy=[52, 2048, 1, 2048], **pl.dk154_old)
+\end{minted}
+\paragraph*{2013 Apr 20:}
+\begin{minted}{python}
+coords_xy = [[109,515],[87,195],[445,201],[577,273],[601,369]]
+ts, phot = pl.pipeline(files_path="raw/w19*.fits", calib_path="calib/*.fits",
+                    coords_xy=coords_xy, target="WASP-19",
+                    object_in_hdr="w19-20130420",
+                    stamp_rad=25, recenter=True, brightest=1,
+                    sky_test=[16,24], sector=[55,80],
+                    filter_band="R", labelsize=16,
+                    ccd_lims_xy=[0,700,0,650],
+                    max_counts = 600000, **pl.dk154_old)
+\end{minted}
+\paragraph*{2015 Mar 04:}
+\begin{minted}{python}
+coords_xy = [[1074,967],[586,954],[1397,557],[1565,821],[1489,975],[1480,1201]]
+ts, phot = pl.pipeline(files_path="raw/WASP19_*.fits", calib_path="calib/*.fits",
+                    coords_xy=coords_xy, object_in_hdr="WASP19",
+                    target="WASP-19",
+                    stamp_rad=30, recenter=True, brightest=4,
+                    sector=[1,30], labelsize=16,
+                    filter_band="R", ccd_lims_xy=[0,2148,0,2048],
+                    max_counts = 600000, **pl.dk154_old)
+\end{minted}
+\paragraph*{2016 Apr 14:}
+\begin{minted}{python}
+coords_xy = [[1125,1064], [708,1054], [718,828], [1318,151], [1031,524]]
+ts, phot = pl.pipeline(files_path="raw/wasp19_*.fits", calib_path="calib/*.fits",
+                    object_in_hdr="wasp19", target="WASP-19",
+                    coords_xy=coords_xy,
+                    stamp_rad=35, recenter=True, brightest=2,
+                    sector=[1,30], filter_band="I",
+                    labelsize=16, ccd_lims_xy=[0,2128,0,1376],
+                    max_counts = 600000, **pl.dk154_old)
+\end{minted}
+\paragraph*{2017 Feb 14:}
+\begin{minted}{python}
+coords_xy = [[525,686], [119,452], [432,149], [111,678],[192,1002]]
+ts, phot = pl.pipeline(files_path="raw/WASP_19_*.fits", calib_path="calib/*.fits",
+				   target="WASP-19",
+                    object_in_hdr= "WASP_19", coords_xy=coords_xy,
+                    stamp_rad=35, recenter=True, brightest=4,
+                    sector=[1,30], sky_test=[10,24],
+                    aps=[10,20], labelsize=16,
+                    ccd_lims_xy=[0,1019,0,1165], max_counts = 600000,
+                    filter_band="I", **pl.dk154_2017)
+\end{minted}
+\paragraph*{2017 Apr 08:}
+\begin{minted}{python}
+coords_xy = [[374,361], [866,215], [790, 369], [782, 595],[468,899]]
+ts, phot = pl.pipeline(files_path="raw/WASP19R*.fits", calib_path="calib/*.fits",
+                    target="WASP-19", object_in_hdr="WASP19R",
+                    coords_xy=coords_xy,
+                    stamp_rad=35, recenter=True, brightest=2,
+                    sector=[1,30], sky_test=[10,24],
+                    aps=[10,20], labelsize=16,
+                    filter_band="R", ccd_lims_xy=[0,1019,0,925],
+                    max_counts = 600000,
+                    filter_band="I", **pl.dk154_2017)
+\end{minted}
+\paragraph*{2017 Oct 03:}
+\begin{minted}{python}
+coords_xy = [[1087,1001],[892,1912],[1408,590],[1575,853],[1501,1009],[1491,1235]]
+ts, phot = pl.pipeline(files_path="raw/Wasp19_*.fits", calib_path="calib/*.fits",
+                    object_in_hdr="Wasp19", target="WASP-19",
+                    coords_xy=coords_xy,
+                    stamp_rad=25, recenter=True, brightest=1,
+                    aps=[10,20], sector=[1,15],
+                    sky_test=[10,24], labelsize=16,
+                    filter_band="R",ccd_lims_xy=[0,2148,0,2048],
+                    max_counts = 600000, **pl.dk154_2017)
+\end{minted}
+
+\subsection*{WASP-77A}
+
+\paragraph*{2015 Sep 29:}
+\begin{minted}{python}
+coords_xy = [[1801,1558],[1558,681]]
+ts, phot = pl.pipeline(files_path="raw/*.fits", calib_path="calib/*.fits",
+                    coords_xy=coords_xy, target="WASP-77",
+                    object_in_hdr = "wasp77_",
+                    stamp_rad=40, recenter=True, brightest=1,
+                    sector=[55,90], sky_test=[30,35],
+                    aps=[20,28], filter_band = "R",
+                    labelsize=16,  ccd_lims_xy=[1,1995,1,1655],
+                    max_counts = 600000, **pl.dk154_2017)
+\end{minted}
+\paragraph*{2015 Oct 03:}
+\begin{minted}{python}
+coords_xy = [[1572,118],[1819,996],[121,1433]]
+ts, phot = pl.pipeline(files_path="raw/wasp*.fits", calib_path="calib/*.fits",
+                    coords_xy=coords_xy, target="WASP-77",
+                    object_in_hdr = "wasp77",
+                    stamp_rad=40, recenter=True, brightest=2,
+                    sector=[50,75], sky_test=[31,35],
+                    aps=[20,30], filter_band = "R",
+                    labelsize=16, ccd_lims_xy=[1,1961,1,1546],
+                    max_counts = 600000, **pl.dk154_2017)
+\end{minted}
+\paragraph*{2016 Sep 26:}
+\begin{minted}{python}
+coords_xy = [[134,254],[378,1126],[518,1427]]
+ts, phot = pl.pipeline(files_path="raw/wasp*.fits", calib_path="calib/*.fits",
+                    coords_xy=coords_xy, target="WASP-77",
+                    object_in_hdr = "wasp77",
+                    stamp_rad=45, recenter=True, brightest=1,
+                    sector=[44,53], sky_test=[37,42],
+                    aps=[25,35], filter_band = "I",
+                    labelsize=16, ccd_lims_xy=[1,1010,1,1540],
+                    max_counts = 600000, **pl.dk154_2017)
+\end{minted}
+
+\paragraph*{2016 Oct 07:}
+\begin{minted}{python}
+coords_xy = [[1035,2120],[694,783],[1711,2094],[1820,2816]]
+ts, phot = pl.pipeline(files_path="raw/*.ftsc", calib_path="calib/*.fts",
+                    coords_xy=coords_xy, target="WASP-77",
+                    object_in_hdr = "WASP-77",
+                    stamp_rad=90, recenter=True, brightest=1,
+                    sector=[145,160], sky_test=[50,70],
+                    aps=[21,31], filter_band = "I",
+                    labelsize=16, ccd_lims_xy=[1,2048,1,4102],
+                    max_counts = 600000, **pl.warsaw_2016)
+\end{minted}
+
+\paragraph*{2017 Oct 01:}
+\begin{minted}{python}
+coords_xy = [[1054,1490],[1501,1471],[1520,372]]
+ts, phot = pl.pipeline(files_path="raw/*.fits", calib_path="calib/*.fits",
+                    coords_xy=coords_xy, target="WASP-77",
+                    object_in_hdr = "Wasp-11",
+                    stamp_rad=35, recenter=True, brightest=1,
+                    sector=[10,30], sky_test=[21,34],
+                    aps=[10,20], filter_band = "B",
+                    labelsize=16, ccd_lims_xy=[1,2148,1,2048],
+                    max_counts = 600000, **pl.dk154_2017)
+\end{minted}
+
+\section{Example of output file}
+
+The following joined document is an example of the PDF file generated by the data reduction pipeline. This corresponds to the reduction of the light curve of WASP-19 during March 4th, 2015.
+
+\includepdf[pages={-}]{WASP-19_extraction.pdf}

### 2019-08-16 introduction.tex
More work in Intro

@@
 During the sixteenth century, the Italian philosopher Giordano Bruno suggested, for the first time in history, that more planet could be outside the Solar System.
-Even though the first claims of exoplanet detection began at the end of the nineteenth century, it was not until more than four hundred years after the statement of Giordano Bruno, that the first exoplanet was confirmed in 1992.
+Even though the first claims of exoplanet detection began at the end of the nineteenth century, it was not until more than four hundred years after the statement of Bruno, that the first exoplanet was confirmed in 1992.
 Surprisingly, it was not just one exoplanet but three, orbiting the pulsar PSR B1257+12 more than 1000 light-years away from us.
-Today, more than 4,000 exoplanet are confirmed, and thousands more are waiting for their confirmation.
+Today, more than 4,000 exoplanets are confirmed, and thousands more are waiting for their confirmation.
 
@@
 \includegraphics[width=1.0\columnwidth]{imagenes/exoplanets_hd.pdf}
-\caption{Mass and orbital period distribution of Exoplanets, and their corresponding discovery methods in color. In this plot are shown only the exoplanets with known masses}
+\caption{Mass and orbital period distribution of Exoplanets, and their corresponding discovery methods in color. This plot only shows the exoplanets with known masses}
 \label{exoplanets}

### 2019-08-17 conclusion.tex
Writting in last chapter

@@
-\chapter{Conclusions and Future work}\label{chap:conclusion}
+\chapter{Summary and future work}\label{chap:conclusion}
+
+The TraMos project started more than 10 years ago aiming, on one hand, to refine orbital and physical of already known exoplanets, and on the other, to search for variation in the transit time -- or other planet parameters -- that could suggest the existence of smaller bodies on their systems.
+Since the beginning, the targets has been hot Jupiter due to their short-periods allowing to obtain more consecutive transit light curves in a reduced timespan.
+
+%To date, we have not detected periodic TTV signal on any of the analyzed exoplanets.
+
+The Transit Timing Variation (TTV) technique was proposed as a technique to detect Earth-mass planet in gas giant systems, due to their mutual dynamical interaction.
+The variation in the transit time is enhanced when the two bodies are near to Mean Motion Resonances (MMR), therefore, this kind of interaction is easier to detect from ground-based follow-up.
+Through the years, the TTV technique has demonstrated to be an efficient and powerful tool not only to detect small exoplanets in the Earth-mass regime but to obtain essential information of multi-exoplanetary systems.
+By analyzing and modeling TTV curves of planetary systems in near MMR, the bodies' masses can be estimated, whence RV could be no longer a requirement for masses estimation.
+
+During this Master project, I studied three exoplanets: WASP-18b, WASP-19b, and WASP-77Ab.
+For these targets, I analyzed a total of 26 light curves: 8 of WASP-18b, 9 of WASP-19b and 9 of WASP-77Ab.
+In the case of WASP-77Ab, 4 light curves were taken from the Exoplanet Transit Database (ETD)\footnote{\url{var2.astro.cz/ETD}} to obtain a wider time coverage.
+For the light curves coming from the TraMoS project, I started from performing aperture photometry of the targets using our data reduction pipeline (for further details see \ref{chap:pipeline}), in order to obtain high-precision light curves.
+Then, I used EXOFASTv2 \cite{Eastman2013,Eastman2017} to get best-fit for the light curve's data and hence, to refine their orbital and physical parameters and obtain their transit times.
+
+The TTV curves were constructed from the residuals between the observed transit time and the expected from the linear ephemeris.
+Any of the targets studied in this thesis, shows a clear, periodic sinusoidal signal.
+This suggest the lack of close-in companions in MMR in their systems.
+However, upper mass limit of hypothetical perturbers -- not only in MMR -- could be computed with the time-scatter from the linear ephemeris.
+The hot Jupiter WASP-18b shows 83 seconds of scatter, WASP-19b shows 75 seconds and WASP-77ab shows 121 seconds, being the target with larger deviation from the linear ephemeris, but at the same time, the target with less transit times.

### 2019-08-17 introduction.tex
Fixed details

@@
 
-This thesis is an extension of the Transit Monitoring in the South project (TraMoS, see Chapter\ref{chap:tramos}) started in 2008 by Sergio Hoyer and Patricio Rojo.
+This thesis is an extension of the Transit Monitoring in the South project (TraMoS, see Chapter \ref{chap:tramos}) started in 2008 by Sergio Hoyer and Patricio Rojo.
 I selected a new sample of transiting exoplanets, all of them hot Jupiters without any companions detected to date.
@@
 Chapter \ref{chap:paper} shows the analysis and results of the hot Jupiters WASP-18b, WASP-19b and WASP-77Ab, including  their observations and data reduction, light curve and RV analysis, measurements of TTVs and upper mass limit for possible companions in their systems.
-Then, Chapter\ref{chap:tess}  recapitulates the current stage of the TraMoS project on which TESS data is being incorporated.
-Here, I re-analyze the TTV curves of the previous targets WASP-18b, WASP-19b, and WASP-77Ab with new light curves from TESS and also, the preliminary results of WASP-36b are shown.
+Then, Chapter \ref{chap:tess}  recapitulates the current stage of the TraMoS project on which TESS data is being incorporated.
+Here, I re-analyze the TTV curves of the previous targets WASP-18b, WASP-19b, and WASP-77Ab with new light curves from TESS and also, preliminary results of WASP-36b are shown.
 Finally, Chapter \ref{chap:conclusion} contains the principal conclusions of this thesis as well as some ideas for future work.

### 2019-08-17 paper.tex
TESS blablabla
Fixed details

@@
 
-As suggested by \cite{Southworth2009}, most of our observation, especially those conducted after 2011, used the defocus technique, which allows longer exposure times in bright targets and improves the photometric precision.
+Most of our observation, especially those conducted after 2011, used the defocus technique as suggested by \cite{Southworth2009},  which allows longer exposure times in bright targets and improves the photometric precision.
 We adjust the exposure time during the observations if the weather is not ideal.
@@
 After it finished, we took the values from its best model and used them as priors for the next short run.
-This process was repeated until the chains were converged and well-mixed.
+This process was repeated until the chains converged and were well-mixed.
 
@@
 In the other hand, our estimation of $T_{14}$ is significantly larger than \cite{Hebb2010} by $9\sigma$, but the difference is only $3.5\sigma$ when compared with \cite{Lendl2013}.
-We also report a preciser impact parameter $b$ and transit depth $\delta$.
+We also report a more precise impact parameter $b$ and transit depth $\delta$.
 
@@
 
-Almost all the stellar parameters are in agreement with \citep{Maxted2013}, except for a $-9.7\sigma$ difference in the stellar surface gravity $\log{g}$, where our reported value is preciser.
+Almost all the stellar parameters are in agreement with \citep{Maxted2013}, except for a $-9.7\sigma$ difference in the stellar surface gravity $\log{g}$, where our reported value is more precise.
 
@@
 
-\begin{equation} \label{eq1}
+\begin{equation} \label{eq1_wasp19}
 T_{\rm C}(E)=T_{\rm C}(0)+E \cdot P
@@
 Considering all the transit times in Table~\ref{times_wasp18} without the epochs $-1904$ and $-1184$, all the TTVs lie within $1.6\sigma$ in the linear fit.
-
 The epoch $-1184$ has the greatest error in our sample because it is not a complete transit.

### 2019-08-17 tess.tex
Fixed details

@@
 It is crucial for TTV studies to continue the work of space missions from ground.
-It is unlike to only with space-based observations to cover the interaction timescales to dynamically prove the TTV signal and the existence of some exoplanets companions, as in shown in Figure \ref{koinet} from the KOINet project.
+It is unlike, only with space-based observations, to cover the interaction timescales to dynamically prove the TTV signal and the existence of possible companions, as in shown in Figure \ref{koinet}.
 In this figure, new data from ground-based telescopes were fundamental to confirm the TTV signal, and therefore to perform a proper characterization of the system.
@@
 Between Sector 1 and Sector 13, TESS observed around 15\% of the stars with confirmed exoplanets but not all of them will produce a transit event within the 27 days of a sector duration (see Figure \ref{chap:tess}).
-Anyway, several complete light curves could be obtain and analyzed.
+Anyway, several complete light curves could be obtained and analyzed.
 TESS data are reduced by the Science Processing Operations Center (SPOC) and after being processed, they are archived in the Mikulski Archive for Space Telescopes (MAST) catalogue, where can be downloaded directly by anyone.
@@
 \caption{Match between all the stars with confirmed exoplanets and the TESS targets from Sector 1 to Sector 13.
-The empty red circles correspond to the star with confirmed exoplanets distributed by its position in the sky while the filled red circles indicate if the exoplanet has an orbital period of less than 27 days, which is the duration of one TESS sector.
+The empty red circles correspond to the star with confirmed exoplanets distributed by its position in the sky, while the filled red circles indicate if the exoplanet has an orbital period of less than 27 days, which is the duration of one TESS sector.
 The black cross indicates which star was already observed by TESS.
@@
 The main goal of the project will remain the same: refine orbital and physical parameters of exoplanetary system and search for variations in the transit time, that could suggest the presence of additional small bodies in the system.
-The KOINet project proved that ground-based follow-up are, in some cases, are essential to complete a possible TTV signal, and therefore, to confirm or rule out variations in the transit time.
+The KOINet project proved that ground-based follow-up are, in some cases, essential to complete a possible TTV signal, and therefore, to confirm or rule out variations in the transit time.
 During its first year of mission, TESS will supply with consecutive transit light curves from southern targets, specially from short-period planets, such as hot Jupiters.
@@
 
-In the following subsections, I present a re-analisys of the TTV curves of the hot Jupiters: WASP-18b, WASP-19b and WASP-77Ab including new transit times from TESS: 45, 28, and 15 for WASP-18b, WASP-19b and WASP-77Ab respectively.
+In the following subsections, I present a re-analysis of the TTV curves of the hot Jupiters: WASP-18b, WASP-19b and WASP-77Ab including new transit times from TESS: 45, 28, and 15 for WASP-18b, WASP-19b and WASP-77Ab respectively.
 In order to compute the transit time of each light curve, I used EXOFASTv2 but only to fit the transit time and the flux baseline.
@@
 The star WASP-18 was observed continuously during Sector 2 and 3 of the TESS mission, between August 22nd and October 18th, 2018.
-Theses observations provided 47 transits events of WASP-18b, but only 45 of them were complete transits, and therefore included into the TTV analysis.
+These observations provided 47 transits events of WASP-18b, but only 45 of them were complete transits, and therefore included into the TTV analysis.
 

### 2019-08-17 tramos.tex
Fixed details

@@
 The Transit method is today the most successful technique to discover extrasolar planets (see Fig.~\ref{amount_exoplanet}).
-The Kepler mission was launched in 2009 and during its almost nine years of provided thousands of discoveries due to this method.
+The Kepler mission was launched in 2009 and during its almost nine years of operation provided thousands of discoveries due to this method.
 
@@
 The light curve produced by a transit event provides important information of the planetary system.
-For example, it is the only way on which we can derived directly the proportion between the exoplanet and star radius.
-It can also give information about the impact parameter, and therefore, the inclination of the orbit.
+For example, it is the only way on which we can derive directly the proportion between the exoplanet and star radius.
+It can also gives information about the impact parameter, and therefore, the inclination of the orbit.
 
@@
 For example, Figure \ref{transit_examples} shows how the light curve reflects the configuration of the system.
-Hot Jupiters are the kind of planet easier to detect, since their planet-to-star radius ratio is larger.
-But an smaller planet orbiting a dwarf star could produce a similar ratio of the radius.
+Hot Jupiters are the kind of planet easier to detect, since their planet-to-star radius ratio is larger, but a smaller planet orbiting a dwarf star could produce a similar ratio of the radius.
 In the other hand, exoplanets with larger orbital inclinations will produce shorter drops in the flux, in comparison with planets in the same orbital-plane with the host star.
@@
 The Transit Timing Variations (TTV) technique was first proposed as a way to detect Earth-mass planets in multiplanetary systems due to gravitational interactions with a transiting exoplanet \citep{Holman2005,Agol2005}.
-However, TTVs can be also use to measure tidal interactions between the planet and the star or to detect exomoons \citep{Kipping2009a,Kipping2009b}, among others.
+However, TTVs can be also used to measure tidal interactions between the planet and the star or to detect exomoons \citep{Kipping2009a,Kipping2009b}, among others phenomena.
 
@@
 
-The TTV method is a efficient tool to search for additional unseen companions, since in order to employ this technique only photometry of the transiting exoplanet during a transit events is required.
+The TTV method is an efficient tool to search for additional unseen companions since, in order to employ this technique, only photometry of the transiting exoplanet during a transit events is required.
 Moreover, this technique enhances its sensitivity when the two bodies in the system are close to Mean Motion Resonances (MMR) \citep{Agol2005,Steffen2005,Agol2007} (see Figure~\ref{rms_ttv_amplitude}) .
@@
 \caption{Example of a system with a transiting exoplanet of $1~M_{J}$ in a 10-day orbit, around a star with $0.367~M_{\odot}$.
-The perturber is a Earth-mass planet.
+The perturber is an Earth-mass planet.
 Panel \textbf{a} is an O-C diagram showing the measured TTV when the pertuber has a period of 16.11 days, not in Mean Motion Resonance with the transiting planet.
@@
 
-Trough the TTV method not only the transiting exoplanet is being studied but the whole planetary system.
+Through the TTV method not only the transiting exoplanet is being studied but the whole planetary system.
 Even the lack of variation in the transit timing gives clues related to the formation of close-in gas giant.

### 2019-08-18 conclusion.tex
Done Summary and future work

@@
 During this Master project, I studied three exoplanets: WASP-18b, WASP-19b, and WASP-77Ab.
-For these targets, I analyzed a total of 26 light curves: 8 of WASP-18b, 9 of WASP-19b and 9 of WASP-77Ab.
+For these targets, I analyzed a total of 26 new light curves: 8 of WASP-18b, 9 of WASP-19b and 9 of WASP-77Ab.
 In the case of WASP-77Ab, 4 light curves were taken from the Exoplanet Transit Database (ETD)\footnote{\url{var2.astro.cz/ETD}} to obtain a wider time coverage.
@@
 The TTV curves were constructed from the residuals between the observed transit time and the expected from the linear ephemeris.
-Any of the targets studied in this thesis, shows a clear, periodic sinusoidal signal.
+Any of the targets studied in this thesis, shows a clear, periodic sinusoidal signal in the variation of their transit times and moreover, the structure of the transit times are comparable with a random distribution after a Lomb-Scargle analyis.
 This suggest the lack of close-in companions in MMR in their systems.
-However, upper mass limit of hypothetical perturbers -- not only in MMR -- could be computed with the time-scatter from the linear ephemeris.
+However, upper mass limit of hypothetical perturbers -- placed not only in near MMR -- could be computed with the time-scatter from the linear ephemeris.
 The hot Jupiter WASP-18b shows 83 seconds of scatter, WASP-19b shows 75 seconds and WASP-77ab shows 121 seconds, being the target with larger deviation from the linear ephemeris, but at the same time, the target with less transit times.
+
+In summary, the upper mass limit for possible perturbers that could produced the observed scatter in the transit time are:
+\begin{itemize}
+\item WASP-18b: $1.9\,M_{\odot}$, $4.0\,M_{\odot}$, $5.0\,M_{\odot}$, $25\,M_{\odot}$, $10\,M_{\odot}$, $7.0\,M_{\odot}$, $50\,M_{\odot}$ in 1:3, 2:5, 1:2, 2:1, 5:2, 3:1 and 4:1 resonances, respectively.
+\item WASP-19b: $2.0\,M_{\odot}$, $6.0\,M_{\odot}$, $0.9\,M_{\odot}$, $3.0\,M_{\odot}$, $2.0\,M_{\odot}$ in 1:2, 5:3, 2:1, 5:2 and 3:1 resonances, respectively. 
+\item WASP-77Ab: $1.0\,M_{\odot}$, $3.5\,M_{\odot}$, $2.0\,M_{\odot}$, $7.0\,M_{\odot}$, $6.0\,M_{\odot}$, $10\,M_{\odot}$, $3.5\,M_{\odot}$, $4.5\,M_{\odot}$ in 1:3, 1:2, 3:5, 2:3, 5:3, 7:4, 2:1 and 3:1 resonances, respectively.
+\end{itemize}
+
+After the released of TESS data, I included transit times of the targets studied in this thesis, in order to extend their TTV curves and confirm the lack of periodic variations in the transit time.
+The results came out as expected and the scatter in the transit time were reduced for the three targets: 47 seconds for WASP-18b, 65 seconds for WASP-19b and 86 seconds for WASP-77Ab.
+Moreover, I refined each orbital period obtaining a precision of the order of milli-seconds.
+
+To date, any of the previous and current targets of the TraMoS project have shown TTVs.
+As they are all hot Jupiters, these studies support the theory of "alone hot Jupiters", on which this kind of exoplanets are probably alone in their systems or company of small bodies not in MMR.
+How WASP-47b and Kepler-730b, the only two hot Jupiters showing TTVs, have close-in companions is still unknown.
+The migration theory of hot Jupiters could give us a possible explanation of how these gas giant ended-up with companions in MMR, as they are supposed their migration process in far-away orbits.
+While migrating, they could catch other bodies settling down in close orbits.
+But the lack of more hot Jupiters with TTVs, on the other hand, suggest that probably during migration they cleaned-up their orbits of small bodies.
+
+The TraMoS catalogue stores more than 400 transits events of near 130 exoplanets.
+As future work I propose to continue performing ground-based photometric follow-up of the target in this catalogue, as well as new targets, combining the efforts with TESS data of Sector 1 to 13.
+In this way, we could obtain better estimations of TTVs with wider time-span data from TraMoS, and an important amount of consecutive transit times from TESS.
+In the near future, I will analyze the exoplanets WASP-36b and HATS-34b, which each one has five transit times from TraMoS and twelve and twenty six from TESS, respectively.
+For the following targets: WASP-22, WASP-46, WASP-45, WASP-23 and WASP-123, TESS provided five, seventeen, eight, seven and thirteen light curves, respectively.
+These target are within the 30 targets with most light curve from TraMoS, therefore, they should be the next in line.
+
+The reduction pipeline is fully functional and provides high-precision photometry, nevertheless several improvements were left behind because of the lack of time to implement them.
+For example, the coordinates selection could be done inside the program to avoid mistakes when typing them by hand before calling the pipeline.
+Any new idea for improvement the reduction pipeline could be done within an undergrad project or graduate semester-workshop.

### 2019-08-18 conclusion.tex
Summary ready.

@@
 
-The TraMos project started more than 10 years ago aiming, on one hand, to refine orbital and physical of already known exoplanets, and on the other, to search for variation in the transit time -- or other planet parameters -- that could suggest the existence of smaller bodies on their systems.
-Since the beginning, the targets has been hot Jupiter due to their short-periods allowing to obtain more consecutive transit light curves in a reduced timespan.
+The TraMos project started more than 10 years ago aiming to refine orbital and physical parameters of already known exoplanets, and to search for variation in the transit time -- or other planet parameters -- that could suggest the existence of smaller bodies on their systems.
+Since the beginning, the targets have been hot Jupiters due to their short-periods, allowing to obtain more consecutive transit light curves in a reduced timespan.
 
@@
 During this Master project, I studied three exoplanets: WASP-18b, WASP-19b, and WASP-77Ab.
-For these targets, I analyzed a total of 26 new light curves: 8 of WASP-18b, 9 of WASP-19b and 9 of WASP-77Ab.
-In the case of WASP-77Ab, 4 light curves were taken from the Exoplanet Transit Database (ETD)\footnote{\url{var2.astro.cz/ETD}} to obtain a wider time coverage.
+For these targets, I analyzed a total of twentysix new light curves: eight of WASP-18b, nine of WASP-19b and nine of WASP-77Ab.
+In the case of WASP-77Ab, four light curves were taken from the Exoplanet Transit Database (ETD)\footnote{\url{var2.astro.cz/ETD}} to obtain a wider time coverage.
 For the light curves coming from the TraMoS project, I started from performing aperture photometry of the targets using our data reduction pipeline (for further details see \ref{chap:pipeline}), in order to obtain high-precision light curves.
-Then, I used EXOFASTv2 \cite{Eastman2013,Eastman2017} to get best-fit for the light curve's data and hence, to refine their orbital and physical parameters and obtain their transit times.
+Then, I used EXOFASTv2 \cite{Eastman2013,Eastman2017} to get the best-fit for the light curve's data and hence, to refine their orbital and physical parameters and obtain their transit times.
 
 The TTV curves were constructed from the residuals between the observed transit time and the expected from the linear ephemeris.
-Any of the targets studied in this thesis, shows a clear, periodic sinusoidal signal in the variation of their transit times and moreover, the structure of the transit times are comparable with a random distribution after a Lomb-Scargle analyis.
-This suggest the lack of close-in companions in MMR in their systems.
+None of the targets studied in this thesis, shows a clear, periodic sinusoidal signal in the variation of their transit times and moreover, the structure of the transit times are comparable with a random distribution after a Lomb-Scargle analysis.
+This suggests the lack of close-in companions in MMR in their systems.
 However, upper mass limit of hypothetical perturbers -- placed not only in near MMR -- could be computed with the time-scatter from the linear ephemeris.
-The hot Jupiter WASP-18b shows 83 seconds of scatter, WASP-19b shows 75 seconds and WASP-77ab shows 121 seconds, being the target with larger deviation from the linear ephemeris, but at the same time, the target with less transit times.
+The hot Jupiter WASP-18b shows 83 seconds of scatter, WASP-19b shows 75 seconds and WASP-77ab shows 121 seconds.
+The latter being the target with larger deviation from the linear ephemeris, but at the same time, the target with less transit times.
 
@@
 
-After the released of TESS data, I included transit times of the targets studied in this thesis, in order to extend their TTV curves and confirm the lack of periodic variations in the transit time.
+After the release of TESS data, I included transit times of the targets studied in this thesis, in order to extend their TTV curves and confirm the lack of periodic variations in the transit time.
 The results came out as expected and the scatter in the transit time were reduced for the three targets: 47 seconds for WASP-18b, 65 seconds for WASP-19b and 86 seconds for WASP-77Ab.
@@
 
-To date, any of the previous and current targets of the TraMoS project have shown TTVs.
-As they are all hot Jupiters, these studies support the theory of "alone hot Jupiters", on which this kind of exoplanets are probably alone in their systems or company of small bodies not in MMR.
+To date, none of the previous and current targets of the TraMoS project have shown TTVs.
+As they are all hot Jupiters, these studies support the theory of "alone hot Jupiters", on which this kind of exoplanets are probably alone in their systems or accompanied of small bodies not in MMR.
 How WASP-47b and Kepler-730b, the only two hot Jupiters showing TTVs, have close-in companions is still unknown.
-The migration theory of hot Jupiters could give us a possible explanation of how these gas giant ended-up with companions in MMR, as they are supposed their migration process in far-away orbits.
-While migrating, they could catch other bodies settling down in close orbits.
-But the lack of more hot Jupiters with TTVs, on the other hand, suggest that probably during migration they cleaned-up their orbits of small bodies.
+The migration theory of hot Jupiters could give us a possible explanation of how these gas giant ended-up with companions in MMR, as they are supposed to start their migration process in far-away orbits.
+While migrating, they could catch other bodies to then settling down in close orbits.
+But the lack of more hot Jupiters with TTVs suggest that probably during migration they cleaned-up their orbits of small bodies.
 
-The TraMoS catalogue stores more than 400 transits events of near 130 exoplanets.
-As future work I propose to continue performing ground-based photometric follow-up of the target in this catalogue, as well as new targets, combining the efforts with TESS data of Sector 1 to 13.
+The TraMoS catalogue stores more than 400 transits events of near 140 exoplanets.
+As future work I propose to continue performing ground-based photometric follow-up of the targets in this catalogue, as well as new targets, combining the efforts with TESS data of Sector 1 to 13.
 In this way, we could obtain better estimations of TTVs with wider time-span data from TraMoS, and an important amount of consecutive transit times from TESS.
 In the near future, I will analyze the exoplanets WASP-36b and HATS-34b, which each one has five transit times from TraMoS and twelve and twenty six from TESS, respectively.
-For the following targets: WASP-22, WASP-46, WASP-45, WASP-23 and WASP-123, TESS provided five, seventeen, eight, seven and thirteen light curves, respectively.
-These target are within the 30 targets with most light curve from TraMoS, therefore, they should be the next in line.
+For WASP-22, WASP-46, WASP-45, WASP-23 and WASP-123, TESS provided five, seventeen, eight, seven and thirteen light curves, respectively.
+These targets are within the 30 targets with most light curves from TraMoS, therefore, they should be the next in line.
 
 The reduction pipeline is fully functional and provides high-precision photometry, nevertheless several improvements were left behind because of the lack of time to implement them.
-For example, the coordinates selection could be done inside the program to avoid mistakes when typing them by hand before calling the pipeline.
-Any new idea for improvement the reduction pipeline could be done within an undergrad project or graduate semester-workshop.
+For example, the coordinates selection could be done inside the program, to avoid mistakes when typing them by hand before calling the pipeline.
+Any new idea to improvement the reduction pipeline could be done within an undergrad project or graduate semester-workshop.

### 2019-08-18 introduction.tex
TraMoS chapter ready.

@@
 
-The increasing number of discovered exoplanets have been reached thank to two techniques: Radial Velocity and Transits.
+The increasing number of discovered exoplanets have been reached thanks to two techniques: Radial Velocity and Transits (see Figure \ref{exoplanets}).
 Each one of these techniques had their own advantages depending on the physical properties of the planetary system.
 When the orbit of the exoplanet is aligned with the line of sight from Earth, the pass of the planet in front of its host star causes that the star's flux decreases proportionally to the size of the planet.
-Thus, its radius, in comparison with the radius of the star, can be determined directly using the Transit method.
+Thus, its radius can be determined directly using the Transit method.
 In the other hand, the gravity due to the presence of a planet will set the center of mass of the system, in a place different from the star's center.
@@
 
-\begin{figure}[H]
+The study of exoplanets does not end with their discovery.
+
+\begin{figure}[ht]
 \centering
@@
 I selected a new sample of transiting exoplanets, all of them hot Jupiters without any companions detected to date.
-I analized 22 new light curves of the hot Jupiters WASP-18b, WASP-19b, and WASP-77Ab searching for periodic variations in the transit time (TTV) that could suggest the presence of additional bodies in their systems.
+I analized 27 new light curves of the hot Jupiters WASP-18b, WASP-19b, and WASP-77Ab searching for periodic variations in the transit time (TTV) that could suggest the presence of additional bodies in their systems.
 
@@
 Then, Chapter \ref{chap:tess}  recapitulates the current stage of the TraMoS project on which TESS data is being incorporated.
-Here, I re-analyze the TTV curves of the previous targets WASP-18b, WASP-19b, and WASP-77Ab with new light curves from TESS and also, preliminary results of WASP-36b are shown.
+Here, I re-analyze the TTV curves of the previous targets WASP-18b, WASP-19b, and WASP-77Ab with new light curves from TESS.
 Finally, Chapter \ref{chap:conclusion} contains the principal conclusions of this thesis as well as some ideas for future work.
+The Appendix section includes a brief description of the aperture photometry pipeline utilized, all the Python scripts used to generate each light curve, and an example of the PDF file obtained after the aperture photometry procedure.

### 2019-08-18 tramos.tex
TraMoS chapter ready.

@@
 
-\begin{figure}
+\begin{figure}[ht]
 \centering
-\includegraphics[width=1.0\columnwidth]{imagenes/tramos.png}
+\includegraphics[width=0.9\columnwidth]{imagenes/tramos.png}
 \caption{Histogram of the 30 transiting exoplanets with the largest amount of observations within the TraMoS project.
@@
 2019 (submitted, see Chapter \ref{chap:paper} for further details).
-In any of those systems a significant TTV signal was detected.}
+In none of those systems a significant TTV signal was detected.}
 \label{tramos}
@@
 
-\section{Transiting Exoplanets}
-The Transit method is today the most successful technique to discover extrasolar planets (see Fig.~\ref{amount_exoplanet}).
+In the following section \ref{lightcurve}, I describe the light curve produced from a transiting exoplanet --the principal target of the TraMoS project --  what information about the planet can be obtain from them and how these light curves can give us information about the architecture of this kind of systems.
+Then, in section \ref{ttv}, I detail on an specific type of phenomena of transiting exoplanets: the variation of the transit time of its light curve (TTV).
+
+\section{Transiting exoplanets' light curve\label{lightcurve}}
+The Transit method is today the most successful technique to discover extrasolar planets (see Figure \ref{amount_exoplanet}).
 The Kepler mission was launched in 2009 and during its almost nine years of operation provided thousands of discoveries due to this method.
 
-\begin{figure}[H]
+\begin{figure}[ht]
 \centering
 \includegraphics[width=0.7\columnwidth]{imagenes/exo_dischist_cumulative.png}
-\caption{Accumulative number of discovered exoplanets by year.}
+\caption{Accumulative number of discovered exoplanets by year and their corresponding method of discovery.
+To date, the Transit technique, along with Radial Velocity, are the most successful methods to discovery exoplanets.
+Figure from the NASA Exoplanet Archive (\url{exoplanetarchive.ipac.caltech.edu})}
 \label{amount_exoplanet}
@@
 In Figure~\ref{transit} is described the architecture of a transiting exoplanet.
-Thanks to its geometry, the transit event as well as some parameters of the planetary system can be described with a few simple relations (cite Seager and Mallean y Winn).
+Thanks to its geometry, the transit event as well as some parameters of the planetary system can be described with a few simple relations \cite{Seager2003,Winn2010}.
 When the planet passes in front of its star produced a dimming in its flux called primary transit.
@@
 
-\section{Transit Timing Variations}
+\section{Transit Timing Variations\label{ttv}}
 
@@
 Besides the Solar System, Kepler-90 has the same number of confirmed exoplanets: eight.
-Statistically, around a 20\% of the confirmed exoplanets live in a multiplanetary system, but this number is theoretically larger (cite).
+Statistically, around a 20\% of the confirmed exoplanets live in a multiplanetary system\footnote{Information obtained from the NASA Exoplanet Archive \url{exoplanetarchive.ipac.caltech.edu}}, but this number is theoretically larger.
+\cite{Fressin2013} computed the occurrence of exoplanets through numerical simulation in Kepler data, obtaining that around $52\%$ of the stars should have at least one planet within a 85 days-orbit.
 
@@
 
-For a given light curve of a transiting exoplanet (see Fig. \ref{transit}), the transit time $T_{c}$ (or central time of the transit) is computed as:
+For a given light curve of a transiting exoplanet (see Figure \ref{transit}), the transit time $T_{c}$ (or central time of the transit) is computed as:
 
@@
 
-\begin{figure}
+\begin{figure}[ht]
 \centering
-\includegraphics[width=0.6\columnwidth]{imagenes/rms_ttv_amplitude}
-\caption{Example of a system with a transiting exoplanet of $1~M_{J}$ in a 10-day orbit, around a star with $0.367~M_{\odot}$.
-The perturber is an Earth-mass planet.
-Panel \textbf{a} is an O-C diagram showing the measured TTV when the pertuber has a period of 16.11 days, not in Mean Motion Resonance with the transiting planet.
-Panel \textbf{b} shows the TTV when the transiting planet and the perturbing planet are near an interior 2:1 resonance.
+\includegraphics[width=1.0\columnwidth]{imagenes/jupiter_ttv.pdf}
+\caption{Example of a system with a transiting exoplanet of $1~M_{J}$ in a 10-day orbit and an Earth-mass perturber planet.
+The top panel is an Observed minus Computed diagram showing the measured TTV of the Jupiter-mass planet when the pertuber has a period of 16.11 days, not in Mean Motion Resonance with the transiting planet.
+The panel at the bottom shows the TTV of the transiting planet when both are near an interior 2:1 resonance.
+In this case the small planet has a period of 19.7 days.
 The amplification of the TTV signal is by an order of magnitude.
-(Figure from \cite{Haghighipour2011})}
+Figure generated with the Python package: \texttt{ttv2fast2furious}.}
 \label{rms_ttv_amplitude}
@@
 
-To date, only two hot Jupiters have been found to show TTV signals due to the presence of additional companions on their systems: WASP-47b \citep{Becker2015} and Kepler-730b \citep{Canas2019}, even though the TTV was proposed as a technique to search for additional companions of gas giants.
+To date, only two hot Jupiters have been found to show TTV signals due to the presence of additional companions on their systems: WASP-47b \citep{Becker2015} and Kepler-730b \citep{Canas2019}, even though the TTVs was proposed as a technique to search for additional companions of gas giants.
 The lack of observed companions in hot Jupiter systems could provide crucial information about planetary formation processes.
+Through the TTV method not only the transiting exoplanet is being studied but the whole planetary system.
 
-Through the TTV method not only the transiting exoplanet is being studied but the whole planetary system.
-Even the lack of variation in the transit timing gives clues related to the formation of close-in gas giant.
-
-The no detection of TTV is also important: architecture of the system.
+\cite{Steffen2012b} analyzed Kepler data in order to constraint the occurrence rate of companions in hot Jupiter system.
+In a sample of 63 hot Jupiter candidates, none of them show evidence of possible companions in their system.
+When comparing with other types of exoplanets, 30\% of hot Neptunes candidates could have companions and 10\% of warm Jupiter candidates.
+This could suggest that hot Jupiter may have a different formation processes on which smaller companions are not allowed in their system: probably they are ejected through planet-planet scatter during migration.
+TTV studies could provide important clues about formation processes and dynamical evolution, and their mass and period dependence.

### 2019-08-18 introduction.tex
Finished Introduction

@@
 \chapter{Introduction}\label{chap:intro}
-The existence of planets orbiting other stars different from our Sun, lived in the human imagination for centuries.
-During the sixteenth century, the Italian philosopher Giordano Bruno suggested, for the first time in history, that more planet could be outside the Solar System.
-Even though the first claims of exoplanet detection began at the end of the nineteenth century, it was not until more than four hundred years after the statement of Bruno, that the first exoplanet was confirmed in 1992.
+The existence of planets orbiting other stars different from our Sun lived in the human imagination for centuries.
+During the sixteenth century, the Italian philosopher Giordano Bruno suggested, for the first time in history, that more planets could be outside the Solar System.
+Even though the first claims of exoplanet detection began at the end of the nineteenth century, it was not until more than four hundred years after Bruno's statement, that the first exoplanet was confirmed in 1992.
 Surprisingly, it was not just one exoplanet but three, orbiting the pulsar PSR B1257+12 more than 1000 light-years away from us.
@@
 
+Having billions of billions of galaxies in the Universe each one with billions of stars, the current number of discovered exoplanets is still very low.
+Furthermore, the hunting zone of exoplanets is limited by our current technology and finding an exoplanet in the closer galaxy -- Andromeda -- can be considered science fiction.
+If the Milky Way has \textit{only} around $2\,\times10^{11}$ stars, how could be the Solar System unique?
+How could be the Earth the only planet with life on it?
+Until today, it is still difficult to answer those questions.
+The Solar System presents a logic structure where the small rocky planets are closer to the Sun, and the gas giants are located beyond.
+But no other exoplanetary system have been found having similar features and even not exoplanetary life has been detected yet\footnote{By the date of writing this thesis}.
+Our knowledge about the Solar System challenges the existence of other kinds of planetary architectures with close-in gas giants, for instance, suggesting that there is not a single, universal planetary process formation.
+Answering such questions makes studying exoplanets a relevant matter nowadays.
+
 The increasing number of discovered exoplanets have been reached thanks to two techniques: Radial Velocity and Transits (see Figure \ref{exoplanets}).
 Each one of these techniques had their own advantages depending on the physical properties of the planetary system.
-When the orbit of the exoplanet is aligned with the line of sight from Earth, the pass of the planet in front of its host star causes that the star's flux decreases proportionally to the size of the planet.
+When the orbit of the exoplanet is aligned with the line of sight from Earth, the pass of the planet in front of its host star causes that the star's flux decreases, proportionally to the size of the planet.
 Thus, its radius can be determined directly using the Transit method.
@@
 In this case, the Radial Velocity method unveils the planet's minimum mass ($M_{p}\sin i$).
-The perfect scenario comes when both methods can be used in the same planetary system, allowing to derive essential properties such as the real mass and the mean density of the planet.
+The perfect scenario comes when both methods can be used in the same planetary system, allowing to derive essential properties such as the real mass and the mean density of the planet, among others.
 
-The study of exoplanets does not end with their discovery.
+Anyway, the rising research field of exoplanets does not end with their discovery.
+Performing follow-up and proper characterization of discovered exoplanets is essential to obtain a full list of orbital and planetary parameters.
+For instance,  39\%  of the total of discovered exoplanets have a proper characterization of their masses, and only 17\% have their mass and radius computed.
+Moreover, through follow-up studies several phenomena, such as atmospheres, can be unveiled.
 
-\begin{figure}[ht]
+Photometric follow-up of transiting exoplanets provides not only fundamental information about the exoplanet, but their environment.
+Variations in the transit timing -- when the planet passes in front of its star -- could be induce by companions gravitationally bounded, such as other planets in their systems or even exomoons.
+As most of the space mission have strict fields of view, performing photometric follow-up with ground-based telescopes is crucial to reveal important features of their systems.
+The Transit Timing Variation (TTV) technique is an efficient and powerful tool to detect small, unseen companions of already discovered exoplanets (see Figure \ref{exoplanets}).
+Kepler provided the firsts breaktrough discoveries of exoplanets showing TTV, and after the mission ended some project started to complete its legacy searching for TTVs.
+The Transit Monitoring in the South project (TraMoS) is one of its kind in the southern hemisphere, aiming to detect multi-exoplanetary systems trough the TTV method.
+
+\begin{figure}[t]
 \centering
@@
 I selected a new sample of transiting exoplanets, all of them hot Jupiters without any companions detected to date.
-I analized 27 new light curves of the hot Jupiters WASP-18b, WASP-19b, and WASP-77Ab searching for periodic variations in the transit time (TTV) that could suggest the presence of additional bodies in their systems.
+I analyzed 27 new light curves of the hot Jupiters WASP-18b, WASP-19b, and WASP-77Ab searching for periodic variations in the transit time (TTV) that could suggest the presence of additional bodies in their systems.
 

### 2019-08-18 abstract.tex
Finished Abstract

@@
-\begin{resumen}
+%\begin{resumen}
 
-\end{resumen}
+%\end{resumen}
 
-%\begin{abstract}
+\begin{abstract}
+The Transit Monitoring in the South (TraMoS) project aims to perform photometric follow-up in known transiting exoplanets.
+Trough photometric follow-up not only essential information about the transiting planet is provided, but their planetary system's architecture.
+Departures from the linear ephemeris given by Keplerian motion can only be spotted through extensive follow-up, these phenomena are called Transit Timing Variations (TTV) and could suggest the existence of additional bodies in the system, such as planetary companions or exomoons.
 
-%\end{abstract}
+This Master thesis recapitulates the last years of the TraMoS project, on which new targets were selected, new tools were used and new analysis were performed.
+I studied 27 new light curves of three hot Jupiters: WASP-18b, WASP-19b, and WASP-77Ab.
+Their orbital and physical parameters were refined, and their linear ephemeris updated thanks to the inclusion of archival transit time data.
+Given the lack of significant variations in their transit times, bodies with masses greater than $50\,M_{\odot}$ can be discarded for WASP-18b, $6\,M_{\odot}$ for WASP-19b, and $10\,M_{\odot}$ for WASP-77Ab.
+After the inclusion of the recent TESS data for the three targets, the linear ephemeris remains as the best fit for their transit times.
+These results support the rare existence of companions in hot Jupiters systems.
+\end{abstract}

### 2019-08-19 abstract.tex
Final draft.

--- 2019-06-03 abstract.tex
@@
-\begin{resumen}
+%\begin{resumen}
 
-\end{resumen}
+%\end{resumen}
 
-%\begin{abstract}
+\begin{abstract}
+The Transit Monitoring in the South (TraMoS) project aims to perform photometric follow-up in known transiting exoplanets.
+This process provides not only essential information about the transiting planet but also about their planetary system's architecture.
+Departures from the linear ephemeris given by Keplerian motion, the so-called Transit Timing Variations (TTV), can only be spotted through extensive follow-up, and could suggest the existence of additional bodies in the system, such as planetary companions or exomoons.
 
-%\end{abstract}
+This Master thesis recapitulates the last years of the TraMoS project, on which new targets were selected, modern tools were used and new analysis were performed.
+I studied 27 new light curves of three hot Jupiters: WASP-18b, WASP-19b, and WASP-77Ab.
+Their orbital and physical parameters were refined, and their linear ephemeris updated thanks to the inclusion of archival transit time data.
+Given the lack of significant variations in their transit times, dynamical analysis can place upper mass limits in hypothetical pertubers.
+Bodies with masses greater than $50\,M_{\odot}$ can be discarded for WASP-18b, $6\,M_{\odot}$ for WASP-19b, and $10\,M_{\odot}$ for WASP-77Ab.
+Furthermore, I included recent TESS data for the three targets, supporting the linear ephemeris as the best fit for their transit times
+
+The results presented in this thesis support the rare occurrence  of companions in hot Jupiters systems.
+Further studies may confirm if this kind of planet goes through a different formation process ending up orbiting alone on their systems or they have very small and unseen companions.
+\end{abstract}

### 2019-08-19 conclusion.tex
Final draft.

@@
 The TraMos project started more than 10 years ago aiming to refine orbital and physical parameters of already known exoplanets, and to search for variation in the transit time -- or other planet parameters -- that could suggest the existence of smaller bodies on their systems.
-Since the beginning, the targets have been hot Jupiters due to their short-periods, allowing to obtain more consecutive transit light curves in a reduced timespan.
+Since the beginning, the targets have been hot Jupiters due to their short-periods, allowing to obtain more consecutive transit light curves in a reduced period.
 
@@
 During this Master project, I studied three exoplanets: WASP-18b, WASP-19b, and WASP-77Ab.
-For these targets, I analyzed a total of twentysix new light curves: eight of WASP-18b, nine of WASP-19b and nine of WASP-77Ab.
+For these targets, I analyzed a total of twenty-six new light curves: eight of WASP-18b, nine of WASP-19b and nine of WASP-77Ab.
 In the case of WASP-77Ab, four light curves were taken from the Exoplanet Transit Database (ETD)\footnote{\url{var2.astro.cz/ETD}} to obtain a wider time coverage.
 For the light curves coming from the TraMoS project, I started from performing aperture photometry of the targets using our data reduction pipeline (for further details see \ref{chap:pipeline}), in order to obtain high-precision light curves.
-Then, I used EXOFASTv2 \cite{Eastman2013,Eastman2017} to get the best-fit for the light curve's data and hence, to refine their orbital and physical parameters and obtain their transit times.
+Then, I used EXOFASTv2 \cite{Eastman2013,Eastman2017} to get the best fit for the light curve's data and hence, to refine their orbital and physical parameters and obtain their transit times.
 
 The TTV curves were constructed from the residuals between the observed transit time and the expected from the linear ephemeris.
-None of the targets studied in this thesis, shows a clear, periodic sinusoidal signal in the variation of their transit times and moreover, the structure of the transit times are comparable with a random distribution after a Lomb-Scargle analysis.
+None of the targets studied in this thesis shows a clear, periodic sinusoidal signal in the variation of their transit times and moreover, the structure of the transit times are comparable with a random distribution after a Lomb-Scargle analysis.
 This suggests the lack of close-in companions in MMR in their systems.
-However, upper mass limit of hypothetical perturbers -- placed not only in near MMR -- could be computed with the time-scatter from the linear ephemeris.
+However, upper mass limits of hypothetical perturbers -- placed not only in near MMR -- could be computed with the time-scatter from the linear ephemeris.
 The hot Jupiter WASP-18b shows 83 seconds of scatter, WASP-19b shows 75 seconds and WASP-77ab shows 121 seconds.
-The latter being the target with larger deviation from the linear ephemeris, but at the same time, the target with less transit times.
+The latter being the target with a larger deviation from the linear ephemeris, but at the same time, the target with fewer transit times.
 
@@
 
-After the release of TESS data, I included transit times of the targets studied in this thesis, in order to extend their TTV curves and confirm the lack of periodic variations in the transit time.
+After the release of TESS data, I included transit times of the targets studied in this thesis, to extend their TTV curves and confirm the lack of periodic variations in the transit time.
 The results came out as expected and the scatter in the transit time were reduced for the three targets: 47 seconds for WASP-18b, 65 seconds for WASP-19b and 86 seconds for WASP-77Ab.
-Moreover, I refined each orbital period obtaining a precision of the order of milli-seconds.
+Moreover, I refined each orbital period obtaining a precision of the order of milliseconds.
 
 To date, none of the previous and current targets of the TraMoS project have shown TTVs.
-As they are all hot Jupiters, these studies support the theory of "alone hot Jupiters", on which this kind of exoplanets are probably alone in their systems or accompanied of small bodies not in MMR.
+As they are all hot Jupiters, these studies support the theory of "alone hot Jupiters", on which this kind of exoplanets are probably alone in their systems or accompanied of small bodies, not in MMR.
 How WASP-47b and Kepler-730b, the only two hot Jupiters showing TTVs, have close-in companions is still unknown.
@@
 
-The TraMoS catalogue stores more than 400 transits events of near 140 exoplanets.
-As future work I propose to continue performing ground-based photometric follow-up of the targets in this catalogue, as well as new targets, combining the efforts with TESS data of Sector 1 to 13.
+The TraMoS catalog stores more than 400 transits events of near 140 exoplanets.
+As future work, I propose to continue performing a ground-based photometric follow-up of the targets in this catalog, as well as new targets, combining the efforts with TESS data of Sector 1 to 13.
 In this way, we could obtain better estimations of TTVs with wider time-span data from TraMoS, and an important amount of consecutive transit times from TESS.
-In the near future, I will analyze the exoplanets WASP-36b and HATS-34b, which each one has five transit times from TraMoS and twelve and twenty six from TESS, respectively.
-For WASP-22, WASP-46, WASP-45, WASP-23 and WASP-123, TESS provided five, seventeen, eight, seven and thirteen light curves, respectively.
+In the near future, given the new scatter of the transit time in the three targets analyzed in this thesis, more accurate upper mass limits for hypothetical perturbers could be computed.
+Also, I will analyze the exoplanets WASP-36b and HATS-34b, which each one has five transit times from TraMoS and twelve and twenty-six from TESS, respectively.
+For WASP-22, WASP-46, WASP-45, WASP-23, and WASP-123, TESS provided five, seventeen, eight, seven and thirteen light curves, respectively.
 These targets are within the 30 targets with most light curves from TraMoS, therefore, they should be the next in line.
 
-The reduction pipeline is fully functional and provides high-precision photometry, nevertheless several improvements were left behind because of the lack of time to implement them.
+The reduction pipeline is fully functional and provides high-precision photometry, nevertheless, several improvements were left behind because of the lack of time to implement them.
 For example, the coordinates selection could be done inside the program, to avoid mistakes when typing them by hand before calling the pipeline.
-Any new idea to improvement the reduction pipeline could be done within an undergrad project or graduate semester-workshop.
+Any new idea to improve the reduction pipeline could be done within an undergrad project or graduate semester-workshop.

### 2019-08-19 introduction.tex
Final draft.

@@
 
-Having billions of billions of galaxies in the Universe each one with billions of stars, the current number of discovered exoplanets is still very low.
-Furthermore, the hunting zone of exoplanets is limited by our current technology and finding an exoplanet in the closer galaxy -- Andromeda -- can be considered science fiction.
+Having billions of billions of galaxies in the Universe each one with millions of stars, the current number of discovered exoplanets is still very low.
+Furthermore, the hunting zone of exoplanets is limited by our current technology and finding an exoplanet in the closer galaxy -- Andromeda -- could be considered science fiction.
 If the Milky Way has \textit{only} around $2\,\times10^{11}$ stars, how could be the Solar System unique?
@@
 Until today, it is still difficult to answer those questions.
-The Solar System presents a logic structure where the small rocky planets are closer to the Sun, and the gas giants are located beyond.
-But no other exoplanetary system have been found having similar features and even not exoplanetary life has been detected yet\footnote{By the date of writing this thesis}.
+The Solar System presents a logic structure where the small, rocky planets are closer to the Sun, and the gas giants are located beyond.
+But no other exoplanetary system have been found having similar features and even not exoplanetary life has been detected yet\footnote{By the date of writing this thesis.}.
 Our knowledge about the Solar System challenges the existence of other kinds of planetary architectures with close-in gas giants, for instance, suggesting that there is not a single, universal planetary process formation.
@@
 Performing follow-up and proper characterization of discovered exoplanets is essential to obtain a full list of orbital and planetary parameters.
-For instance,  39\%  of the total of discovered exoplanets have a proper characterization of their masses, and only 17\% have their mass and radius computed.
-Moreover, through follow-up studies several phenomena, such as atmospheres, can be unveiled.
-
-Photometric follow-up of transiting exoplanets provides not only fundamental information about the exoplanet, but their environment.
-Variations in the transit timing -- when the planet passes in front of its star -- could be induce by companions gravitationally bounded, such as other planets in their systems or even exomoons.
-As most of the space mission have strict fields of view, performing photometric follow-up with ground-based telescopes is crucial to reveal important features of their systems.
-The Transit Timing Variation (TTV) technique is an efficient and powerful tool to detect small, unseen companions of already discovered exoplanets (see Figure \ref{exoplanets}).
-Kepler provided the firsts breaktrough discoveries of exoplanets showing TTV, and after the mission ended some project started to complete its legacy searching for TTVs.
-The Transit Monitoring in the South project (TraMoS) is one of its kind in the southern hemisphere, aiming to detect multi-exoplanetary systems trough the TTV method.
+For instance,  39\%  of the total number of discovered exoplanets have a proper measurement of their masses, and only 17\% have their mass and radius computed.
+Moreover, through follow-up studies several phenomena, such as their atmospheres, can be unveiled.
 
@@
 \includegraphics[width=1.0\columnwidth]{imagenes/exoplanets_hd.pdf}
-\caption{Mass and orbital period distribution of Exoplanets, and their corresponding discovery methods in color. This plot only shows the exoplanets with known masses}
+\caption{Mass and orbital period distribution of Exoplanets, and their corresponding discovery methods in color.
+This plot only shows the exoplanets with measured masses.
+The Transit and Radial Velocity methods (in orange and blue, respectively) are the most successful techniques to discover extrasolar planets.
+However, both techniques are still more sensitive to detect Jupiter-mass planets rather than Earth-mass, but the Transit method is more sensitive to short-period planets.}
 \label{exoplanets}
 \end{figure}
+
+Photometric follow-up of transiting exoplanets provides not only fundamental information about the exoplanet but their environment.
+Variations in the transit timing -- when the planet passes in front of its star -- could be induced by companions gravitationally bounded, such as other planets in their systems or even exomoons \citep{Kipping2009a,Kipping2009b}.
+As most of the space mission have strict fields of view, performing photometric follow-up with ground-based telescopes is crucial to reveal important features of their systems.
+The Transit Timing Variation (TTV) technique \citep{Holman2005,Agol2005} is an efficient and powerful tool to detect small, unseen companions of already discovered exoplanets (see Figure \ref{exoplanets}).
+Kepler provided the firsts breakthrough discoveries of exoplanets showing TTV \citep{Holman2010}, and after the mission ended some projects started aiming to complete its legacy searching for TTVs.
+The Transit Monitoring in the South project (TraMoS) is one of its kind in the southern hemisphere, aiming to detect multi-exoplanetary systems trough the TTV method.
 
@@
 Here, I re-analyze the TTV curves of the previous targets WASP-18b, WASP-19b, and WASP-77Ab with new light curves from TESS.
-Finally, Chapter \ref{chap:conclusion} contains the principal conclusions of this thesis as well as some ideas for future work.
+Finally, Chapter \ref{chap:conclusion} contains a summary of this thesis as well as some ideas for future work.
 The Appendix section includes a brief description of the aperture photometry pipeline utilized, all the Python scripts used to generate each light curve, and an example of the PDF file obtained after the aperture photometry procedure.

### 2019-08-19 tess.tex
TraMoS chapter ready.
Final draft.

@@
 
-Thus, for the currently and future stage of the TraMoS project, archival data - collected since 2008 - will be combined with the upcoming TESS data and new ground-based observations using one-meter class telescopes.
+Thus, for the currently and future stage of the TraMoS project, archival data -- collected since 2008 -- will be combined with the upcoming TESS data and new ground-based observations using one-meter class telescopes.
 The main goal of the project will remain the same: refine orbital and physical parameters of exoplanetary system and search for variations in the transit time, that could suggest the presence of additional small bodies in the system.
@@
 In the following subsections, I present a re-analysis of the TTV curves of the hot Jupiters: WASP-18b, WASP-19b and WASP-77Ab including new transit times from TESS: 45, 28, and 15 for WASP-18b, WASP-19b and WASP-77Ab respectively.
-In order to compute the transit time of each light curve, I used EXOFASTv2 but only to fit the transit time and the flux baseline.
+In order to compute the transit time of each light curve, I used EXOFASTv2 to only fit the transit time and the flux's baseline.
 The remaining planetary parameters were fixed with the values from Tables \ref{wasp18}, \ref{tab:wasp19}, \ref{tab:wasp77}.
@@
 
-\section{WASP-36b}
+%\section{WASP-36b}
 
-The exoplanet WASP-36b was selected as the
+%The exoplanet WASP-36b was selected as the

### 2019-08-19 tramos.tex
Final draft.

@@
 
-The Transit Monitoring in the South (TraMoS) project started in 2008 aiming to perform photometric follow-up of transiting exoplanets using telescopes located in Chile.
+The Transit Monitoring in the South (TraMoS) project started in 2008 aiming to perform a photometric follow-up of transiting exoplanets using telescopes located in Chile.
 Through photometric monitoring of transiting events, important information of the planetary system can be obtained, such as the planetary radius, inclination of the orbit, precise planetary mass, among others.
 Moreover, this kind of analysis allows the detection of variability in the transit's parameters (TPV), if several epochs of the transit event are included.
-The TraMoS project aims, on the one hand, to refine the physical and orbital parameters of selected exoplanets systems through photometric follow-up and, on the other hand, to search variations in that parameters that could suggest the presence of additional bodies in the system.
+The TraMoS project aims, on one hand, to refine the physical and orbital parameters of selected exoplanets systems through photometric follow-up and, on the other, to search variations in those parameters that could suggest the presence of additional bodies in the system.
 
@@
 \caption{Histogram of the 30 transiting exoplanets with the largest amount of observations within the TraMoS project.
-The exoplanets WASP-4b and WASP5-b were presented in \cite{Hoyer2012} and \cite{Hoyer2013}.
+The exoplanets WASP-4b and WASP5-b were presented in \cite{Hoyer2012} and \cite{Hoyer2013}, respectively.
 The results from the analysis of WASP-18b, WASP-19b and WASP77-Ab are in Cortés-Zuleta et al.
@@
 
-In the following section \ref{lightcurve}, I describe the light curve produced from a transiting exoplanet --the principal target of the TraMoS project --  what information about the planet can be obtain from them and how these light curves can give us information about the architecture of this kind of systems.
-Then, in section \ref{ttv}, I detail on an specific type of phenomena of transiting exoplanets: the variation of the transit time of its light curve (TTV).
+In the following section \ref{lightcurve}, I describe the light curve produced from a transiting exoplanet --the principal target of the TraMoS project --  what information about the planet can be obtained from them and how these light curves can give us information about the architecture of this kind of systems.
+Then, in section \ref{ttv}, I detail on a specific type of phenomena of transiting exoplanets: the variation of the transit time of its light curve (TTV).
 
@@
 
-The light curve produced by a transit event provides important information of the planetary system.
+The light curve produced by a transit event provides important information about the planetary system.
 For example, it is the only way on which we can derive directly the proportion between the exoplanet and star radius.
-It can also gives information about the impact parameter, and therefore, the inclination of the orbit.
+It can also give information about the impact parameter, and therefore, the inclination of the orbit.
 
 In Figure~\ref{transit} is described the architecture of a transiting exoplanet.
-Thanks to its geometry, the transit event as well as some parameters of the planetary system can be described with a few simple relations \cite{Seager2003,Winn2010}.
+Thanks to its geometry, the transit event, as well as some parameters of the planetary system, can be described with a few simple relations \cite{Seager2003,Winn2010}.
 When the planet passes in front of its star produced a dimming in its flux called primary transit.
@@
 \caption{Architecture of a transiting exoplanet and the observed light curve.
-Based on the light curve itself it is possible to measure the transit depth $\Delta F$, the impact parameter $b$.
+Based on the light curve itself it is possible to measure the transit depth $\Delta F$ and the impact parameter $b$.
 From them, the planet-to-star radius ratio $R_{p}/R_{*}$ and the orbital inclination $i$ can be derived.
@@
 Statistically, around a 20\% of the confirmed exoplanets live in a multiplanetary system\footnote{Information obtained from the NASA Exoplanet Archive \url{exoplanetarchive.ipac.caltech.edu}}, but this number is theoretically larger.
-\cite{Fressin2013} computed the occurrence of exoplanets through numerical simulation in Kepler data, obtaining that around $52\%$ of the stars should have at least one planet within a 85 days-orbit.
+\cite{Fressin2013} computed the occurrence of exoplanets through numerical simulation in Kepler data, obtaining that around $52\%$ of the stars should have at least one planet within a 85 days orbit.
 
@@
 
-\cite{Holman2010} presented the first multiplanetary system confirmed using the TTV method: two planets orbiting Kepler-9, a Sun-like star.
+\cite{Holman2010} presented the first multi-planetary system confirmed using the TTV method: two planets orbiting Kepler-9, a Sun-like star.
 These two Saturn-size planets are in near 2:1 orbital resonance with periods of 38.9 and 19.2 days.
-In order to model the dynamical interaction of the system, only 9 transits of Kepler-9b and 6 from Kepler-9c were required.
+To model the dynamical interaction of the system, only 9 transits of Kepler-9b and 6 from Kepler-9c were required.
 This confirmed the effectiveness of the TTV method to characterize planetary systems with a scarce number of transits.
 
-Since the discovery of \cite{Holman2010}, around 20 exoplanets have been discovered and characterized thanks to the measurement of variations on their transit times and the following proper dynamical model ling of the system.
+Since the discovery of \cite{Holman2010}, around 20 exoplanets have been discovered and characterized thanks to the measurement of variations on their transit times and the following proper dynamical modeling of the system.
 Most of them are Kepler systems because of its high duty-cycle, on which it provided years on transits data.
-Kepler stopped working on 2018, but the Transit Exoplanet Satellite Survey (TESS) is currently providing its first results providing planetary systems showing TTVs.
-For example, two exoplanets (possibly one Jupiter and a sub-Saturn like) were recently discovered by \cite{Dawson2019} orbiting TOI-216, in near 2:1 resonance.
+Kepler stopped working on 2018, but the Transit Exoplanet Satellite Survey (TESS) is currently delivering its first results with new planetary systems showing TTVs.
+For example, two exoplanets -- possibly one Jupiter and a sub-Saturn like -- were recently discovered by \cite{Dawson2019} orbiting TOI-216, in near 2:1 resonance.
 
@@
 
-\cite{Steffen2012b} analyzed Kepler data in order to constraint the occurrence rate of companions in hot Jupiter system.
+\cite{Steffen2012b} analyzed Kepler data to constraint the occurrence rate of companions in hot Jupiter system.
 In a sample of 63 hot Jupiter candidates, none of them show evidence of possible companions in their system.
-When comparing with other types of exoplanets, 30\% of hot Neptunes candidates could have companions and 10\% of warm Jupiter candidates.
-This could suggest that hot Jupiter may have a different formation processes on which smaller companions are not allowed in their system: probably they are ejected through planet-planet scatter during migration.
+When comparing with other types of exoplanets, 30\% of hot Neptune candidates may have companions and 10\% of warm Jupiter candidates.
+This could suggest that hot Jupiter may have different formation processes on which smaller companions are not allowed in their system: probably they are ejected through planet-planet scatter during migration.
 TTV studies could provide important clues about formation processes and dynamical evolution, and their mass and period dependence.

### 2019-08-21 introduction.tex
Changes after first revision

@@
 \chapter{Introduction}\label{chap:intro}
-The existence of planets orbiting other stars different from our Sun lived in the human imagination for centuries.
+The idea of the existence of planets orbiting other stars different from our Sun lived in the human imagination for centuries.
 During the sixteenth century, the Italian philosopher Giordano Bruno suggested, for the first time in history, that more planets could be outside the Solar System.
@@
 
+%cita del sixteenth century
+%frases sobre otros métodos
+
 Having billions of billions of galaxies in the Universe each one with millions of stars, the current number of discovered exoplanets is still very low.
-Furthermore, the hunting zone of exoplanets is limited by our current technology and finding an exoplanet in the closer galaxy -- Andromeda -- could be considered science fiction.
+Furthermore, the distance at which we can detect exoplanets is limited by our current technology, thus finding a candidate in the closer galaxy -- Andromeda -- could be considered science fiction.
 If the Milky Way has \textit{only} around $2\,\times10^{11}$ stars, how could be the Solar System unique?
@@
 
-The increasing number of discovered exoplanets have been reached thanks to two techniques: Radial Velocity and Transits (see Figure \ref{exoplanets}).
+The discovery of three exoplanets orbiting the pulsar PSR B1257+12 is still very rare.
+The technique used to find them is called Pulsar Timing and it consists in measuring the variation of a pulsar's pulsation period due to the presence of a body orbiting it.
+As pulsars are not very common and we know that planet may be orbiting main sequence stars -- as the Earth and all the Solar System --, the latter become the principal target on which the hunting of exoplanet is dedicated.
+Planets are small when compare to their host star, that is why most of the current discovery techniques are focus in observing the effects in the stars, or how what we observed from them changed, caused by the presence of planets.
+Nevertheless, Direct Imaging is the only technique on which the planet is observed directly but the star needs to be covered to only received the thermal emission produced by the planet.
+
+Microlensing is different from all the other discovery techniques, because a third, bright background star is required to obtain the desire effect: a gravitational lensing is produced by the star with a planet (multiple lens).
+As the primary lens is small -- around $1\,M_{odot}$ -- the two images produced by the gravitational lensing are very close between each other and the event can not be resolved.
+The presence of a planet will cause a deviation in the magnification curve of the event.
+In the other hand, Astrometry measurements can be use to discover exoplanets too.
+With the current high-precision in the position of the stars, even their displacement in the sky can be detected.
+Similar to the Radial Velocity technique, through Astrometry the displacement of the star due to the gravity of a planet can be measure.
+
+The two techniques that have contributed the most to the discovery of extrasolar planets are Radial Velocity and Transits (see Figure \ref{exoplanets}).
 Each one of these techniques had their own advantages depending on the physical properties of the planetary system.
-When the orbit of the exoplanet is aligned with the line of sight from Earth, the pass of the planet in front of its host star causes that the star's flux decreases, proportionally to the size of the planet.
-Thus, its radius can be determined directly using the Transit method.
+When the orbit of the exoplanet is aligned with the line of sight from Earth, the pass of the planet in front of its host star causes that the star's flux decreases, proportionally to the radius of the planet.
+Thus, the radius ratio between the planet and the star, $R_{p}/R_{*}$ can be determined directly using the Transit method.
 In the other hand, the gravity due to the presence of a planet will set the center of mass of the system, in a place different from the star's center.
-Therefore, the star will move in its own small orbit with a size proportional to the mass of the planet.
+Therefore, the star will move in its own small orbit with a radius proportional to the mass of the planet.
 In this case, the Radial Velocity method unveils the planet's minimum mass ($M_{p}\sin i$).
-The perfect scenario comes when both methods can be used in the same planetary system, allowing to derive essential properties such as the real mass and the mean density of the planet, among others.
 
@@
 Performing follow-up and proper characterization of discovered exoplanets is essential to obtain a full list of orbital and planetary parameters.
-For instance,  39\%  of the total number of discovered exoplanets have a proper measurement of their masses, and only 17\% have their mass and radius computed.
-Moreover, through follow-up studies several phenomena, such as their atmospheres, can be unveiled.
+For instance,  39\%  of the total number of discovered exoplanets have a proper measurement of their masses, and only 17\% have their mass and radius computed\footnote{c.f.
+NASA Exoplanet Archive Database.}.
+
+%Moreover, through follow-up studies important information about the planet can be unveiled, even their atmospheric composition and dynamics.
+
+The perfect scenario comes when both methods, Transits and Radial Velocity, can be used in the same planetary system, allowing to derive essential properties of the planet.
+Combining Transits and Radial Velocity follow-up the whole system can be characterize.
+From Transits we get the orbital inclination, then the real mass can be computed with Radial Velocity measurements.
+From Transits we get the radius ratio of the system, assuming that the star is previously well characterized, the radius of the planet is derived.
+Then, as we already have the mass of the planet, the mean density can be estimated.
+This parameter gives a clue of the possible composition of the planet.
+Moreover, if the follow-up is performed combining Transits with big telescopes, for instance the Very Large Telescope, important information about the planet can be unveiled, even their atmospheric composition and dynamics.
 
@@
 
-Photometric follow-up of transiting exoplanets provides not only fundamental information about the exoplanet but their environment.
+% Photometric follow-up of transiting exoplanets provides not only fundamental information about the exoplanet but their environment.
+
+%The Transit method is today the most successful technique to discover extrasolar planets (see Figure \ref{amount_exoplanet}).
+The Kepler mission was launched in 2009 and during its almost nine years of operation provided thousands of discoveries due to this method.
+
+Continued photometric monitoring not only increased precision of planetary parameters but provides potential information about the planet and its environment. Through the continued 
  Variations in the transit timing -- when the planet passes in front of its star -- could be induced by companions gravitationally bounded, such as other planets in their systems or even exomoons \citep{Kipping2009a,Kipping2009b}.

### 2019-08-21 paper.tex
Changes after first revision

@@
 It is an extremely close-in planet orbiting a F6 type star with a period of 0.94 days.
-Regarding its physical properties, WASP-18b is about ten times more massive than Jupiter with approximately the same size ($M_{P}=10.3\,{\rm M_{Jupiter}}$, $R_{P}=1.1\,{\rm R_{Jupiter}}$).
+Regarding its physical properties, WASP-18b is about ten times more massive than Jupiter with approximately the same radius ($M_{P}=10.3\,{\rm M_{Jupiter}}$, $R_{P}=1.1\,{\rm R_{Jupiter}}$).
 Even though a rapid orbital decay was predicted theoretically \citep{Hellier2009}, it is not observed yet \citep{Wilkins2017} and new theoretical models proposed a variation of less than 4 seconds in the transit time over a 20-yr baseline \citep{CollierCameron2018}.

### 2019-08-21 tess.tex
Changes after first revision

@@
 
-Between Sector 1 and Sector 13, TESS observed around 15\% of the stars with confirmed exoplanets but not all of them will produce a transit event within the 27 days of a sector duration (see Figure \ref{chap:tess}).
+Between Sector 1 and Sector 13, TESS observed around 15\% (see Figure \ref{tess_match.pdf}) of the stars with confirmed exoplanets but not all of them will produce a transit event within the 27 days sector's duration (see Figure \ref{chap:tess}).
 Anyway, several complete light curves could be obtained and analyzed.
@@
 The black cross indicates which star was already observed by TESS.
-However, this does not indicate that transit light curves will be provided for sure since the orbital period of the exoplanet needs to be taken into account.
-Thus, the first year mission of TESS will provide for sure transit data of the exoplanets with filled red circle and a black cross .}
+However, this does not indicate that transit light curves will be provided for sure since the orbital period of the exoplanet needs to be considered.
+Thus, the first year mission of TESS will provide for sure transit data of the exoplanets with filled red circle and a black cross.
+The zone in the sky within the big black circle corresponds to the Kepler field of view, where the bulk of discovered exoplanets are located.}
 \label{match_tess}
@@
 
+% Did I include only transiting exoplanets?
+
 Thus, for the currently and future stage of the TraMoS project, archival data -- collected since 2008 -- will be combined with the upcoming TESS data and new ground-based observations using one-meter class telescopes.
-The main goal of the project will remain the same: refine orbital and physical parameters of exoplanetary system and search for variations in the transit time, that could suggest the presence of additional small bodies in the system.
+The main goal of the project remains the same: refine orbital and physical parameters of exoplanetary system and search for variations in those parameters, that could suggest the presence of additional small bodies in the system.
 The KOINet project proved that ground-based follow-up are, in some cases, essential to complete a possible TTV signal, and therefore, to confirm or rule out variations in the transit time.

### 2019-08-21 tramos.tex
Changes after first revision

@@
 \section{Transiting exoplanets' light curve\label{lightcurve}}
-The Transit method is today the most successful technique to discover extrasolar planets (see Figure \ref{amount_exoplanet}).
-The Kepler mission was launched in 2009 and during its almost nine years of operation provided thousands of discoveries due to this method.
 
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.7\columnwidth]{imagenes/exo_dischist_cumulative.png}
-\caption{Accumulative number of discovered exoplanets by year and their corresponding method of discovery.
+%\begin{figure}[ht]
+%\centering
+%\includegraphics[width=0.7\columnwidth]{imagenes/exo_dischist_cumulative.png}
+%\caption{Accumulative number of discovered exoplanets by year and their corresponding method of discovery.
 To date, the Transit technique, along with Radial Velocity, are the most successful methods to discovery exoplanets.
 Figure from the NASA Exoplanet Archive (\url{exoplanetarchive.ipac.caltech.edu})}
-\label{amount_exoplanet}
-\end{figure}
+%\label{amount_exoplanet}
+%\end{figure}
 
@@
 In Figure~\ref{transit} is described the architecture of a transiting exoplanet.
-Thanks to its geometry, the transit event, as well as some parameters of the planetary system, can be described with a few simple relations \cite{Seager2003,Winn2010}.
+Thanks to its geometry, the transit light curve and the parameters of the planetary system can be described with a few simple relations \cite{Seager2003,Winn2010}.
 When the planet passes in front of its star produced a dimming in its flux called primary transit.
@@
 Besides the Solar System, Kepler-90 has the same number of confirmed exoplanets: eight.
-Statistically, around a 20\% of the confirmed exoplanets live in a multiplanetary system\footnote{Information obtained from the NASA Exoplanet Archive \url{exoplanetarchive.ipac.caltech.edu}}, but this number is theoretically larger.
-\cite{Fressin2013} computed the occurrence of exoplanets through numerical simulation in Kepler data, obtaining that around $52\%$ of the stars should have at least one planet within a 85 days orbit.
+Statistically, around a 20\% of the confirmed exoplanets live in a multiplanetary system\footnote{Information obtained from the NASA Exoplanet Archive Database \url{exoplanetarchive.ipac.caltech.edu}}, but this number is theoretically larger.
+\cite{Fressin2013} computed the occurrence of exoplanets through numerical simulation with Kepler data, obtaining that around $52\%$ of the stars should have at least one planet within a 85 days orbit.
 

### 2019-08-22 abstract.tex
Version 3.0

@@
 This process provides not only essential information about the transiting planet but also about their planetary system's architecture.
-Departures from the linear ephemeris given by Keplerian motion, the so-called Transit Timing Variations (TTV), can only be spotted through extensive follow-up, and could suggest the existence of additional bodies in the system, such as planetary companions or exomoons.
+Departures from the linear ephemeris given by Keplerian motion, the so-called Transit Timing Variations (TTV), can only be spotted through extensive follow-up and could suggest the existence of additional bodies in the system, such as planetary companions or exomoons.
 
-This Master thesis recapitulates the last years of the TraMoS project, on which new targets were selected, modern tools were used and new analysis were performed.
+This Master thesis recapitulates the last years of the TraMoS project, on which new targets were selected, modern tools were used and new analysis was performed.
 I studied 27 new light curves of three hot Jupiters: WASP-18b, WASP-19b, and WASP-77Ab.
 Their orbital and physical parameters were refined, and their linear ephemeris updated thanks to the inclusion of archival transit time data.
-Given the lack of significant variations in their transit times, dynamical analysis can place upper mass limits in hypothetical pertubers.
+Given the lack of significant variations in their transit times, dynamical analysis can place upper mass limits in hypothetical perturbers.
 Bodies with masses greater than $50\,M_{\odot}$ can be discarded for WASP-18b, $6\,M_{\odot}$ for WASP-19b, and $10\,M_{\odot}$ for WASP-77Ab.
@@
 Further studies may confirm if this kind of planet goes through a different formation process ending up orbiting alone on their systems or they have very small and unseen companions.
+
 \end{abstract}

### 2019-08-22 conclusion.tex
Version 3.0

@@
 In the case of WASP-77Ab, four light curves were taken from the Exoplanet Transit Database (ETD)\footnote{\url{var2.astro.cz/ETD}} to obtain a wider time coverage.
-For the light curves coming from the TraMoS project, I started from performing aperture photometry of the targets using our data reduction pipeline (for further details see \ref{chap:pipeline}), in order to obtain high-precision light curves.
+For the light curves coming from the TraMoS project, I started from performing aperture photometry of the targets using our data reduction pipeline (for further details see \ref{chap:pipeline}), to obtain high-precision light curves.
 Then, I used EXOFASTv2 \cite{Eastman2013,Eastman2017} to get the best fit for the light curve's data and hence, to refine their orbital and physical parameters and obtain their transit times.

### 2019-08-22 introduction.tex
Version 3.0

@@
 During the sixteenth century, the Italian philosopher Giordano Bruno suggested, for the first time in history, that more planets could be outside the Solar System.
-Even though the first claims of exoplanet detection began at the end of the nineteenth century, it was not until more than four hundred years after Bruno's statement, that the first exoplanet was confirmed in 1992.
+Even though the first claims of exoplanet detection began at the begin of the twentieth century\footnote{The van Maanen 2 star, which later was confirmed as a white dwarf.}, it was not until more than four hundred years after Bruno's statement, that the first exoplanet was confirmed in 1992.
 Surprisingly, it was not just one exoplanet but three, orbiting the pulsar PSR B1257+12 more than 1000 light-years away from us.
 Today, more than 4,000 exoplanets are confirmed, and thousands more are waiting for their confirmation.
-
-%cita del sixteenth century
-%frases sobre otros métodos
 
@@
 The technique used to find them is called Pulsar Timing and it consists in measuring the variation of a pulsar's pulsation period due to the presence of a body orbiting it.
-As pulsars are not very common and we know that planet may be orbiting main sequence stars -- as the Earth and all the Solar System --, the latter become the principal target on which the hunting of exoplanet is dedicated.
-Planets are small when compare to their host star, that is why most of the current discovery techniques are focus in observing the effects in the stars, or how what we observed from them changed, caused by the presence of planets.
-Nevertheless, Direct Imaging is the only technique on which the planet is observed directly but the star needs to be covered to only received the thermal emission produced by the planet.
+As pulsars are not very common and we know that planet may be orbiting main-sequence stars -- as the Earth and all the Solar System --, the latter become the principal target on which the hunting of exoplanet is dedicated.
+Planets are small when compare to their host star, that is why most of the current discovery techniques are focused on observing the effects in the stars, or how what we observed from them changed, caused by the presence of planets.
+Nevertheless, Direct Imaging is the only technique in which the planet is observed directly but the star needs to be covered to only received the thermal emission produced by the planet.
 
-Microlensing is different from all the other discovery techniques, because a third, bright background star is required to obtain the desire effect: a gravitational lensing is produced by the star with a planet (multiple lens).
-As the primary lens is small -- around $1\,M_{odot}$ -- the two images produced by the gravitational lensing are very close between each other and the event can not be resolved.
+Microlensing is different from all the other discovery techniques because a third, bright background star is required to obtain the desired effect: gravitational lensing produced by the star with a planet (multiple lenses).
+As the primary lens is small -- around $1\,M_{\odot}$ -- the two images produced by the gravitational lensing are very close between each other and the event can not be resolved.
 The presence of a planet will cause a deviation in the magnification curve of the event.
-In the other hand, Astrometry measurements can be use to discover exoplanets too.
+On the other hand, Astrometry measurements can be used to discover exoplanets too.
 With the current high-precision in the position of the stars, even their displacement in the sky can be detected.
-Similar to the Radial Velocity technique, through Astrometry the displacement of the star due to the gravity of a planet can be measure.
+Similar to the Radial Velocity technique, through Astrometry the displacement of the star due to the gravity of a planet is measured.
 
@@
 Thus, the radius ratio between the planet and the star, $R_{p}/R_{*}$ can be determined directly using the Transit method.
-In the other hand, the gravity due to the presence of a planet will set the center of mass of the system, in a place different from the star's center.
+On the other hand, the gravity due to the presence of a planet will set the center of mass of the system, in a place different from the star's center.
 Therefore, the star will move in its own small orbit with a radius proportional to the mass of the planet.
-In this case, the Radial Velocity method unveils the planet's minimum mass ($M_{p}\sin i$).
+In this case, the Radial Velocity method unveils the planet's minimum mass $M_{p}\sin i$.
 
 Anyway, the rising research field of exoplanets does not end with their discovery.
-Performing follow-up and proper characterization of discovered exoplanets is essential to obtain a full list of orbital and planetary parameters.
-For instance,  39\%  of the total number of discovered exoplanets have a proper measurement of their masses, and only 17\% have their mass and radius computed\footnote{c.f.
-NASA Exoplanet Archive Database.}.
+Performing follow-up and proper characterization of discovered exoplanets are essential to obtain a full list of orbital and planetary parameters.
+For instance,  39\%  of the total number of discovered exoplanets have a proper measurement of their masses, and only 17\% have their mass and radius computed\footnote{Information obtained from the NASA Exoplanet Archive Database \url{exoplanetarchive.ipac.caltech.edu}}.
 
@@
 The perfect scenario comes when both methods, Transits and Radial Velocity, can be used in the same planetary system, allowing to derive essential properties of the planet.
-Combining Transits and Radial Velocity follow-up the whole system can be characterize.
+Combining Transits and Radial Velocity follow-up the whole system can be characterized.
 From Transits we get the orbital inclination, then the real mass can be computed with Radial Velocity measurements.
@@
 Then, as we already have the mass of the planet, the mean density can be estimated.
-This parameter gives a clue of the possible composition of the planet.
-Moreover, if the follow-up is performed combining Transits with big telescopes, for instance the Very Large Telescope, important information about the planet can be unveiled, even their atmospheric composition and dynamics.
+This parameter gives a clue about the possible composition of the planet.
+Moreover, if the follow-up is performed combining Transits with big telescopes, for instance, the Very Large Telescope, important information about the planet can be unveiled, even their atmospheric composition and dynamics.
 
@@
 
-Continued photometric monitoring not only increased precision of planetary parameters but provides potential information about the planet and its environment. Through the continued 
- Variations in the transit timing -- when the planet passes in front of its star -- could be induced by companions gravitationally bounded, such as other planets in their systems or even exomoons \citep{Kipping2009a,Kipping2009b}.
+Continued photometric monitoring not only increased the precision of planetary parameters but provides potential information about the planet and its environment.
+Through the observation of transit events during several epochs, variability in the planetary system can be detected.
+For instance, the first measurement of two planets gravitationally bounded was made by \citep{Holman2010}, this discovery was made thanks to the continued observations performed by the Kepler mission.
+This phenomenon is detectable observing during several epochs just one of the planets involved and analyzing how the presence of a companion produces such variability.
+Moreover, variability in transiting exoplanets -- specifically in the time of the transit -- can be attributed not only to planetary companions, but exomoons\citep{Kipping2009a,Kipping2009b}, tidal orbital decay\citep{Hoyer2016,Hoyer2016b}, secular orbits changes\citep{Adams2006} or relativistic effects \citep{Heyl2007}, among others.
+
+The Transit Monitoring in the South project (TraMoS) is one of its kind in the southern hemisphere, aiming to detect multi-exoplanetary systems trough the variability in transit parameters of transiting exoplanets.
+To achieve this goal, extensive photometric follow-up of transiting exoplanets is being carry-on, using one-meter class telescopes located in Chile.
+
+% Variations in the transit timing -- when the planet passes in front of its star -- could be induced by companions gravitationally bounded, such as other planets in their systems or even exomoons \citep{Kipping2009a,Kipping2009b}.
 As most of the space mission have strict fields of view, performing photometric follow-up with ground-based telescopes is crucial to reveal important features of their systems.
@@
 
-This thesis is organized as follows: Chapter \ref{chap:tramos} summarizes the TraMoS project, its goals, techniques and achievements to date.
+This thesis is organized as follows: Chapter \ref{chap:tramos} summarizes the TraMoS project, its goals, techniques, and achievements to date.
 Also, this chapter includes what we can learn from transit exoplanets' light curves and Transit Timing Variations.
-Chapter \ref{chap:paper} shows the analysis and results of the hot Jupiters WASP-18b, WASP-19b and WASP-77Ab, including  their observations and data reduction, light curve and RV analysis, measurements of TTVs and upper mass limit for possible companions in their systems.
+Chapter \ref{chap:paper} shows the analysis and results of the hot Jupiters WASP-18b, WASP-19b, and WASP-77Ab, including their observations and data reduction, light curve and RV analysis, measurements of TTVs and an upper mass limit for possible companions in their systems.
 Then, Chapter \ref{chap:tess}  recapitulates the current stage of the TraMoS project on which TESS data is being incorporated.

### 2019-08-22 pipeline.tex
Version 3.0

@@
 
-Since the beginning of the TraMoS project, an aperture photometry pipeline has been in development, on which several graduate and undergraduates students worked and are currently working on it.
-This pipeline is Python-based and includes standard procedures of reduction, calibrations and aperture photometry, including bias and flat field corrections.
+Since the beginning of the TraMoS project, an aperture photometry pipeline has been in development, on which several graduates and undergraduates students worked and are currently working on it.
+This pipeline is Python-based and includes standard procedures of reduction, calibrations, and aperture photometry, including bias and flat-field corrections.
 The user needs to give the coordinates of the target and reference stars and a range of pixels for a possible aperture.
-Then, in order to produce high-precision light curves of the target and reference stars, the pipeline semi-automatic finds the best aperture and ring size, for the sky that produces the less RMS in the light curves.
+Then, to produce high-precision light curves of the target and reference stars, the pipeline semi-automatic finds the best aperture and ring size, for the sky that produces the less RMS in the light curves.
 
@@
 \item data: Empty folder which will contain the output data after the aperture photometry procedure.
-\item figures: Empty folder on which all the figures generated in the reduction process will be store.
+\item figures: Empty folder on which all the figures generated in the reduction process will be stored.
 \item log: Folder containing the Python script to run the pipeline for the specific data set.
-\item extraction.tex: Latex file which generates the PDF file with all the important information related to the aperture photometry procedure process, such as images of the stamps, radial profile of the target star, FWHM plots, preview of the light curve, etc.
-\item tramos\_custom.sty: Customizable file containing the information related to the telescope, target's name, filter, date of the observation, RA, DEC and target's magnitude.
+\item extraction.tex: Latex file which generates the PDF file with all the important information related to the aperture photometry procedure process, such as images of the stamps, the radial profile of the target star, FWHM plots, preview of the light curve, etc.
+\item tramos\_custom.sty: A customizable file containing the information related to the telescope, target's name, filter, date of the observation, RA, DEC and target's magnitude.
 When the pipeline finishes, it fills this file with the best aperture size obtained.
@@
 One of the biggest problems that I faced when I started reducing data, was the distinctness between the headers produced from different telescopes.
-For example, while some of them recorded the type of filter as \textit{FILTER}, other use could use \textit{FILTERB}.
-Also, as the TraMoS project has been collecting data since more than 10 year ago, some of our used telescopes were updated with new CCDs, producing that the pipeline were not longer functional.
+For example, while some of them recorded the type of filter as \textit{FILTER}, others use \textit{FILTERB}.
+Also, as the TraMoS project has been collecting data for more than 10 years ago, some of our used telescopes were updated with new CCDs, producing that the pipeline was no longer functional.
 Currently, the pipeline works with data from the following telescopes:

### 2019-08-22 tess.tex
Version 3.0

@@
 With the end of the Kepler mission, thousands of possible exoplanets remain as candidates known as Kepler Objects of Interest (KOI).
-The Kepler Object of Interest Network (KOINet: \citep{vonEssen2018,Freuddenthal2018}) in the Northern hemisphere, is a network of ground-based telescopes performing photometric follow-up of KOIs to continue what Kepler left undone.
-The main goal of KOINet is to combine Kepler data with ground-based observations in order to confirm and characterize the masses of exoplanet candidates using TTVs.
+The Kepler Object of Interest Network (KOINet: \citep{vonEssen2018,Freuddenthal2018}) in the Northern hemisphere, is a network of ground-based telescopes performing a photometric follow-up of KOIs to continue what Kepler left undone.
+The main goal of KOINet is to combine Kepler data with ground-based observations to confirm and characterize the masses of exoplanet candidates using TTVs.
 
-It is crucial for TTV studies to continue the work of space missions from ground.
+TTV studies must continue the work of space missions from the ground.
 It is unlike, only with space-based observations, to cover the interaction timescales to dynamically prove the TTV signal and the existence of possible companions, as in shown in Figure \ref{koinet}.
@@
 The observations from Kepler are in blue, and two different models were fitted on those data: an orbital decay model is in red, and a periodical TTV model is in green.
-If only Kepler data is considered, the two model could be plausible.
+If only Kepler data is considered, the two models could be plausible.
 The new ground-based observations (in pink) were essential to confirm the TTV nature of the system, discarding an orbital decay}
@@
 The new space telescope Transiting Exoplanet Survey Satellite (TESS: \cite{Ricker2014}) is providing its first discoveries.
-The TESS observation plan divided in 13 sectors will challenge the confirmation process and characterization of possible exoplanets.
+The TESS observation plan divided into 13 sectors will challenge the confirmation process and characterization of possible exoplanets.
 During the $\sim27$ days of each sector, many candidates will not be observed enough time to confirm and characterize them.
-However, this special feature will provide a huge amount of new transit events of already known transiting exoplanets, specially for those with short-period.
-Combining the new TESS data with ground-base follow- up observations, many possible TTVs could be confirm or rule out.
+However, this special feature will provide a huge amount of new transit events of already known transiting exoplanets, especially for those with short-period.
+Combining the new TESS data with ground-based follow- up observations, many possible TTVs could be confirmed or ruled out.
 Moreover, \cite{Ballard2018} predicted that around 5\% of the planets discovered by TESS will exhibit measurable TTV signals, similar to Kepler’s results.
 
-Between Sector 1 and Sector 13, TESS observed around 15\% (see Figure \ref{tess_match.pdf}) of the stars with confirmed exoplanets but not all of them will produce a transit event within the 27 days sector's duration (see Figure \ref{chap:tess}).
+Between Sector 1 and Sector 13, TESS observed around 15\% (see Figure \ref{match_tess}) of the stars with confirmed exoplanets but not all of them will produce a transit event within the 27 days sector's duration (see Figure \ref{chap:tess}).
 Anyway, several complete light curves could be obtained and analyzed.
-TESS data are reduced by the Science Processing Operations Center (SPOC) and after being processed, they are archived in the Mikulski Archive for Space Telescopes (MAST) catalogue, where can be downloaded directly by anyone.
+TESS data are reduced by the Science Processing Operations Center (SPOC) and after being processed, they are archived in the Mikulski Archive for Space Telescopes (MAST) catalog, where can be downloaded directly by anyone.
 
@@
 \caption{Match between all the stars with confirmed exoplanets and the TESS targets from Sector 1 to Sector 13.
-The empty red circles correspond to the star with confirmed exoplanets distributed by its position in the sky, while the filled red circles indicate if the exoplanet has an orbital period of less than 27 days, which is the duration of one TESS sector.
+The empty red circles correspond to the star with confirmed exoplanets distributed by its position in the sky, while the filled red circles indicate if the exoplanet has an orbital period of fewer than 27 days, which is the duration of one TESS sector.
 The black cross indicates which star was already observed by TESS.
 However, this does not indicate that transit light curves will be provided for sure since the orbital period of the exoplanet needs to be considered.
-Thus, the first year mission of TESS will provide for sure transit data of the exoplanets with filled red circle and a black cross.
+Thus, the first-year mission of TESS will provide for sure transit data of the exoplanets with a filled red circle and a black cross.
 The zone in the sky within the big black circle corresponds to the Kepler field of view, where the bulk of discovered exoplanets are located.}
@@
 
-Thus, for the currently and future stage of the TraMoS project, archival data -- collected since 2008 -- will be combined with the upcoming TESS data and new ground-based observations using one-meter class telescopes.
-The main goal of the project remains the same: refine orbital and physical parameters of exoplanetary system and search for variations in those parameters, that could suggest the presence of additional small bodies in the system.
-The KOINet project proved that ground-based follow-up are, in some cases, essential to complete a possible TTV signal, and therefore, to confirm or rule out variations in the transit time.
-During its first year of mission, TESS will supply with consecutive transit light curves from southern targets, specially from short-period planets, such as hot Jupiters.
+Thus, for the current and future stage of the TraMoS project, archival data -- collected since 2008 -- will be combined with the upcoming TESS data and new ground-based observations using one-meter class telescopes.
+The main goal of the project remains the same: refine orbital and physical parameters of the exoplanetary system and search for variations in those parameters, that could suggest the presence of additional small bodies in the system.
+The KOINet project proved that ground-based follow-up is, in some cases, essential to complete a possible TTV signal, and therefore, to confirm or rule out variations in the transit time.
+During its first year of the mission, TESS will supply with consecutive transit light curves from southern targets, especially from short-period planets, such as hot Jupiters.
 This special feature is fundamental to construct TTV curves and then, complete them from ground-based follow-up.
 
-In the following subsections, I present a re-analysis of the TTV curves of the hot Jupiters: WASP-18b, WASP-19b and WASP-77Ab including new transit times from TESS: 45, 28, and 15 for WASP-18b, WASP-19b and WASP-77Ab respectively.
-In order to compute the transit time of each light curve, I used EXOFASTv2 to only fit the transit time and the flux's baseline.
+In the following subsections, I present a re-analysis of the TTV curves of the hot Jupiters: WASP-18b, WASP-19b, and WASP-77Ab including new transit times from TESS: 45, 28, and 15 for WASP-18b, WASP-19b and WASP-77Ab respectively.
+To compute the transit time of each light curve, I used EXOFASTv2 to only fit the transit time and the flux's baseline.
 The remaining planetary parameters were fixed with the values from Tables \ref{wasp18}, \ref{tab:wasp19}, \ref{tab:wasp77}.
@@
 The star WASP-18 was observed continuously during Sector 2 and 3 of the TESS mission, between August 22nd and October 18th, 2018.
-These observations provided 47 transits events of WASP-18b, but only 45 of them were complete transits, and therefore included into the TTV analysis.
+These observations provided 47 transits events of WASP-18b, but only 45 of them were complete transits, and therefore included in the TTV analysis.
 
@@
 
-This value differs from the previous reported in Eq.~\ref{eq1_w18} by $0.016$ seconds, and the error was reduced to a third.
+This value differs from the previously reported in Eq.~\ref{eq1_w18} by $0.016$ seconds, and the error was reduced to a third.
 
@@
 Including these new transit times, the scatter from the linear ephemeris was reduced to 47 seconds.
-A possible second order fit of a hypothetical orbital decay, has a reduced chi squared of $\chi^{2}_{red}=0.35$, while the linear fit - which corresponds to the linear ephemeris - has $\chi^{2}_{red}=0.36$.
-Furthermore, as there is no strong evidence for an orbital decay in this system as proposed by \cite{Wilkins2017}, the simpler model should be chosen: the linear model.
+A possible second-order fit of a hypothetical orbital decay has a reduced chi-squared of $\chi^{2}_{red}=0.35$, while the linear fit - which corresponds to the linear ephemeris - has $\chi^{2}_{red}=0.36$.
+Furthermore, as there is no strong evidence for orbital decay in this system as proposed by \cite{Wilkins2017}, the simpler model should be chosen: the linear model.
 
@@
 WASP-19 was observed during Sector 9 between February 28th and March 26th, 2019.
-During this time, 29 complete transit event were provided, and then considered to compute the new TTVs of WASP-19b show in Figure \ref{wasp19_ttv}.
+During this time, 29 complete transit event was provided and then considered to compute the new TTVs of WASP-19b shown in Figure \ref{wasp19_ttv}.
 The new best fit for the orbital period P, considering a total of 88 transit times is:
@@
 
-The previous reported value in Eq.~\ref{eq1_wasp19} is $0.007$ seconds larger.
+The previously reported value in Eq.~\ref{eq1_wasp19} is $0.007$ seconds larger.
 
@@
 In Eq.~\ref{eq1_w77}, the value for the orbital period P is $0.01\,\rm seconds$ lower, and the scatter from the linear ephemeris was reduced to 86 seconds.
-The linear fit has a reduced chi squared of $\chi^2_{red}=1.03$, while a second degree polynomial has $\chi^2_{red}=0.72$.
-Anyway, the second order fit is highly dominated by the outlier transit time of epoch $229$ (see Figure \ref{wasp77_ttv}).
-After removing it, the reduced chi squared is  $\chi^2_{red}=0.37$.
-In all cases, the best fit correspond to the linear ephemeris.
+The linear fit has a reduced chi-squared of $\chi^2_{red}=1.03$, while a second-degree polynomial has $\chi^2_{red}=0.72$.
+Anyway, the second-order fit is highly dominated by the outlier transit time of epoch $229$ (see Figure \ref{wasp77_ttv}).
+After removing it, the reduced chi-squared is  $\chi^2_{red}=0.37$.
+In all cases, the best fit corresponds to the linear ephemeris.
 
-As the previous two targets, extending the TTV curve of WASP-77Ab with transit times from TESS light curve supported the conclusion from the previous study: there is not a clear sinusoidal signal in the variations of the transit times, that could suggest a periodic TTV in WASP-77Ab.
-However, from the current work this target is the one with less transit time data, thus, follow-up observations would be required to confirm the no existence of close-in companions in MMR.
+Like the previous two targets, extending the TTV curve of WASP-77Ab with transit times from TESS light curve supported the conclusion from the previous study: there is not a clear sinusoidal signal in the variations of the transit times, that could suggest a periodic TTV in WASP-77Ab.
+However, from the current work, this target is the one with less transit time data, thus, follow-up observations would be required to confirm the no existence of close-in companions in MMR.
 

### 2019-08-22 tramos.tex
Version 3.0

@@
 The diameter size of the used telescopes ranges from 0.6 meters to 8 meters.
-However, in the last stage of the TraMoS project, we built the team expertise using 1 meter-class telescopes, for example in the Danish, SWOPE and SMARTS.
+However, in the last stage of the TraMoS project, we built the team expertise using 1 meter-class telescope, for example in the Danish, SWOPE and SMARTS.
 
@@
 
-\begin{figure}[H]
+\begin{figure}[ht]
 \centering
@@
 For example, Figure \ref{transit_examples} shows how the light curve reflects the configuration of the system.
-Hot Jupiters are the kind of planet easier to detect, since their planet-to-star radius ratio is larger, but a smaller planet orbiting a dwarf star could produce a similar ratio of the radius.
-In the other hand, exoplanets with larger orbital inclinations will produce shorter drops in the flux, in comparison with planets in the same orbital-plane with the host star.
+Hot Jupiters are the kind of planet easier to detect since their planet-to-star radius ratio is larger, but a smaller planet orbiting a dwarf star could produce a similar ratio of the radius.
+On the other hand, exoplanets with larger orbital inclinations will produce shorter drops in the flux, in comparison with planets in the same orbital-plane with the host star.
 
-\begin{figure}[H]
+\begin{figure}[h]
 \centering
@@
 
+When modeling the light curve's data, not only the physical parameters of the planet need to be taken into account, but the stars' too.
+The Limb Darkening effect of the star will change the shape of the observed light curve, as what we are observing are photons coming from the star itself, especially when carrying-out observations with different filters.
+This effect produces that the stars appear to be brighter in the center of it and darker closer to the edge.
+The most general analytic formulae to model a light curve produced by a transiting exoplanet includes the Limb Darkening coefficients \citep{Mandel2002}, which can be quadratic or non-quadratic.
+
 \section{Transit Timing Variations\label{ttv}}
@@
 Since the discovery of the first exoplanet, one of the principal questions that arose was: are they alone in their systems?
-The idea of multiplanetary systems is a consequence of our knowledge about the planetary system where we live in, and until today the Solar System has the larger number of orbiting planets.
+The idea of multi-planetary systems is a consequence of our knowledge about the planetary system where we live in, and until today the Solar System has a larger number of orbiting planets.
 Besides the Solar System, Kepler-90 has the same number of confirmed exoplanets: eight.
-Statistically, around a 20\% of the confirmed exoplanets live in a multiplanetary system\footnote{Information obtained from the NASA Exoplanet Archive Database \url{exoplanetarchive.ipac.caltech.edu}}, but this number is theoretically larger.
-\cite{Fressin2013} computed the occurrence of exoplanets through numerical simulation with Kepler data, obtaining that around $52\%$ of the stars should have at least one planet within a 85 days orbit.
+Statistically, around a 20\% of the confirmed exoplanets live in a multi-planetary system\footnote{Information obtained from the NASA Exoplanet Archive Database \url{exoplanetarchive.ipac.caltech.edu}}, but this number is theoretically larger.
+\cite{Fressin2013} computed the occurrence of exoplanets through numerical simulation with Kepler data, obtaining that around $52\%$ of the stars should have at least one planet within an 85 days orbit.
 
-The Transit Timing Variations (TTV) technique was first proposed as a way to detect Earth-mass planets in multiplanetary systems due to gravitational interactions with a transiting exoplanet \citep{Holman2005,Agol2005}.
-However, TTVs can be also used to measure tidal interactions between the planet and the star or to detect exomoons \citep{Kipping2009a,Kipping2009b}, among others phenomena.
+The Transit Timing Variations (TTV) technique was first proposed as a way to detect Earth-mass planets in multi-planetary systems due to gravitational interactions with a transiting exoplanet \citep{Holman2005,Agol2005}.
+However, TTVs can be also used to measure tidal interactions between the planet and the star, such as orbital decays for instance, or to detect exomoons \citep{Kipping2009a,Kipping2009b}, among others phenomena in the star itself.
 
@@
 As the transit times will be no longer a linear function,  the time between transits varies.
-The variation in time produced by the perturbing body depends on the mass and geometry of their orbits.
-The magnitude of this variation between successive transits of the transiting planet is:
+The variation in time produced by the perturber body depends on the mass and geometry of their orbits.
+The magnitude of this variation between successive transits of the transiting planet \citep{Holman2005}, assuming that the perturber body is in a inner orbit, $a_2 < a_1$, and follows a parabolic orbit with a pariastron distance of $a_2(1-e_2)$, is:
 
@@
 
-Where $\alpha_e = a_1/(a_2(1-e_2))$ is the ratio of the semi-major axis of the planets, considering a nonzero eccentricity for the perturbing planet ($e_2 \neq 0$) and $a_1 < a_2$.
-The semi-major axis of the transiting exoplanet is $a_1$ and its orbital period $P_1$, while the perturbing planet has a mass $M_2$, semi-major axis $a_2$, orbital period $P_2$ and eccentricity $e_2$.
-Assuming that the orbital parameters of the known transiting exoplanet are already derived from its light curve, the orbital parameters and mass of the hypothetical pertuber can be estimate numerically \citep{Nesvorny2008,Nesvorny2009}, even if the second planet does not transit the star.
+Where $\alpha_e = a_1/(a_2(1-e_2))$ is the ratio of the semi-major axis of the planets, considering a nonzero eccentricity for the perturbing planet ($e_2 \neq 0$).The orbital period of transiting exoplanet is $P_1$, while the perturbing planet has a mass $M_2$, and orbital period $P_2$.
+When $e_2>0.3$, the relation \ref{delta_t} has the best performance with numerical simulations.
 
-The TTV method is an efficient tool to search for additional unseen companions since, in order to employ this technique, only photometry of the transiting exoplanet during a transit events is required.
+Assuming that the orbital parameters of the known transiting exoplanet are already derived from its light curve, the orbital parameters and mass of the hypothetical perturber can be estimated numerically \citep{Nesvorny2008,Nesvorny2009}, even if the second planet does not transit the star.
+
+The TTV method is an efficient tool to search for additional unseen companions since, to employ this technique, only photometry of the transiting exoplanet during transit events is required.
 Moreover, this technique enhances its sensitivity when the two bodies in the system are close to Mean Motion Resonances (MMR) \citep{Agol2005,Steffen2005,Agol2007} (see Figure~\ref{rms_ttv_amplitude}) .
@@
 \caption{Example of a system with a transiting exoplanet of $1~M_{J}$ in a 10-day orbit and an Earth-mass perturber planet.
-The top panel is an Observed minus Computed diagram showing the measured TTV of the Jupiter-mass planet when the pertuber has a period of 16.11 days, not in Mean Motion Resonance with the transiting planet.
+The top panel is an Observed minus Computed diagram showing the measured TTV of the Jupiter-mass planet when the perturber has a period of 16.11 days, not in Mean Motion Resonance with the transiting planet.
 The panel at the bottom shows the TTV of the transiting planet when both are near an interior 2:1 resonance.
-In this case the small planet has a period of 19.7 days.
+In this case, the small planet has a period of 19.7 days.
 The amplification of the TTV signal is by an order of magnitude.

### 2019-10-07 abstract.tex
Final version

@@
-%\begin{resumen}
+\begin{resumen}
+El proyecto Transit Monitoring in the South (TraMoS) busca realizar seguimiento fotométrico de exoplanetas transitantes conocidos.
+Este proceso provee no sólo información acerca del planeta transitante, sino también sobre la arquitectura del sustema planetario.
+Desviaciones de la efemeris lineal producida por el movimiento Kepleriano, conocidas como Transit Timing Variations (TTV), sólo se pueden detectar mediante intensivo seguimiento y pueden sugerir la existencia de cuerpos adicionales en el sistema, tales como compañeros planetarios o exolunas.
 
-%\end{resumen}
+Esta tesis de magíster recapitula los últimos años del proyecto TraMoS, se seleccionaron nuevos objetivos, se utilizaron nuevas heramientas, y se desarrollaron nuevos analisis.
+Se estudiaron 27 nuevas curvas de luz de tres Jupiter calientes: WASP-18b, WASP-19b, y WASP-77Ab.
+Se refinaron sus parámetros físicos y orbitales, y la ecuación de efemeris lineal fue actualizada gracias a la inclusión de datos de transito históricos.
+Debido a la carencia de variaciones significativas en sus tiempos central de tránsito, la realización de análisis dinámicos puede imponer límites superiores a la masa de perturbadores hipotéticos.
+Se descartaron cuerpos que poseen masas más grandes que $50\,M_{\oplus}$ para WASP-18b, $6\,M_{\oplus}$ para WASP-19b, y $10\,M_{\oplus}$ para WASP-77Ab.
+Adicionalmente, se incluyeron datos de TESS para los tres objetivos, lo que apoya que la efemeris lineal es el mejor modelo para los tiempos de tránsito.
+
+Los resultados presentados en esta tesis apoyan la poco frecuente aparición de compañeros en sistemas de Júpiters calientes.
+Estudios futuros podrían evidenciar si estos tipos de planeta sufrieron un proceso de formación diferente por el cual terminan orbitando solos, o si efectivamente poseen compañeros enanos que no se han detectado.
+\end{resumen}
 
@@
 Their orbital and physical parameters were refined, and their linear ephemeris updated thanks to the inclusion of archival transit time data.
-Given the lack of significant variations in their transit times, dynamical analysis can place upper mass limits in hypothetical perturbers.
-Bodies with masses greater than $50\,M_{\odot}$ can be discarded for WASP-18b, $6\,M_{\odot}$ for WASP-19b, and $10\,M_{\odot}$ for WASP-77Ab.
-Furthermore, I included recent TESS data for the three targets, supporting the linear ephemeris as the best fit for their transit times
+Given the lack of significant variations in their mid-transit times, dynamical analysis can place upper mass limits in hypothetical perturbers.
+Bodies with masses greater than $50\,M_{\oplus}$ can be discarded for WASP-18b, $6\,M_{\oplus}$ for WASP-19b, and $10\,M_{\oplus}$ for WASP-77Ab.
+Furthermore, I included recent TESS data for the three targets, supporting the linear ephemeris as the best fit for their transit times.
 
-The results presented in this thesis support the rare occurrence of companions in hot Jupiters systems.
+The results presented in this thesis support the rare occurrence of companions in hot Jupiter systems.
 Further studies may confirm if this kind of planet goes through a different formation process ending up orbiting alone on their systems or they have very small and unseen companions.

### 2019-10-07 agradecimientos.tex
Final version

\begin{thanks} % opcional

Quiero agradecer en primer lugar a mis padres, quienes han sido mi apoyo fundamental tanto emocional como económico todos estos años (desde que nací). Gracias por nunca cortarme las alas, darme la libertad de soñar en grande y recogerme cada vez que me caí (literal y metafóricamente).

También quiero agradecer a mi profe guía, Pato Rojo, por la confianza de pasarme TraMoS y la libertad creativa que tuve para desarrollar este proyecto. Gracias por el apoyo y las enseñanzas estos años, me siento mucho más cerca de ser una astrónoma.

A todas las amigas y amigos que me acompañaron en este largo proceso. La oficina de los Calan-bozos se volvió una zona de comfort para mi y agradezco todos los momentos que pasamos juntos en este inhóspito lugar llamado Calán. A mis amigas de Beauchef, que nos hemos acompañado desde el primer día (casi) del Plan Común y que siempre me dieron ánimos y me apoyaron en los momentos difíciles. A Pierina, mi amiga de la vida, que aunque el universo se encarga de separarnos la amistad sigue intacta como hace catorce (?) años. A las Cazadoras de Estrellas, agredezco haber sido partícipe de este proyecto tan maravilloso que solo me dio alegrías. Sé que seguirán creciendo y motivando a más niñas a ser científicas.

A Matías, por todo tu apoyo y amor incodicional todos estos años. Por ayudarme a pararme cada vez que me caí, darme confianza las veces que ya no creía en mi misma y por escucharme atento con todas mis dudas existenciales. Gracias por ser mi fan número 1 siempre.

A Bibi, la compañera gatuna que apareció en mi vida solo para darme suavidad, ronroneos y tranquilidad.

\end{thanks}

### 2019-10-07 conclusion.tex
Final version

@@
 
-The TraMos project started more than 10 years ago aiming to refine orbital and physical parameters of already known exoplanets, and to search for variation in the transit time -- or other planet parameters -- that could suggest the existence of smaller bodies on their systems.
-Since the beginning, the targets have been hot Jupiters due to their short-periods, allowing to obtain more consecutive transit light curves in a reduced period.
+The TraMos project started more than 10 years ago aiming to refine orbital and physical parameters of already known exoplanets, and to search for variation in the transit time -- or other planet parameters -- that could suggest the existence of additional massive bodies on their systems.
+Our search focused on hot Jupiter planetary systems on short orbital periods, allowing to obtain additional photometric data from ground as well as space-based telescopes.
 
@@
 For these targets, I analyzed a total of twenty-six new light curves: eight of WASP-18b, nine of WASP-19b and nine of WASP-77Ab.
-In the case of WASP-77Ab, four light curves were taken from the Exoplanet Transit Database (ETD)\footnote{\url{var2.astro.cz/ETD}} to obtain a wider time coverage.
-For the light curves coming from the TraMoS project, I started from performing aperture photometry of the targets using our data reduction pipeline (for further details see \ref{chap:pipeline}), to obtain high-precision light curves.
+In the case of WASP-77Ab, four light curves were taken from the Exoplanet Transit Database (ETD)\footnote{\url{https://var2.astro.cz/ETD}} to obtain a wider time coverage.
+For the light curves coming from the TraMoS project, I started from performing aperture photometry of the targets using our data reduction pipeline (for further details see Appendix \ref{chap:pipeline}), to obtain high-precision light curves.
 Then, I used EXOFASTv2 \cite{Eastman2013,Eastman2017} to get the best fit for the light curve's data and hence, to refine their orbital and physical parameters and obtain their transit times.
@@
 The TTV curves were constructed from the residuals between the observed transit time and the expected from the linear ephemeris.
-None of the targets studied in this thesis shows a clear, periodic sinusoidal signal in the variation of their transit times and moreover, the structure of the transit times are comparable with a random distribution after a Lomb-Scargle analysis.
+None of the targets studied in this thesis shows a clear, periodic sinusoidal signal in the variation of their transit mid-times and moreover, the structure of the transit times are comparable with a random distribution after a Lomb-Scargle analysis.
 This suggests the lack of close-in companions in MMR in their systems.
@@
 \begin{itemize}
-\item WASP-18b: $1.9\,M_{\odot}$, $4.0\,M_{\odot}$, $5.0\,M_{\odot}$, $25\,M_{\odot}$, $10\,M_{\odot}$, $7.0\,M_{\odot}$, $50\,M_{\odot}$ in 1:3, 2:5, 1:2, 2:1, 5:2, 3:1 and 4:1 resonances, respectively.
-\item WASP-19b: $2.0\,M_{\odot}$, $6.0\,M_{\odot}$, $0.9\,M_{\odot}$, $3.0\,M_{\odot}$, $2.0\,M_{\odot}$ in 1:2, 5:3, 2:1, 5:2 and 3:1 resonances, respectively. 
-\item WASP-77Ab: $1.0\,M_{\odot}$, $3.5\,M_{\odot}$, $2.0\,M_{\odot}$, $7.0\,M_{\odot}$, $6.0\,M_{\odot}$, $10\,M_{\odot}$, $3.5\,M_{\odot}$, $4.5\,M_{\odot}$ in 1:3, 1:2, 3:5, 2:3, 5:3, 7:4, 2:1 and 3:1 resonances, respectively.
+\item WASP-18b: $1.9\,M_{\oplus}$, $4.0\,M_{\oplus}$, $5.0\,M_{\oplus}$, $25\,M_{\oplus}$, $10\,M_{\oplus}$, $7.0\,M_{\oplus}$, $50\,M_{\oplus}$ in 1:3, 2:5, 1:2, 2:1, 5:2, 3:1 and 4:1 resonances, respectively.
+\item WASP-19b: $2.0\,M_{\oplus}$, $6.0\,M_{\oplus}$, $0.9\,M_{\oplus}$, $3.0\,M_{\oplus}$, $2.0\,M_{\oplus}$ in 1:2, 5:3, 2:1, 5:2 and 3:1 resonances, respectively. 
+\item WASP-77Ab: $1.0\,M_{\oplus}$, $3.5\,M_{\oplus}$, $2.0\,M_{\oplus}$, $7.0\,M_{\oplus}$, $6.0\,M_{\oplus}$, $10\,M_{\oplus}$, $3.5\,M_{\oplus}$, $4.5\,M_{\oplus}$ in 1:3, 1:2, 3:5, 2:3, 5:3, 7:4, 2:1 and 3:1 resonances, respectively.
 \end{itemize}
@@
 To date, none of the previous and current targets of the TraMoS project have shown TTVs.
-As they are all hot Jupiters, these studies support the theory of "alone hot Jupiters", on which this kind of exoplanets are probably alone in their systems or accompanied of small bodies, not in MMR.
+As they are all hot Jupiters, these studies support the theory of "isolated hot Jupiters", on which this kind of exoplanets are probably alone in their systems or accompanied of small bodies, not in MMR.
 How WASP-47b and Kepler-730b, the only two hot Jupiters showing TTVs, have close-in companions is still unknown.
@@
 The TraMoS catalog stores more than 400 transits events of near 140 exoplanets.
-As future work, I propose to continue performing a ground-based photometric follow-up of the targets in this catalog, as well as new targets, combining the efforts with TESS data of Sector 1 to 13.
-In this way, we could obtain better estimations of TTVs with wider time-span data from TraMoS, and an important amount of consecutive transit times from TESS.
+As future work, I propose to continue performing a ground-based photometric follow-up of the targets in this catalog, as well as new targets.
+Combining the efforts of TESS and TraMoS the amount of mid-transit times will cover a wider time-span and hence detect possible long-periodic TTV trends.
+TESS can provide hints of possible short and long-term TTVs -- or TPVs in general -- with an important amount of consecutive transit light curves.
+Then, performing ground-based follow-up is the most efficient way to prove or discard this variations, as the number of possible transit data from TESS is constrain by the duration of the sectors -- for most of the targets --.
+We proved that our current used telescopes provides high-precision light curves, comparable with TESS.
+
+% with TESS data of Sector 1 to 13. In this way, we could obtain better estimations of TTVs with wider time-span data from TraMoS, and an important amount of consecutive transit times from TESS.
+
 In the near future, given the new scatter of the transit time in the three targets analyzed in this thesis, more accurate upper mass limits for hypothetical perturbers could be computed.
-Also, I will analyze the exoplanets WASP-36b and HATS-34b, which each one has five transit times from TraMoS and twelve and twenty-six from TESS, respectively.
+Also, the next step is to analyze the exoplanets WASP-36b and HATS-34b, which each one has five transit times from TraMoS and twelve and twenty-six from TESS, respectively.
 For WASP-22, WASP-46, WASP-45, WASP-23, and WASP-123, TESS provided five, seventeen, eight, seven and thirteen light curves, respectively.
@@
 
-The reduction pipeline is fully functional and provides high-precision photometry, nevertheless, several improvements were left behind because of the lack of time to implement them.
+The reduction pipeline is fully functional and provides high-precision photometry.
+During this thesis project, I included dictionaries that allows the reduction photometry of new telescopes.
+Currently, the pipelines works for data coming from: Danish 1.54 m, Warsaw, Swope, Du Pont, REM, SMARTS 0.9 m and 1 m and SOAR.
+Nevertheless, several improvements were left behind because of the lack of time to implement them.
 For example, the coordinates selection could be done inside the program, to avoid mistakes when typing them by hand before calling the pipeline.

### 2019-10-07 introduction.tex
Final version

@@
 \chapter{Introduction}\label{chap:intro}
-The idea of the existence of planets orbiting other stars different from our Sun lived in the human imagination for centuries.
-During the sixteenth century, the Italian philosopher Giordano Bruno suggested, for the first time in history, that more planets could be outside the Solar System.
-Even though the first claims of exoplanet detection began at the begin of the twentieth century\footnote{The van Maanen 2 star, which later was confirmed as a white dwarf.}, it was not until more than four hundred years after Bruno's statement, that the first exoplanet was confirmed in 1992.
+The idea of the existence of planets orbiting other stars different from our Sun has lived in the human imagination for centuries.
+During the sixteenth century, the Italian philosopher Giordano Bruno suggested\footnote{In the book: \textit{De l'infinito, universo e mondi}, 1584}, for the first time in history, that more planets could be outside the Solar System.
+More than four hundred years after Bruno's statement, the first exoplanet was confirmed in 1992.
 Surprisingly, it was not just one exoplanet but three, orbiting the pulsar PSR B1257+12 more than 1000 light-years away from us.
 Today, more than 4,000 exoplanets are confirmed, and thousands more are waiting for their confirmation.
+
+%Even though the first claims of exoplanet detection began at the begin of the twentieth century\footnote{The van Maanen 2 star, which later was confirmed as a white dwarf.}, it was not until more than four hundred years after Bruno's statement, that
 
@@
 If the Milky Way has \textit{only} around $2\,\times10^{11}$ stars, how could be the Solar System unique?
-How could be the Earth the only planet with life on it?
+How could the Earth be the only planet with life on it?
 Until today, it is still difficult to answer those questions.
 The Solar System presents a logic structure where the small, rocky planets are closer to the Sun, and the gas giants are located beyond.
-But no other exoplanetary system have been found having similar features and even not exoplanetary life has been detected yet\footnote{By the date of writing this thesis.}.
+But no other exoplanetary system has been found having similar features and even not exoplanetary life has been detected yet.
 Our knowledge about the Solar System challenges the existence of other kinds of planetary architectures with close-in gas giants, for instance, suggesting that there is not a single, universal planetary process formation.
@@
 The technique used to find them is called Pulsar Timing and it consists in measuring the variation of a pulsar's pulsation period due to the presence of a body orbiting it.
-As pulsars are not very common and we know that planet may be orbiting main-sequence stars -- as the Earth and all the Solar System --, the latter become the principal target on which the hunting of exoplanet is dedicated.
+As pulsars are not very common and we know that planet may be orbiting main-sequence stars -- as the Earth and all the Solar System --, they become the principal target on which the hunting of exoplanet is dedicated.
 Planets are small when compare to their host star, that is why most of the current discovery techniques are focused on observing the effects in the stars, or how what we observed from them changed, caused by the presence of planets.
-Nevertheless, Direct Imaging is the only technique in which the planet is observed directly but the star needs to be covered to only received the thermal emission produced by the planet.
 
-Microlensing is different from all the other discovery techniques because a third, bright background star is required to obtain the desired effect: gravitational lensing produced by the star with a planet (multiple lenses).
-As the primary lens is small -- around $1\,M_{\odot}$ -- the two images produced by the gravitational lensing are very close between each other and the event can not be resolved.
-The presence of a planet will cause a deviation in the magnification curve of the event.
-On the other hand, Astrometry measurements can be used to discover exoplanets too.
+The most used and successful planet detection techniques are: transits, radial velocity, direct imaging, microlensing and astrometry.
+Direct imaging is the only technique in which the planet is observed directly but the star needs to be masked in order to only received the thermal emission from the planet.
+Microlensing is different from all the other discovery techniques because a background star is required to obtain the desired effect: gravitational lensing produced by the star with a planet (multiple lenses).
+As the primary lens is small -- around $1\,M_{\odot}$ -- the two images produced by the gravitational lensing effect are very close to each other and cannot be resolved with current imaging techniques.
+The presence of a planet in orbit around the lens star will cause a deviation in the magnification curve of the event.
+On the other hand, astrometry measurements can be used to discover exoplanets too.
 With the current high-precision in the position of the stars, even their displacement in the sky can be detected.
-Similar to the Radial Velocity technique, through Astrometry the displacement of the star due to the gravity of a planet is measured.
+Similar to the radial velocity technique, through astrometry the displacement of the star due to the gravity of a planet is measured.
 
-The two techniques that have contributed the most to the discovery of extrasolar planets are Radial Velocity and Transits (see Figure \ref{exoplanets}).
+The two techniques that have contributed the most to the discovery of extrasolar planets are radial velocity and transits (see Figure \ref{exoplanets}).
 Each one of these techniques had their own advantages depending on the physical properties of the planetary system.
-When the orbit of the exoplanet is aligned with the line of sight from Earth, the pass of the planet in front of its host star causes that the star's flux decreases, proportionally to the radius of the planet.
-Thus, the radius ratio between the planet and the star, $R_{p}/R_{*}$ can be determined directly using the Transit method.
+When the orbit of the exoplanet is aligned with the line of sight from Earth, the pass of the planet in front of its host star causes that the star's flux decreases, proportionally to the square of the ratio between the radius of the planet and the star.
+Thus, the radius ratio between the planet and the star, $R_{p}/R_{*}$ can be determined directly using the transit method.
 On the other hand, the gravity due to the presence of a planet will set the center of mass of the system, in a place different from the star's center.
 Therefore, the star will move in its own small orbit with a radius proportional to the mass of the planet.
-In this case, the Radial Velocity method unveils the planet's minimum mass $M_{p}\sin i$.
+In this case, the radial velocity method unveils the planet's minimum mass $M_{p}\sin i$.
 
@@
 Performing follow-up and proper characterization of discovered exoplanets are essential to obtain a full list of orbital and planetary parameters.
-For instance,  39\%  of the total number of discovered exoplanets have a proper measurement of their masses, and only 17\% have their mass and radius computed\footnote{Information obtained from the NASA Exoplanet Archive Database \url{exoplanetarchive.ipac.caltech.edu}}.
+For instance,  39\%  of the total number of discovered exoplanets have a proper measurement of their masses, and only 17\% have their mass and radius computed\footnote{Information obtained from the NASA Exoplanet Archive Database \url{https://exoplanetarchive.ipac.caltech.edu}}.
 
@@
 
-The perfect scenario comes when both methods, Transits and Radial Velocity, can be used in the same planetary system, allowing to derive essential properties of the planet.
-Combining Transits and Radial Velocity follow-up the whole system can be characterized.
-From Transits we get the orbital inclination, then the real mass can be computed with Radial Velocity measurements.
-From Transits we get the radius ratio of the system, assuming that the star is previously well characterized, the radius of the planet is derived.
+One of the perfect scenarios comes when the two methods, transits and radial velocity, can be used in the same planetary system, allowing to derive essential properties of the planet and its orbit.
+Combining transits and radial velocity follow-up the whole system can be characterized.
+From transits we get the orbital inclination, then the real mass can be computed with radial velocity measurements.
+From transits we get the radius ratio of the system, assuming that the star is previously well characterized, the radius of the planet is derived.
 Then, as we already have the mass of the planet, the mean density can be estimated.
 This parameter gives a clue about the possible composition of the planet.
-Moreover, if the follow-up is performed combining Transits with big telescopes, for instance, the Very Large Telescope, important information about the planet can be unveiled, even their atmospheric composition and dynamics.
+Moreover, if the follow-up is performed combining transits with big telescopes, important information about the planet can be unveiled, perhaps even their atmospheric composition and dynamics.
 
@@
 This plot only shows the exoplanets with measured masses.
-The Transit and Radial Velocity methods (in orange and blue, respectively) are the most successful techniques to discover extrasolar planets.
+The transit and radial velocity methods (in orange and blue, respectively) are the most successful techniques to discover extrasolar planets.
 However, both techniques are still more sensitive to detect Jupiter-mass planets rather than Earth-mass, but the Transit method is more sensitive to short-period planets.}
@@
 Continued photometric monitoring not only increased the precision of planetary parameters but provides potential information about the planet and its environment.
-Through the observation of transit events during several epochs, variability in the planetary system can be detected.
+Through the observation of transit events during a long observing baseline, variability in the planetary system can be detected.
 For instance, the first measurement of two planets gravitationally bounded was made by \citep{Holman2010}, this discovery was made thanks to the continued observations performed by the Kepler mission.
-This phenomenon is detectable observing during several epochs just one of the planets involved and analyzing how the presence of a companion produces such variability.
-Moreover, variability in transiting exoplanets -- specifically in the time of the transit -- can be attributed not only to planetary companions, but exomoons\citep{Kipping2009a,Kipping2009b}, tidal orbital decay\citep{Hoyer2016,Hoyer2016b}, secular orbits changes\citep{Adams2006} or relativistic effects \citep{Heyl2007}, among others.
+This phenomenon is detectable by observing the same transit event multiple times over an extended number of epochs.
+Any variability in the mid-transit times could be attributed to an additional body.
+Moreover, variability in transiting exoplanets -- specifically in the time of the mid-transit -- can be attributed not only to planetary companions, but exomoons\citep{Kipping2009a,Kipping2009b}, tidal orbital decay\citep{Hoyer2016,Hoyer2016b}, secular orbits changes\citep{Adams2006} or relativistic effects \citep{Heyl2007}, among others.
 
-The Transit Monitoring in the South project (TraMoS) is one of its kind in the southern hemisphere, aiming to detect multi-exoplanetary systems trough the variability in transit parameters of transiting exoplanets.
-To achieve this goal, extensive photometric follow-up of transiting exoplanets is being carry-on, using one-meter class telescopes located in Chile.
+The Transit Monitoring in the South project (TraMoS) aims to detect multi-exoplanetary systems trough the variability in parameters of transiting exoplanets.
+To achieve this goal, extensive photometric follow-up of transit is being carried on, using one-meter class telescopes located in Chile.
 
@@
 
-This thesis is organized as follows: Chapter \ref{chap:tramos} summarizes the TraMoS project, its goals, techniques, and achievements to date.
-Also, this chapter includes what we can learn from transit exoplanets' light curves and Transit Timing Variations.
+This thesis is organized as follows: Chapter \ref{chap:tramos} summarizes the TraMoS project, its scientific goals, techniques, and achievements to date.
+Also, this chapter describes what we can learn from transit exoplanets' light curves and Transit Timing Variations.
 Chapter \ref{chap:paper} shows the analysis and results of the hot Jupiters WASP-18b, WASP-19b, and WASP-77Ab, including their observations and data reduction, light curve and RV analysis, measurements of TTVs and an upper mass limit for possible companions in their systems.
@@
 Finally, Chapter \ref{chap:conclusion} contains a summary of this thesis as well as some ideas for future work.
-The Appendix section includes a brief description of the aperture photometry pipeline utilized, all the Python scripts used to generate each light curve, and an example of the PDF file obtained after the aperture photometry procedure.
+The Appendix section includes a brief description of the aperture photometry pipeline utilized, all the Python scripts used to generate each light curve, and an example of the PDF file obtained as a result of the aperture photometry procedure.

### 2019-10-07 paper.tex
Final version

@@
 We simultaneously model our newly collected transit light curves, as well as archival photometry and radial velocity data to obtain refined physical and orbital parameters.
-We did not find significant $\rm TTV_{RMS}$ variations larger than 83, 75, and 121 seconds for WASP-18b, WASP-19b, and WASP-77Ab, respectively.
+We did not find significant $\rm TTV_{RMS}$\footnote{RMS: root-mean-square} variations larger than 83, 75, and 121 seconds for WASP-18b, WASP-19b, and WASP-77Ab, respectively.
 Dynamical simulations were carried out to constrain the masses of a possible perturber.

### 2019-10-07 pipeline.tex
Final version

@@
 The user needs to give the coordinates of the target and reference stars and a range of pixels for a possible aperture.
-Then, to produce high-precision light curves of the target and reference stars, the pipeline semi-automatic finds the best aperture and ring size, for the sky that produces the less RMS in the light curves.
+Then, to produce high-precision light curves of the target and reference stars, the pipeline semi-automatically finds the best aperture and ring size, for the sky that produces the less RMS in the light curves.
 
@@
 \begin{itemize}
-\item raw: Folder containing the raw data of the observations. It could be fits files or compressed fits (e.g \textit{fit.ZIP}).
+\item raw: Folder containing the raw data of the observations. It could be FITS files or compressed FITS (e.g \textit{fit.ZIP}).
 \item calib: This folder should include the flats -- sky or dome -- and bias files.
@@
 I have implemented dictionaries to ease the use of the pipeline with different telescopes.
-One of the biggest problems that I faced when I started reducing data, was the distinctness between the headers produced from different telescopes.
+One of the biggest problems that I faced when I started reducing data, was the distinctness between the FITS headers produced from different telescopes.
 For example, while some of them recorded the type of filter as \textit{FILTER}, others use \textit{FILTERB}.

### 2019-10-07 tess.tex
Final version

@@
 TTV studies must continue the work of space missions from the ground.
-It is unlike, only with space-based observations, to cover the interaction timescales to dynamically prove the TTV signal and the existence of possible companions, as in shown in Figure \ref{koinet}.
-In this figure, new data from ground-based telescopes were fundamental to confirm the TTV signal, and therefore to perform a proper characterization of the system.
+Ground-based photometric follow-up observations are important and contribute with significant scientific measurements and complement space-based observations to detect astrophysical interesting signals like TTVs.
+In Figure \ref{koinet}, new data from ground-based telescopes were fundamental to confirm the TTV signal, and therefore to perform a proper characterization of the system.
 
@@
 
-The new space telescope Transiting Exoplanet Survey Satellite (TESS: \cite{Ricker2014}) is providing its first discoveries.
+The new space telescope Transiting Exoplanet Survey Satellite (TESS: \cite{Ricker2014}) is delivering its first discoveries.
 The TESS observation plan divided into 13 sectors will challenge the confirmation process and characterization of possible exoplanets.
-During the $\sim27$ days of each sector, many candidates will not be observed enough time to confirm and characterize them.
+During the $\sim27$ days of each sector, many candidates will not be observed for a long enough time to confirm and characterize them.
 However, this special feature will provide a huge amount of new transit events of already known transiting exoplanets, especially for those with short-period.
@@
 
-Between Sector 1 and Sector 13, TESS observed around 15\% (see Figure \ref{match_tess}) of the stars with confirmed exoplanets but not all of them will produce a transit event within the 27 days sector's duration (see Figure \ref{chap:tess}).
+Between Sector 1 and Sector 13 -- sectors dedicated to the southern hemisphere -- TESS observed around 15\% (see Figure \ref{match_tess}) of the stars with confirmed exoplanets but not all of them will produce a transit event within the 27 days sector's duration (see Figure \ref{chap:tess}).
 Anyway, several complete light curves could be obtained and analyzed.
-TESS data are reduced by the Science Processing Operations Center (SPOC) and after being processed, they are archived in the Mikulski Archive for Space Telescopes (MAST) catalog, where can be downloaded directly by anyone.
+TESS data are reduced by the Science Processing Operations Center (SPOC: \cite{Jenkins2016}) and after being processed, they are archived in the Mikulski Archive for Space Telescopes (MAST\footnote{http://archive.stsci.edu/}) catalog, where can be downloaded directly by anyone.
 
@@
 In the following subsections, I present a re-analysis of the TTV curves of the hot Jupiters: WASP-18b, WASP-19b, and WASP-77Ab including new transit times from TESS: 45, 28, and 15 for WASP-18b, WASP-19b and WASP-77Ab respectively.
-To compute the transit time of each light curve, I used EXOFASTv2 to only fit the transit time and the flux's baseline.
+To compute the transit time of each light curve, I used EXOFASTv2\footnote{https://github.com/jdeast/EXOFASTv2} \citep{Eastman2013} to only fit the transit time and the flux's baseline.
 The remaining planetary parameters were fixed with the values from Tables \ref{wasp18}, \ref{tab:wasp19}, \ref{tab:wasp77}.
@@
 
-The new best linear fit for the period considering a total of 63 transit times is:
+The new linear ephemeris equation considering a total of 63 transit mid-times is:
 
 \begin{equation}
-P = 0.941452232 \pm 2.7\times10^{-8} ~\rm days
+T_{\rm C}(E)=2456926.27460\pm(94)+E \cdot 0.941452232 \pm(27)
 \end{equation}
 
-This value differs from the previously reported in Eq.~\ref{eq1_w18} by $0.016$ seconds, and the error was reduced to a third.
+The best fit for the period $P= 0.941452232 \pm 2.7\times10^{-8} ~\rm days$ differs from the previously reported in Eq.~\ref{eq1_w18} by $0.016$ seconds, and the error was reduced to a third.
 
@@
 Including these new transit times, the scatter from the linear ephemeris was reduced to 47 seconds.
-A possible second-order fit of a hypothetical orbital decay has a reduced chi-squared of $\chi^{2}_{red}=0.35$, while the linear fit - which corresponds to the linear ephemeris - has $\chi^{2}_{red}=0.36$.
+A possible second-order fit of a hypothetical orbital decay has a reduced chi-squared of $\chi^{2}_{red,quad}=0.35$, while the linear fit - which corresponds to the linear ephemeris - has $\chi^{2}_{red,lin}=0.36$.
 Furthermore, as there is no strong evidence for orbital decay in this system as proposed by \cite{Wilkins2017}, the simpler model should be chosen: the linear model.
@@
 For that, we considered 63 transit times from the TraMoS project (in light blue), published works and TESS (both in black).
-The grey area corresponds to the error propagation at $1\sigma$.
+The grey area corresponds to the error propagation at $1\sigma$, which follows a imperceptible quadratic trend.
 The RMS scatter from the linear ephemeris is 47 seconds.}
@@
 During this time, 29 complete transit event was provided and then considered to compute the new TTVs of WASP-19b shown in Figure \ref{wasp19_ttv}.
-The new best fit for the orbital period P, considering a total of 88 transit times is:
+The new proposed linear ephemeris equation considering a total of 88 transit times is:
 
 \begin{equation}
-P = 0.788838940 \pm 3.0\times10^{-8} ~\rm days
+T_{\rm C}(E)=2456402.7128\pm(16)+E \cdot 0.788838940 \pm(30)
 \end{equation}
 
-The previously reported value in Eq.~\ref{eq1_wasp19} is $0.007$ seconds larger.
+The new best fit value for the period $P=0.788838940 \pm 3.0\times10^{-8} ~\rm days$ is $0.007$ seconds larger than the previously reported value in Eq.~\ref{eq1_wasp19}.
 
 As in the case of WASP-18b, the TTV scatter of WASP-19b was reduced when including new transit times data from TESS to: $TTV_{RMS}=65~\rm seconds$.
-Again, a second order fit is not better that the linear one: $\chi^{2}_{red,lineal}= 0.65$ and $\chi^{2}_{red,cuad}= 0.64$.
+Again, a second order fit is not better that the linear one: $\chi^{2}_{red,lin}= 0.65$ and $\chi^{2}_{red,quad}= 0.64$.
 
@@
 For that, we considered 87 transit times from the TraMoS project (in light blue), published works and TESS (both in black).
-The grey area corresponds to the error propagation at $1\sigma$.
+The grey area corresponds to the error propagation at $1\sigma$, which follows a imperceptible quadratic trend..
 The RMS scatter from the linear ephemeris is 65 seconds.}
@@
 From the previous study presented in this thesis, WASP-77Ab was the most interesting target, since its variation from the linear ephemeris was around  $121\,\rm seconds$.
-After including the new transit times, the best linear fit for the orbital period is:
+After including the new transit times, the new proposed linear ephemeris equation is:
 
 \begin{equation}
-P = 1.36002866 \pm 1.7\times10^{-7} ~\rm days
+T_{\rm C}(E)=2457420.88439\pm(85)+E \cdot 1.36002866 \pm(17)
 \end{equation}
 
+With a best fit period of $P=1.36002866 \pm 1.7\times10^{-7} ~\rm days$.
 In Eq.~\ref{eq1_w77}, the value for the orbital period P is $0.01\,\rm seconds$ lower, and the scatter from the linear ephemeris was reduced to 86 seconds.
-The linear fit has a reduced chi-squared of $\chi^2_{red}=1.03$, while a second-degree polynomial has $\chi^2_{red}=0.72$.
+The linear fit has a reduced chi-squared of $\chi^2_{red,lin}=1.03$, while a second-degree polynomial has $\chi^2_{red,quad}=0.72$.
 Anyway, the second-order fit is highly dominated by the outlier transit time of epoch $229$ (see Figure \ref{wasp77_ttv}).
-After removing it, the reduced chi-squared is  $\chi^2_{red}=0.37$.
+After removing it, the reduced chi-squared is  $\chi^2_{red,quad}=0.37$.
 In all cases, the best fit corresponds to the linear ephemeris.
@@
 For that, we considered 26 transit times from the TraMoS project (in light blue), published works and TESS (both in black).
-The grey area corresponds to the error propagation at $1\sigma$.
+The grey area corresponds to the error propagation at $1\sigma$, which follows a imperceptible quadratic trend.
 The RMS scatter from the linear ephemeris is 86 seconds.}

### 2019-10-07 tramos.tex
Final version

@@
 
-The Transit Monitoring in the South (TraMoS) project started in 2008 aiming to perform a photometric follow-up of transiting exoplanets using telescopes located in Chile.
-Through photometric monitoring of transiting events, important information of the planetary system can be obtained, such as the planetary radius, inclination of the orbit, precise planetary mass, among others.
-Moreover, this kind of analysis allows the detection of variability in the transit's parameters (TPV), if several epochs of the transit event are included.
-The TraMoS project aims, on one hand, to refine the physical and orbital parameters of selected exoplanets systems through photometric follow-up and, on the other, to search variations in those parameters that could suggest the presence of additional bodies in the system.
+The Transit Monitoring in the South (TraMoS) project started in 2008 aiming to perform photometric follow-up of transiting exoplanets using telescopes located in Chile.
+Through photometric monitoring of transiting events, important information of the planetary system can be obtained, such as the planetary radius, inclination of the orbit, and, in combination with radial velocity data, the planetary mass, among others.
+Moreover, this kind of analysis allows the detection of variability in the transit's parameters (TPV), if several epochs of the transit event are obtained.
+The TraMoS project aims, on one hand, to refine the physical and orbital parameters of selected exoplanets systems through photometric follow-up and, on the other, to search for variations in those parameters that could suggest the presence of additional bodies in the system.
 
@@
 The diameter size of the used telescopes ranges from 0.6 meters to 8 meters.
-However, in the last stage of the TraMoS project, we built the team expertise using 1 meter-class telescope, for example in the Danish, SWOPE and SMARTS.
+However, in the later stage of the TraMoS project, we built the team expertise using 1 meter-class telescope, for example in the Danish, SWOPE and SMARTS.
 
@@
 2019 (submitted, see Chapter \ref{chap:paper} for further details).
-In none of those systems a significant TTV signal was detected.}
+In none of those systems a significant TPV signal was detected.}
 \label{tramos}
@@
 
-The first studies within the TraMoS project were conducted by Sergio Hoyer, former PhD student of Professor Patricio Rojo.
-In summary, a possible orbital decay of WASP-43b \citep{Hoyer2016b} and OGLE-TR-113b \citep{Hoyer2016} was ruled out, and no significant TTV signal was detected in WASP-4b \citep{Hoyer2012} and WASP-5b \citep{Hoyer2013}.
+The first studies within the TraMoS project were conducted for Segio Hoyer's PhD dissertation (advisor: Patricio Rojo).
+Current results are summarized as: a possible orbital decay of WASP-43b \citep{Hoyer2016b} and OGLE-TR-113b \citep{Hoyer2016} was ruled out, and no significant TTV signal was detected in WASP-4b \citep{Hoyer2012} and WASP-5b \citep{Hoyer2013}.
 
 In the following section \ref{lightcurve}, I describe the light curve produced from a transiting exoplanet --the principal target of the TraMoS project --  what information about the planet can be obtained from them and how these light curves can give us information about the architecture of this kind of systems.
-Then, in section \ref{ttv}, I detail on a specific type of phenomena of transiting exoplanets: the variation of the transit time of its light curve (TTV).
+Then, in section \ref{ttv}, I detail on a specific type of phenomena of transiting exoplanets: the variation of the transit mid-time of its light curve (TTV).
 
@@
 
-In Figure~\ref{transit} is described the architecture of a transiting exoplanet.
-Thanks to its geometry, the transit light curve and the parameters of the planetary system can be described with a few simple relations \cite{Seager2003,Winn2010}.
+In Figure~\ref{transit} is shown the geometry of a transiting exoplanet.
+From geometric considerations the transit light curve and the parameters of the planetary system can be described with a few simple relations \cite{Seager2003,Winn2010}.
 When the planet passes in front of its star produced a dimming in its flux called primary transit.
@@
 Where $R_{p}$ and $R_{*}$ are the planet and star radius, respectively.
-The numbers 1, 2, 3 and 4 correspond to the contact times: $t_{1}$, $t_{2}$, $t_{3}$ and $t_{4}$.
+The numbers 1, 2, 3 and 4 correspond to the contact times: $t_{1}$, $t_{2}$, $t_{3}$ and $t_{4}$ (see.
+Fig.
+\ref{transit}).
 The total duration of the transit is $t_{T} = t_{4}-t_{1}$ and the full duration is $t_{F}=t_{3}-t_{2}$.
@@
 
-Where $\omega$ is the periastron longitude. In the case of circular orbits, the eccentricity is zero, thus Eq.~\ref{impact_param} is simplified to:
+Where $\omega$ is the argument of pericenter. In the case of circular orbits, the eccentricity $e$ is zero, thus Eq.~\ref{impact_param} is simplified to:
 
@@
 \includegraphics[width=1.0\columnwidth]{imagenes/transit_architecture.pdf}
-\caption{Architecture of a transiting exoplanet and the observed light curve.
-Based on the light curve itself it is possible to measure the transit depth $\Delta F$ and the impact parameter $b$.
-From them, the planet-to-star radius ratio $R_{p}/R_{*}$ and the orbital inclination $i$ can be derived.
+\caption{Geometry of a transiting exoplanet and the observed light curve.
+Based on the light curve itself it is possible to measure the transit depth $\Delta F$ and the orbit's inclination $i$.
+The numbers in circle indicate the four contact times: $t_{1}$, $t_{2}$, $t_{3}$ and $t_{4}$.
 Figure from The Handbook of Exoplanets by M.
@@
 For example, Figure \ref{transit_examples} shows how the light curve reflects the configuration of the system.
-Hot Jupiters are the kind of planet easier to detect since their planet-to-star radius ratio is larger, but a smaller planet orbiting a dwarf star could produce a similar ratio of the radius.
-On the other hand, exoplanets with larger orbital inclinations will produce shorter drops in the flux, in comparison with planets in the same orbital-plane with the host star.
+Hot Jupiters are the kind of planet that is relatively easier to detect since their planet-to-star radius ratio is larger, but a smaller planet orbiting a dwarf star could produce a similar ratio of the radius.
+On the other hand, exoplanets with smaller orbital inclinations will produce shallower drops in the flux, in comparison with planets in the same orbital-plane with the host star.
 
@@
 When modeling the light curve's data, not only the physical parameters of the planet need to be taken into account, but the stars' too.
-The Limb Darkening effect of the star will change the shape of the observed light curve, as what we are observing are photons coming from the star itself, especially when carrying-out observations with different filters.
-This effect produces that the stars appear to be brighter in the center of it and darker closer to the edge.
+The Limb Darkening effect of the star will change the shape of the observed light curve (during the time period $t3 - t2$ in Fig.~\ref{transit}), as what we are observing are photons coming from the star itself, especially when carrying-out observations with different filters.
+The effect of stellar limb-darkening describes the intensity variation across the disk of the star: the star appears brighter at the center and darker closer to the edge (stellar limb).
 The most general analytic formulae to model a light curve produced by a transiting exoplanet includes the Limb Darkening coefficients \citep{Mandel2002}, which can be quadratic or non-quadratic.
@@
 Besides the Solar System, Kepler-90 has the same number of confirmed exoplanets: eight.
-Statistically, around a 20\% of the confirmed exoplanets live in a multi-planetary system\footnote{Information obtained from the NASA Exoplanet Archive Database \url{exoplanetarchive.ipac.caltech.edu}}, but this number is theoretically larger.
+Statistically, around 20\% of the confirmed exoplanets are part of a multi-planetary system\footnote{Information obtained from the NASA Exoplanet Archive Database \url{https://exoplanetarchive.ipac.caltech.edu}}, but this number is theoretically larger.
 \cite{Fressin2013} computed the occurrence of exoplanets through numerical simulation with Kepler data, obtaining that around $52\%$ of the stars should have at least one planet within an 85 days orbit.
@@
 The Transit Timing Variations (TTV) technique was first proposed as a way to detect Earth-mass planets in multi-planetary systems due to gravitational interactions with a transiting exoplanet \citep{Holman2005,Agol2005}.
-However, TTVs can be also used to measure tidal interactions between the planet and the star, such as orbital decays for instance, or to detect exomoons \citep{Kipping2009a,Kipping2009b}, among others phenomena in the star itself.
+However, as mention in Chapter \ref{chap:intro}, TTVs can be also used to measure tidal interactions between the planet and the star, such as orbital decays for instance, or to detect exomoons \citep{Kipping2009a,Kipping2009b}, among others phenomena in the star itself.
 
-For a given light curve of a transiting exoplanet (see Figure \ref{transit}), the transit time $T_{c}$ (or central time of the transit) is computed as:
+For a given light curve of a transiting exoplanet (see Figure \ref{transit}), the transit mid-time $T_{c}$ (or central time of the transit) is computed as:
 
 \begin{equation}
-T_{c} = \frac{t_T}{2}
+T_{c} = \frac{t_{4}+t_{1}}{2}
 \end{equation}
 
-A single transiting planet will stay in a Keplerian orbit around its host star, producing a transit time strictly periodic.
-Thus, the transit time $T_c$ follows a linear function of the orbital period $P$:
+A single (non-perturbed) transiting planet will stay in a Keplerian orbit around its host star, producing a transit time strictly periodic.
+Thus, the transit time $T_c$ follows a linear function in the transit epoch $E$:
 
@@
 
-Where $T_0$ is a reference transit time and $E$ is the number of epochs since $T_0$.
-The presence of a second planet produces transits no exactly periodic, hence Eq.~\ref{linear_ephemeris} will not be valid.
+Where $T_0$ is a reference transit time, $E$ is the number of epochs since $T_0$, and $P$ is the orbital period of the planet.
+The presence of a second (perturbing) planet produces transits no exactly periodic, hence Eq.~\ref{linear_ephemeris} will not be valid.
 As the transit times will be no longer a linear function,  the time between transits varies.
 The variation in time produced by the perturber body depends on the mass and geometry of their orbits.
-The magnitude of this variation between successive transits of the transiting planet \citep{Holman2005}, assuming that the perturber body is in a inner orbit, $a_2 < a_1$, and follows a parabolic orbit with a pariastron distance of $a_2(1-e_2)$, is:
+The magnitude of this variation between successive transits of the transiting planet \citep{Holman2005}, assuming that the perturber body is in a inner orbit, $a_2 < a_1$, and follows a eccentric orbit with a periastron distance of $a_2(1-e_2)$, is:
 
 \begin{equation}
-\Delta t = \frac{45\pi}{16} \frac{M_2}{M_*} P_{1} \alpha^3_{e} (1-	\sqrt{2}\alpha^{3/2})^{-2}
+\Delta t = \frac{45\pi}{16} \frac{M_2}{M_*} P_{1} \alpha^3_{e} (1-	\sqrt{2}\alpha_{e}^{3/2})^{-2}
 \label{delta_t}
@@
 Where $\alpha_e = a_1/(a_2(1-e_2))$ is the ratio of the semi-major axis of the planets, considering a nonzero eccentricity for the perturbing planet ($e_2 \neq 0$).The orbital period of transiting exoplanet is $P_1$, while the perturbing planet has a mass $M_2$, and orbital period $P_2$.
-When $e_2>0.3$, the relation \ref{delta_t} has the best performance with numerical simulations.
+The Eq.
+\ref{delta_t} obtains the best results, compared with numerical simulations, when $e_2>0.3$.
+
+%When $e_2>0.3$, the relation \ref{delta_t} has the best performance with numerical simulations.
 
@@
 
-\cite{Steffen2012b} analyzed Kepler data to constraint the occurrence rate of companions in hot Jupiter system.
+\cite{Steffen2012b} analyzed Kepler data to constrain the occurrence rate of companions in hot Jupiter system.
 In a sample of 63 hot Jupiter candidates, none of them show evidence of possible companions in their system.
@@
 This could suggest that hot Jupiter may have different formation processes on which smaller companions are not allowed in their system: probably they are ejected through planet-planet scatter during migration.
-TTV studies could provide important clues about formation processes and dynamical evolution, and their mass and period dependence.
+TTV studies could provide important clues about formation processes and dynamical evolution, and their mass and period dependency.
